### 2020-09-04 draft.tex
Initial Overleaf Import

% mnras_template.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}

% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
\DeclareRobustCommand{\VAN}[3]{#2}
\let\VANthebibliography\thebibliography
\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[DES SN Ia Galactic Rate]{Supernova Host Galaxies in the Dark Energy Survey: II. The Evolving Galactic Rate of Type Ia Supernovae}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. Wiseman et al.]{
P. Wiseman,$^{1}$\thanks{E-mail: p.s.wiseman@soton.ac.uk}
A. N. Other,$^{2}$
Third Author$^{2,3}$
and Fourth Author$^{3}$
\\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2015}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

Type Ia supernovae (SNe Ia) are extensively used by cosmologists to measure relative distances in the Universe. The small intrinsic dispersion in their peak brightnesses can be reduced further through empirical relations between brightness and light curve properties, such as decline rate (stretch) or optical colour.

Despite reducing dispersions to \textbf{X mag} over samples with over one thousand SNe \citep{Scolnic2018},

\subsection{Maths}
\label{sec:maths} % used for referring to this section from elsewhere

Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
as a numbered equation:

\begin{equation}
    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
	\label{eq:quadratic}
\end{equation}

Refer back to them as e.g. equation~(\ref{eq:quadratic}).

\subsection{Figures and tables}

Figures and tables should be placed at logical positions in the text. Don't
worry about the exact layout, which will be handled by the publishers.

Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
e.g. Table~\ref{tab:example_table}.

% Example figure
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{example}
    \caption{This is an example figure. Captions appear below each figure.
	Give enough detail for the reader to understand what they're looking at,
	but leave detailed discussion to the main body of the text.}
    \label{fig:example_figure}
\end{figure}

% Example table
\begin{table}
	\centering
	\caption{This is an example table. Captions appear above each table.
	Remember to define the quantities, symbols and units used.}
	\label{tab:example_table}
	\begin{tabular}{lccr} % four columns, alignment for each
		\hline
		A & B & C & D\\
		\hline
		1 & 2 & 3 & 4\\
		2 & 4 & 6 & 8\\
		3 & 5 & 7 & 9\\
		\hline
	\end{tabular}
\end{table}

\section{Conclusions}

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data Availability}

The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS. Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article. The statement may refer to original data generated in the course of the study or to third-party data analysed in the article. The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{example} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
%Others S., 2012, Journal of Interesting Stuff, 17, 198
%\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2020-10-22 draft.tex
Updates from Overleaf

@@
 % Enter the current year, for the copyright statements etc.
-\pubyear{2015}
+\pubyear{2020}
 
@@
 
-Type Ia supernovae (SNe Ia) are extensively used by cosmologists to measure relative distances in the Universe.
+Type Ia supernovae (SNe Ia) are explosions of white dwarves (WDs) at masses close to the Chandrasehkar limit of 1.44 $M_{\odot}$ extensively used by cosmologists to measure relative distances in the Universe.
 The small intrinsic dispersion in their peak brightnesses can be reduced further through empirical relations between brightness and light curve properties, such as decline rate (stretch) or optical colour.
 
-Despite reducing dispersions to \textbf{X mag} over samples with over one thousand SNe \citep{Scolnic2018},
+Despite reducing dispersions to \textbf{X mag} in samples with over one thousand SNe \citep{Scolnic2018}, the exact nature of the progenitor scenarios for SNe Ia is yet to be confirmed.
+While it is accepted that SNe Ia are caused by accretion of matter onto a WD from a companion star, multiple possible scenarios exist for the nature of that companion star.
+The leading models invovle a main sequence (MS) star in the single-degenerate (SD) scenario, a secondary white dwarf in the double-degenerate scenario (DD), while more exotic models such as the core-degenerate (CD) scenario invoke white dwarves merging with the cores of massive stars.
 
-\subsection{Maths}
-\label{sec:maths} % used for referring to this section from elsewhere
+The progenitors of a number of core-collapse SNe (CCSNe) have been identified in high-resolution pre-explosion images, allowing detailed analysis of the latter stages of massive star evolution.
+However, due to their lower luminosities this approach has not yet been successful in identifying a progenitor of a SN Ia.
+Conversely, it has been possible to search for remnants of the binary system -- main sequence or white dwarves left behind at the SN location or kicked.
 
-Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
-or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
-as a numbered equation:
+Another method of inferring progenitor channels is the study of global properties of SN Ia host galaxies.
+By measuring characteristics of the stellar populations of hosts it is possible to constrain models of the delay-time distribution (DTD), which details the elapsed time from progenitor formation to SN explosion and contain signatures of the progenitor channels.
+Simple examples of such analyses are comparisons of the rates of SNe Ia in hosts that have been split by some observational property, such as morphology or colour, and have shown that SNe Ia rate per unit stellar mass (SNuM) is significantly larger in late-type spiral galaxies as well as in bluer galaxies \citep[e.g.][]{Mannucci2005}.
+These observations heavily imply that SNe Ia rates are dependent on recent or ongoing star-formation, and thus that the majority of SNe Ia explode after short delay times.
+Conversely, the SNuM in E/S0 and red galaxies is non-negligible, suggesting that there is a secondary, much older component to the DTD.
 
+The rate of SNe per galaxy ($R$) per year in a transient survey can be approximated by the simple equation:
 \begin{equation}
-    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
-	\label{eq:quadratic}
+    R = \frac{N_{\mathrm{SN}}}{N_{\mathrm{G}}} \frac{A_{\mathrm{G}}}{A_{\mathrm{SN}}} \frac{1}{T_{\mathrm{SN  survey}}}\,,
+\label{eq:rate1}
 \end{equation}
-
-Refer back to them as e.g. equation~(\ref{eq:quadratic}).
-
-\subsection{Figures and tables}
-
-Figures and tables should be placed at logical positions in the text. Don't
-worry about the exact layout, which will be handled by the publishers.
-
-Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
-e.g. Table~\ref{tab:example_table}.
-
-% Example figure
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{example}
-    \caption{This is an example figure. Captions appear below each figure.
-	Give enough detail for the reader to understand what they're looking at,
-	but leave detailed discussion to the main body of the text.}
-    \label{fig:example_figure}
-\end{figure}
-
-% Example table
+where $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ are the respective number of SNe and galaxies detected, $A_{\mathrm{SN}}$ and $A_{\mathrm{G}}$ the sky areas from which the SNe and G samples were taken, and $T$ the duration of the SN survey in years.
+This rate can be split by
 \begin{table}
 	\centering
-	\caption{This is an example table. Captions appear above each table.
-	Remember to define the quantities, symbols and units used.}
-	\label{tab:example_table}
+	\caption{Numbers of field galaxies and SN hosts passing various quality cuts.}
+	\label{tab:field_vuts}
 	\begin{tabular}{lccr} % four columns, alignment for each
 		\hline
-		A & B & C & D\\
+		Cut & N (galaxies, X3)  & N (SN hosts)\\
 		\hline
-		1 & 2 & 3 & 4\\
-		2 & 4 & 6 & 8\\
-		3 & 5 & 7 & 9\\
+		Chosen fields & 1364311  & 1766\\
+	    Kron mag in all bands & 1069004  & 1764 \\
+	    Masked chips & 816950  & - \\
+	    Has ugrizJHK photometry & 545748  & -\\
+	    Edge of chip & 481731 & 1716 \\
+	    Star/galaxy separation & 400051 &  1678\\
+	    Has good redshift & 395034 & 1678 \\
+	    SNR $\geq 3$& 338256  & 1678 \\
+	    $m_r \leq 26.5$ & 196109 &  1678 \\
+	    $0.2 \leq z \leq 0.8$ & 48177 & 1414\\
+
 		\hline
@@
 \end{table}
+
+\section{Data \label{sec:data}}
+\subsection{Dark Energy Survey supernova programme \label{subsec:des}}
+The DES Supernova Programme (DES-SN) is a transient survey based on five six-month seasons of observations with the Dark Energy Camera (DECam; \citealt{Flaugher2015}), designed primarily to measure the light curves of SNe Ia for use as cosmological distance indicators.
+Transients were detected and processed using a difference imaging program \citep{Kessler2015} and vetted using a machine learning (ML) algorithm \citep{Goldstein2015}.
+Spectral follow-up was performed on a suite of large optical telescopes \citet{Smith2020b}, leading to the initial publication of a measurement of cosmological parameters using 207 spectroscopically confirmed SNe (\citealt{DESCollaboration2018a}, and references therein).
+\subsection{Supernovae \label{subsec:host_sample}}
+\subsubsection{Photometric classification and quality cuts \label{subsubsec:sn_classify}}
+With over 30,000 transients passing ML cuts it was not possible to obtain spectral follow up of every object.
+Instead we make use of photometric classification techniques, in particular the recurrent neural network \texttt{superNNova} (SNN; \citealt{Moller2019}).
+We derive our SN Ia sample following the approach of \citet{Scolnic2020}, but use a threshold probability of $P(\mathrm{Ia})\geq0.5)$.
+The photometricially classified SNe Ia are then passed through the \texttt{SALT2} framework \citep{Betoule2014} and are subject to quality cuts on the light curve width (stretch; $x_1$) and colour ($c$) parameters: $-3 \leq x_1 \leq 3$, $-0.3 \leq c \leq 0.3$.
+These cuts help to reduce the potential contamination from core-collapse SNe (CCSNe) and outlying SNe Ia whose physical mechanisms may diverge from the general cosmologically useful population.
+
+\subsubsection{Host galaxy selection \label{subsubsec:sn_hosts}}
+Host galaxies for all transients in DES-SN are derived from the deep-stacked $g, r, i, z$-band images presented in \citet{Wiseman2020}.
+SN are associated to hosts using the directional light radius method \citep[e.g.][]{Sullivan2006,Gupta2016}, while spectroscopic redshifts are provided by OzDES \citep{Yuan2015,Childress2017,Lidman2020}, leading to an initial sample of 1766 SNe.
+
+\subsection{Field galaxies\label{subsec:field_sample}}
+A sample of field galaxies is obtained from the same catalogue to which the SNe are matched to obtain host galaxies.
+Since the vast majority of objects in this catalogue do not have a spectroscopic redshift measurement, we rely on photometric redshifts in order to proceed with the analysis.
+\subsubsection{Photometric redshifts \label{subsubsec:photozs}}
+
+Photometric redshifts are estimated using the \texttt{EAZY} photometric redshift code \citep{Brammer2008} as described in \citet{Amon2020}.
+We supplement the DES optical data with DECam $u$-band data as well as near-infrared (NIR) $J$, $H$, and $K$-band imaging from the ultraVISTA and VIDEO surveys.
+We use the X3 and E2 fields, and .
+
+\section{Galaxy properties \label{sec:properties}}
+
+We estimate global galaxy properties for both the SN host and field galaxy samples by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{Kelsey2020,Smith2020,Wiseman2020}.
+For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists (a minority of cases), or more commonly the photometrically derived value.
+The fitting procedure returns a best fitting template and corresponding stellar mass ($M_*$) and SFR averaged over the proceeding 250 Myr.
+Uncertainties on the properties are estimated by refitting the templates to the photometry that has been resampled from Gaussian PDFs formed by the photometric fluxes and their uncertainties.
+
+\subsection{Use of multiwavelength data \label{subsec: fits_ugrizJHK}}
+
+\section{Incompleteness corrections \label{sec:incompleteness}}
+
+Although Eq.
+\ref{eq:rate1} serves as an approximation to the SN rate per galaxy per year, both the SN and field galaxy samples introduced in Sections \ref{subsec:host_sample} and \ref{subsec:field_sample} are affected by incompleteness, which is likely to be the dominant systematic effect in the analysis.
+In this section we describe our method of correcting for various sources incompleteness in the data.
+
+\subsection{Supernova hosts \label{subsec:incompletenss_SNe}}
+The limiting factor in the SN host sample is the requirement of a spectroscopic redshift.
+The majority of SN host spectroscopic redshifts in DES are provided by the dedicated follow-up survey OzDES, for which the limiting magnitude is around 24 to 24.5 mag in the $r$ band.
+The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citetalias{V20} who provide the spectroscopic redshift efficiency as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible exposure time for SNe discovered earlier in the survey.
+So that we reduce any bias towards SNe in bright hosts that are easier to obtain spectroscopic redshifts for, we assign each SN in the sample described in Section \ref{subsec:host_sample} a weight equal to the inverse of the spectroscopic efficiency for its host.
+This is equivalent to assuming that an efficiency of 0.1 means that for every ten SNe with hosts at that magnitude, only 1 will make it into the sample.
+
+\subsection{Field galaxies \label{subsec:incompleteness_field}}
+
+As we use photometric, rather than spectroscopic, redshifts for the field galaxies, they do not suffer from spectroscopic incompleteness as the SN hosts do.
+Instead, the inclusion of any given galaxy in the survey area in the sample is determined simply by whether it is detected above a prescribed threshold in signal-to-noise ratio, i.e.
+the sample is magnitude limited.
+To determine the apparent magnitude limit in each of the optical bands we employ the method of \citet[][hereafter Completeness I, II, III respectively]{Johnston2007,Teodoro2011,Johnston2012}.
+Test statistics $T_C$ and $T_V$ are computed based on absolute magnitude and distance modulus by calculating the rank of each galaxy's absolute magnitude (distance modulus) when compared to all other galaxies in a survey within a certain slice of distance modulus (absolute magnitude).
+For a galaxy of apparent magnitude $m < m_{\mathrm{lim, trial}}$ observed in a survey complete to magnitude $m_{\mathrm{lim, true}}$ where  $m_{\mathrm{lim, trial}} \leq m_{\mathrm{lim, true}}$, the expectation value of the rank is 0.5.
+However, if a trial limiting magnitude $m_{\mathrm{lim, trial}} \geq m_{\mathrm{lim, true}}$, there will be a lack of observed faint objects, such that the expectation value of the rank drops.
+Completeness I, II, and III show that for surveys with sharp, well defined magnitude limits the test statistics $T_C$ and $T_V$ drop sharply.
+The DES deep stacks present a more challenging case.
+They cover a wide area and are compiled from tens of separate CCDs, each with its own detection efficiency.
+Moreover, galaxy redshifts have been estimated using photometry only, and $K$-corrections performed using an imperfect template fit, potentially leading to large systematic and statistical fluctuations in absolute magnitudes and distance moduli.
+To reduce the inhomogeneity while still including  large sample of objects, we split the sample into the deep (X3) and shallow (E2) fields and calculate limiting magnitudes separately.
+Figs.
+\ref{fig:completeness_X3, fig:completenessE2} show the values of $T_C$ and $T_V$ for the two fields respectively.
+The values of the test statistics
+
+\section{Rates as a function of host galaxy properties \label{sec:rates}}
+
+\subsection{Dependence of the SN Ia rate on stellar mass \label{subsec:rates_mass}}
+
+\subsection{Dependence of the SN Ia rate on SFR \label{subsec:rates_sfr}}
 
@@
 \bibliographystyle{mnras}
-\bibliography{example} % if your bibtex file is called example.bib
+\bibliography{PhilMendeley} % if your bibtex file is called example.bib
 

### 2020-10-28 draft.tex

@@
 
+\subsection{Quality cuts \label{subsec:cuts}}
+
+In order to refine the sample of host and field galaxies for the rate analysis we perform a series of quality cuts.
+Firstly, we require that a galaxy must be detected and have a Kron magnitude measurement in all four DES optical bands.
+We also require that it is not within a given number of pixels of the CCD edge, as the co-addition of slightly misaligned images introduced a region of significant noise in this part of the detector.
+To remove high-probability stellar sources we apply a cut of 0.95 in the star/galaxy (S/G) separation \texttt{CLASS\_STAR} provided by \texttt{Source Extractor} \citep{Bertin1996}.
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/z_dist.png}
+\caption{Redshift distribution for the host galaxies of RETs in DES for which a measurement was obtained.
+\label{fig:z_dist}}
+\end{figure}
+
 \section{Galaxy properties \label{sec:properties}}
@@
 
+\subsubsection{Apparent magnitude limits \label{subsubsec:mag_lims}}
 As we use photometric, rather than spectroscopic, redshifts for the field galaxies, they do not suffer from spectroscopic incompleteness as the SN hosts do.
@@
 the sample is magnitude limited.
-To determine the apparent magnitude limit in each of the optical bands we employ the method of \citet[][hereafter Completeness I, II, III respectively]{Johnston2007,Teodoro2011,Johnston2012}.
+To determine the apparent magnitude limit in each of the optical bands we employ the method of \citet{Johnston2007,Teodoro2010,Johnston2012} (hereafter Completeness I, II, III respectively).
 Test statistics $T_C$ and $T_V$ are computed based on absolute magnitude and distance modulus by calculating the rank of each galaxy's absolute magnitude (distance modulus) when compared to all other galaxies in a survey within a certain slice of distance modulus (absolute magnitude).
@@
 \ref{fig:completeness_X3, fig:completenessE2} show the values of $T_C$ and $T_V$ for the two fields respectively.
-The values of the test statistics
+The values of the test statistics increase with $m_{\mathrm{lim, trial}}$ until a peak, before decreasing to stable values at magnitudes far beyond the limit of the survey.
+The shape at brighter $m_{\mathrm{lim, trial}}$ is likely caused by incompleteness at the bright end: due to the small sky area, we simply do not probe enough volume to sample the bright end of the galaxy luminosity function well enough for the statistics to be robust.
+To approximate an efficiency function, we fit the peak of the statistics with a polynomial function, and then normalise by the maximum and minimum values.
+We then interpolate between the peak and the faint-magnitude floor to find the 50\% completeness limit at the point where the normalised value of the test statistic is 0.5.
+These values are consistent with the value at which 50\% of the true sources are detected but have the advantage of being derived from the data without a simulation that is based on assumptions and thus susceptible to bias.
+
+\subsubsection{$V_{\mathrm{max}}$ correction \label{subsubsec:vmax_corr}}
+
+To correct for incompleteness caused by the magnitude limited nature of the survey we follow the prescription of e.g.
+\citet{Sullivan2006, Smith2012} by using a $V_{\mathrm{max}}$ method of \citet{Schmid1968}.
+For each galaxy in the sample we calculate the maximum volume within which it would have been observed given its absolute magnitude and $k-$correction.
+A correction of $V_{\mathrm{survey}}/V_{\mathrm{max}}$ is applied to all galaxies for which $V_{\mathrm{max}} < V_{\mathrm{survey}}$, where $V_{\mathrm{survey}}$ is the maximum volume reached by the survey.
+In our case this corresponds to the volume at $z=0.8$.
+Figs.
+\ref{fig:vmax_gals} and \ref{fig:vmax_hist} show the distribution of the correction among galaxies in the sample.
+The vast majority of galaxies require no correction, meaning they would have been observed beyond the maximum volume considered.
+Roughly 1\% of objects have a correction greater than 1, with the distribution well described by a power-law function.
+In Section \ref{sec:rates} we split the samples into redshift bins in order to measure cosmic evolution of the SN Ia rate.
+For each redshift bin, we reevaluate the value of $V_{\mathrm{survey}}$ used in the incompleteness correction to be the volume of the bin.
 

### 2020-12-11 draft.tex
Updates from Overleaf

@@
 % Keep the title short and informative.
-\title[DES SN Ia Galactic Rate]{Supernova Host Galaxies in the Dark Energy Survey: II. The Evolving Galactic Rate of Type Ia Supernovae}
+\title[DES SN Ia Galactic Rate]{Supernova Host Galaxies in the Dark Energy Survey: III. The Evolving Galactic Rate of Type Ia Supernovae}
 
@@
 
-Type Ia supernovae (SNe Ia) are explosions of white dwarves (WDs) at masses close to the Chandrasehkar limit of 1.44 $M_{\odot}$ extensively used by cosmologists to measure relative distances in the Universe.
-The small intrinsic dispersion in their peak brightnesses can be reduced further through empirical relations between brightness and light curve properties, such as decline rate (stretch) or optical colour.
+Type Ia supernovae (SNe Ia) are explosions of white dwarves (WDs) at masses close to the Chandrasekhar limit of 1.44 $M_{\odot}$.
+The small observed dispersion in their peak brightnesses can be reduced further through empirical relations between brightness and light curve properties, such as decline rate (stretch) or optical colour.
+These properties have led SNe Ia to be used extensively by cosmologists to measure relative distances in the Universe.
 
-Despite reducing dispersions to \textbf{X mag} in samples with over one thousand SNe \citep{Scolnic2018}, the exact nature of the progenitor scenarios for SNe Ia is yet to be confirmed.
-While it is accepted that SNe Ia are caused by accretion of matter onto a WD from a companion star, multiple possible scenarios exist for the nature of that companion star.
-The leading models invovle a main sequence (MS) star in the single-degenerate (SD) scenario, a secondary white dwarf in the double-degenerate scenario (DD), while more exotic models such as the core-degenerate (CD) scenario invoke white dwarves merging with the cores of massive stars.
+Despite reducing dispersions to $\sim 0.1$ mag in samples with over one thousand SNe \citep{Scolnic2018}, the exact nature of the progenitor scenarios for SNe Ia is yet to be confirmed.
+While it is accepted that SNe Ia are caused by accretion of matter onto a WD from a companion star, multiple possible scenarios exist for the nature of that companion star and the search for this has formed a significant field of research (see \citealt{Maoz2014} for a review).
+The leading models involve a main sequence (MS) star in the single-degenerate (SD) scenario \citep{Whelan1973,Nomoto1982}, a secondary white dwarf in the double-degenerate (DD) scenario \citep{Tutukov1974,Iben1984,Webbink1084}, while more exotic models such as the core-degenerate (CD) scenario invoke white dwarves merging with the cores of massive stars \citep{Soaker2019}.
 
 The progenitors of a number of core-collapse SNe (CCSNe) have been identified in high-resolution pre-explosion images, allowing detailed analysis of the latter stages of massive star evolution.
-However, due to their lower luminosities this approach has not yet been successful in identifying a progenitor of a SN Ia.
-Conversely, it has been possible to search for remnants of the binary system -- main sequence or white dwarves left behind at the SN location or kicked.
+However, this approach has not yet been successful in identifying a progenitor of a SN Ia.
+Conversely, it has been possible to search for surviving remnants of the binary system -- main sequence stars or white dwarves left behind at the SN location or kicked \citep{Shen2018} -- displaying tentative evidence for a DD scenario.
+As yet, there is no conclusive evidence ruling out any progenitor channel from being a significant contribution to the total population of SNe Ia.
 
-Another method of inferring progenitor channels is the study of global properties of SN Ia host galaxies.
-By measuring characteristics of the stellar populations of hosts it is possible to constrain models of the delay-time distribution (DTD), which details the elapsed time from progenitor formation to SN explosion and contain signatures of the progenitor channels.
+Another method of inferring progenitor channels is the study of the SN Ia delay time distribution (DTD).
+The DTD can be interpreted as the rate at which SNe Ia occur as a function of the delay time $\tau$ since an episode of star-formation, and thus carries characteristic signatures of the progenitor channel (see \citealt{Wang2012} for a review).
+While the SD scenario is able to produce a broad range of functional forms of the DTD, the DD scenario predicts a power law of the form $t^{\beta}$, with $\beta \sim -1$ \citep[e.g]{Ruiter2009,Mennekens2010}.
+
+Given the vast range of timescales to which the DTD is sensitive, it is non-trivial to measure and various techniques have been developed to infer it indirectly.
+One such approach is to measure the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008}.
+This technique is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clsuters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Maoz2014}.
+Conversely, it is also possible to estimate the SFH of an individual galaxy through the modelling of its stellar populations via spectral energy distribution (SED) fitting.
+Works such as \citet{Maoz2011}, \citet{Maoz2012}, \citet{Graur2013} estimated the DTD by measuring SFHs for a sample of field galaxies and comparing them to the number of SNe detected in each galaxy.
+and has led to results that suggest a DTD power law with $\beta$ consistent with $-1$ \citep[e.g.][]{Maoz2011,Graur2013}.
+
+global properties of SN Ia host galaxies.
+By measuring characteristics of the stellar populations of hosts it is possible to constrain models of the delay-time distribution (DTD), which details the elapsed time from a burst of star formation to SN explosion and contain signatures of the progenitor channels.
 Simple examples of such analyses are comparisons of the rates of SNe Ia in hosts that have been split by some observational property, such as morphology or colour, and have shown that SNe Ia rate per unit stellar mass (SNuM) is significantly larger in late-type spiral galaxies as well as in bluer galaxies \citep[e.g.][]{Mannucci2005}.
 These observations heavily imply that SNe Ia rates are dependent on recent or ongoing star-formation, and thus that the majority of SNe Ia explode after short delay times.
-Conversely, the SNuM in E/S0 and red galaxies is non-negligible, suggesting that there is a secondary, much older component to the DTD.
+Conversely, the SNuM in E/S0 and red galaxies is non-negligible, suggesting that there is a secondary, much older component to the DTD \citep{Sullivan2006,Smith2012}.
+The DTD itself is often mathematically approximated by a power law taking the form:
 
-The rate of SNe per galaxy ($R$) per year in a transient survey can be approximated by the simple equation:
 \begin{equation}
-    R = \frac{N_{\mathrm{SN}}}{N_{\mathrm{G}}} \frac{A_{\mathrm{G}}}{A_{\mathrm{SN}}} \frac{1}{T_{\mathrm{SN  survey}}}\,,
+    \Phi(\tau) = A\left(\frac{\tau}{\mathrm{Gyr}}\right)^{\alpha}\,,
+\end{equation} 
+where $\tau$ is the time since a burst of star formation, and $A$ is a normalisation at $\tau=1\mathrm{Gyr}$.
+
+ The shape of this function is driven by two components: the star-formation histories of galaxies, which detail the mass of stars formed at any given epoch in the past (or equally the age distribution of stellar mass in the galaxy at any epoch); and the SN Ia DTD, which prescribes the probability distribution of the stars exploding.
+Indeed, the rate $R_{\mathrm{G}}(M_*)$ is a simple convolution of the two:
+
+\begin{equation}
+    R_{\mathrm{G}}(M_*) = \int_0^{\infty} \Psi(t-\tau)\Phi(\tau)\,d\tau
+\end{equation}
+
+The rate of SNe per galaxy ($R_{\mathrm{G}}$) per year in a transient survey can be approximated by the simple equation:
+\begin{equation}
+    R_{\mathrm{G}} = \frac{N_{\mathrm{SN}}}{N_{\mathrm{G}}} \frac{A_{\mathrm{G}}}{A_{\mathrm{SN}}} \frac{1}{T_{\mathrm{SN  survey}}}\,,
 \label{eq:rate1}
@@
 where $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ are the respective number of SNe and galaxies detected, $A_{\mathrm{SN}}$ and $A_{\mathrm{G}}$ the sky areas from which the SNe and G samples were taken, and $T$ the duration of the SN survey in years.
-This rate can be split by
+By binning both the SN hosts and field galaxies by their stellar mass we can approximate the function $R_{\mathrm{G}}(M_*)$.
+
 \begin{table}
@@
 \subsection{Field galaxies\label{subsec:field_sample}}
-A sample of field galaxies is obtained from the same catalogue to which the SNe are matched to obtain host galaxies.
-Since the vast majority of objects in this catalogue do not have a spectroscopic redshift measurement, we rely on photometric redshifts in order to proceed with the analysis.
+A sample of field galaxies is obtained from the same catalogue to which the SNe are matched to obtain host galaxies, and is presented in a companion paper \citet{Wiseman2021}.
+The steps relevant to this analysis are outlined in the following sections.
+
 \subsubsection{Photometric redshifts \label{subsubsec:photozs}}
 
-Photometric redshifts are estimated using the \texttt{EAZY} photometric redshift code \citep{Brammer2008} as described in \citet{Amon2020}.
-We supplement the DES optical data with DECam $u$-band data as well as near-infrared (NIR) $J$, $H$, and $K$-band imaging from the ultraVISTA and VIDEO surveys.
-We use the X3 and E2 fields, and .
+Since the vast majority of objects in the \citet{Wiseman2021} catalogue do not have a spectroscopic redshift measurement, we rely on photometric redshifts (photo-$z$s) in order to proceed with the analysis.
+Photometric redshifts are taken, where available, from the catalogue of \citet{Hartley2020}, and have been estimated using the \texttt{EAZY} photometric redshift code \citep{Brammer2008}.
+These photo-$z$s make use of deep DES optical photometry alongside DECam $u$-band data and near-infrared (NIR) $J$, $H$, and $K$-band imaging from the ultraVISTA and VIDEO surveys.
+
+\subsubsection{Galaxy properties \label{subsubsec:properties}}
+
+We estimate global galaxy properties for both the SN host and field galaxy samples by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{Kelsey2020,Smith2020,Wiseman2020}.
+For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists (a minority of cases), or more commonly the photometrically derived value.
+The fitting procedure returns a best fitting template and corresponding stellar mass ($M_*$) and SFR averaged over the proceeding 250 Myr.
+Uncertainties on the properties are estimated by refitting the templates to the photometry that has been resampled from Gaussian PDFs formed by the photometric fluxes and their uncertainties.
 
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/z_dist.png}
-\caption{Redshift distribution for the host galaxies of RETs in DES for which a measurement was obtained.
-\label{fig:z_dist}}
+\includegraphics[width=0.5\textwidth]{figs/mass_hist_log.png}
+\caption{Distribution of the stellar mass of the field galaxies used in the analysis. The distribution is well desribed by a Schechter function.
+\label{fig:log_mass_field}}
 \end{figure}
-
-\section{Galaxy properties \label{sec:properties}}
-
-We estimate global galaxy properties for both the SN host and field galaxy samples by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{Kelsey2020,Smith2020,Wiseman2020}.
-For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists (a minority of cases), or more commonly the photometrically derived value.
-The fitting procedure returns a best fitting template and corresponding stellar mass ($M_*$) and SFR averaged over the proceeding 250 Myr.
-Uncertainties on the properties are estimated by refitting the templates to the photometry that has been resampled from Gaussian PDFs formed by the photometric fluxes and their uncertainties.
-
-\subsection{Use of multiwavelength data \label{subsec: fits_ugrizJHK}}
 
@@
 
-\subsection{Supernova hosts \label{subsec:incompletenss_SNe}}
-The limiting factor in the SN host sample is the requirement of a spectroscopic redshift.
+\subsection{Supernovae \label{subsec:incompleteness_SNe}}
+
+Incompleteness in a SN survey arises from a number of sources.
+The primary source of incompleteness is caused by the magnitude limit of the survey: SNe with apparent magnitudes below the survey limit will not be detected.
+Since SNe Ia are relatively uniform in absolute luminosity, this form of incompleteness is primarily redshift dependent.
+On the other hand, DES-SN comprises 10 separate pointings, each with different visibility and thus airmass throughout the observing season.
+These differences lead to different detection efficiencies across the fields.
+
+To correct for these incompleteness, we follow a similar method to that used in the PTF rates analyses of \citet{Frohmaier2019,Frohmaier2020} as well as the DES-SN superluminous SN rate of \citet{Thomas2020}.
+We run a suite of simulations using \texttt{SNANA} \citet{Kessler2009a}.
+We simulate 230,000 SNe in the redshift range $0.05 \leq z_{\mathrm{SN}} \leq 1.3$, and draw peak magnitudes from \textbf{ADD DETAILS}.
+We then run mock versions of the DES-SN survey, using the exact cadence, conditions, and zeropoints from the survey itself.
+All of the detected simulated SNe are passed through the light curve fit of SALT2 \citep{Betoule2014}, as per the implementation in \texttt{SNANA}, and those that fail the light curve cuts outlined in Section \ref{subsubsec:sn_classify} are discarded.
+We are left with a fraction of the original simulated SNe, and that fraction is dependent on location, explosion epoch, and redshift, which we define as the SN efficiency.
+For the $i$th SN the efficiency $\eta_{\mathrm{SN}, i}$ in field $F$, exploding at time $t_0$ at redshift $z$, is:
+\begin{equation}
+    \eta_{\mathrm{SN},i} (F_i,z_i,t_{0,i}) = \left( \frac{N_{\mathrm{obs}}\left(F_i,z_i,t_{0,i}\right)}{N_{\mathrm{sim}}\left(F_i,z_i,t_{0,i}\right)}\right)\,.
+\end{equation}
+
+The distribution of efficiency as a function of redshift is shown in Figure \ref{fig:efficiencies}.
+It is evident that the deep fields (X3, C3) are sensitive to SNe at higher redshifts, while there is no drastic shifts between efficiencies in the eight shallow fields.
+
+\subsection{Supernova hosts \label{subsec:incompletenss_SN_hosts}}
+A further limiting factor in the SN host sample is the requirement of a spectroscopic redshift.
 The majority of SN host spectroscopic redshifts in DES are provided by the dedicated follow-up survey OzDES, for which the limiting magnitude is around 24 to 24.5 mag in the $r$ band.
-The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citetalias{V20} who provide the spectroscopic redshift efficiency as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible exposure time for SNe discovered earlier in the survey.
+The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citetalias{V20} who provide the spectroscopic redshift efficiency as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey.
 So that we reduce any bias towards SNe in bright hosts that are easier to obtain spectroscopic redshifts for, we assign each SN in the sample described in Section \ref{subsec:host_sample} a weight equal to the inverse of the spectroscopic efficiency for its host.

### 2020-12-11 draft.tex
Updates from Overleaf

@@
 While it is accepted that SNe Ia are caused by accretion of matter onto a WD from a companion star, multiple possible scenarios exist for the nature of that companion star and the search for this has formed a significant field of research (see \citealt{Maoz2014} for a review).
-The leading models involve a main sequence (MS) star in the single-degenerate (SD) scenario \citep{Whelan1973,Nomoto1982}, a secondary white dwarf in the double-degenerate (DD) scenario \citep{Tutukov1974,Iben1984,Webbink1084}, while more exotic models such as the core-degenerate (CD) scenario invoke white dwarves merging with the cores of massive stars \citep{Soaker2019}.
+The leading models involve a main sequence (MS) star in the single-degenerate (SD) scenario \citep{Whelan1973,Nomoto1982}, a secondary white dwarf in the double-degenerate (DD) scenario \citep{Tutukov1976,Iben1984,Webbink1984}, while more exotic models such as the core-degenerate (CD) scenario invoke white dwarves merging with the cores of massive stars \citep{Soker2019}.
 
@@
 One such approach is to measure the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008}.
-This technique is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clsuters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Maoz2014}.
+This technique is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clsuters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Graur2014,Maoz2014}.
 Conversely, it is also possible to estimate the SFH of an individual galaxy through the modelling of its stellar populations via spectral energy distribution (SED) fitting.

### 2020-12-17 draft.tex

@@
 The DTD can be interpreted as the rate at which SNe Ia occur as a function of the delay time $\tau$ since an episode of star-formation, and thus carries characteristic signatures of the progenitor channel (see \citealt{Wang2012} for a review).
-While the SD scenario is able to produce a broad range of functional forms of the DTD, the DD scenario predicts a power law of the form $t^{\beta}$, with $\beta \sim -1$ \citep[e.g]{Ruiter2009,Mennekens2010}.
+While the SD scenario is able to produce a broad range of functional forms of the DTD, the DD scenario predicts a power law of the form $t^{\beta}$, with $\beta \sim -1$ \citep[e.g][]{Ruiter2009,Mennekens2010}.
 
 Given the vast range of timescales to which the DTD is sensitive, it is non-trivial to measure and various techniques have been developed to infer it indirectly.
-One such approach is to measure the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008}.
+One such approach is to measure global properties of SN Ia host galaxies.
+Simple examples of such analyses are comparisons of the rates of SNe Ia in hosts that have been split by some observational property, such as morphology or colour, and have shown that SNe Ia rate per unit stellar mass (SNuM) is significantly larger in late-type spiral galaxies as well as in bluer galaxies \citep[e.g.][]{Mannucci2005}.
+These observations heavily imply that SNe Ia rates are dependent on recent or ongoing star-formation, and thus that the majority of SNe Ia explode after short delay times.
+Conversely, the SNuM in E/S0 and red galaxies is non-negligible, suggesting that there is a secondary, much older component to the DTD \citep{Sullivan2006,Smith2012}.
+The DTD is thus approximated by a two-component ("$A + B$") model, where $A$ and $B$ are the normalizations of the DTD for "prompt" (i.e.
+proportional to instantaneous SFR) and "tardy" (i.e.
+proportional to overall stellar mass) SNe, respectively A complementary technique involves measuring the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008}.
 This technique is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clsuters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Graur2014,Maoz2014}.
@@
 and has led to results that suggest a DTD power law with $\beta$ consistent with $-1$ \citep[e.g.][]{Maoz2011,Graur2013}.
+\citet{Childress2014} showed that the $A+B$ parameterisation arises as a direct consequence of the combination of a power-law DTD with the SFHs of galaxies.
 
-global properties of SN Ia host galaxies.
-By measuring characteristics of the stellar populations of hosts it is possible to constrain models of the delay-time distribution (DTD), which details the elapsed time from a burst of star formation to SN explosion and contain signatures of the progenitor channels.
-Simple examples of such analyses are comparisons of the rates of SNe Ia in hosts that have been split by some observational property, such as morphology or colour, and have shown that SNe Ia rate per unit stellar mass (SNuM) is significantly larger in late-type spiral galaxies as well as in bluer galaxies \citep[e.g.][]{Mannucci2005}.
-These observations heavily imply that SNe Ia rates are dependent on recent or ongoing star-formation, and thus that the majority of SNe Ia explode after short delay times.
-Conversely, the SNuM in E/S0 and red galaxies is non-negligible, suggesting that there is a secondary, much older component to the DTD \citep{Sullivan2006,Smith2012}.
-The DTD itself is often mathematically approximated by a power law taking the form:
+In this work, we combine parts of the above methods and derive a new, independent measurement of the SN Ia DTD.
+Instead of measuring the volumetric rate of SNe Ia, we measure the rate per galaxy as a function of stellar mass, as per \citet{Sullivan2006,Smith2012}.
+We use the stellar mass assembly model of \citet{Childress2014} to predict the stellar age distribution of galaxies for a given stellar mass at the mean redshift of our SN sample, and then forward model the DTD by convolving it with the stellar age distribution and comparing the predicted rates to the observed rates.
+
+\section{Method \label{sec:method}}
+
+We represent the SN Ia DTD by a power law of the form:
 
 \begin{equation}
-    \Phi(\tau) = A\left(\frac{\tau}{\mathrm{Gyr}}\right)^{\alpha}\,,
+    \Phi(\tau) = A\left(\frac{\tau}{\mathrm{Gyr}}\right)^{\beta}\,,
 \end{equation} 
 where $\tau$ is the time since a burst of star formation, and $A$ is a normalisation at $\tau=1\mathrm{Gyr}$.
-
- The shape of this function is driven by two components: the star-formation histories of galaxies, which detail the mass of stars formed at any given epoch in the past (or equally the age distribution of stellar mass in the galaxy at any epoch); and the SN Ia DTD, which prescribes the probability distribution of the stars exploding.
-Indeed, the rate $R_{\mathrm{G}}(M_*)$ is a simple convolution of the two:
+If all stars in a galaxy were formed at a single epoch $t_f$, the DTD would describe the rate of SNe at an observation time $\tau = t_0$.
+However in reality galaxies are formed by the gradual build up of stellar mass over several epochs of star formation -- the distribution of this mass build up is known as the star-formation history (SFH).
+The rate of SNe Ia is thus the sum of the DTD evaluated for each epoch of star formation, multiplied by the stellar mass formed in that epoch.
+Mathematically this is represented by the convolution of the DTD and SFH:
 
 \begin{equation}
-    R_{\mathrm{G}}(M_*) = \int_0^{\infty} \Psi(t-\tau)\Phi(\tau)\,d\tau
+    R_{\mathrm{G}} = \int_{t_0}^{\infty} \psi(t_0-\tau)\Phi(\tau)\,d\tau \,,
 \end{equation}
+where $t_0$ is the epoch at which the galaxy is observed, and $\psi$ is the SFH.
+
+\subsection{Modeling the star formation histories of galaxies \label{subsec:method_sfh}}
+To model the SFH of galaxies as a function of their stellar mass we adopt the model of \citet{Childress2014}.
+In the model, galaxies are expected to evolve smoothly along the so-called "main sequence of star formation" whereby the SFR of a galaxy of stellar mass $M_*$ at redshift $z$ is determined by a simple relationship (the SMz relation, \citealt{Zahid2012}).
+Specifically, we implement their "fine-tuned" model (C14 Eq.
+A7), whereby the SMz flattens above $z\sim2$ in line with observations \citep{Stark2013}.
+We adjust this model slightly and arrive at a final SMz:
+
+\begin{equation}
+    \Psi(M_*,z) = \left(\frac{M_*}{10^{10}}\right)^{0.7}\frac{\exp{\left(1.9z\right)}}{\exp{\left(1.7\left(z-2\right)\right)} + \exp{\left(0.2\left(z-2\right)\right)} } [\mathrm{M}_{\odot} \mathrm{yr}^{-1}]\,.
+\end{equation}
+
+As galaxies grow, their SFR begins to slow down and eventually shut off almost entirely in a process known as quenching. We adopt the quenching penalty $p_Q$ directly from \citet{Childress2014}:
+\begin{equation}
+    p_Q(M_*,z) = \frac{1}{2}\left[1 - \mathrm{erf}\left(\frac{\log(M_*) - \log(M_Q(z)}{\sigma_Q}\right)\right]\,,
+\end{equation}
+where $M_Q(z)$ describes how the quenching mass evolves with redshift, and $\sigma_Q$ is the transition scale which controls how fast a galaxy quenches.
+We adopt the observationally motivated form of the quenching mass evolution (Eq.
+A8 from \citealt{Childress2014}):
+\begin{equation}
+    \log(M_q(z)/\mathrm{M}_{\odot}) = 10.077 + 0.636z \,, 
+\end{equation}
+and a transition scale of $\sigma_Q = 1.1$.
+
+As per \citet{Childress2014} we plant seed galaxies with initial masses of $10^6 \mathrm{M}_{\odot}$ at intervals of 50 Myr for look-back times $1 \leq t_f \leq 10$ Gyr, and 25 Myr for look-back times $10 \leq t_f \leq 13$ Gyr, and evaluate the model with a time step of 0.5 Myr.
 

### 2020-12-17 draft.tex

@@
 proportional to overall stellar mass) SNe, respectively A complementary technique involves measuring the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008}.
-This technique is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clsuters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Graur2014,Maoz2014}.
+This technique is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clusters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Graur2014,Maoz2014}.
 Conversely, it is also possible to estimate the SFH of an individual galaxy through the modelling of its stellar populations via spectral energy distribution (SED) fitting.

### 2020-12-17 draft.tex
Updates from Overleaf

@@
 
-\section{Method \label{sec:method}}
-
-We represent the SN Ia DTD by a power law of the form:
-
-\begin{equation}
-    \Phi(\tau) = A\left(\frac{\tau}{\mathrm{Gyr}}\right)^{\beta}\,,
-\end{equation} 
-where $\tau$ is the time since a burst of star formation, and $A$ is a normalisation at $\tau=1\mathrm{Gyr}$.
-If all stars in a galaxy were formed at a single epoch $t_f$, the DTD would describe the rate of SNe at an observation time $\tau = t_0$.
-However in reality galaxies are formed by the gradual build up of stellar mass over several epochs of star formation -- the distribution of this mass build up is known as the star-formation history (SFH).
-The rate of SNe Ia is thus the sum of the DTD evaluated for each epoch of star formation, multiplied by the stellar mass formed in that epoch.
-Mathematically this is represented by the convolution of the DTD and SFH:
-
-\begin{equation}
-    R_{\mathrm{G}} = \int_{t_0}^{\infty} \psi(t_0-\tau)\Phi(\tau)\,d\tau \,,
-\end{equation}
-where $t_0$ is the epoch at which the galaxy is observed, and $\psi$ is the SFH.
-
-\subsection{Modeling the star formation histories of galaxies \label{subsec:method_sfh}}
-To model the SFH of galaxies as a function of their stellar mass we adopt the model of \citet{Childress2014}.
-In the model, galaxies are expected to evolve smoothly along the so-called "main sequence of star formation" whereby the SFR of a galaxy of stellar mass $M_*$ at redshift $z$ is determined by a simple relationship (the SMz relation, \citealt{Zahid2012}).
-Specifically, we implement their "fine-tuned" model (C14 Eq.
-A7), whereby the SMz flattens above $z\sim2$ in line with observations \citep{Stark2013}.
-We adjust this model slightly and arrive at a final SMz:
-
-\begin{equation}
-    \Psi(M_*,z) = \left(\frac{M_*}{10^{10}}\right)^{0.7}\frac{\exp{\left(1.9z\right)}}{\exp{\left(1.7\left(z-2\right)\right)} + \exp{\left(0.2\left(z-2\right)\right)} } [\mathrm{M}_{\odot} \mathrm{yr}^{-1}]\,.
-\end{equation}
-
-As galaxies grow, their SFR begins to slow down and eventually shut off almost entirely in a process known as quenching. We adopt the quenching penalty $p_Q$ directly from \citet{Childress2014}:
-\begin{equation}
-    p_Q(M_*,z) = \frac{1}{2}\left[1 - \mathrm{erf}\left(\frac{\log(M_*) - \log(M_Q(z)}{\sigma_Q}\right)\right]\,,
-\end{equation}
-where $M_Q(z)$ describes how the quenching mass evolves with redshift, and $\sigma_Q$ is the transition scale which controls how fast a galaxy quenches.
-We adopt the observationally motivated form of the quenching mass evolution (Eq.
-A8 from \citealt{Childress2014}):
-\begin{equation}
-    \log(M_q(z)/\mathrm{M}_{\odot}) = 10.077 + 0.636z \,, 
-\end{equation}
-and a transition scale of $\sigma_Q = 1.1$.
-
-As per \citet{Childress2014} we plant seed galaxies with initial masses of $10^6 \mathrm{M}_{\odot}$ at intervals of 50 Myr for look-back times $1 \leq t_f \leq 10$ Gyr, and 25 Myr for look-back times $10 \leq t_f \leq 13$ Gyr, and evaluate the model with a time step of 0.5 Myr.
-
-The rate of SNe per galaxy ($R_{\mathrm{G}}$) per year in a transient survey can be approximated by the simple equation:
-\begin{equation}
-    R_{\mathrm{G}} = \frac{N_{\mathrm{SN}}}{N_{\mathrm{G}}} \frac{A_{\mathrm{G}}}{A_{\mathrm{SN}}} \frac{1}{T_{\mathrm{SN  survey}}}\,,
-\label{eq:rate1}
-\end{equation}
-where $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ are the respective number of SNe and galaxies detected, $A_{\mathrm{SN}}$ and $A_{\mathrm{G}}$ the sky areas from which the SNe and G samples were taken, and $T$ the duration of the SN survey in years.
-By binning both the SN hosts and field galaxies by their stellar mass we can approximate the function $R_{\mathrm{G}}(M_*)$.
-
 \begin{table}
@@
 
-\subsubsection{Galaxy properties \label{subsubsec:properties}}
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/mass_hist_sn_field_BC03.png}
+    \caption{Distribution of the stellar mass of the SN host and field galaxies used in the analysis. }
+    \label{fig:mass_hist_hosts_field}
+\end{figure}
+
+\subsection{Galaxy properties \label{subsec:properties}}
 
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/mass_hist_log.png}
-\caption{Distribution of the stellar mass of the field galaxies used in the analysis. The distribution is well desribed by a Schechter function.
+    \centering
+    \includegraphics[width=0.5\textwidth]{figs/mass_hist_log_BC03.png}
+    \caption{Distribution of the stellar mass of the field galaxies used in the analysis. The distribution is well described by a Schechter function.
     \label{fig:log_mass_field}}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm.png}
+    \caption{The rate per galaxy of SNe Ia as a function of stellar mass.
+The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \label{fig:rate_fit}
+\end{figure}
 \section{Incompleteness corrections \label{sec:incompleteness}}
@@
 
-\section{Rates as a function of host galaxy properties \label{sec:rates}}
+\begin{figure*}
+    \centering
+    \includegraphics{}
+    \caption{Caption}
+    \label{fig:my_label}
+\end{figure*}
+
+\section{Modeling the rate of type Ia supernovae \label{sec:method}}
+
+We represent the SN Ia DTD by a power law of the form:
+
+\begin{equation}
+    \Phi(\tau) = A\left(\frac{\tau}{\mathrm{Gyr}}\right)^{\beta}\,,
+\end{equation} 
+where $\tau$ is the time since a burst of star formation, and $A$ is a normalisation at $\tau=1\mathrm{Gyr}$.
+If all stars in a galaxy were formed at a single epoch $t_f$, the DTD would describe the rate of SNe at an observation time $\tau = t_0$.
+However in reality galaxies are formed by the gradual build up of stellar mass over several epochs of star formation -- the distribution of this mass build up is known as the star-formation history (SFH).
+The rate of SNe Ia is thus the sum of the DTD evaluated for each epoch of star formation, multiplied by the stellar mass formed in that epoch.
+Mathematically this is represented by the convolution of the DTD and SFH:
+
+\begin{equation}
+    R_{\mathrm{G}} = \int_{t_0}^{\infty} \psi(t_0-\tau)\Phi(\tau)\,d\tau \,,
+\end{equation}
+where $t_0$ is the epoch at which the galaxy is observed, and $\psi$ is the SFH.
+
+\subsection{Modeling the star formation histories of galaxies \label{subsec:method_sfh}}
+To model the SFH of galaxies as a function of their stellar mass we adopt the model of \citet{Childress2014}.
+In the model, galaxies are expected to evolve smoothly along the so-called "main sequence of star formation" whereby the SFR of a galaxy of stellar mass $M_*$ at redshift $z$ is determined by a simple relationship (the SMz relation, \citealt{Zahid2012}).
+Specifically, we implement their "fine-tuned" model (C14 Eq.
+A7), whereby the SMz flattens above $z\sim2$ in line with observations \citep{Stark2013}.
+We adjust this model slightly and arrive at a final SMz:
+
+\begin{equation}
+    \Psi(M_*,z) = \left(\frac{M_*}{10^{10}}\right)^{0.7}\frac{\exp{\left(1.9z\right)}}{\exp{\left(1.7\left(z-2\right)\right)} + \exp{\left(0.2\left(z-2\right)\right)} } [\mathrm{M}_{\odot} \mathrm{yr}^{-1}]\,.
+\end{equation}
+
+As galaxies grow, their SFR begins to slow down and eventually shut off almost entirely in a process known as quenching. We adopt the quenching penalty $p_Q$ directly from \citet{Childress2014}:
+\begin{equation}
+    p_Q(M_*,z) = \frac{1}{2}\left[1 - \mathrm{erf}\left(\frac{\log(M_*) - \log(M_Q(z)}{\sigma_Q}\right)\right]\,,
+\end{equation}
+where $M_Q(z)$ describes how the quenching mass evolves with redshift, and $\sigma_Q$ is the transition scale which controls how fast a galaxy quenches.
+We adopt the observationally motivated form of the quenching mass evolution (Eq.
+A8 from \citealt{Childress2014}):
+\begin{equation}
+    \log(M_q(z)/\mathrm{M}_{\odot}) = 10.077 + 0.636z \,, 
+\end{equation}
+and a transition scale of $\sigma_Q = 1.1$.
+
+As per \citet{Childress2014} we plant seed galaxies with initial masses of $10^6 \mathrm{M}_{\odot}$ at intervals of 50 Myr for look-back times $1 \leq t_f \leq 10$ Gyr, and 25 Myr for look-back times $10 \leq t_f \leq 13$ Gyr, and evaluate the model with a time step of 0.5 Myr.
+
+The result of our toy model is shown in Fig. \ref{fig:SFHs}
+
+\section{Results \label{sec:rates}}
+
+The rate of SNe per galaxy ($R_{\mathrm{G}}$) per year in a transient survey can be approximated by the simple equation:
+\begin{equation}
+    R_{\mathrm{G}} = \frac{N_{\mathrm{SN}}}{N_{\mathrm{G}}} \frac{A_{\mathrm{G}}}{A_{\mathrm{SN}}} \frac{1}{T_{\mathrm{SN  survey}}}\,,
+\label{eq:rate1}
+\end{equation}
+where $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ are the respective number of SNe and galaxies detected, $A_{\mathrm{SN}}$ and $A_{\mathrm{G}}$ the sky areas from which the SNe and G samples were taken, and $T$ the duration of the SN survey in years.
+By binning both the SN hosts and field galaxies by their stellar mass we can approximate the function $R_{\mathrm{G}}(M_*)$.
 

### 2020-12-18 draft.tex
Updates from Overleaf

@@
 % Keep the title short and informative.
-\title[DES SN Ia Galactic Rate]{Supernova Host Galaxies in the Dark Energy Survey: III. The Evolving Galactic Rate of Type Ia Supernovae}
+\title[Rates of SNe Ia in DES]{Supernova Host Galaxies in the Dark Energy Survey: III. Constraining the SN Ia delay time dstribution}
 
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figs/mass_hist_log_BC03.png}
+    \caption{Distribution of the stellar mass of the field galaxies used in the analysis. The distribution is well described by a Schechter function.
+    \label{fig:log_mass_field}}
+\end{figure}
+
 \subsection{Galaxy properties \label{subsec:properties}}
@@
 
-\begin{figure}
+\begin{figure*}
     \centering
-    \includegraphics[width=0.5\textwidth]{figs/mass_hist_log_BC03.png}
-    \caption{Distribution of the stellar mass of the field galaxies used in the analysis. The distribution is well described by a Schechter function.
-    \label{fig:log_mass_field}}
-\end{figure}
+    \includegraphics[width=\textwidth]{figs/SFHs_colour.png}
+    \caption{The stellar mass assembly of the Universe as prescribed by the toy model of \citet{Childress2014}}
+    \label{fig:SFHs}
+\end{figure*}
 
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics{}
-    \caption{Caption}
-    \label{fig:my_label}
-\end{figure*}
-
 \section{Modeling the rate of type Ia supernovae \label{sec:method}}
@@
 
-The result of our toy model is shown in Fig. \ref{fig:SFHs}
+The result of our toy model is shown in Fig.
+\ref{fig:SFHs}.
+Galaxies with high masses at $z=0$ formed the vast majority of their stars in the first few Gyr and are now likely to be passive with old stellar populations, while low-mass galaxies are currently strongly star-forming with a vast majority of young stars.
+Galaxies with masses around $10^10 \mathrm{M}_{\odot}$ are composed of a mixture of young and older stellar populations.
 
@@
 where $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ are the respective number of SNe and galaxies detected, $A_{\mathrm{SN}}$ and $A_{\mathrm{G}}$ the sky areas from which the SNe and G samples were taken, and $T$ the duration of the SN survey in years.
+As described in Section \ref{sec:incompleteness}, the values of $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ that we observe are underestimates of the true numbers due to observational incompleteness.
+We thus estimate the intrinsic numbers of SNe and galaxies by multiplying the observed numbers by their respective incompleteness corrections,
+
+\begin{equation}
+    N_{\mathrm{SN,intrinsic}} = \eta_{\mathrm{SN}} \cdot N_{\mathrm{SN, obs}}
+\end{equation}
+and
+\begin{equation}
+    N_{\mathrm{G,intrinsic}} = \eta_{\mathrm{G}} \cdot N_{\mathrm{G, obs}}
+\end{equation}
+
 By binning both the SN hosts and field galaxies by their stellar mass we can approximate the function $R_{\mathrm{G}}(M_*)$.

### 2021-01-04 draft.tex

@@
 The DTD can be interpreted as the rate at which SNe Ia occur as a function of the delay time $\tau$ since an episode of star-formation, and thus carries characteristic signatures of the progenitor channel (see \citealt{Wang2012} for a review).
-While the SD scenario is able to produce a broad range of functional forms of the DTD, the DD scenario predicts a power law of the form $t^{\beta}$, with $\beta \sim -1$ \citep[e.g][]{Ruiter2009,Mennekens2010}.
+While the SD scenario is able to produce a broad range of functional forms of the DTD, the DD scenario predicts a power law of the form $\tau^{\beta}$, with $\beta \sim -1$ \citep[e.g][]{Ruiter2009,Mennekens2010}.
 
@@
 We use the stellar mass assembly model of \citet{Childress2014} to predict the stellar age distribution of galaxies for a given stellar mass at the mean redshift of our SN sample, and then forward model the DTD by convolving it with the stellar age distribution and comparing the predicted rates to the observed rates.
+
+We introduce the SN host and field galaxy samples in Section \ref{sec:data} and describe our handling of incompleteness in Section \ref{sec:incompleteness}.
+We outline the modelling of star-formation histories in Section \ref{sec:method}, and present our results in Section \ref{sec:rates}.
+In Section \ref{sec:discussion} we discuss the robustness of the result and its meaning in a wider context, before concluding in Section \ref{sec:conclusion}.
+Where relevant, we assume a spatially flat $\Lambda$CDM cosmology with $\Omega_m = 0.3$ and $H_0 = 70 \mathrm{ km s}^{-1}\mathrm{Mpc}^{-1}$.
+Unless otherwise stated, we assume Gaussian uncertainties quoted at the $1\sigma$ level.
+Magnitudes are quoted in the AB system \citep{Oke1983}.
 
@@
 
-\section{Data \label{sec:data}}
+%%%% DATA %%%%
+\section{Data}
+\label{sec:data}
 \subsection{Dark Energy Survey supernova programme \label{subsec:des}}
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm.png}
-    \caption{The rate per galaxy of SNe Ia as a function of stellar mass.
-The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
-    \label{fig:rate_fit}
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_all.png}
+    \caption{The rate per galaxy of SNe Ia as a function of stellar mass.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \label{fig:rate_raw}
 \end{figure}
-\section{Incompleteness corrections \label{sec:incompleteness}}
-
+%%%% INCOMPLETENESS %%%%
+\section{Incompleteness corrections}
+\label{sec:incompleteness}
 Although Eq.
@@
 
-\section{Modeling the rate of type Ia supernovae \label{sec:method}}
-
+%%% MODEL %%%
+\section{Modelling the rate of type Ia supernovae}
+ \label{sec:method}
 We represent the SN Ia DTD by a power law of the form:
-
 \begin{equation}
@@
     R_{\mathrm{G}} = \int_{t_0}^{\infty} \psi(t_0-\tau)\Phi(\tau)\,d\tau \,,
+    \label{eq:galaxy_rate}
 \end{equation}
@@
 
-\subsection{Modeling the star formation histories of galaxies \label{subsec:method_sfh}}
-To model the SFH of galaxies as a function of their stellar mass we adopt the model of \citet{Childress2014}.
+In previous work \citep[e.g.][]{Strolger2004,Maoz2012} it has been common to determine the SFH for every galaxy in the survey via SED fitting.
+Eq.
+\ref{eq:galaxy_rate} is then used to calculate an expected number of SNe in each galaxy given the effective survey time, which is compared to the observed number in that galaxy (usually 0 and occasionally 1) using Poisson statistics.
+This method relies on either photometry covering several wavelength bands, or optical spectra with high signal-to-noise ratio (S/N), in order to distinguish accurately between SFHs.
+Such accuracy is not possible for the DES sample: we do not possess spectra of all galaxies in the field, and in some cases only have the four optical bands available -- and have a maximum of eight from NUV to NIR -- from which to infer a SFH.
+This lack of detail is compounded by our relying on photometric redshifts which add an extra layer of uncertainty to the calculation.
+
+Instead of determining individual SFHs for each galaxy in our field sample, we use an empirical approach to estimate mean SFHs for galaxies as a function of their stellar mass at any given redshift (or equivalently, time $t_0$), that can be represented as $\hat \psi \left(t_0 -\tau; M_* \right)$.
+This method paves the way for modelling the SN Ia rate as a function of stellar mass by combining the mean SFHs and the DTD through Eq.
+\ref{eq:galaxy_rate}, and thus placing constraints on the DTD.
+
+\subsection{Modelling the star formation histories of galaxies \label{subsec:method_sfh}}
+
+To model the SFH of galaxies as a function of their stellar mass we adopt the prescription of stellar mass assembly of \citet{Childress2014}, which draws on the work of \citet{Zahid2012}.
 In the model, galaxies are expected to evolve smoothly along the so-called "main sequence of star formation" whereby the SFR of a galaxy of stellar mass $M_*$ at redshift $z$ is determined by a simple relationship (the SMz relation, \citealt{Zahid2012}).
@@
 Galaxies with high masses at $z=0$ formed the vast majority of their stars in the first few Gyr and are now likely to be passive with old stellar populations, while low-mass galaxies are currently strongly star-forming with a vast majority of young stars.
-Galaxies with masses around $10^10 \mathrm{M}_{\odot}$ are composed of a mixture of young and older stellar populations.
+Galaxies with masses around $10^{10} \mathrm{M}_{\odot}$ are composed of a mixture of young and older stellar populations.
 
-\section{Results \label{sec:rates}}
+%%%%%% RESULTS %%%%%%%%
 
-The rate of SNe per galaxy ($R_{\mathrm{G}}$) per year in a transient survey can be approximated by the simple equation:
+\section{Results }
+\label{sec:rates}
+The rate of SNe per galaxy ($R_{\mathrm{G}}$) per year in a transient survey can be approximated by the equation:
 \begin{equation}
-    R_{\mathrm{G}} = \frac{N_{\mathrm{SN}}}{N_{\mathrm{G}}} \frac{A_{\mathrm{G}}}{A_{\mathrm{SN}}} \frac{1}{T_{\mathrm{SN  survey}}}\,,
+    R_{\mathrm{G}} = \frac{N_{\mathrm{SN}}}{N_{\mathrm{G}}} \frac{V_{\mathrm{G}}}{V_{\mathrm{SN}}}\frac{1}{T_{\mathrm{SN  survey}}}\,,
 \label{eq:rate1}
 \end{equation}
-where $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ are the respective number of SNe and galaxies detected, $A_{\mathrm{SN}}$ and $A_{\mathrm{G}}$ the sky areas from which the SNe and G samples were taken, and $T$ the duration of the SN survey in years.
-As described in Section \ref{sec:incompleteness}, the values of $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ that we observe are underestimates of the true numbers due to observational incompleteness.
-We thus estimate the intrinsic numbers of SNe and galaxies by multiplying the observed numbers by their respective incompleteness corrections,
+where $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ are the respective number of SNe and galaxies detected, $V_{\mathrm{SN}}$ and $V_{\mathrm{G}}$ the volumes from which the SNe and G samples were taken, and $T$ the duration of the SN survey in years.
+
+As described in Section \ref{sec:incompleteness}, the values of $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ that we observe are underestimates of the true numbers due to observational incompleteness -- we do not detect and count all SNe in the volume $V_{\mathrm{SN}}$, nor do we detect and count all galaxies in the volume $V_{\mathrm{G}}$.
+We thus estimate the intrinsic numbers of SNe and galaxies by multiplying the observed numbers by their respective incompleteness corrections calculated in Sections \ref{subsec:incompleteness_SNe} and \ref{subsec:incompletenss_SN_hosts} for SNe and Section \ref{subsec:incompleteness_field} for field galaxies:
 
 \begin{equation}
-    N_{\mathrm{SN,intrinsic}} = \eta_{\mathrm{SN}} \cdot N_{\mathrm{SN, obs}}
+    N_{\mathrm{SN,intrinsic}} = \sum_i^{n_{\mathrm{SN}}}\eta_{\mathrm{SN,}i}\,,
+    \label{eq:corr_SN}
 \end{equation}
@@
 \begin{equation}
-    N_{\mathrm{G,intrinsic}} = \eta_{\mathrm{G}} \cdot N_{\mathrm{G, obs}}
+    N_{\mathrm{G,intrinsic}} = \sum_j^{n_{\mathrm{G}}} \eta_{\mathrm{G,}j} 
+    \label{eq:corr_G}
 \end{equation}
-
-By binning both the SN hosts and field galaxies by their stellar mass we can approximate the function $R_{\mathrm{G}}(M_*)$.
+for each SN $i$ and galaxy $j$.
 
@@
 
+By binning both the SN hosts and field galaxies by their stellar mass we measure the mean SN Ia rate per galaxy as a function of stellar mass, $R_{\mathrm{G}}(M_*)$.
+We employ a bootstrap Monte-Carlo approach in order to estimate the uncertainty in the value of the rate in each stellar mass bin.
+The probability distribution function (PDF) of each galaxy's stellar mass is represented by the sum of two half Gaussian distributions to represent the asymmetric positive and negative uncertainties derived in the SED fitting stage (Section \ref{sec:data}).
+For each SN host and field galaxy, we take 100 samples of its stellar mass by drawing at random from its PDF.
+For each of the 100 samples we calculate the SN rate per galaxy in each stellar mass bin via Eq \ref{eq:rate1}, using the completeness-corrected values of $N_{\mathrm{SN}}$ and $N_{\mathrm{SN}}$ from Eqs.
+\ref{eq:corr_SN} and \ref{eq:corr_G} respectively.
+
+The rate of SNe Ia per galaxy as a function of stellar mass is shown in Fig. \ref{fig:rate_raw}.
+
 \subsection{Dependence of the SN Ia rate on SFR \label{subsec:rates_sfr}}
 
+\section{Discussion}
+\label{sec:discussion}
+
 \section{Conclusions}
-
+\label{sec:conclusion}
 The last numbered section should briefly summarise what has been done, and describe

### 2021-01-04 draft.tex

@@
 
-\section{Results }
+\section{Results}
 \label{sec:rates}
@@
 
-The rate of SNe Ia per galaxy as a function of stellar mass is shown in Fig. \ref{fig:rate_raw}.
-
+The rate of SNe Ia per galaxy as a function of stellar mass is shown in Fig.
+\ref{fig:rate_raw}.
+The relationship between SN Ia rate and galaxy stellar mass is well described by a linear function.
+To find the slope and intercept that best describe the data we employ Hamiltonian Monte-Carlo (HMC), which we implement via the \texttt{pystan} package and describe in full detail in Appendix \ref{appendix:linear_fits}.
 \subsection{Dependence of the SN Ia rate on SFR \label{subsec:rates_sfr}}
@@
 
-\section{Some extra material}
+\section{Linear fits using Hamiltonian Monte Carlo}
+In this section we describe the procedures used to fit slopes and intercepts to the relationships measured in the analysis.
 
-If you want to present additional material which would interrupt the flow of the main paper,
-it can be placed in an Appendix which appears after the list of references.
+\label{appendix:linear_fits}
+We model the relation with the linear relationship: 
+\begin{equation}
+    R_{\mathrm{G}} = dR/dM_* M_* + c \,,
+\label{eq:rate_fit}
+\end{equation}
+where $dR/dM_*$ signifies the change of the rate of SNe as a function of the stellar mass, $c$ is a constant that sets the normalisation of the rate.
+We fit the model assuming a normal likelihood, such that the observed rate in each stellar mass bin is itself modelled as a Gaussian distribution described by the mean and standard deviation of the data in that bin.
 

### 2021-01-12 draft.tex
Updates from Overleaf

@@
 % Keep the title short and informative.
-\title[Rates of SNe Ia in DES]{Supernova Host Galaxies in the Dark Energy Survey: III. Constraining the SN Ia delay time dstribution}
+\title[Rates of SNe Ia in DES]{Measuring the Type Ia supernova delay time distribution via host galaxy rates in the Dark Energy Survey}
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_all.png}
-    \caption{The rate per galaxy of SNe Ia as a function of stellar mass.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
-    \label{fig:rate_raw}
-\end{figure}
 %%%% INCOMPLETENESS %%%%
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_all.png}
+    \caption{The rate per galaxy of SNe Ia as a function of stellar mass.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \label{fig:rate_raw}
+\end{figure}
+
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_split_sfr.png}
+%    \caption{The rate per galaxy of SNe Ia as a function of stellar mass for moderately and highly star-forming galaxies, as well as passive galaxies.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+%    \label{fig:rate_raw_split_sfr}
+%\end{figure}
 %%% MODEL %%%
@@
  \label{sec:method}
-We represent the SN Ia DTD by a power law of the form:
+We represent the SN Ia DTD by a power law.
+We consider the DTD effective after some "prompt time" $t_{\mathrm{p}}$, before which its value is set to 0.
+This is generally interpreted as the time taken for WDs to form after the burst of star formation.
+The DTD is thus:
 \begin{equation}
-    \Phi(\tau) = A\left(\frac{\tau}{\mathrm{Gyr}}\right)^{\beta}\,,
+ \Phi(\tau) = \left\{
+    \begin{array}{@{}cc@{}}
+    0 , & \tau < t_{\mathrm{p}} \\
+    A\left(\frac{\tau}{\mathrm{Gyr}}\right)^{\beta} , & \tau \geq t_{\mathrm{p}}
+    \end{array}\right.
+        \label{eq:dtd}
 \end{equation} 
-where $\tau$ is the time since a burst of star formation, and $A$ is a normalisation at $\tau=1\mathrm{Gyr}$.
+where $\tau$ is the time since a burst of star formation, and $A$ is a normalisation at $\tau=1$ Gyr.
 If all stars in a galaxy were formed at a single epoch $t_f$, the DTD would describe the rate of SNe at an observation time $\tau = t_0$.
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_all.png}
+    \caption{The rate per galaxy of SNe Ia as a function of stellar mass.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \label{fig:rate_raw}
+\end{figure}
+
 \subsection{Dependence of the SN Ia rate on stellar mass \label{subsec:rates_mass}}
@@
 \ref{fig:rate_raw}.
-The relationship between SN Ia rate and galaxy stellar mass is well described by a linear function.
+The relationship between SN Ia rate and galaxy stellar mass is well described by a linear function in log space, which corresponds to a power law.
 To find the slope and intercept that best describe the data we employ Hamiltonian Monte-Carlo (HMC), which we implement via the \texttt{pystan} package and describe in full detail in Appendix \ref{appendix:linear_fits}.
-\subsection{Dependence of the SN Ia rate on SFR \label{subsec:rates_sfr}}
+We measure a slope of $0.70\pm0.02$, which is broadly consistent with the values found in SNLS and SDSS by \citet{Sullivan2006} and \citet{Smith2012} respectively.
+It is evident that the linear fit is not consistent with the data across the full range of stellar mass considered.
+In particular, there appear to be two locations of interest: firstly, the slope is steeper at masses lower than $10^9$ M$_{\odot}$; secondly there is an apparent flattening and possibly a turnover at masses around and above $10^11$ M$_{\odot}$.
+The most likely cause of these divergences is because the SN rate is driven by the SFH which is not a linear function of stellar mass (see Section \ref{sec:method}).
+Second order effects may also be important, and we address these in Section \ref{sec:discussion}.
+
+%\textbf{TEMPTED TO DITCH THIS SINCE OUR SFR IS SKETCHY}
+%In order to make a more detailed comparison of our results with those of \citet{Sullivan2006} and \citet{Smith2012}, we split galaxies according to their sSFR: galaxies with sSFR$\leq -11.5$ yr$^{-1}$ are denoted as passive, those with $-11.5 < \mathrm{sSFR} \leq -9.5$ are moderately star-forming, and those with sSFR $>-9.5$ are labelled as highly star-forming.
+The results when split this way are shown in Fig.
+\ref{fig:rate_raw_split_sfr}.
+Star-forming galaxies show a steeper slope than their passive counterparts, with values of $1.10 \pm 0.05$ and $0.84 \pm 0.04$ for moderate and highly star-forming galaxies respectively, while passive galaxies show a much shallower slope of $0.55 \pm 0.08$.
+These values are broadly similar to those measured in SDSS by \citet{Smith2012}, with star-forming galaxies showing steeper slopes than passives (\citet{Smith2012} found 1.01 and 0.72 for SF and passive, respectively).
+We note that we detect no passive galaxies with mass below $10^{10} \mathrm{M}_{\odot}$.
+Above this value, the \citet{Smith2012} data for passive galaxies is considerably flatter than that which we measure.
+On the other hand our results are inconsistent with those found at a similar redshift to the DES data in SLNS \citep{Sullivan2006}, who measured a slope of 1.10 in passives but 0.66 and 0.74 in moderate and highly star-forming galaxies respectively.
+We note that the moderately star-forming slope is thus consistent between DES and SNLS, but the slopes of passive and highly star-forming galaxies are swapped.
+
+\subsection{Constraints on the SN Ia delay time distribution}
+\label{subsec:results_dtd}
+
+In Section \ref{sec:method} we showed how the rate of SNe Ia is driven by the convolution of the SFH of galaxies and the SN Ia DTD (Eq.
+\ref{eq:galaxy_rate}).
+We then prescribed a model to infer the mean SFHs of galaxies of any given stellar mass.
+In this section, we measure the DTD by forward modelling it through Eq.
+\ref{eq:galaxy_rate} at the stellar masses corresponding to the centres of the bins in Fig.
+\ref{fig:rate_raw}.
+
+We assume a DTD $\Phi(\tau)$ with a power-law form described by index $\beta$ (Eq.
+\ref{eq:dtd}), normalisation $A$ and effective after prompt time $t_{\mathrm{p}}$.
+As per Section \ref{subsec:rates_mass}, we constrain the parameters via Bayesian inference, using HMC.
+At each step of the sampling procedure the model is re-calculated via Eq.
+\ref{eq:galaxy_rate}, and evaluate the likelihood assuming that the rate data are normally distributed about their means.
+For $\beta$ we adopt a Gaussian prior with hyper-parameters $p(\beta) \sim \mathcal{N}(-1\,,0.3)$.
+We fit for $A$ in log space, and adopt a Gaussian prior (in log space) with hyper-parameters $p(A) \sim \mathcal{N}(-12.7\,, 0.5)$.
+
+SNe Ia do not occur instantaneously after an episode of star formation.
+Instead stars with zero-age main-sequence (ZAMS) masses less than $8 \mathrm{M}_{\odot}$ take time to evolve along the main sequence and form WDs and this time is not well constrained.
+In many works this ``prompt time" $t_{\mathrm{p}}$ is fixed to some value expected to be the minimum time for a star to evolve off the MS and become a WD, such as 40 Myr \citep{Maoz2012,Graur2014,Graur2018}.
+Other studies have left $t_{\mathrm{p}}$ as a free parameter \citep{Heringer2019,Asier2020}.
+We perform two fits: one with $t_{\mathrm{p}}$ fixed at 40 Myr, and one with it as a free parameter.
+We fit $t_{\mathrm{p}}$ in log space and adopt a Gaussian prior with hyper-parameters $p(\log(t_{\mathrm{p}})) \sim \mathcal{N}(-1.3\,,0.2)$, which corresponds to being centred around 50 Myr.
+Choosing this regime to fit allows more prior weight to be placed on shorter prompt times as per the majority of the literature.
+
+The posterior distributions for the fit parameters are found in Figs.
+\ref{fig:corner_beta_norm} and \ref{fig:corner_beta_norm_tp} for the fixed and free $t_{\mathrm{p}}$ fits respectively, and the posterior means and standard deviations are summarised in Table \ref{tab:dtd_results}.
+The inclusion of $t_{\mathrm{p}}$ in the fit produces results for all three parameters that are significantly different than in the fixed case, suggesting either that the prompt time is different to 40 Myr, or that the method is incapable of constraining these three parameters simultaneously.
 

### 2021-01-13 draft.tex

@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figs/completeness_combined.png}
+    \caption{Measuring the completeness of the field galaxy sample.
+\textit{Upper}: the $T_{\mathrm{C}}$ statistic as a function of apparent magnitude; \textit{middle} as per \textit{upper}, but for $T_{\mathrm{V}}$; \textit{lower}: the combined, normalised completeness in each band.
+    \label{fig:completeness}}
+\end{figure}
+
 \subsection{Galaxy properties \label{subsec:properties}}
@@
 %%%% INCOMPLETENESS %%%%
+
 \section{Incompleteness corrections}
@@
 To determine the apparent magnitude limit in each of the optical bands we employ the method of \citet{Johnston2007,Teodoro2010,Johnston2012} (hereafter Completeness I, II, III respectively).
-Test statistics $T_C$ and $T_V$ are computed based on absolute magnitude and distance modulus by calculating the rank of each galaxy's absolute magnitude (distance modulus) when compared to all other galaxies in a survey within a certain slice of distance modulus (absolute magnitude).
+Test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ are computed based on absolute magnitude and distance modulus by calculating the rank of each galaxy's absolute magnitude (distance modulus) when compared to all other galaxies in a survey within a certain slice of distance modulus (absolute magnitude).
 For a galaxy of apparent magnitude $m < m_{\mathrm{lim, trial}}$ observed in a survey complete to magnitude $m_{\mathrm{lim, true}}$ where  $m_{\mathrm{lim, trial}} \leq m_{\mathrm{lim, true}}$, the expectation value of the rank is 0.5.
 However, if a trial limiting magnitude $m_{\mathrm{lim, trial}} \geq m_{\mathrm{lim, true}}$, there will be a lack of observed faint objects, such that the expectation value of the rank drops.
-Completeness I, II, and III show that for surveys with sharp, well defined magnitude limits the test statistics $T_C$ and $T_V$ drop sharply.
+Completeness I, II, and III show that for surveys with sharp, well defined magnitude limits the test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ drop sharply.
 The DES deep stacks present a more challenging case.
@@
 To reduce the inhomogeneity while still including  large sample of objects, we split the sample into the deep (X3) and shallow (E2) fields and calculate limiting magnitudes separately.
-Figs.
-\ref{fig:completeness_X3, fig:completenessE2} show the values of $T_C$ and $T_V$ for the two fields respectively.
+Fig.
+\ref{fig:completeness} shows the values of $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$.
 The values of the test statistics increase with $m_{\mathrm{lim, trial}}$ until a peak, before decreasing to stable values at magnitudes far beyond the limit of the survey.

### 2021-01-13 draft.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_all.png}
-    \caption{The rate per galaxy of SNe Ia as a function of stellar mass.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm.png}
+    \caption{The rate per galaxy of SNe Ia as a function of stellar mass along with the best fitting model.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
     \label{fig:rate_raw}

### 2021-01-14 draft.tex

--- 2021-01-13 draft.tex
@@
 proportional to instantaneous SFR) and "tardy" (i.e.
-proportional to overall stellar mass) SNe, respectively A complementary technique involves measuring the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008}.
+proportional to overall stellar mass) SNe, respectively A complementary technique involves measuring the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008, Graur2018, Frohmaier2019}.
 This technique is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clusters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Graur2014,Maoz2014}.
@@
 
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{figs/SFHs_colour.png}
-    \caption{The stellar mass assembly of the Universe as prescribed by the toy model of \citet{Childress2014}}
-    \label{fig:SFHs}
-\end{figure*}
-
 %%%% INCOMPLETENESS %%%%
@@
 %%% MODEL %%%
-\section{Modelling the rate of type Ia supernovae}
- \label{sec:method}
-We represent the SN Ia DTD by a power law.
-We consider the DTD effective after some "prompt time" $t_{\mathrm{p}}$, before which its value is set to 0.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{figs/SFHs_colour.png}
+    \caption{The stellar mass assembly of the Universe as prescribed by the toy model of \citet{Childress2014}}
+    \label{fig:SFHs}
+\end{figure*}
+
+%%%%%% RESULTS %%%%%%%%
+
+\section{The per-galaxy rate of type Ia supernovae}
+\label{sec:rates}
+The rate of SNe per galaxy ($R_{\mathrm{G}}$) per year in a transient survey can be approximated by the equation:
+\begin{equation}
+    R_{\mathrm{G}} = \frac{N_{\mathrm{SN}}}{N_{\mathrm{G}}} \frac{V_{\mathrm{G}}}{V_{\mathrm{SN}}}\frac{1}{T_{\mathrm{SN  survey}}}\,,
+\label{eq:rate1}
+\end{equation}
+where $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ are the respective number of SNe and galaxies detected, $V_{\mathrm{SN}}$ and $V_{\mathrm{G}}$ the volumes from which the SNe and G samples were taken, and $T$ the duration of the SN survey in years.
+
+As described in Section \ref{sec:incompleteness}, the values of $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ that we observe are underestimates of the true numbers due to observational incompleteness -- we do not detect and count all SNe in the volume $V_{\mathrm{SN}}$, nor do we detect and count all galaxies in the volume $V_{\mathrm{G}}$.
+We thus estimate the intrinsic numbers of SNe and galaxies by multiplying the observed numbers by their respective incompleteness corrections calculated in Sections \ref{subsec:incompleteness_SNe} and \ref{subsec:incompletenss_SN_hosts} for SNe and Section \ref{subsec:incompleteness_field} for field galaxies:
+
+\begin{equation}
+    N_{\mathrm{SN,intrinsic}} = \sum_i^{n_{\mathrm{SN}}}\eta_{\mathrm{SN,}i}\,,
+    \label{eq:corr_SN}
+\end{equation}
+and
+\begin{equation}
+    N_{\mathrm{G,intrinsic}} = \sum_j^{n_{\mathrm{G}}} \eta_{\mathrm{G,}j} 
+    \label{eq:corr_G}
+\end{equation}
+for each SN $i$ and galaxy $j$.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/beta_A_corner.png}
+    \caption{Posterior distributions for DTD slope $\beta$ and normalisation $A$.
+%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \label{fig:corner_beta_norm}}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/beta_A_tp_corner.png}
+    \caption{Posterior distributions for DTD parameters $\beta$, $A$, and $t_{\mathrm{p}}$.
+%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \label{fig:corner_beta_norm_tp}}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm.png}
+    \caption{Rate per galaxy of SNe Ia as a function of stellar mass (green points) along with the prediction from the best fitting DTD parameters $\beta$, $A$, and $t_{\mathrm{p}}$ forward modelled through Eq.
+\ref{eq:galaxy_rate}.
+Samples from the posterior distribution of the model log rate are drawn in cyan while the black dashed line is the mean of the posterior.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \label{fig:rate_fitted}}
+\end{figure}
+
+By binning both the SN hosts and field galaxies by their stellar mass we measure the mean SN Ia rate per galaxy as a function of stellar mass, $R_{\mathrm{G}}(M_*)$.
+We employ a bootstrap Monte-Carlo approach in order to estimate the uncertainty in the value of the rate in each stellar mass bin.
+The probability distribution function (PDF) of each galaxy's stellar mass is represented by the sum of two half Gaussian distributions to represent the asymmetric positive and negative uncertainties derived in the SED fitting stage (Section \ref{sec:data}).
+For each SN host and field galaxy, we take 100 samples of its stellar mass by drawing at random from its PDF.
+For each of the 100 samples we calculate the SN rate per galaxy in each stellar mass bin via Eq \ref{eq:rate1}, using the completeness-corrected values of $N_{\mathrm{SN}}$ and $N_{\mathrm{SN}}$ from Eqs.
+\ref{eq:corr_SN} and \ref{eq:corr_G} respectively.
+
+The rate of SNe Ia per galaxy as a function of stellar mass is shown in Fig.
+\ref{fig:rate_raw}.
+The relationship between SN Ia rate and galaxy stellar mass is well described by a linear function in log space, which corresponds to a power law.
+To find the slope and intercept that best describe the data we employ Hamiltonian Monte-Carlo (HMC), which we implement via the \texttt{pystan} package and describe in full detail in Appendix \ref{appendix:linear_fits}.
+We measure a slope of $0.70\pm0.02$, which is broadly consistent with the values found in SNLS and SDSS by \citet{Sullivan2006} and \citet{Smith2012} respectively.
+It is evident that the linear fit is not consistent with the data across the full range of stellar mass considered.
+In particular, there appear to be two locations of interest: firstly, the slope is steeper at masses lower than $10^9$ M$_{\odot}$; secondly there is an apparent flattening and possibly a turnover at masses around and above $10^{11}$ M$_{\odot}$.
+The most likely cause of these divergences is because the SN rate is driven by the SFH which is not a linear function of stellar mass (see Section \ref{sec:method}).
+Second order effects may also be important, and we address these in the following sections.
+
+\section{Modelling the per-galaxy rate of type Ia supernovae}
+ \label{sec:model}
+
+In Section \ref{sec:rates} and Fig.
+\ref{fig:rate_raw} we showed that the SN Ia rate per galaxy as a function of stellar mass is approximated by, but not perfectly described by, a power-law (and thus a linear relationship in log space).
+In this section, we introduce a physical model in order to better fit the observed rate vs stellar mass relationship.
+
+We begin by considering the delay time distribution of SNe Ia.
+We represent the SN Ia DTD by a power law, which we consider effective after some "prompt time" $t_{\mathrm{p}}$, before which its value is set to 0.
 This is generally interpreted as the time taken for WDs to form after the burst of star formation.
@@
 
-%%%%%% RESULTS %%%%%%%%
-
-\section{Results}
-\label{sec:rates}
-The rate of SNe per galaxy ($R_{\mathrm{G}}$) per year in a transient survey can be approximated by the equation:
-\begin{equation}
-    R_{\mathrm{G}} = \frac{N_{\mathrm{SN}}}{N_{\mathrm{G}}} \frac{V_{\mathrm{G}}}{V_{\mathrm{SN}}}\frac{1}{T_{\mathrm{SN  survey}}}\,,
-\label{eq:rate1}
-\end{equation}
-where $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ are the respective number of SNe and galaxies detected, $V_{\mathrm{SN}}$ and $V_{\mathrm{G}}$ the volumes from which the SNe and G samples were taken, and $T$ the duration of the SN survey in years.
-
-As described in Section \ref{sec:incompleteness}, the values of $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ that we observe are underestimates of the true numbers due to observational incompleteness -- we do not detect and count all SNe in the volume $V_{\mathrm{SN}}$, nor do we detect and count all galaxies in the volume $V_{\mathrm{G}}$.
-We thus estimate the intrinsic numbers of SNe and galaxies by multiplying the observed numbers by their respective incompleteness corrections calculated in Sections \ref{subsec:incompleteness_SNe} and \ref{subsec:incompletenss_SN_hosts} for SNe and Section \ref{subsec:incompleteness_field} for field galaxies:
-
-\begin{equation}
-    N_{\mathrm{SN,intrinsic}} = \sum_i^{n_{\mathrm{SN}}}\eta_{\mathrm{SN,}i}\,,
-    \label{eq:corr_SN}
-\end{equation}
-and
-\begin{equation}
-    N_{\mathrm{G,intrinsic}} = \sum_j^{n_{\mathrm{G}}} \eta_{\mathrm{G,}j} 
-    \label{eq:corr_G}
-\end{equation}
-for each SN $i$ and galaxy $j$.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_all.png}
-    \caption{The rate per galaxy of SNe Ia as a function of stellar mass.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
-    \label{fig:rate_raw}
-\end{figure}
-
-\subsection{Dependence of the SN Ia rate on stellar mass \label{subsec:rates_mass}}
-
-By binning both the SN hosts and field galaxies by their stellar mass we measure the mean SN Ia rate per galaxy as a function of stellar mass, $R_{\mathrm{G}}(M_*)$.
-We employ a bootstrap Monte-Carlo approach in order to estimate the uncertainty in the value of the rate in each stellar mass bin.
-The probability distribution function (PDF) of each galaxy's stellar mass is represented by the sum of two half Gaussian distributions to represent the asymmetric positive and negative uncertainties derived in the SED fitting stage (Section \ref{sec:data}).
-For each SN host and field galaxy, we take 100 samples of its stellar mass by drawing at random from its PDF.
-For each of the 100 samples we calculate the SN rate per galaxy in each stellar mass bin via Eq \ref{eq:rate1}, using the completeness-corrected values of $N_{\mathrm{SN}}$ and $N_{\mathrm{SN}}$ from Eqs.
-\ref{eq:corr_SN} and \ref{eq:corr_G} respectively.
-
-The rate of SNe Ia per galaxy as a function of stellar mass is shown in Fig.
-\ref{fig:rate_raw}.
-The relationship between SN Ia rate and galaxy stellar mass is well described by a linear function in log space, which corresponds to a power law.
-To find the slope and intercept that best describe the data we employ Hamiltonian Monte-Carlo (HMC), which we implement via the \texttt{pystan} package and describe in full detail in Appendix \ref{appendix:linear_fits}.
-We measure a slope of $0.70\pm0.02$, which is broadly consistent with the values found in SNLS and SDSS by \citet{Sullivan2006} and \citet{Smith2012} respectively.
-It is evident that the linear fit is not consistent with the data across the full range of stellar mass considered.
-In particular, there appear to be two locations of interest: firstly, the slope is steeper at masses lower than $10^9$ M$_{\odot}$; secondly there is an apparent flattening and possibly a turnover at masses around and above $10^11$ M$_{\odot}$.
-The most likely cause of these divergences is because the SN rate is driven by the SFH which is not a linear function of stellar mass (see Section \ref{sec:method}).
-Second order effects may also be important, and we address these in Section \ref{sec:discussion}.
-
 %\textbf{TEMPTED TO DITCH THIS SINCE OUR SFR IS SKETCHY}
@@
 
-\subsection{Constraints on the SN Ia delay time distribution}
+\begin{table}
+	\centering
+	\caption{This is an example table. Captions appear above each table.
+	Remember to define the quantities, symbols and units used.}
+	\label{tab:dtd_results}
+	\begin{tabular}{lccr} % four columns, alignment for each
+		\hline
+		 &$\beta$ & $A$ & $t_{\mathrm{p}}$\\
+		 &-       & $10^{-13}$ M$_{\odot}^{-1}$yr$^{-1}$ & Gyr \\
+		\hline
+		Fixed $t_{\mathrm{p}}$ & $-1.04$ &  $1.7$ & -\\
+		Free $t_{\mathrm{p}}$ & $-0.99 \pm 0.09$ & $2.1 \pm 0.2$ & $0.09 \pm 0.05$\\
+		\hline
+	\end{tabular}
+\end{table}
+
+\subsection{Constraining the SN Ia delay time distribution}
 \label{subsec:results_dtd}
 
-In Section \ref{sec:method} we showed how the rate of SNe Ia is driven by the convolution of the SFH of galaxies and the SN Ia DTD (Eq.
+At the beginning of this Section, we showed how the rate of SNe Ia is driven by the convolution of the SFH of galaxies and the SN Ia DTD (Eq.
 \ref{eq:galaxy_rate}).
 We then prescribed a model to infer the mean SFHs of galaxies of any given stellar mass.
-In this section, we measure the DTD by forward modelling it through Eq.
+Here, we measure the DTD by forward modelling it through Eq.
 \ref{eq:galaxy_rate} at the stellar masses corresponding to the centres of the bins in Fig.
@@
 Instead stars with zero-age main-sequence (ZAMS) masses less than $8 \mathrm{M}_{\odot}$ take time to evolve along the main sequence and form WDs and this time is not well constrained.
-In many works this ``prompt time" $t_{\mathrm{p}}$ is fixed to some value expected to be the minimum time for a star to evolve off the MS and become a WD, such as 40 Myr \citep{Maoz2012,Graur2014,Graur2018}.
+In many works this ``prompt time" $t_{\mathrm{p}}$ is fixed to some value expected to be the minimum time for a star to evolve off the MS and become a WD, such as 40~Myr \citep{Maoz2012,Graur2014,Graur2018}.
 Other studies have left $t_{\mathrm{p}}$ as a free parameter \citep{Heringer2019,Asier2020}.
 We perform two fits: one with $t_{\mathrm{p}}$ fixed at 40 Myr, and one with it as a free parameter.
-We fit $t_{\mathrm{p}}$ in log space and adopt a Gaussian prior with hyper-parameters $p(\log(t_{\mathrm{p}})) \sim \mathcal{N}(-1.3\,,0.2)$, which corresponds to being centred around 50 Myr.
+We fit $t_{\mathrm{p}}$ in log space and adopt a Gaussian prior with hyper-parameters $p(\log(t_{\mathrm{p}})) \sim \mathcal{N}(-1.3\,,0.2)$, which corresponds to being centred around 50~Myr.
 Choosing this regime to fit allows more prior weight to be placed on shorter prompt times as per the majority of the literature.
@@
 \ref{fig:corner_beta_norm} and \ref{fig:corner_beta_norm_tp} for the fixed and free $t_{\mathrm{p}}$ fits respectively, and the posterior means and standard deviations are summarised in Table \ref{tab:dtd_results}.
-The inclusion of $t_{\mathrm{p}}$ in the fit produces results for all three parameters that are significantly different than in the fixed case, suggesting either that the prompt time is different to 40 Myr, or that the method is incapable of constraining these three parameters simultaneously.
+In Fig.
+\ref{fig:rate_fitted} we show the SN rate per galaxy predicted by the model assuming the best fitting DTD parameters from Table \ref{tab:dtd_results} compared to the data as presented in Section \ref{sec:rates}.
+The model provides a good fit across a wide range of stellar mass.
+The model clearly diverges from the simple log-linear fit, describing better the suppressed rate at the low and high ends of the stellar mass range, as well as the enhanced rate around $10^{10}$ M$_{\odot}$.
+This improvement provides evidence to support the DTD*SFH model.
+However, the model prediction still diverges from the data at low ($<10^9$ M$_{\odot}$) and high ($>10^{11.25}$ M$_{\odot}$), suggesting that these data cannot be explained by the our model, but are driven by further processes that we have not included.
+We discuss these in Section \ref{subsec:discussion}.
 
-\section{Discussion}
-\label{sec:discussion}
+\subsection{Comparison to previous DTD measurements \label{subsec:compare_dtd}}
+
+\subsubsection{The DTD power law index \label{subsubsec:compare_beta}}
+The index of the DTD power law measured here is consistent with the majority of previous analyses using various methods.
+Our measurement provides an independent support to the values close to $-1$ found using volumetric rates \citep[e.g.][]{Graur2018,Frohmaier2019}, individual galaxy SFHs \citep[e.g.][]{Maoz2012,Graur2013}, and galaxy clusters \citep[e.g.][]{Maoz2010} although our slope is marginally inconsistent with that of \citet{Heringer2019}.
+
+\subsubsection{The DTD normalisation \label{subsubsec:compare_A}}
+The normalisation of the DTD is less frequently reported.
+\citet{Graur2013} found a value of $7 \times 10^{-14}$~M$_{\odot}^{-1}$~yr$^{-1}$ using the SFH technique, whereas \citet{Heringer2019} report $7 \times 10^{-13}$~M$_{\odot}^{-1}$~yr$^{-1}$.
+These results lie either side of our measured value.
+\citet{Heringer2019} note that the normalisation recovered from the SFHR method is sensitive to the assumed prompt time $t_{\mathrm{p}}$, which we also find using our method.
+
+\subsubsection{The SN Ia prompt time \label{subsubsec:compare_tp}}
+
+The majority of works in the field have constrained the DTD power-law slope, and many also estimate its normalisation.
+Conversely, few have attempted to constrain the time after a burst of star-formation at which SNe Ia begin to explode -- the prompt time $t_{\mathrm{p}}$.
+In most cases, $t_{\mathrm{p}}$ has been fixed at some fiducial value such as 40~Myr, which is derived from the lifetime of 8~M$_{\odot}$ stars.
+
+\subsection{Second order processes affecting the supernova rate \label{subsec:discussion}}
+
+\subsubsection{Stochastic SFHs}
 

### 2021-01-15 draft.tex

@@
 \begin{equation}
-    p_Q(M_*,z) = \frac{1}{2}\left[1 - \mathrm{erf}\left(\frac{\log(M_*) - \log(M_Q(z)}{\sigma_Q}\right)\right]\,,
+    p_Q(M_*,z) = \frac{1}{2}\left[1 - \mathrm{erf}\left(\frac{\log(M_*) - \log(M_Q(z))}{\sigma_Q}\right)\right]\,,
+    \label{eq:pq}
 \end{equation}
@@
     \log(M_q(z)/\mathrm{M}_{\odot}) = 10.077 + 0.636z \,, 
+    \label{eq:mq}
 \end{equation}
-and a transition scale of $\sigma_Q = 1.1$.
+and a transition scale of $\sigma_Q = 1.1$ which provides a good fit to data from the Galaxy And Mass Assembly (GAMA) survey \citep{Baldry2012}.
 
@@
 		\hline
-		Fixed $t_{\mathrm{p}}$ & $-1.04$ &  $1.7$ & -\\
+		Fixed $t_{\mathrm{p}}$ & $-1.03\pm 0.06$ &  $1.7 \pm 0.05$ & -\\
 		Free $t_{\mathrm{p}}$ & $-0.99 \pm 0.09$ & $2.1 \pm 0.2$ & $0.09 \pm 0.05$\\
@@
 These results lie either side of our measured value.
-\citet{Heringer2019} note that the normalisation recovered from the SFHR method is sensitive to the assumed prompt time $t_{\mathrm{p}}$, which we also find using our method.
+\citet{Heringer2019} note that the normalisation recovered from the SFHR method is sensitive to the assumed prompt time $t_{\mathrm{p}}$ (see Section \ref{subsubsec:compare_tp}, which we also find using our method.
 
@@
 In most cases, $t_{\mathrm{p}}$ has been fixed at some fiducial value such as 40~Myr, which is derived from the lifetime of 8~M$_{\odot}$ stars.
+\citet{Asier2020} included $t_{\mathrm{p}}$ (which they denote $\Delta$) in their fit, and find a value of $50_{-35}^{+100}$~Myr which is consistent with both 40~Myr as well as our best fitting value of $90 \pm 50$~Myr.
+\citet{Heringer2019} also present fits with varying prompt times, although they don't fit for the parameter itself.
+They find that varying $t_{\mathrm{p}}$ changes the recovered normalisation, which is consistent with the degeneracy seen in our results (Fig.
+\ref{fig:corner_beta_norm_tp}).
+We therefore report results that are consistent with the fiducial value of 40~Myr.
 
@@
 
-\subsubsection{Stochastic SFHs}
+The use of SN Ia rates to constrain the SN Ia DTD has consistently led to a $t^{-1}$ power-law, which is widely accepted as evidence for the DD scenario.
+While our results are also consistent with those derived in previous studies, our model is mildly inconsistent with the SN rate per galaxy at very low and very high stellar mass.
+In both cases, the model over predicts the observed rate of SNe Ia in galaxies in that stellar mass range, and thus any second order effects must act to suppress the rate compared to the fiducial model.
+
+\subsubsection{Stochasticity of galaxy evolution}
+
+The toy model of stellar mass assembly used in this work includes several assumptions about the evolution of galaxies.
+In particular, it is assumed that galaxies evolve independent of each other, growing up the SFMS until they reach a mass at which they quench and star formation ceases.
+While these simplifications describe the average properties of galaxies well \citep{Zahid2012, Childress2014}, they struggle to describe the more stochastic nature of galaxy evolution that occurs at the low and high mass ends: starbursts and quenching episodes, respectively.
+
+Low mass galaxies are highly sensitive to environmental effects and may often be found in the so-called starburst state with abnormally high (above the SFMS) levels of star formation that could drive environmental evolution \citep[e.g.][]{Vader1986,Marlowe1995,Tremonti2004,Lee2006}, although studies have shown that only 6 percent of dwarf galaxies are starbursts \citep{Lee2009}.
+It is possible that the averaging effects of the mass assembly model overestimate the true, instantaneous SFR for a significant fraction of the dwarf galaxies.
+Since the SN Ia rate is dominated by short delay times in these populations, an overestimated SFR in the model would lead to an overestimate in the SN Ia rate.
+
+At some point along the evolutionary pathway, galaxies begin to cease star formation due to a combination of processes that together are known as quenching.
+In our model of mass assembly the characteristic mass at which quenching occurs is described by Eq.
+\ref{eq:mq}, and the rate of the transition from star forming to passive (as a function of the stellar mass) is determined by the transition scale $sigma_{\mathrm{Q}}$ which we set to 1.1 based on GAMA observations.
+It is possible that this transition is too narrow and that quenching happens too fast in our model, leading to an under-prediction of the prompt fraction of SNe in the highest mass galaxies.
+To address this issue we rerun the mass assembly model with $sigma_{\mathrm{Q}} = 1.5$ as per the nominal analysis of \citet{Childress2014} and refit the SN Ia rate data.
+
+\subsubsection{Effects of stellar metallicity}
+
+One possible cause of the discrepant SN Ia rate at high stellar mass is the effect of stellar metallicity.
+Metallicity has been previously invoked to explain irregularities or divergences from the fiducial DTD \citep[e.g.][]{Strolger2010,Meng2011,Kistler2013}.
+Metallicity may affect the observed rate of SNe in two ways: firstly, it can affect the time taken for a star to evolve along the main sequence ($t_{\mathrm{MS}}$) -- Stellar metallicity has varying effects on the MS lifetime of stars \citep[e.g.][]{Georgy2007,Amard2020}, which is also dependent upon initial rotation and degree of mixing; secondly it can affect the time taken from WD formation to SN Ia explosion -- low metallicity stars should produce higher-mass WDs \citep[e.g.][]{Umeda1999,Marigo2007}, resulting in a higher SN Ia rate \citep{Kistler2013}.
+
+The mass-metallicity relation (MZR) is a strong observed correlation between galaxy stellar mass and gas-phase metallicity \citep[e.g.][]{Tremonti2004}, whereby higher mass galaxies have undergone more cycles of stellar evolution and have been polluted with heavy elements created in stars and released in SNe.
+Thus, the mass of a host galaxy is inextricably linked to the metallicity of its hot gas.
+However, the nature of the DTD complicates matters, since stars of different ages were formed at different epochs where the galaxy had a different stellar mass and thus different metallicity.
+Therefore, there is not a direct correlation between the metallicity of SN Ia progenitors and their observed host galaxy stellar mass.
+This caveat notwithstanding, it may be an expected consequence of the stipulations of e.g.
+\citet{Kistler2013} that the rate of SNe Ia is suppressed in the highest mass galaxies where the metallicity is highest, as is the case in our data.
+However, we would also expect to see this effect reversed at the low stellar mass end -- the rate should be enhanced in the lowest-mass, lowest-metallicity galaxies, yet instead we see a further suppression compared to the intermediate masses.
+Perhaps at low stellar mass, the effect of metallicity is negligible compared to the limitations of our SFH model.
 

### 2021-01-15 draft.tex
Updates from Overleaf

@@
     \includegraphics[width=.5\textwidth]{figs/mass_hist_sn_field_BC03.png}
-    \caption{Distribution of the stellar mass of the SN host and field galaxies used in the analysis. }
+    \caption{Upper: Distribution of the stellar mass of the SN host and field galaxies used in the analysis.
+Lower: As upper for field galaxies, but shown on a log scale.
+The distribution is well described by a Schechter function.}
     \label{fig:mass_hist_hosts_field}

### 2021-01-18 draft.tex

@@
 
-Given the vast range of timescales to which the DTD is sensitive, it is non-trivial to measure and various techniques have been developed to infer it indirectly.
+A power law DTD implies that most SNe Ia explode soon after star formation, but also that there is a non-neglible fraction that explode on the order of Gyrs after the star formation episode.
+The DTD is therefore non-trivial to measure and various techniques have been developed to infer it indirectly.
 One such approach is to measure global properties of SN Ia host galaxies.
@@
 proportional to instantaneous SFR) and "tardy" (i.e.
-proportional to overall stellar mass) SNe, respectively A complementary technique involves measuring the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008, Graur2018, Frohmaier2019}.
-This technique is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clusters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Graur2014,Maoz2014}.
-Conversely, it is also possible to estimate the SFH of an individual galaxy through the modelling of its stellar populations via spectral energy distribution (SED) fitting.
-Works such as \citet{Maoz2011}, \citet{Maoz2012}, \citet{Graur2013} estimated the DTD by measuring SFHs for a sample of field galaxies and comparing them to the number of SNe detected in each galaxy.
-and has led to results that suggest a DTD power law with $\beta$ consistent with $-1$ \citep[e.g.][]{Maoz2011,Graur2013}.
+proportional to overall stellar mass) SNe, respectively.
+
+A complementary technique involves measuring the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008, Graur2018, Frohmaier2019}.
+This technique (the volumetric rate method) is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clusters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Graur2014,Maoz2014}.
+These studies have, almost ubiquitously, found $\beta$ to be consistent with $-1$.
+
+It is also possible to estimate the SFH of an individual galaxy through the modelling of its stellar populations via spectral energy distribution (SED) fitting.
+Works such as \citet{Maoz2011}, \citet{Maoz2012} and \citet{Graur2013} estimated the DTD by measuring SFHs for a sample of field galaxies and comparing them to the number of SNe detected in each galaxy (the SFHR method), and have led to results that suggest a DTD power law with $\beta$ consistent with $-1$ \citep[e.g.][]{Maoz2011,Graur2013}.
 \citet{Childress2014} showed that the $A+B$ parameterisation arises as a direct consequence of the combination of a power-law DTD with the SFHs of galaxies.
+The recent advances of integral field spectroscopy (IFS) allows for an extension of the SFHR method, by reconstructing the SFH for hundreds or thousands of local regions of each SN Ia host galaxy.
+Using this method, \citet{Castrillo2020} find a power-law slope of $-1.1\pm0.3$, while \citet{Shen2021} find $-1.4\pm0.3$.
 
@@
 We introduce the SN host and field galaxy samples in Section \ref{sec:data} and describe our handling of incompleteness in Section \ref{sec:incompleteness}.
-We outline the modelling of star-formation histories in Section \ref{sec:method}, and present our results in Section \ref{sec:rates}.
-In Section \ref{sec:discussion} we discuss the robustness of the result and its meaning in a wider context, before concluding in Section \ref{sec:conclusion}.
+We present the SN Ia rate per galaxy in Section \ref{sec:rates}.
+We outline the modelling of star-formation histories and measurement of the DTD in Section \ref{sec:model} before concluding in Section \ref{sec:conclusion}.
 Where relevant, we assume a spatially flat $\Lambda$CDM cosmology with $\Omega_m = 0.3$ and $H_0 = 70 \mathrm{ km s}^{-1}\mathrm{Mpc}^{-1}$.
@@
 	\caption{Numbers of field galaxies and SN hosts passing various quality cuts.}
-	\label{tab:field_vuts}
+	\label{tab:cuts}
 	\begin{tabular}{lccr} % four columns, alignment for each
 		\hline
-		Cut & N (galaxies, X3)  & N (SN hosts)\\
+		Cut & N (field galaxies)  & N (SN hosts)\\
 		\hline
@@
 \section{Data}
+
+In order to measure the rate of SNe Ia per galaxy per year, we require a sample of SNe Ia and a sample of field galaxies that are normalised to the same selection criteria -- the final rate calculation must be corrected for differences in sky area, redshift depth, and survey time.
+In this section, we introduce our SN and field galaxy samples.
+
 \label{sec:data}
@@
 Transients were detected and processed using a difference imaging program \citep{Kessler2015} and vetted using a machine learning (ML) algorithm \citep{Goldstein2015}.
-Spectral follow-up was performed on a suite of large optical telescopes \citet{Smith2020b}, leading to the initial publication of a measurement of cosmological parameters using 207 spectroscopically confirmed SNe (\citealt{DESCollaboration2018a}, and references therein).
+Spectral follow-up was performed on a suite of large optical telescopes \citet{Smith2020a}, leading to the initial publication of a measurement of cosmological parameters using 207 spectroscopically confirmed SNe (\citealt{DESCollaboration2018a}, and references therein).
 \subsection{Supernovae \label{subsec:host_sample}}
@@
 With over 30,000 transients passing ML cuts it was not possible to obtain spectral follow up of every object.
-Instead we make use of photometric classification techniques, in particular the recurrent neural network \texttt{superNNova} (SNN; \citealt{Moller2019}).
+Instead we make use of photometric classification techniques, in particular the recurrent neural network classifier \texttt{superNNova} (SNN; \citealt{Moller2019}).
 We derive our SN Ia sample following the approach of \citet{Scolnic2020}, but use a threshold probability of $P(\mathrm{Ia})\geq0.5)$.
@@
 \subsection{Field galaxies\label{subsec:field_sample}}
-A sample of field galaxies is obtained from the same catalogue to which the SNe are matched to obtain host galaxies, and is presented in a companion paper \citet{Wiseman2021}.
+Along with a sample of SNe, we also require a sample of field galaxies in order to determine a per-galaxy rate.
+In order to maintain consistency between the SN host and field galaxy sample selections, we obtain a field galaxy sample from the same catalogue as that from which the SNe are matched to obtain host galaxies.
 The steps relevant to this analysis are outlined in the following sections.
@@
 
-Since the vast majority of objects in the \citet{Wiseman2021} catalogue do not have a spectroscopic redshift measurement, we rely on photometric redshifts (photo-$z$s) in order to proceed with the analysis.
+Since the vast majority of objects detected in the deep photometry do not have a spectroscopic redshift measurement, we rely on photometric redshifts (photo-$z$s) in order to proceed with the analysis.
 Photometric redshifts are taken, where available, from the catalogue of \citet{Hartley2020}, and have been estimated using the \texttt{EAZY} photometric redshift code \citep{Brammer2008}.
 These photo-$z$s make use of deep DES optical photometry alongside DECam $u$-band data and near-infrared (NIR) $J$, $H$, and $K$-band imaging from the ultraVISTA and VIDEO surveys.
+Photo-$z$ accuracy from \citet{Hartley2020} at $17 < i<24$, as quantified by the Normalised Absolute Median Deviation (NMAD) is estimated around 0.03.
+This accuracy is degraded to 0.07 at $17 < i<26$, a range that includes all galaxies in our sample, but is more than adequate for the purposes of this work, where all field galaxies will be grouped into stellar mass bins of 0.5 dex.
 
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/mass_hist_sn_field_BC03.png}
+    \includegraphics[width=.5\textwidth]{figs/mass_hist_linlog_sn_field_BC03.png}
     \caption{Upper: Distribution of the stellar mass of the SN host and field galaxies used in the analysis.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figs/mass_hist_log_BC03.png}
-    \caption{Distribution of the stellar mass of the field galaxies used in the analysis. The distribution is well described by a Schechter function.
-    \label{fig:log_mass_field}}
+    \includegraphics[width=0.5\textwidth]{figs/completeness_combined.png}
+    \caption{Measuring the completeness of the field galaxy sample.
+\textit{Upper}: the $T_{\mathrm{C}}$ statistic as a function of apparent magnitude; \textit{middle} as per \textit{upper}, but for $T_{\mathrm{V}}$; \textit{lower}: the combined, normalised completeness in each band.
+    \label{fig:completeness}}
 \end{figure}
@@
 We estimate global galaxy properties for both the SN host and field galaxy samples by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{Kelsey2020,Smith2020,Wiseman2020}.
-For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists (a minority of cases), or more commonly the photometrically derived value.
+For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists in the OzDES Global Redshift Catalog \citep{Lidman2020}, or more commonly the photometrically derived value.
+We use the stellar population templates of \citet{Bruzual2003} and adopt a \citet{Chabrier2003} initial mass function (IMF).
 The fitting procedure returns a best fitting template and corresponding stellar mass ($M_*$) and SFR averaged over the proceeding 250 Myr.
-Uncertainties on the properties are estimated by refitting the templates to the photometry that has been resampled from Gaussian PDFs formed by the photometric fluxes and their uncertainties.
+Upper and lower bounds on physical parameter estimates are taken as the largest and smallest values of a given parameter for which the reduced $\chi^2$ parameter corresponds to $\chi^2_{\mathrm{red, min}} +1$.
+%To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit.
+This procedure is repeated 1000 times.
 
@@
 
-In order to refine the sample of host and field galaxies for the rate analysis we perform a series of quality cuts.
-Firstly, we require that a galaxy must be detected and have a Kron magnitude measurement in all four DES optical bands.
-We also require that it is not within a given number of pixels of the CCD edge, as the co-addition of slightly misaligned images introduced a region of significant noise in this part of the detector.
-To remove high-probability stellar sources we apply a cut of 0.95 in the star/galaxy (S/G) separation \texttt{CLASS\_STAR} provided by \texttt{Source Extractor} \citep{Bertin1996}.
+In order to refine the sample of host and field galaxies for the rate analysis we perform a series of quality cuts:
 
+\begin{enumerate}
+    \item[i)] objects must be detected and have a Kron magnitude measurement in all four DES optical bands
+
+    \item[ii)] field galaxies are limited to unmasked region of the SN-X3 chip \cite{Hartley2020}
+
+    \item[iii)] objects must not be within a given number (20 in $x$, 50 in $y$) of pixels of the CCD edge, as the co-addition of slightly misaligned images introduced a region of significant noise in this part of the detector
+
+    \item[iv)] objects must have a value of 0.95 in the star/galaxy (S/G) separation \texttt{CLASS\_STAR} provided by \texttt{Source Extractor} \citep{Bertin1996}
+
+    \item[v)]  objects must be covered by $ugrizJHK$ photometry, but do not require detections in all bands
+
+    \item[vi)] objects must have a spectroscopic or photometric redshift measurement
+
+    \item[vii)] objects must be detected at signal-to-noise ratio (SNR) greater than 3 in the $r$ band
+
+    \item[viii)] galaxies must be brighter than $m_r \leq 24.5$
+
+    \item[ix)] galaxies must be within the redshift range $0.2 \leq z \leq 0.8$.
+\end{enumerate}
+
+The numbers of SN hosts and field galaxies passing these cuts are listed in Table \ref{tab:cuts}. The final samples comprise 1414 SN host galaxies and 48,177 field galaxies.
 %%%% INCOMPLETENESS %%%%
@@
 \label{sec:incompleteness}
-Although Eq.
-\ref{eq:rate1} serves as an approximation to the SN rate per galaxy per year, both the SN and field galaxy samples introduced in Sections \ref{subsec:host_sample} and \ref{subsec:field_sample} are affected by incompleteness, which is likely to be the dominant systematic effect in the analysis.
+The simple ratio of the number of SN hosts and field galaxies presented at the end of the previous section provides a first approximation of the SN rate per galaxy, and the addition of factor equal to the survey duration normalises the rate to per year.
+However both the SN and field galaxy samples introduced in Sections \ref{subsec:host_sample} and \ref{subsec:field_sample} are affected by incompleteness, which is likely to be the dominant systematic effect in the analysis.
 In this section we describe our method of correcting for various sources incompleteness in the data.

### 2021-01-18 draft.tex

@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figs/completeness_combined.png}
-    \caption{Measuring the completeness of the field galaxy sample.
-\textit{Upper}: the $T_{\mathrm{C}}$ statistic as a function of apparent magnitude; \textit{middle} as per \textit{upper}, but for $T_{\mathrm{V}}$; \textit{lower}: the combined, normalised completeness in each band.
-    \label{fig:completeness}}
+    \includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.png}
+    \caption{SN detection efficiencies split up by DES field.
+The $y-$axis represents the fraction of simulated SNe in a given redshift bin that would have been detected by DES-SN and passed light curve quality cuts.
+    \label{fig:SN_efficiency}}
 \end{figure}
@@
 
-    \item[v)]  objects must be covered by $ugrizJHK$ photometry, but do not require detections in all bands
+    \item[v)]  objects must be covered by $ugrizJHK$ photometry with either detections or upper limits
 
@@
 
-    \item[viii)] galaxies must be brighter than $m_r \leq 24.5$
+    \item[viii)] galaxies must be brighter than $m_r \leq 24.5$, as this is the magnitude of the faintest SN host with a spectroscopic redshift.
 

### 2021-01-18 draft.tex

@@
 The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citetalias{V20} who provide the spectroscopic redshift efficiency as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey.
-So that we reduce any bias towards SNe in bright hosts that are easier to obtain spectroscopic redshifts for, we assign each SN in the sample described in Section \ref{subsec:host_sample} a weight equal to the inverse of the spectroscopic efficiency for its host.
+So that we reduce any bias towards SNe in bright hosts that are eCastrillo to obtain spectroscopic redshifts for, we assign each SN in the sample described in Section \ref{subsec:host_sample} a weight equal to the inverse of the spectroscopic efficiency for its host.
 This is equivalent to assuming that an efficiency of 0.1 means that for every ten SNe with hosts at that magnitude, only 1 will make it into the sample.
@@
 In many works this ``prompt time" $t_{\mathrm{p}}$ is fixed to some value expected to be the minimum time for a star to evolve off the MS and become a WD, such as 40~Myr \citep{Maoz2012,Graur2014,Graur2018}.
-Other studies have left $t_{\mathrm{p}}$ as a free parameter \citep{Heringer2019,Asier2020}.
+Other studies have left $t_{\mathrm{p}}$ as a free parameter \citep{Heringer2019,Castrillo2020}.
 We perform two fits: one with $t_{\mathrm{p}}$ fixed at 40 Myr, and one with it as a free parameter.
@@
 In most cases, $t_{\mathrm{p}}$ has been fixed at some fiducial value such as 40~Myr, which is derived from the lifetime of 8~M$_{\odot}$ stars.
-\citet{Asier2020} included $t_{\mathrm{p}}$ (which they denote $\Delta$) in their fit, and find a value of $50_{-35}^{+100}$~Myr which is consistent with both 40~Myr as well as our best fitting value of $90 \pm 50$~Myr.
+\citet{Castrillo2020} included $t_{\mathrm{p}}$ (which they denote $\Delta$) in their fit, and find a value of $50_{-35}^{+100}$~Myr which is consistent with both 40~Myr as well as our best fitting value of $90 \pm 50$~Myr.
 \citet{Heringer2019} also present fits with varying prompt times, although they don't fit for the parameter itself.
@@
 
-Low mass galaxies are highly sensitive to environmental effects and may often be found in the so-called starburst state with abnormally high (above the SFMS) levels of star formation that could drive environmental evolution \citep[e.g.][]{Vader1986,Marlowe1995,Tremonti2004,Lee2006}, although studies have shown that only 6 percent of dwarf galaxies are starbursts \citep{Lee2009}.
+Low mass galaxies are highly sensitive to environmental effects and may often be found in the so-called starburst state with abnormally high (above the SFMS) levels of star formation that could drive environmental evolution \citep[e.g.][]{Dekel1986,Marlowe1995,Tremonti2004,Lee2006}, although studies have shown that only 6 percent of dwarf galaxies are starbursts \citep{Lee2009}.
 It is possible that the averaging effects of the mass assembly model overestimate the true, instantaneous SFR for a significant fraction of the dwarf galaxies.
@@
 Metallicity has been previously invoked to explain irregularities or divergences from the fiducial DTD \citep[e.g.][]{Strolger2010,Meng2011,Kistler2013}.
-Metallicity may affect the observed rate of SNe in two ways: firstly, it can affect the time taken for a star to evolve along the main sequence ($t_{\mathrm{MS}}$) -- Stellar metallicity has varying effects on the MS lifetime of stars \citep[e.g.][]{Georgy2007,Amard2020}, which is also dependent upon initial rotation and degree of mixing; secondly it can affect the time taken from WD formation to SN Ia explosion -- low metallicity stars should produce higher-mass WDs \citep[e.g.][]{Umeda1999,Marigo2007}, resulting in a higher SN Ia rate \citep{Kistler2013}.
+Metallicity may affect the observed rate of SNe in two ways: firstly, it can affect the time taken for a star to evolve along the main sequence ($t_{\mathrm{MS}}$) -- Stellar metallicity has varying effects on the MS lifetime of stars \citep[e.g.][]{Georgy2013,Amard2020}, which is also dependent upon initial rotation and degree of mixing; secondly it can affect the time taken from WD formation to SN Ia explosion -- low metallicity stars should produce higher-mass WDs \citep[e.g.][]{Umeda1999,Marigo2007}, resulting in a higher SN Ia rate \citep{Kistler2013}.
 

### 2021-01-18 draft.tex
Updates from Overleaf

@@
 The majority of SN host spectroscopic redshifts in DES are provided by the dedicated follow-up survey OzDES, for which the limiting magnitude is around 24 to 24.5 mag in the $r$ band.
-The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citetalias{V20} who provide the spectroscopic redshift efficiency as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey.
+The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citet{Vincenzi2020} who provide the spectroscopic redshift efficiency as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey.
 So that we reduce any bias towards SNe in bright hosts that are eCastrillo to obtain spectroscopic redshifts for, we assign each SN in the sample described in Section \ref{subsec:host_sample} a weight equal to the inverse of the spectroscopic efficiency for its host.

### 2021-01-19 draft.tex

@@
 	    SNR $\geq 3$& 338256  & 1678 \\
-	    $m_r \leq 26.5$ & 196109 &  1678 \\
+	    $m_r \leq 24.5$ & 196109 &  1678 \\
 	    $0.2 \leq z \leq 0.8$ & 48177 & 1414\\
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figs/field_vmax.png}
+    \caption{Distribution of $V_{\mathrm{max}}$ corrections applied to field galaxies in the DES sample.
+The majority of galaxies have no correction, and the distribution of the 1\% that do follows a power-law.
+    \label{fig:vmax_field}}
+\end{figure}
 \subsection{Galaxy properties \label{subsec:properties}}
@@
 
-The distribution of efficiency as a function of redshift is shown in Figure \ref{fig:efficiencies}.
+The distribution of efficiency as a function of redshift is shown in Figure \ref{fig:SN_efficiency}.
 It is evident that the deep fields (X3, C3) are sensitive to SNe at higher redshifts, while there is no drastic shifts between efficiencies in the eight shallow fields.
@@
 To correct for incompleteness caused by the magnitude limited nature of the survey we follow the prescription of e.g.
-\citet{Sullivan2006, Smith2012} by using a $V_{\mathrm{max}}$ method of \citet{Schmid1968}.
+\citet{Sullivan2006, Smith2012} by using a $V_{\mathrm{max}}$ method of \citet{Schmidt1968}.
 For each galaxy in the sample we calculate the maximum volume within which it would have been observed given its absolute magnitude and $k-$correction.
@@
 In our case this corresponds to the volume at $z=0.8$.
-Figs.
-\ref{fig:vmax_gals} and \ref{fig:vmax_hist} show the distribution of the correction among galaxies in the sample.
+Fig \ref{fig:vmax_field} shows the distribution of the correction among galaxies in the sample.
 The vast majority of galaxies require no correction, meaning they would have been observed beyond the maximum volume considered.
 Roughly 1\% of objects have a correction greater than 1, with the distribution well described by a power-law function.
-In Section \ref{sec:rates} we split the samples into redshift bins in order to measure cosmic evolution of the SN Ia rate.
+%In Section \ref{sec:rates} we split the samples into redshift bins in order to measure cosmic evolution of the SN Ia rate.
 For each redshift bin, we reevaluate the value of $V_{\mathrm{survey}}$ used in the incompleteness correction to be the volume of the bin.
@@
 In particular, there appear to be two locations of interest: firstly, the slope is steeper at masses lower than $10^9$ M$_{\odot}$; secondly there is an apparent flattening and possibly a turnover at masses around and above $10^{11}$ M$_{\odot}$.
-The most likely cause of these divergences is because the SN rate is driven by the SFH which is not a linear function of stellar mass (see Section \ref{sec:method}).
+The most likely cause of these divergences is because the SN rate is driven by the SFH which is not a linear function of stellar mass (see Section \ref{sec:model}).
 Second order effects may also be important, and we address these in the following sections.

### 2021-01-19 draft.tex

@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/beta_A_corner.png}
+    \includegraphics[width=.5\textwidth]{figs/beta_A_Qerf1.1_corner.png}
     \caption{Posterior distributions for DTD slope $\beta$ and normalisation $A$.
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm.png}
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1.png}
     \caption{Rate per galaxy of SNe Ia as a function of stellar mass (green points) along with the prediction from the best fitting DTD parameters $\beta$, $A$, and $t_{\mathrm{p}}$ forward modelled through Eq.
@@
 The relationship between SN Ia rate and galaxy stellar mass is well described by a linear function in log space, which corresponds to a power law.
-To find the slope and intercept that best describe the data we employ Hamiltonian Monte-Carlo (HMC), which we implement via the \texttt{pystan} package and describe in full detail in Appendix \ref{appendix:linear_fits}.
+To find the slope and intercept that best describe the data we use Bayesian inference.
+To sample the posterior we use the enhanced no-U-turn Sampler (NUTS) algorithm \citep{Betancourt2017}, which is a variant of Hamiltonian Monte-Carlo (HMC), implemented in the Stan programming language \citep{Carpenter2017} and describe in full detail in Appendix \ref{appendix:linear_fits}.
 We measure a slope of $0.70\pm0.02$, which is broadly consistent with the values found in SNLS and SDSS by \citet{Sullivan2006} and \citet{Smith2012} respectively.
@@
 		\hline
-		Fixed $t_{\mathrm{p}}$ & $-1.03\pm 0.06$ &  $1.7 \pm 0.05$ & -\\
+		Fixed $t_{\mathrm{p}}$ & $-0.96\pm 0.05$ &  $1.7 \pm 0.05$ & -\\
 		Free $t_{\mathrm{p}}$ & $-0.99 \pm 0.09$ & $2.1 \pm 0.2$ & $0.09 \pm 0.05$\\
@@
 \ref{eq:dtd}), normalisation $A$ and effective after prompt time $t_{\mathrm{p}}$.
-As per Section \ref{subsec:rates_mass}, we constrain the parameters via Bayesian inference, using HMC.
+As per Section \ref{sec:rates}, we constrain the parameters via Bayesian inference, using HMC.
 At each step of the sampling procedure the model is re-calculated via Eq.
@@
 
+\section{Changes to the nominal SFH model}
+
+In Section \ref{sec:model} we describe our toy model of galaxy SFHs based on the work of \citet{Childress2014}. Here we
+
+\label{appendix:linear_fits}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-19 draft.tex
Updates from Overleaf

@@
 To find the slope and intercept that best describe the data we use Bayesian inference.
-To sample the posterior we use the enhanced no-U-turn Sampler (NUTS) algorithm \citep{Betancourt2017}, which is a variant of Hamiltonian Monte-Carlo (HMC), implemented in the Stan programming language \citep{Carpenter2017} and describe in full detail in Appendix \ref{appendix:linear_fits}.
+To sample the posterior we use the enhanced no-U-turn Sampler (NUTS) algorithm \citep{Betancourt2017}, which is a variant of Hamiltonian Monte-Carlo (HMC), implemented in the Stan programming language \citep{Carpenter2017} and we describe in full detail in Appendix \ref{appendix:linear_fits}.
 We measure a slope of $0.70\pm0.02$, which is broadly consistent with the values found in SNLS and SDSS by \citet{Sullivan2006} and \citet{Smith2012} respectively.

### 2021-01-19 draft.tex
Updates from Overleaf

--- 2021-01-19 draft.tex
@@
 To find the slope and intercept that best describe the data we use Bayesian inference.
-To sample the posterior we use the enhanced no-U-turn Sampler (NUTS) algorithm \citep{Betancourt2017}, which is a variant of Hamiltonian Monte-Carlo (HMC), implemented in the Stan programming language \citep{Carpenter2017} and describe in full detail in Appendix \ref{appendix:linear_fits}.
+To sample the posterior we use the enhanced no-U-turn Sampler (NUTS) algorithm \citep{Betancourt2017}, which is a variant of Hamiltonian Monte-Carlo (HMC), implemented in the Stan programming language \citep{Carpenter2017}.
+We describe the fitting procedure in full detail in Appendix \ref{appendix:linear_fits}.
 We measure a slope of $0.70\pm0.02$, which is broadly consistent with the values found in SNLS and SDSS by \citet{Sullivan2006} and \citet{Smith2012} respectively.
@@
 \begin{equation}
-    R_{\mathrm{G}} = dR/dM_* M_* + c \,,
+    R_{\mathrm{G}} = \frac{\mathrm{d}R}{\mathrm{d}M_*} M_* + c \,,
 \label{eq:rate_fit}
@@
 We fit the model assuming a normal likelihood, such that the observed rate in each stellar mass bin is itself modelled as a Gaussian distribution described by the mean and standard deviation of the data in that bin.
+We adopt weakly informative normal priors on the slope and intercept: $p\left(\frac{\mathrm{d}R}{\mathrm{d}M_*}\right) \sim \mathcal{N}\left(0,5\right)$ and  $p\left(c\right) \sim \mathcal{N}\left(-12,5\right)$ respectively.
+We sample using 4 chains, each with 2000 warm up and 2000 sampling iterations.
+We report parameter estimates based on the mean and standard deviation of their posterior samples.
+
+The joint posterior distribution for the slope and intercept are shown in Fig.
+\ref{fig:corner_slope_int}.
+The two parameters are highly degenerate, yet well constrained.
+This degeneracy manifests as the spread of potential linear fits as drawn in light blue on Fig.
+\ref{fig:rate_fitted}.
 
 \section{Changes to the nominal SFH model}
-
+\label{appendix:model_adjustments}
 In Section \ref{sec:model} we describe our toy model of galaxy SFHs based on the work of \citet{Childress2014}. Here we
 
-\label{appendix:linear_fits}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-19 draft.tex
Updates from Overleaf

@@
 
-\section{Linear fits using Hamiltonian Monte Carlo}
+\section{Linear fits using Bayesian inference}
 In this section we describe the procedures used to fit slopes and intercepts to the relationships measured in the analysis.
@@
 \label{appendix:linear_fits}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figs/fit_fine_BC03_corner.png}
+    \caption{Joint posterior distribution for the slope and intercept of the linear fit to the SN rate per galaxy per year as a function of stellar mass (Section \ref{sec:rates}; Fig.
+\ref{fig:rate_fitted}).}
+    \label{fig:corner_slope_int}
+\end{figure}
 We model the relation with the linear relationship: 

### 2021-01-19 draft.tex

@@
     \includegraphics[width=.5\textwidth]{figs/mass_hist_linlog_sn_field_BC03.png}
-    \caption{Upper: Distribution of the stellar mass of the SN host and field galaxies used in the analysis.
+    \caption{Upper: Distribution of the stellar mass of the SN host (green dot-dashed) and field galaxies (orange solid) used in the analysis.
 Lower: As upper for field galaxies, but shown on a log scale.
-The distribution is well described by a Schechter function.}
+The distribution closely matches data from the ZFOURGE survey at $0.2<z<0.5$ (cyan dashes) and $0.5<z<0.75$ (magenta dots).}
     \label{fig:mass_hist_hosts_field}
@@
 \end{figure}
-\subsection{Galaxy properties \label{subsec:properties}}
-
-We estimate global galaxy properties for both the SN host and field galaxy samples by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{Kelsey2020,Smith2020,Wiseman2020}.
-For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists in the OzDES Global Redshift Catalog \citep{Lidman2020}, or more commonly the photometrically derived value.
-We use the stellar population templates of \citet{Bruzual2003} and adopt a \citet{Chabrier2003} initial mass function (IMF).
-The fitting procedure returns a best fitting template and corresponding stellar mass ($M_*$) and SFR averaged over the proceeding 250 Myr.
-Upper and lower bounds on physical parameter estimates are taken as the largest and smallest values of a given parameter for which the reduced $\chi^2$ parameter corresponds to $\chi^2_{\mathrm{red, min}} +1$.
-%To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit.
-This procedure is repeated 1000 times.
 
@@
 The numbers of SN hosts and field galaxies passing these cuts are listed in Table \ref{tab:cuts}. The final samples comprise 1414 SN host galaxies and 48,177 field galaxies.
+
+\subsection{Galaxy properties \label{subsec:properties}}
+
+We estimate global galaxy properties for both the SN host and field galaxies that pass the quality cuts by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{Kelsey2020,Smith2020,Wiseman2020}.
+For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists in the OzDES Global Redshift Catalog \citep{Lidman2020}, or more commonly the photometrically derived value.
+We use the stellar population templates of \citet{Bruzual2003} and adopt a \citet{Chabrier2003} initial mass function (IMF).
+The fitting procedure returns a best fitting template and corresponding stellar mass ($M_*$).
+Upper and lower bounds on stellar mass estimates are taken as the largest and smallest values of a given parameter for which the reduced $\chi^2$ parameter corresponds to $\chi^2_{\mathrm{red, min}} +1$.
+
+The results of our SED fitting are shown in Fig.
+\ref{fig:mass_hist_hosts_field}.
+The upper panel, with both the SN hosts and field galaxies displayed, shows the vastly different distributions of the two samples.
+SN hosts are preferentially high mass galaxies, whereas the field galaxy distributions increases down to lower masses, peaking around $10^{8.5}~\mathrm{M}_{\odot}$.
+In the bottom panel, the same field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass functions (SMFs) from the ZFOURGE survey \citep{Tomczak2014} that best represent the redshift range of the DES field galaxies.
+Above $10^{8.5}~\mathrm{M}_{\odot}$, the DES field galaxy distribution closely follows the ZFOURGE SMFs, particularly that from $0.5<z<0.75$, indicating that the DES sample is representative of field galaxies in this redshift range.%To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit.
+This procedure is repeated 1000 times.
 %%%% INCOMPLETENESS %%%%
@@
 The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citet{Vincenzi2020} who provide the spectroscopic redshift efficiency as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey.
-So that we reduce any bias towards SNe in bright hosts that are eCastrillo to obtain spectroscopic redshifts for, we assign each SN in the sample described in Section \ref{subsec:host_sample} a weight equal to the inverse of the spectroscopic efficiency for its host.
+So that we reduce any bias towards SNe in bright hosts that are easier to obtain spectroscopic redshifts for, we assign each SN in the sample described in Section \ref{subsec:host_sample} a weight equal to the inverse of the spectroscopic efficiency for its host.
 This is equivalent to assuming that an efficiency of 0.1 means that for every ten SNe with hosts at that magnitude, only 1 will make it into the sample.

### 2021-01-20 draft.tex

@@
 
+\subsection{Rate per unit stellar mass \label{subsec:snum}}
+\textbf{short section showing SNUM and how it matches past results}
+
 \section{Modelling the per-galaxy rate of type Ia supernovae}
@@
 
+\textbf{Add plot showing that the toy model recreates the stellar mass function?}
+
 %\textbf{TEMPTED TO DITCH THIS SINCE OUR SFR IS SKETCHY}
@@
 
+\textbf{Or's suggestion: Fix beta, A and fit for tp}
+
 \subsection{Comparison to previous DTD measurements \label{subsec:compare_dtd}}
@@
 In our model of mass assembly the characteristic mass at which quenching occurs is described by Eq.
-\ref{eq:mq}, and the rate of the transition from star forming to passive (as a function of the stellar mass) is determined by the transition scale $sigma_{\mathrm{Q}}$ which we set to 1.1 based on GAMA observations.
+\ref{eq:mq}, and the rate of the transition from star forming to passive (as a function of the stellar mass) is determined by the transition scale $\sigma_{\mathrm{Q}}$ which we set to 1.1 based on GAMA observations.
 It is possible that this transition is too narrow and that quenching happens too fast in our model, leading to an under-prediction of the prompt fraction of SNe in the highest mass galaxies.
-To address this issue we rerun the mass assembly model with $sigma_{\mathrm{Q}} = 1.5$ as per the nominal analysis of \citet{Childress2014} and refit the SN Ia rate data.
+To address this issue we rerun the mass assembly model with $\sigma_{\mathrm{Q}} = 1.5$ as per the nominal analysis of \citet{Childress2014} and refit the SN Ia rate data.
 
@@
 the final conclusions which the authors draw from their work.
+
+\section*{Software}
+
+All software used in this publication is publicly available.
+In particular, we made extensive use of \texttt{numpy} \citep{Harris2020}, \texttt{Astropy} \citep{Price-Whelan2018}, \texttt{matplotlib} \citep{Hunter2007}, \texttt{SciPy} \citep{Virtanen2020}, \texttt{pandas} \citep{Mckinney2010}, \texttt{Stan} \citep{Carpenter2017}, \texttt{seaborn}, and \texttt{arviz} \citep{Kumar2019}.
 

### 2021-01-20 draft.tex

@@
 All software used in this publication is publicly available.
-In particular, we made extensive use of \texttt{numpy} \citep{Harris2020}, \texttt{Astropy} \citep{Price-Whelan2018}, \texttt{matplotlib} \citep{Hunter2007}, \texttt{SciPy} \citep{Virtanen2020}, \texttt{pandas} \citep{Mckinney2010}, \texttt{Stan} \citep{Carpenter2017}, \texttt{seaborn}, and \texttt{arviz} \citep{Kumar2019}.
+In particular, we made extensive use of \texttt{numpy} \citep{Harris2020}, \texttt{Astropy} \citep{AstropyCollaboration2013,AstropyCollaboration2018}, \texttt{matplotlib} \citep{Hunter2007}, \texttt{SciPy} \citep{Virtanen2020}, \texttt{pandas} \citep{Mckinney2010}, \texttt{Stan} \citep{Carpenter2017}, \texttt{seaborn} \citep{Waskom2020}, and \texttt{arviz} \citep{Kumar2019}.
 

### 2021-01-22 draft.tex
Updates from Overleaf

@@
 \begin{abstract}
-This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.
+Measuring the rate of type Ia supernovae (SNe Ia) is crucial method by which to understand the progenitors and physical processes involved in these explosions.
+Since SNe Ia are a key source of heavy elements, the SN Ia rate is also an important ingredient in models of galaxy evolution.
+We use a sample of 1411 photometrically classified SNe discovered by the Dark Energy Survey (DES) along with \textbf{final number} field galaxies to calculate the rate of SNe Ia per galaxy as a function of galaxy stellar mass across a broad range of scales $8.5 \leq \log(M_*/\mathrm{M}_{\odot}) \leq 11.25$.
+We find that the SN Ia rate increases with stellar mass with a slope of $0.70 \pm 0.02$, which is consistent with previous work.
+We use an empirical model of stellar mass assembly to estimate the average star-formation histories (SFHs) of galaxies across the stellar mass range of our measurement.
+We combine the modelled SFHs with the SN Ia rates to estimate constraints on the SN Ia delay time distribution (DTD), and find a power-law with index $\beta = -0.96 \pm 0.5$ and normalisation $A = 1.7 \pm0.05 \times 10^{-13}~\mathrm{SNe}~{\mathrm{M}_{\odot}}^{-1}~\mathrm{yr}^{-1}$.
 \end{abstract}
@@
     \includegraphics[width=\textwidth]{figs/SFHs_colour.png}
-    \caption{The stellar mass assembly of the Universe as prescribed by the toy model of \citet{Childress2014}}
+    \caption{The stellar mass assembly of the Universe as prescribed by the toy model of \citet{Childress2014}.
+Galaxies with high stellar mass at $z=0$ formed the majority of their stars in the distant past, while lower-mass galaxies are still actively star forming in the present day.}
     \label{fig:SFHs}
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/beta_A_tp_corner.png}
+    \includegraphics[width=.5\textwidth]{figs/beta_A_tp_Qerf1.1_corner.png}
     \caption{Posterior distributions for DTD parameters $\beta$, $A$, and $t_{\mathrm{p}}$.
-%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+\textbf{This needs updating once final chains are run.
+Axes labels need sorting.} %The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
     \label{fig:corner_beta_norm_tp}}
@@
 		Free $t_{\mathrm{p}}$ & $-0.99 \pm 0.09$ & $2.1 \pm 0.2$ & $0.09 \pm 0.05$\\
+		Fixed $A$, $\beta$ & - & - & \textbf{add}\\
 		\hline
@@
 
-\subsection{Constraining the SN Ia delay time distribution}
+\subsection{Constraints on the SN Ia delay time distribution}
 \label{subsec:results_dtd}
@@
 \subsubsection{The DTD power law index \label{subsubsec:compare_beta}}
-The index of the DTD power law measured here is consistent with the majority of previous analyses using various methods.
+We measure a DTD power law index of $-0.96\pm0.05$.
+This value is consistent with the majority of previous analyses using various methods.
 Our measurement provides an independent support to the values close to $-1$ found using volumetric rates \citep[e.g.][]{Graur2018,Frohmaier2019}, individual galaxy SFHs \citep[e.g.][]{Maoz2012,Graur2013}, and galaxy clusters \citep[e.g.][]{Maoz2010} although our slope is marginally inconsistent with that of \citet{Heringer2019}.
@@
 \subsubsection{The DTD normalisation \label{subsubsec:compare_A}}
-The normalisation of the DTD is less frequently reported.
+We measure a DTD normalisation (i.e.
+the rate of SNe 1 Gyr after star-formation) of $1.70 \pm 0.05 \times 10^{-13}$~M$_{\odot}^{-1}$~yr$^{-1}$.
 \citet{Graur2013} found a value of $7 \times 10^{-14}$~M$_{\odot}^{-1}$~yr$^{-1}$ using the SFH technique, whereas \citet{Heringer2019} report $7 \times 10^{-13}$~M$_{\odot}^{-1}$~yr$^{-1}$.
@@
 \citet{Heringer2019} note that the normalisation recovered from the SFHR method is sensitive to the assumed prompt time $t_{\mathrm{p}}$ (see Section \ref{subsubsec:compare_tp}, which we also find using our method.
+
+By integrating the normalised DTD over cosmic time, we obtain an estimate of the average SN Ia efficiency $N_{\mathrm{Ia}}/M_*$ which represents the number of SNe Ia formed per unit mass of stars formed.
+We measure $N_{\mathrm{Ia}}/M_* = 2.0~_{-1.6}^{+5.0} \times 10^{-3}~\mathrm{SNe}~\mathrm{M}_{\odot}^{-1}$.
 

### 2021-01-27 draft.tex
Updates from Overleaf

@@
 We derive our SN Ia sample following the approach of \citet{Scolnic2020}, but use a threshold probability of $P(\mathrm{Ia})\geq0.5)$.
-The photometricially classified SNe Ia are then passed through the \texttt{SALT2} framework \citep{Betoule2014} and are subject to quality cuts on the light curve width (stretch; $x_1$) and colour ($c$) parameters: $-3 \leq x_1 \leq 3$, $-0.3 \leq c \leq 0.3$.
-These cuts help to reduce the potential contamination from core-collapse SNe (CCSNe) and outlying SNe Ia whose physical mechanisms may diverge from the general cosmologically useful population.
+The photometricially classified SNe Ia are then passed through the \texttt{SALT2} framework \citep{Betoule2014} and are subject to quality cuts on the light curve width (stretch; $x_1$) and colour ($c$) parameters in an identical manner to \citet{Vincenzi2020}: $-3 \leq x_1 \leq 3$, $-0.3 \leq c \leq 0.3$.
+These cuts help to reduce the potential contamination from core-collapse SNe (CCSNe) and outlying thermonuclear SNe.
+We impose further cuts on the quality of those measured parameters, which are: the uncertainty on $x_1$: $\sigma_{x_1} <1$; the uncertainty on the date at which the light curve peaked: $\sigma_{t_{\mathrm{peak}}} <2$; the SALT2 fit probability $>0.001$.
+% whose physical mechanisms may diverge from the general cosmologically useful population.
 
@@
 
-The numbers of SN hosts and field galaxies passing these cuts are listed in Table \ref{tab:cuts}. The final samples comprise 1414 SN host galaxies and 48,177 field galaxies.
+The numbers of SN hosts and field galaxies passing these cuts are listed in Table \ref{tab:cuts}. The final samples comprise 1204 SN host galaxies and 48,177 field galaxies.
 
@@
 Roughly 1\% of objects have a correction greater than 1, with the distribution well described by a power-law function.
+
 %In Section \ref{sec:rates} we split the samples into redshift bins in order to measure cosmic evolution of the SN Ia rate.
@@
     \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_all.png}
-    \caption{The rate per galaxy of SNe Ia as a function of stellar mass.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \caption{The rate per galaxy of SNe Ia as a function of stellar mass.
+Horizontal error bars represent the width of the stellar mass bins.
+Vertical error bars are estimated via a Monte-Carlo resampling of the rate given the uncertainties in stellar mass.
+The linear fit is based on all but the lowest and highest mass bins, and takes into account uncertainties in the rate.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
     \label{fig:rate_raw}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/SNuM.png}
+    \caption{SN Ia rate per unit stellar mass as function of galaxy stellar mass.
+Error bars are the same as Fig.
+\ref{fig:rate_raw}.
+SDSS data (orange squares) are taken from \citet{Graur2013}.
+The systematically higher SNuM in DES is likely caused by the higher redshift of the sample.
+}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \label{fig:snum}
 \end{figure}
@@
 We note that the moderately star-forming slope is thus consistent between DES and SNLS, but the slopes of passive and highly star-forming galaxies are swapped.
-
+\renewcommand{\arraystretch}{1.2}
 \begin{table}
 	\centering
-	\caption{This is an example table. Captions appear above each table.
-	Remember to define the quantities, symbols and units used.}
+	\caption{Results of the Bayesian parameter estimation for the SN Ia DTD.}
 	\label{tab:dtd_results}
@@
 		\hline
-		Fixed $t_{\mathrm{p}}$ & $-0.96\pm 0.05$ &  $1.7 \pm 0.05$ & -\\
-		Free $t_{\mathrm{p}}$ & $-0.99 \pm 0.09$ & $2.1 \pm 0.2$ & $0.09 \pm 0.05$\\
-		Fixed $A$, $\beta$ & - & - & \textbf{add}\\
+		Fixed $t_{\mathrm{p}}$ & $-0.97_{-0.05}^{+0.05}$ &  $1.73_{-0.05}^{+0.05}$ & -\\
+		Free $t_{\mathrm{p}}$ & $-1.02 _{-0.11} ^{+0.08}$ & $1.86 _{-0.13} ^{+0.19}$ & $0.067 _{-0.023} ^{+0.043}$\\
+		Fixed $A$, $\beta$ & - & - & $0.047_{-0.007}^{+0.008}$\\
 		\hline

### 2021-01-29 draft.tex
Updates from Overleaf

@@
 The recent advances of integral field spectroscopy (IFS) allows for an extension of the SFHR method, by reconstructing the SFH for hundreds or thousands of local regions of each SN Ia host galaxy.
-Using this method, \citet{Castrillo2020} find a power-law slope of $-1.1\pm0.3$, while \citet{Shen2021} find $-1.4\pm0.3$.
+Using this method, \citet{Castrillo2020} find a power-law slope of $-1.1\pm0.3$, while \citet{Chen2021} find $-1.4\pm0.3$.
 
@@
 The $y-$axis represents the fraction of simulated SNe in a given redshift bin that would have been detected by DES-SN and passed light curve quality cuts.
+The curves are capped at efficiencies around 0.5 because DES is restricted to $\sim6$ month observing seasons each calendar year.
     \label{fig:SN_efficiency}}
@@
 
-The numbers of SN hosts and field galaxies passing these cuts are listed in Table \ref{tab:cuts}. The final samples comprise 1204 SN host galaxies and 48,177 field galaxies.
+The numbers of SN hosts and field galaxies passing these cuts are listed in Table \ref{tab:cuts}.
+The final samples comprise 1204 SN host galaxies and 48,177 field galaxies.
+The volume-weighted mean redshifts are 0.65 and 0.63 for SNe and field galaxies, respectively.
 
@@
 SN hosts are preferentially high mass galaxies, whereas the field galaxy distributions increases down to lower masses, peaking around $10^{8.5}~\mathrm{M}_{\odot}$.
-In the bottom panel, the same field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass functions (SMFs) from the ZFOURGE survey \citep{Tomczak2014} that best represent the redshift range of the DES field galaxies.
-Above $10^{8.5}~\mathrm{M}_{\odot}$, the DES field galaxy distribution closely follows the ZFOURGE SMFs, particularly that from $0.5<z<0.75$, indicating that the DES sample is representative of field galaxies in this redshift range.%To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit.
+In the bottom panel, the same field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass function (SMF) from the ZFOURGE survey \citep{Tomczak2014} that best represents the redshift range of the DES field galaxies.
+Above $10^{8.5}~\mathrm{M}_{\odot}$, the DES field galaxy distribution closely follows the ZFOURGE SMF for $0.5<z<0.75$, indicating that the DES sample is representative of field galaxies in this redshift range.%To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit.
 This procedure is repeated 1000 times.
@@
 To correct for incompleteness caused by the magnitude limited nature of the survey we follow the prescription of e.g.
-\citet{Sullivan2006, Smith2012} by using a $V_{\mathrm{max}}$ method of \citet{Schmidt1968}.
+\citet{Sullivan2006, Smith2012} by using a $V_{\mathrm{max}}$ method based on \citet{Schmidt1968}.
 For each galaxy in the sample we calculate the maximum volume within which it would have been observed given its absolute magnitude and $k-$correction.

### 2021-02-05 draft.tex

@@
 % Keep the title short and informative.
-\title[Rates of SNe Ia in DES]{Measuring the Type Ia supernova delay time distribution via host galaxy rates in the Dark Energy Survey}
+\title[Rates of SNe Ia in DES]{Rates and delay times of type Ia supernovae in the Dark Energy Survey}
 
@@
 \begin{abstract}
-Measuring the rate of type Ia supernovae (SNe Ia) is crucial method by which to understand the progenitors and physical processes involved in these explosions.
-Since SNe Ia are a key source of heavy elements, the SN Ia rate is also an important ingredient in models of galaxy evolution.
-We use a sample of 1411 photometrically classified SNe discovered by the Dark Energy Survey (DES) along with \textbf{final number} field galaxies to calculate the rate of SNe Ia per galaxy as a function of galaxy stellar mass across a broad range of scales $8.5 \leq \log(M_*/\mathrm{M}_{\odot}) \leq 11.25$.
-We find that the SN Ia rate increases with stellar mass with a slope of $0.70 \pm 0.02$, which is consistent with previous work.
+We use a sample of 881 photometrically classified SNe discovered by the Dark Energy Survey (DES) in the redshift range $0.2 < z <0.6$, along with 40415 field galaxies to calculate the rate of type Ia supernovae (SNe Ia) per galaxy.
+We recover the established positive trend of SN Ia rate as a function of galaxy stellar mass across a broad range of scales $8.5 \leq \log(M_*/\mathrm{M}_{\odot}) \leq 11.25$.
+We find that the SN Ia rate increases with stellar mass roughly linearly in log space, with a slope of $0.63 \pm 0.02$, which is consistent with previous work.
 We use an empirical model of stellar mass assembly to estimate the average star-formation histories (SFHs) of galaxies across the stellar mass range of our measurement.
-We combine the modelled SFHs with the SN Ia rates to estimate constraints on the SN Ia delay time distribution (DTD), and find a power-law with index $\beta = -0.96 \pm 0.5$ and normalisation $A = 1.7 \pm0.05 \times 10^{-13}~\mathrm{SNe}~{\mathrm{M}_{\odot}}^{-1}~\mathrm{yr}^{-1}$.
+Combining the modelled SFHs with the SN Ia rates to estimate constraints on the SN Ia delay time distribution (DTD), we find the data are best fit by a power-law DTD with index $\beta = -1.14 \pm 0.05$ and normalisation $A = 2.1 \pm0.05 \times 10^{-13}~\mathrm{SNe}~{\mathrm{M}_{\odot}}^{-1}~\mathrm{yr}^{-1}$.
+Upon splitting the SN sample by properties of the light curves, we find a strong dependence on DTD slope with the SN stretch parameter, with slower-declining SNe exhibiting a steeper DTD slope.
 \end{abstract}
@@
 To correct for these incompleteness, we follow a similar method to that used in the PTF rates analyses of \citet{Frohmaier2019,Frohmaier2020} as well as the DES-SN superluminous SN rate of \citet{Thomas2020}.
-We run a suite of simulations using \texttt{SNANA} \citet{Kessler2009a}.
-We simulate 230,000 SNe in the redshift range $0.05 \leq z_{\mathrm{SN}} \leq 1.3$, and draw peak magnitudes from \textbf{ADD DETAILS}.
-We then run mock versions of the DES-SN survey, using the exact cadence, conditions, and zeropoints from the survey itself.
+We run a suite of simulations using an identical method to that described in detail in \citet{Vincenzi2020}.
+We simulate SNe using the SuperNova ANAlysis software (\texttt{SNANA} \citealt{Kessler2009a}) integrated into the \texttt{pippin} framework \citep{Hinton2020}.
+We simulate 230,000 SNe in the redshift range $0.05 \leq z_{\mathrm{SN}} \leq 1.3$.
+The SNe are generated with SEDs based upon the SALT2 model \citep{Guy2007} and trained on the Joint Lightcurve Analysis dataset \citep{Betoule2014}.
+The SALT2 parameters $x_1$ (stretch) and $c$ (colour) are drawn randomly from the intrinsic asymmetric Gaussian distributions described in \citet{Scolnic2016} and "blurred" following the intrinsic scatter model of \citet{Guy2010}, while redshifts are drawn following the volumetric rate evolution of \citet{Frohmaier2019}.
+The SNe are simulated with explosion epochs $t_0$ uniformly distributed between two months before DES-SN began and two months after it finished.
+We run mock versions of the DES-SN survey, using the exact cadence, conditions, and zeropoints from the survey itself.
 All of the detected simulated SNe are passed through the light curve fit of SALT2 \citep{Betoule2014}, as per the implementation in \texttt{SNANA}, and those that fail the light curve cuts outlined in Section \ref{subsubsec:sn_classify} are discarded.

### 2021-02-09 draft.tex

@@
     \includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.png}
+    \includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.png}
     \caption{SN detection efficiencies split up by DES field.
@@
 All of the detected simulated SNe are passed through the light curve fit of SALT2 \citep{Betoule2014}, as per the implementation in \texttt{SNANA}, and those that fail the light curve cuts outlined in Section \ref{subsubsec:sn_classify} are discarded.
-We are left with a fraction of the original simulated SNe, and that fraction is dependent on location, explosion epoch, and redshift, which we define as the SN efficiency.
-For the $i$th SN the efficiency $\eta_{\mathrm{SN}, i}$ in field $F$, exploding at time $t_0$ at redshift $z$, is:
+We are left with a fraction of the original simulated SNe, and that fraction is dependent on a combination of sky location, explosion epoch, redshift, stretch, and colour.
+The fraction of recovered SNe (the efficiency) is thus described by a 5-dimensional surface.
+For the $i$th SN the efficiency $\eta_{\mathrm{SN}, i}$ in field $F$, exploding at time $t_0$ at redshift $z$, with stretch $x_1$ and colour $c$, is:
 \begin{equation}
-    \eta_{\mathrm{SN},i} (F_i,z_i,t_{0,i}) = \left( \frac{N_{\mathrm{obs}}\left(F_i,z_i,t_{0,i}\right)}{N_{\mathrm{sim}}\left(F_i,z_i,t_{0,i}\right)}\right)\,.
+    \eta_{\mathrm{SN},i} (F_i,z_i,t_{0,i},x_1,c) = \left( \frac{N_{\mathrm{obs}}\left(F_i,z_i,t_{0,i},x_1,c\right)}{N_{\mathrm{sim}}\left(F_i,z_i,t_{0,i},x_{1,i},c_i\right)}\right)\,.
 \end{equation}
 
+In practice, the gradient of the efficiency function is strongest between different DES fields and as a function of redshift, while SN stretch and colour have smaller effects.
+We integrate the efficiencies across the full simulated time range, and as such the efficiency is limited to $\sim 0.5$ due to the 6-month nature of the DES observing seasons.
 The distribution of efficiency as a function of redshift is shown in Figure \ref{fig:SN_efficiency}.
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_x1.png}
+    \caption{As per Fig.
+\ref{fig:rate_fitted} but with the data split by their stretch parameter $x_1$.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \label{fig:rate_fitted_split_x1}}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_c.png}
+    \caption{As per Fig.
+\ref{fig:rate_fitted} but with the data split by their colour parameter $c$.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \label{fig:rate_fitted_split_c}}
+\end{figure}
+
+\renewcommand{\arraystretch}{1.2}
+\begin{table}
+	\centering
+	\caption{Results of the Bayesian parameter estimation for the SN Ia DTD.}
+	\label{tab:dtd_results_split_lc}
+	\begin{tabular}{crr} % four columns, alignment for each
+		\hline
+		 Sample &$\beta$ & $A$ \\
+		 &-       & $10^{-13}$ M$_{\odot}^{-1}$yr$^{-1}$ \\
+		\hline
+		Fiducial & $-1.18\pm0.09$ &  $1.16\pm0.08$ \\
+	    $x_1 < 0$ & $-0.79\pm0.08$ &  $1.19 \pm0.05$ \\
+		$x_1 > 0$ & $-1.68 _{ -0.15} ^{ +0.14}$ & $0.51\pm0.12$ \\
+		$c < 0$ & $-1.09 _{ -0.07} ^{ +0.08}$ & $0.89\pm0.04$ \\
+		$c > 0$ & $-1.19\pm0.09$ & $1.16\pm0.08$ \\
+		\hline
+	\end{tabular}
+\end{table}
 \subsection{Second order processes affecting the supernova rate \label{subsec:discussion}}
@@
 Perhaps at low stellar mass, the effect of metallicity is negligible compared to the limitations of our SFH model.
+
+\section{The delay-time distribution as a function of supernova properties}
+\label{sec:split_x1_c}
+
+In the previous sections we have considered all SNe that passed the various quality, standardisation, and redshift cuts.
+However, it is well established that SNe Ia show correlations of varying strength between properties of their light curves and host galaxies.
+For example, measures of the light curve duration (e.g.
+decline rate $\Delta m_{15}$, or stretch such as SALT2 $x_1$) are known to correlate with host galaxy properties such as stellar mass \citep{Lampeitl2010,Sullivan2010}.
 

### 2021-02-09 draft.tex

@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.png}
-    \includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.png}
-    \caption{SN detection efficiencies split up by DES field.
+    %\includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.png}
+    \includegraphics[width=0.5\textwidth]{figs/SN_efficiencies_z_x1_c.png}
+    \caption{ SN detection efficiencies split by DES-SN field, $x_1$ and $c$.
 The $y-$axis represents the fraction of simulated SNe in a given redshift bin that would have been detected by DES-SN and passed light curve quality cuts.
-The curves are capped at efficiencies around 0.5 because DES is restricted to $\sim6$ month observing seasons each calendar year.
+Lines are polynomial fits that approximate the efficiency curves.
     \label{fig:SN_efficiency}}
@@
 
-    \item[ix)] galaxies must be within the redshift range $0.2 \leq z \leq 0.8$.
+    \item[ix)] galaxies must be within the redshift range $0.2 \leq z \leq 0.6$ (see Section \ref{subsec:incompleteness_SNe} for an explanation of this cut).
 \end{enumerate}
@@
 It is evident that the deep fields (X3, C3) are sensitive to SNe at higher redshifts, while there is no drastic shifts between efficiencies in the eight shallow fields.
+There is evidence that the SN efficiency depends weakly on $x_1$ and more strongly on $c$, which is expected since the colour correction term is larger than the stretch correction term in the SN Ia standardisation formula \citep{Tripp1998}.
+Blue SNe are recovered more readily than red SNe as they are generally brighter.
+
+The deep fields show non-zero efficiencies approaching $z=1$, whereas the shallow fields typically reach $z=0.8$.
+Since fractional uncertainty is large at such low efficiencies, we choose to make a redshift cut of $z=0.6$ where the efficiency is well above 0.1 in all fields.
 

### 2021-02-09 draft.tex
Updates from Overleaf

@@
 
-A complementary technique involves measuring the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008, Graur2018, Frohmaier2019}.
+A complementary technique involves measuring the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008, Graur2013, Frohmaier2019}.
 This technique (the volumetric rate method) is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clusters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Graur2014,Maoz2014}.
@@
 SNe Ia do not occur instantaneously after an episode of star formation.
-Instead stars with zero-age main-sequence (ZAMS) masses less than $8 \mathrm{M}_{\odot}$ take time to evolve along the main sequence and form WDs and this time is not well constrained.
-In many works this ``prompt time" $t_{\mathrm{p}}$ is fixed to some value expected to be the minimum time for a star to evolve off the MS and become a WD, such as 40~Myr \citep{Maoz2012,Graur2014,Graur2018}.
+Instead stars with zero-age main-sequence (ZAMS) masses less than $8~\mathrm{M}_{\odot}$ take time to evolve along the main sequence and form WDs and this time is not well constrained.
+In many works this ``prompt time" which we denote $t_{\mathrm{p}}$ is fixed to some value expected to be the minimum time for a star to evolve off the MS and become a WD, such as 40~Myr \citep{Maoz2012,Graur2013,Graur2014}.
 Other studies have left $t_{\mathrm{p}}$ as a free parameter \citep{Heringer2019,Castrillo2020}.
-We perform two fits: one with $t_{\mathrm{p}}$ fixed at 40 Myr, and one with it as a free parameter.
+We perform three fits: one with $t_{\mathrm{p}}$ fixed at 40 Myr, one with it as a free parameter along with $\beta$ and $A$, and a third with $\beta$ and $A$ fixed and  $t_{\mathrm{p}}$ free.
 We fit $t_{\mathrm{p}}$ in log space and adopt a Gaussian prior with hyper-parameters $p(\log(t_{\mathrm{p}})) \sim \mathcal{N}(-1.3\,,0.2)$, which corresponds to being centred around 50~Myr.
@@
 This improvement provides evidence to support the DTD*SFH model.
-However, the model prediction still diverges from the data at low ($<10^9$ M$_{\odot}$) and high ($>10^{11.25}$ M$_{\odot}$), suggesting that these data cannot be explained by the our model, but are driven by further processes that we have not included.
+However, the model prediction still diverges from the data at high ($>10^{11.25}$ M$_{\odot}$), suggesting that these data cannot be explained by the our model, but are driven by further processes that we have not included.
 We discuss these in Section \ref{subsec:discussion}.
-
-\textbf{Or's suggestion: Fix beta, A and fit for tp}
 
@@
 \subsubsection{The DTD power law index \label{subsubsec:compare_beta}}
-We measure a DTD power law index of $-0.96\pm0.05$.
+We measure a DTD power law index of $-1.14\pm0.05$.
 This value is consistent with the majority of previous analyses using various methods.
-Our measurement provides an independent support to the values close to $-1$ found using volumetric rates \citep[e.g.][]{Graur2018,Frohmaier2019}, individual galaxy SFHs \citep[e.g.][]{Maoz2012,Graur2013}, and galaxy clusters \citep[e.g.][]{Maoz2010} although our slope is marginally inconsistent with that of \citet{Heringer2019}.
+Our measurement provides an independent support to the values close to $-1$ found using volumetric rates \citep[e.g.][]{Graur2013,Frohmaier2019}, individual galaxy SFHs \citep[e.g.][]{Maoz2012,Graur2013}, and galaxy clusters \citep[e.g.][]{Maoz2010} although our slope is marginally inconsistent with that of \citet{Heringer2019}.
 
@@
 We measure a DTD normalisation (i.e.
-the rate of SNe 1 Gyr after star-formation) of $1.70 \pm 0.05 \times 10^{-13}$~M$_{\odot}^{-1}$~yr$^{-1}$.
+the rate of SNe 1 Gyr after star-formation) of $1.73 \pm 0.05 \times 10^{-13}$~M$_{\odot}^{-1}$~yr$^{-1}$.
 \citet{Graur2013} found a value of $7 \times 10^{-14}$~M$_{\odot}^{-1}$~yr$^{-1}$ using the SFH technique, whereas \citet{Heringer2019} report $7 \times 10^{-13}$~M$_{\odot}^{-1}$~yr$^{-1}$.
 These results lie either side of our measured value.
-\citet{Heringer2019} note that the normalisation recovered from the SFHR method is sensitive to the assumed prompt time $t_{\mathrm{p}}$ (see Section \ref{subsubsec:compare_tp}, which we also find using our method.
+\citet{Heringer2019} note that the normalisation recovered from the SFHR method is sensitive to the assumed prompt time $t_{\mathrm{p}}$, a degeneracy that is also apparent our method.
 
@@
 In most cases, $t_{\mathrm{p}}$ has been fixed at some fiducial value such as 40~Myr, which is derived from the lifetime of 8~M$_{\odot}$ stars.
-\citet{Castrillo2020} included $t_{\mathrm{p}}$ (which they denote $\Delta$) in their fit, and find a value of $50_{-35}^{+100}$~Myr which is consistent with both 40~Myr as well as our best fitting value of $90 \pm 50$~Myr.
+\citet{Castrillo2020} included $t_{\mathrm{p}}$ (which they denote $\Delta$) in their fit, and find a value of $50_{-35}^{+100}$~Myr which is consistent with both 40~Myr as well as our best fitting value of $67_{-23}^{+43}$~Myr for the three-parameter fit and $47_{-7}^{+8}$~Myr with $\beta$ and $A$ fixed.
 \citet{Heringer2019} also present fits with varying prompt times, although they don't fit for the parameter itself.
@@
 \ref{fig:corner_beta_norm_tp}).
-We therefore report results that are consistent with the fiducial value of 40~Myr.
+Overall, we find results for $t_{\mathrm{p}}$ that are consistent with the fiducial value of 40~Myr and adopt this value for the remainder of the analysis.
 
@@
 
-The use of SN Ia rates to constrain the SN Ia DTD has consistently led to a $t^{-1}$ power-law, which is widely accepted as evidence for the DD scenario.
-While our results are also consistent with those derived in previous studies, our model is mildly inconsistent with the SN rate per galaxy at very low and very high stellar mass.
-In both cases, the model over predicts the observed rate of SNe Ia in galaxies in that stellar mass range, and thus any second order effects must act to suppress the rate compared to the fiducial model.
+The use of SN Ia rate measurements to constrain the SN Ia DTD has consistently led to a $t^{-1}$ power-law, which is widely accepted as evidence supporting the DD scenario.
+While our results are also consistent with those derived in previous studies, our model is mildly inconsistent with the SN rate per galaxy at very high stellar mass.
+The model over predicts the observed rate of SNe Ia in galaxies in that stellar mass range, caused either by a miscalculation of the rate or second order effects acting to suppress the rate compared to the fiducial model.
 
@@
 
-Low mass galaxies are highly sensitive to environmental effects and may often be found in the so-called starburst state with abnormally high (above the SFMS) levels of star formation that could drive environmental evolution \citep[e.g.][]{Dekel1986,Marlowe1995,Tremonti2004,Lee2006}, although studies have shown that only 6 percent of dwarf galaxies are starbursts \citep{Lee2009}.
-It is possible that the averaging effects of the mass assembly model overestimate the true, instantaneous SFR for a significant fraction of the dwarf galaxies.
-Since the SN Ia rate is dominated by short delay times in these populations, an overestimated SFR in the model would lead to an overestimate in the SN Ia rate.
-
 At some point along the evolutionary pathway, galaxies begin to cease star formation due to a combination of processes that together are known as quenching.
@@
 To address this issue we rerun the mass assembly model with $\sigma_{\mathrm{Q}} = 1.5$ as per the nominal analysis of \citet{Childress2014} and refit the SN Ia rate data.
+We find that the adapted quenching model does not change the ability of the model to adequately fit the high-mass turnover in the SN rate.
 
@@
 \citet{Kistler2013} that the rate of SNe Ia is suppressed in the highest mass galaxies where the metallicity is highest, as is the case in our data.
-However, we would also expect to see this effect reversed at the low stellar mass end -- the rate should be enhanced in the lowest-mass, lowest-metallicity galaxies, yet instead we see a further suppression compared to the intermediate masses.
-Perhaps at low stellar mass, the effect of metallicity is negligible compared to the limitations of our SFH model.
 
@@
 For example, measures of the light curve duration (e.g.
-decline rate $\Delta m_{15}$, or stretch such as SALT2 $x_1$) are known to correlate with host galaxy properties such as stellar mass \citep{Lampeitl2010,Sullivan2010}.
+decline rate $\Delta m_{15}$, or stretch such as SALT2 $x_1$) are known to correlate with host galaxy properties such as stellar mass \citep{Lampeitl2010,Sullivan2010} and specific SFR \citep{Rigault2018}.
+In this section we split the DES SNe Ia by their colour and stretch and assess how the measured rates and DTDs vary across this parameter space.
+To do so we split the sample into sub-samples with $x_1 = 0$ and $c=0$ as the divisions points respectively.
+We repeat the analyses of Sections \ref{sec:rates} and \ref{sec:model}, performing the DTD fitting with a fixed $t_{\mathrm{p}} = 40$~Myr, and present the results in Table \ref{tab:dtd_results_split_lc}.
+
+\subsection{Splitting by SN stretch \label{subsec:split_x1}}
+
+The SN Ia rate as a function of stellar mass and the best fitting model for SNe split by stretch is shown in Fig.
+\ref{fig:rate_fitted_split_x1}.
+The evolution of the rate with stellar mass is significantly different for the two sub-samples: high-stretch SNe dominate the rate at low stellar mass but tail off in the higher mass galaxies, while low-stretch SNe are subdominant in low mass galaxies but display a much stronger correlation with mass and make up nearly all SNe in high-mass hosts.
 

### 2021-02-15 draft.tex

@@
 
-The SN Ia rate as a function of stellar mass and the best fitting model for SNe split by stretch is shown in Fig.
+The SN Ia rate as a function of stellar mass SNe split by stretch is shown in Fig.
 \ref{fig:rate_fitted_split_x1}.
-The evolution of the rate with stellar mass is significantly different for the two sub-samples: high-stretch SNe dominate the rate at low stellar mass but tail off in the higher mass galaxies, while low-stretch SNe are subdominant in low mass galaxies but display a much stronger correlation with mass and make up nearly all SNe in high-mass hosts.
+The evolution of the rate with stellar mass is significantly different for the two sub-samples: high-stretch SNe dominate the rate at low stellar mass but tail off in the higher mass galaxies, while low-stretch SNe are subdominant in low mass galaxies but display a much steeper dependence on stellar mass and make up the vast majority of SNe in high-mass hosts.
+These measurements reflect the observed correlations of $x_1$ with stellar mass and sSFR.
+The corresponding DTD fit results in a steep power-law for high-stretch SNe indicative of a population of predominantly prompt SNe, and a much shallower decay slope for low-stretch SNe representing a much more delayed population.
+Such a distinction has been predicted by \citet{Rigault2013,Childress2014,Rigault2018,Nicolas2020} based on the intrinsic $x_1$ distribution and its observed relationship with stellar mass and age.
+
+From the differing DTDs that describe SNe with low and high stretch values we infer that there are either multiple channels through which SN Ia explode which occur on differing timescales, or that the explosion mechanism evolves with progenitor age.
+Two scenarios, that are not necessarily mutually exclusive, that could lead to different DTD decay rates are as follows.
+The first such scenario is to assume that all SNe Ia come from the same initial population of stars, and thus that the progenitors of both low and high stretch SNe form at the same time.
+It is then necessary to invoke models in which the WD progenitors of low-stretch SNe evolve on longer timescales than those of high-stretch SNe, for example due to a different initial binary separation distribution or accretion rate.
+
+Alternatively, low- and high-stretch SNe could form via identical evolutionary channels but with a different onset time since the episode of star-formation.
+The predominantly high-stretch "prompt" SNe would begin exploding as soon as the WDs are formed (nominally 40 Myr) whereas the mainly low-stretch "tardy" SNe would only begin exploding after an extended period of time of the order 1 Gyr.
+The rates of both populations would then both follow the fiducial $t^{-1}$ distribution beginning at this onset time.
+Such a scenario has been explored theoretically, primarily in the sub-Chandrasekhar mass (sub-$M_{\mathrm{Ch}}$) paradigm \citep[e.g.][]{Sim2010,Blondin2017,Shen2017}, usually associated with various forms of the DD scenario.
+Sub-$M_{\mathrm{Ch}}$ SNe Ia typically involve the merger of two WDs where the SN luminosity is correlated with the mass of the primary WD; a correlation between primary WD mass and age would then lead to the different rates, and apparent DTDs, of low and high-stretch SNe observed in this work.
+
+We explore this scenario by fitting the stretch-separated sub-samples with modified DTDs.
+We fix the DTD to a power-law with index $-1$, and fix the normalisation to the best fitting value from the full sample.
+We model the DTD as comprising two components: the prompt, high-stretch SNe and the tardy, low stretch SNe, and we introduce two timescales, $t_1$ and $t_2$.
+At $\tau\leq t_1$, the DTD is caused solely by prompt SNe; at $\tau \geq t_2$ only tardy SNe explode.
+In between where $t_1 \leq\tau\leq t_2$, the DTD is a sum of DTD (prompt) and DTD (tardy), where we model the relative fraction $f$ as a smooth linear slope between $t_1$ and $t_2$:
+\begin{equation}
+    f_{\mathrm{tardy}} = \frac{\tau - t_1}{t_2 - t_1}\,,
+\end{equation}
+and
+\begin{equation}
+    f_{\mathrm{prompt}} = 1 - f_{\mathrm{tardy}}\,.
+\end{equation}
+With $\beta$ and $A$ fixed,  we fit the split-$x_1$ SN Ia rate with $t_1$ and $t_2$ as free parameters, and weak normal priors $p(t_1) \sim \mathcal{N}\left(0.5~\mathrm{Gyr}, 0.5~\mathrm{Gyr}\right)$ $p(t_2) \sim \mathcal{N}\left(1~\mathrm{Gyr}, 0.5~\mathrm{Gyr}\right)$ and the constraint $t_2 > t_1$.
+
+\subsubsection{The late end of the DTD \label{subsubsec:subtypes}}
+
+Despite the reasonable fit of the evolving population model, the fit to tardy SNe diverges from the data at high stellar mass, corresponding to the oldest average stellar age.
+It is difficult to reconcile this turnover with the simple DTD models used thus far in this work, as it would require a steepening or complete turn-off of the DTD at late ($\tau\gtrsim 5$~Gyr) times.
+Here we describe two possible ways in which the model can be reconciled with the data in the highest-mass galaxies.
+
+One possibility is that sub-luminous SNe are more numerous in such predominantly old stellar populations, such that the fraction passing our light curve cuts is lower than the rest of the sample.
+Such a phenomenon could be caused by SN Ia sub-classes such as SN 1991bg-like SNe, which are known to explode exclusively in old environments \citep{Perets2010} at large delay times $>6$~Gyr \citep{Panther2019}.
 

### 2021-02-16 draft.tex

@@
 
+The SN Ia rates generated by the posterior predictive checks are shown in Fig.
+\ref{fig:rate_fitted_split_x1_joint}.
+The best fitting values are $t_1 = 0.65 \pm 0.1$~Gyr and $t_2 = 0.85 \pm 0.15$~Gyr, corresponding to a relatively sharp transition between the two populations.
+
 \subsubsection{The late end of the DTD \label{subsubsec:subtypes}}
@@
 It is difficult to reconcile this turnover with the simple DTD models used thus far in this work, as it would require a steepening or complete turn-off of the DTD at late ($\tau\gtrsim 5$~Gyr) times.
-Here we describe two possible ways in which the model can be reconciled with the data in the highest-mass galaxies.
 
 One possibility is that sub-luminous SNe are more numerous in such predominantly old stellar populations, such that the fraction passing our light curve cuts is lower than the rest of the sample.
-Such a phenomenon could be caused by SN Ia sub-classes such as SN 1991bg-like SNe, which are known to explode exclusively in old environments \citep{Perets2010} at large delay times $>6$~Gyr \citep{Panther2019}.
+Such a phenomenon could be caused by SN Ia sub-classes such as SN 1991bg-like SNe, which are known to explode exclusively in old environments \citep{Perets2010} at delay times as long as $>6$~Gyr \citep{Panther2019}.
+If the SN 1991bg-like objects are drawn from the same parent population of WDs as the "normal" SNe Ia, they could explain the lack thereof in the sample.
 

### 2021-02-17 draft.tex

@@
 
-Type Ia supernovae (SNe Ia) are explosions of white dwarves (WDs) at masses close to the Chandrasekhar limit of 1.44 $M_{\odot}$.
-The small observed dispersion in their peak brightnesses can be reduced further through empirical relations between brightness and light curve properties, such as decline rate (stretch) or optical colour.
-These properties have led SNe Ia to be used extensively by cosmologists to measure relative distances in the Universe.
+Type Ia supernovae (SNe Ia) are explosions of white dwarf stars (WDs) at masses close to the Chandrasekhar limit of 1.44 $M_{\odot}$.
+The small observed dispersion in their peak brightnesses can be reduced further through empirical relations between brightness and light curve properties, such as decline rate (stretch) or optical colour \citep{Philips1993,Tripp1998}.
+These properties have led SNe Ia to be used extensively by cosmologists to measure relative distances in the Universe \citep{Perlmutter1998,Riess1998}
 
-Despite reducing dispersions to $\sim 0.1$ mag in samples with over one thousand SNe \citep{Scolnic2018}, the exact nature of the progenitor scenarios for SNe Ia is yet to be confirmed.
-While it is accepted that SNe Ia are caused by accretion of matter onto a WD from a companion star, multiple possible scenarios exist for the nature of that companion star and the search for this has formed a significant field of research (see \citealt{Maoz2014} for a review).
+Despite using these relations to correct SN Ia peak brightnesses to within a dispersion of $\sim 0.1$ mag in samples with over one thousand SNe \citep{Scolnic2018}, the exact nature of the progenitor scenarios for SNe Ia is yet to be confirmed.
+While it is accepted that SNe Ia are caused by mass transfer onto a WD from a companion star, multiple possible scenarios exist for the nature of that companion star (see \citealt{Maoz2014} for a review).
 The leading models involve a main sequence (MS) star in the single-degenerate (SD) scenario \citep{Whelan1973,Nomoto1982}, a secondary white dwarf in the double-degenerate (DD) scenario \citep{Tutukov1976,Iben1984,Webbink1984}, while more exotic models such as the core-degenerate (CD) scenario invoke white dwarves merging with the cores of massive stars \citep{Soker2019}.
@@
 Conversely, it has been possible to search for surviving remnants of the binary system -- main sequence stars or white dwarves left behind at the SN location or kicked \citep{Shen2018} -- displaying tentative evidence for a DD scenario.
-As yet, there is no conclusive evidence ruling out any progenitor channel from being a significant contribution to the total population of SNe Ia.
+Without an observation of a SN Ia progenitor system or remnant companion, there is as yet no direct evidence ruling out any progenitor channel from being a significant contribution to the total population of SNe Ia.
 
 Another method of inferring progenitor channels is the study of the SN Ia delay time distribution (DTD).
-The DTD can be interpreted as the rate at which SNe Ia occur as a function of the delay time $\tau$ since an episode of star-formation, and thus carries characteristic signatures of the progenitor channel (see \citealt{Wang2012} for a review).
-While the SD scenario is able to produce a broad range of functional forms of the DTD, the DD scenario predicts a power law of the form $\tau^{\beta}$, with $\beta \sim -1$ \citep[e.g][]{Ruiter2009,Mennekens2010}.
+The DTD describes the rate at which SNe Ia occur as a function of the delay time $\tau$ since an episode of star-formation, and thus carries characteristic signatures of the progenitor channel (see \citealt{Wang2012} for a review).
+While the SD scenario is able to produce a broad range of functional forms of the DTD, most variants of the DD scenario predict a power-law of the form $\tau^{\beta}$, with $\beta \sim -1$ \citep[e.g][]{Ruiter2009,Mennekens2010}.
 
@@
 One such approach is to measure global properties of SN Ia host galaxies.
-Simple examples of such analyses are comparisons of the rates of SNe Ia in hosts that have been split by some observational property, such as morphology or colour, and have shown that SNe Ia rate per unit stellar mass (SNuM) is significantly larger in late-type spiral galaxies as well as in bluer galaxies \citep[e.g.][]{Mannucci2005}.
+Simple examples of such analyses are comparisons of the rates of SNe Ia in hosts that have been split by some observational property, such as morphology or colour, and have shown that SN Ia rate per unit stellar mass (SNuM) is significantly larger in late-type spiral galaxies as well as in bluer galaxies \citep[e.g.][]{Mannucci2005}.
 These observations heavily imply that SNe Ia rates are dependent on recent or ongoing star-formation, and thus that the majority of SNe Ia explode after short delay times.
@@
 
-It is also possible to estimate the SFH of an individual galaxy through the modelling of its stellar populations via spectral energy distribution (SED) fitting.
+Instead of comparing \textit{volumetric} rates to the \textit{cosmic} SFH, it is also possible to estimate the SFH of individual galaxies through the modelling of their stellar populations via spectral energy distribution (SED) fitting.
 Works such as \citet{Maoz2011}, \citet{Maoz2012} and \citet{Graur2013} estimated the DTD by measuring SFHs for a sample of field galaxies and comparing them to the number of SNe detected in each galaxy (the SFHR method), and have led to results that suggest a DTD power law with $\beta$ consistent with $-1$ \citep[e.g.][]{Maoz2011,Graur2013}.
-\citet{Childress2014} showed that the $A+B$ parameterisation arises as a direct consequence of the combination of a power-law DTD with the SFHs of galaxies.
+\citet{Childress2014} showed that the $A+B$ parameterisation arises as a direct consequence of the combination of a power-law DTD with the average SFHs of galaxies.
 The recent advances of integral field spectroscopy (IFS) allows for an extension of the SFHR method, by reconstructing the SFH for hundreds or thousands of local regions of each SN Ia host galaxy.
@@
 We present the SN Ia rate per galaxy in Section \ref{sec:rates}.
-We outline the modelling of star-formation histories and measurement of the DTD in Section \ref{sec:model} before concluding in Section \ref{sec:conclusion}.
+We outline the modelling of star-formation histories and measurement of the DTD in Section \ref{sec:model}.
+In Section \ref{sec:split_x1_c} we investigate how the DTD differs among sub-populations of SNe with different light curve characteristics.
+We conclude in Section \ref{sec:conclusion}.
 Where relevant, we assume a spatially flat $\Lambda$CDM cosmology with $\Omega_m = 0.3$ and $H_0 = 70 \mathrm{ km s}^{-1}\mathrm{Mpc}^{-1}$.
-Unless otherwise stated, we assume Gaussian uncertainties quoted at the $1\sigma$ level.
+Unless otherwise stated, we assume Gaussian measurement uncertainties quoted at the $1\sigma$ level, and we quote $1\sigma$ credible intervals on derived parameters.
 Magnitudes are quoted in the AB system \citep{Oke1983}.
@@
 \subsection{Splitting by SN stretch \label{subsec:split_x1}}
-
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_x1_fitjoint.png}
+    \caption{As per Fig.
+\ref{fig:rate_fitted_split_x1} but with the data fit by a two-component DTD.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \label{fig:rate_fitted_split_x1_2c_DTD}}
+\end{figure}
 The SN Ia rate as a function of stellar mass SNe split by stretch is shown in Fig.
@@
 These measurements reflect the observed correlations of $x_1$ with stellar mass and sSFR.
-The corresponding DTD fit results in a steep power-law for high-stretch SNe indicative of a population of predominantly prompt SNe, and a much shallower decay slope for low-stretch SNe representing a much more delayed population.
-Such a distinction has been predicted by \citet{Rigault2013,Childress2014,Rigault2018,Nicolas2020} based on the intrinsic $x_1$ distribution and its observed relationship with stellar mass and age.
+The corresponding DTD fit results in a steep power-law $\beta = -1.68 \pm 0.15$ for high-stretch SNe indicative of a population of predominantly prompt SNe, and a much shallower decay slope ($\beta = -0.79 \pm 0.08$) for low-stretch SNe representing a much more delayed population.
+Such a distinction between SN stretch and progenitor age has been seen by \citet{Rigault2013,Childress2014,Rigault2018,Nicolas2020}; here we have shown it purely by measuring the rate against stellar mass.
 
@@
 It is then necessary to invoke models in which the WD progenitors of low-stretch SNe evolve on longer timescales than those of high-stretch SNe, for example due to a different initial binary separation distribution or accretion rate.
+In this case, the DTD slopes would indeed take on the different values measured here
 
@@
 The predominantly high-stretch "prompt" SNe would begin exploding as soon as the WDs are formed (nominally 40 Myr) whereas the mainly low-stretch "tardy" SNe would only begin exploding after an extended period of time of the order 1 Gyr.
-The rates of both populations would then both follow the fiducial $t^{-1}$ distribution beginning at this onset time.
+The rates of both populations would both follow the fiducial $t^{-1}$ distribution.
 Such a scenario has been explored theoretically, primarily in the sub-Chandrasekhar mass (sub-$M_{\mathrm{Ch}}$) paradigm \citep[e.g.][]{Sim2010,Blondin2017,Shen2017}, usually associated with various forms of the DD scenario.
 Sub-$M_{\mathrm{Ch}}$ SNe Ia typically involve the merger of two WDs where the SN luminosity is correlated with the mass of the primary WD; a correlation between primary WD mass and age would then lead to the different rates, and apparent DTDs, of low and high-stretch SNe observed in this work.
+Such an evolution of light curve properties with age has recently been seen across the full range of "normal" SNe Ia in 1-dimensional simulations by \citet{Shen2021} and is a promising avenue for further investigation.
 
@@
 The SN Ia rates generated by the posterior predictive checks are shown in Fig.
-\ref{fig:rate_fitted_split_x1_joint}.
+\ref{fig:rate_fitted_split_x1_2c_DTD}.
 The best fitting values are $t_1 = 0.65 \pm 0.1$~Gyr and $t_2 = 0.85 \pm 0.15$~Gyr, corresponding to a relatively sharp transition between the two populations.
-
+In reality, we might expect that the transition is not so sharp, but a gradual correlation of delay time with the average stretch of SNe caused by the age vs WD-mass distribution, as predicted by \citet{Shen2021}.
+However we note that the intrinsic stretch distribution may not be a simple Gaussian, but appears to be bimodal \citep{Scolnic2016,Popovic2021}.
+The correlation of progenitor age and WD mass does not easily reproduce such a bimodal distribution, and we encourage further study of the explosion mechanism in order to reconcile this difference.
 \subsubsection{The late end of the DTD \label{subsubsec:subtypes}}

### 2021-02-17 draft.tex
Updates from Overleaf

@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_c.png}
-    \caption{As per Fig.
-\ref{fig:rate_fitted} but with the data split by their colour parameter $c$.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
-    \label{fig:rate_fitted_split_c}}
-\end{figure}
-
 \renewcommand{\arraystretch}{1.2}
@@
 \subsection{Splitting by SN stretch \label{subsec:split_x1}}
+
 \begin{figure}
@@
 If the SN 1991bg-like objects are drawn from the same parent population of WDs as the "normal" SNe Ia, they could explain the lack thereof in the sample.
+
+\subsection{Splitting by SN colour \label{subsec:split_c}}
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_c.png}
+    \caption{As per Fig.
+\ref{fig:rate_fitted_split_x1} but with the data split by their colour parameter $c$.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \label{fig:rate_fitted_split_c}}
+\end{figure}
+
+In the previous section, we have showed that the slope of the SN Ia rate vs stellar mass relation is different for slow and fast declining supernovae.
+The same is for the most part not true for SNe with different colours (Fig.
+\ref{fig:rate_fitted_split_c}), with best fitting values of $\beta$ of $-1.19\pm0.09$ $-1.09\pm0.08$ for red ($c > 0$) and blue ($c<0$) SNe respectively.
+This lack of difference is in agreement with the findings of \citet{Sullivan2010}.
+Red SNe appear to have a higher normalisation than blue SNe, with roughly 30\% more red than blue SNe.
+This dominance can be explained by a single population of SNe with an intrinsic colour distribution that is Gaussian and centred on $c=0$ combined with an external dust distribution with an exponential form, systematically shifting the SN colour distribution to the red and causing the higher observed rate of those objects.
+Such a scenario has been proposed by \citet{Brout2020}.
+
+The predictions from the DTD model diverge from the data at low stellar mass ($M_* <10^{9.25}$ M$_{\odot}$), where the rate becomes dominated by blue SNe.
+Although this is where the data is noisiest, it is worth investigating the possible causes of this divergence.
+A slight preference for SN to be bluer in lower-mass galaxies has been observed \citep{Scolnic2018,Brout2019,Smith2020,Kelsey2020} and could be the same effect seen at low stellar masses here.
+Physically, the dominance of blue SNe at low stellar masses could either be an intrinsic property of the SNe such as a hotter photosphere in explosions of younger, more massive progenitors, or an extrinsic effect such as a lower average dust column density in low-mass host galaxies.
+An intermediate explanation is that the SNe in low-mass hosts have a smaller dust column density in the immediate vicinity of the progenitor system, either due to the shorter evolutionary timescale or the higher mass and thus brighter system being less conducive to dust production.
+A detailed exploration of the effects of environment on SN colour will be presented in Kelsey et al.
+\textit{in prep}.
 

### 2021-02-17 draft.tex
Updates from Overleaf

@@
 
-Type Ia supernovae (SNe Ia) are explosions of white dwarf stars (WDs) at masses close to the Chandrasekhar limit of 1.44 $M_{\odot}$.
-The small observed dispersion in their peak brightnesses can be reduced further through empirical relations between brightness and light curve properties, such as decline rate (stretch) or optical colour \citep{Philips1993,Tripp1998}.
+Type Ia supernovae (SNe Ia) are explosions of white dwarf stars (WDs) at masses close to the Chandrasekhar limit of 1.44 $M_{\odot}$ ($M_{\mathrm{Ch}}$.
+The small observed dispersion in their peak brightnesses can be reduced further through empirical relations between brightness and light curve properties, such as decline rate (stretch) or optical colour \citep{Phillips1993,Tripp1998}.
 These properties have led SNe Ia to be used extensively by cosmologists to measure relative distances in the Universe \citep{Perlmutter1998,Riess1998}
@@
 
-In this work, we combine parts of the above methods and derive a new, independent measurement of the SN Ia DTD.
+While the majority of observations based on populations point towards a DD scenario for most, if not all, SNe Ia, finding self-consistent explosion models that recreate the observed luminosity function as well as correlations between luminosity, light curve parameters, and host galaxy properties has proven difficult.
+In particular, simulations based around explosions of $M_{\mathrm{Ch}}$ WDs fail to reproduced the observed relationship between SN luminosity and light curve duration (the Phillips relation; \citealt{Phillips1993}) as well as low-luminosity "peculiar" objects known as SN 1991bg-like SNe \citep{Sim2013,Blondin2017}.
+In recent years, attention focussed on explosions of sub-$M_{\mathrm{Ch}}$ WDs triggered by double detonations has led to promising results \citep[e.g.][]{Chen2017,Chen2018,Townsley2019,Gronow2020}.
+An additional factor in support of the double-detonation model is that the SN luminosity is related to the mass of the primary WD which can be related to its age, thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Nicolas2020}
+
+In this work, we combine parts of the traditional methods and derive a new, independent measurement of the SN Ia DTD.
 Instead of measuring the volumetric rate of SNe Ia, we measure the rate per galaxy as a function of stellar mass, as per \citet{Sullivan2006,Smith2012}.
@@
 The evolution of the rate with stellar mass is significantly different for the two sub-samples: high-stretch SNe dominate the rate at low stellar mass but tail off in the higher mass galaxies, while low-stretch SNe are subdominant in low mass galaxies but display a much steeper dependence on stellar mass and make up the vast majority of SNe in high-mass hosts.
-These measurements reflect the observed correlations of $x_1$ with stellar mass and sSFR.
+These measurements reflect the observed correlations of $x_1$ with stellar mass and sSFR (and by inference, stellar age) as been seen by \citet{Rigault2013,Rigault2018,Nicolas2020}.
 The corresponding DTD fit results in a steep power-law $\beta = -1.68 \pm 0.15$ for high-stretch SNe indicative of a population of predominantly prompt SNe, and a much shallower decay slope ($\beta = -0.79 \pm 0.08$) for low-stretch SNe representing a much more delayed population.
-Such a distinction between SN stretch and progenitor age has been seen by \citet{Rigault2013,Childress2014,Rigault2018,Nicolas2020}; here we have shown it purely by measuring the rate against stellar mass.
 
@@
 The rates of both populations would both follow the fiducial $t^{-1}$ distribution.
-Such a scenario has been explored theoretically, primarily in the sub-Chandrasekhar mass (sub-$M_{\mathrm{Ch}}$) paradigm \citep[e.g.][]{Sim2010,Blondin2017,Shen2017}, usually associated with various forms of the DD scenario.
-Sub-$M_{\mathrm{Ch}}$ SNe Ia typically involve the merger of two WDs where the SN luminosity is correlated with the mass of the primary WD; a correlation between primary WD mass and age would then lead to the different rates, and apparent DTDs, of low and high-stretch SNe observed in this work.
+Such a scenario may be explained by the sub-$M_{\mathrm{Ch}}$ double-detonation paradigm \citep[e.g.][]{Sim2010,Blondin2017,Shen2017a}.
+Sub-$M_{\mathrm{Ch}}$ SNe Ia typically involve the merger of two WDs and the SN luminosity can be correlated with the mass of the primary WD; a correlation between primary WD mass and age would then lead to the different rates, and apparent DTDs, of low and high-stretch SNe observed in this work.
 Such an evolution of light curve properties with age has recently been seen across the full range of "normal" SNe Ia in 1-dimensional simulations by \citet{Shen2021} and is a promising avenue for further investigation.

### 2021-02-17 draft.tex

@@
 These observations heavily imply that SNe Ia rates are dependent on recent or ongoing star-formation, and thus that the majority of SNe Ia explode after short delay times.
-Conversely, the SNuM in E/S0 and red galaxies is non-negligible, suggesting that there is a secondary, much older component to the DTD \citep{Sullivan2006,Smith2012}.
-The DTD is thus approximated by a two-component ("$A + B$") model, where $A$ and $B$ are the normalizations of the DTD for "prompt" (i.e.
+Conversely, the SNuM in E/S0 and red galaxies is non-negligible, suggesting that there is a secondary, much older component to the DTD \citep{Sullivan2006,Li2011a,Smith2012}.
+The DTD is thus approximated by a two-component ("$A + B$") model, where $A$ and $B$ are the normalisations of the DTD for "prompt" (i.e.
 proportional to instantaneous SFR) and "tardy" (i.e.
@@
 In recent years, attention focussed on explosions of sub-$M_{\mathrm{Ch}}$ WDs triggered by double detonations has led to promising results \citep[e.g.][]{Chen2017,Chen2018,Townsley2019,Gronow2020}.
-An additional factor in support of the double-detonation model is that the SN luminosity is related to the mass of the primary WD which can be related to its age, thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Nicolas2020}
+An additional factor in support of the double-detonation model is that the SN luminosity is related to the mass of the primary WD which can be related to its age, thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Nicolas2020}.
 
@@
 	    $m_r \leq 24.5$ & 196109 &  1678 \\
-	    $0.2 \leq z \leq 0.8$ & 48177 & 1414\\
+	    $0.2 \leq z \leq 0.6$ & 48177 & 1414\\
 
@@
 With over 30,000 transients passing ML cuts it was not possible to obtain spectral follow up of every object.
-Instead we make use of photometric classification techniques, in particular the recurrent neural network classifier \texttt{superNNova} (SNN; \citealt{Moller2019}).
-We derive our SN Ia sample following the approach of \citet{Scolnic2020}, but use a threshold probability of $P(\mathrm{Ia})\geq0.5)$.
-The photometricially classified SNe Ia are then passed through the \texttt{SALT2} framework \citep{Betoule2014} and are subject to quality cuts on the light curve width (stretch; $x_1$) and colour ($c$) parameters in an identical manner to \citet{Vincenzi2020}: $-3 \leq x_1 \leq 3$, $-0.3 \leq c \leq 0.3$.
+Instead we make use of photometric classification in the form of the recurrent neural network classifier \texttt{superNNova} (SNN; \citealt{Moller2019}), mirroring the approach of \citet{Scolnic2020}.
+We train SNN using a large suite of simulated multi-band SN light curves.
+\textbf{Waiting on final sample and a few words from Maria/Anais to complete this bit.} SNe Ia are simulated based on the \texttt{SALT2} model \citep{Guy2007} trained on the Joint Lightcurve Analysis (JLA) data set \citep{Betoule2014}.
+CCSNe are generated from the templates of \citet{Vincenzi2019}.
+We select SNe with a threshold probability of $P(\mathrm{Ia})\geq0.5$, although the results of this analysis are insensitive to the choice of threshold, since the vast majority of SNe receive classifications close to 1 or 0.
+The photometrically classified SNe Ia are then passed through the \texttt{SALT2} framework light curve fitter and are subject to quality cuts on the light curve width (stretch; $x_1$) and colour ($c$) parameters in an identical manner to \citet{Vincenzi2020}: $-3 \leq x_1 \leq 3$, $-0.3 \leq c \leq 0.3$.
 These cuts help to reduce the potential contamination from core-collapse SNe (CCSNe) and outlying thermonuclear SNe.
 We impose further cuts on the quality of those measured parameters, which are: the uncertainty on $x_1$: $\sigma_{x_1} <1$; the uncertainty on the date at which the light curve peaked: $\sigma_{t_{\mathrm{peak}}} <2$; the SALT2 fit probability $>0.001$.
-% whose physical mechanisms may diverge from the general cosmologically useful population.
 
 \subsubsection{Host galaxy selection \label{subsubsec:sn_hosts}}
-Host galaxies for all transients in DES-SN are derived from the deep-stacked $g, r, i, z$-band images presented in \citet{Wiseman2020}.
-SN are associated to hosts using the directional light radius method \citep[e.g.][]{Sullivan2006,Gupta2016}, while spectroscopic redshifts are provided by OzDES \citep{Yuan2015,Childress2017,Lidman2020}, leading to an initial sample of 1766 SNe.
+Host galaxies for all transients in DES-SN are retrieved from the DES-SN Deep catalogue, which is derived from the $g, r, i, z$-band coadded images presented in \citet{Wiseman2020}.
+SN are associated to hosts using the directional light radius method \citep[e.g.][]{Sullivan2006,Gupta2016}, and spectroscopic redshifts for host galaxies come from the OzDES Global Redshift Catalog\footnote{\url{https://docs.datacentral.org.au/ozdes/overview/dr2/}} \citep{Yuan2015,Childress2017,Lidman2020}, which comprises galaxies targetted as DES-SN hosts with the OzDES programme as well as redshifts from legacy catalogues in the DES-SN fields.
 
 \subsection{Field galaxies\label{subsec:field_sample}}
-Along with a sample of SNe, we also require a sample of field galaxies in order to determine a per-galaxy rate.
+
+To compare the properties of SN hosts to the general galaxy population, we select a sample of field galaxies.
 In order to maintain consistency between the SN host and field galaxy sample selections, we obtain a field galaxy sample from the same catalogue as that from which the SNe are matched to obtain host galaxies.
@@
 
-Since the vast majority of objects detected in the deep photometry do not have a spectroscopic redshift measurement, we rely on photometric redshifts (photo-$z$s) in order to proceed with the analysis.
-Photometric redshifts are taken, where available, from the catalogue of \citet{Hartley2020}, and have been estimated using the \texttt{EAZY} photometric redshift code \citep{Brammer2008}.
-These photo-$z$s make use of deep DES optical photometry alongside DECam $u$-band data and near-infrared (NIR) $J$, $H$, and $K$-band imaging from the ultraVISTA and VIDEO surveys.
-Photo-$z$ accuracy from \citet{Hartley2020} at $17 < i<24$, as quantified by the Normalised Absolute Median Deviation (NMAD) is estimated around 0.03.
+Since the vast majority of objects detected in the SN Deep catalogue do not have a spectroscopic redshift measurement, we rely on photometric redshifts (photo-$z$s).
+Photo-$z$s are taken, where available, from the Y3A2\_DEEP catalogue of \citet{Hartley2020}, and have been estimated using the \texttt{eaZy} code \citep{Brammer2008}.
+\citet{Hartley2020} use deep DES optical photometry alongside DECam $u$-band data and near-infrared (NIR) $J$, $H$, and $K$-band imaging from the ultraVISTA and VIDEO surveys.
+The deep optical photometry in Y3A2\_DEEP was stacked using a different technique to that of SN Deep, but the resulting photometry is consistent within $1\sigma$ uncertainties \citep{Wiseman2020}.
+Photo-$z$ accuracy from \citet{Hartley2020} at $17 < i<24$ is estimated around 0.03 as quantified by the Normalised Absolute Median Deviation (NMAD).
 This accuracy is degraded to 0.07 at $17 < i<26$, a range that includes all galaxies in our sample, but is more than adequate for the purposes of this work, where all field galaxies will be grouped into stellar mass bins of 0.5 dex.
@@
 \begin{enumerate}
-    \item[i)] objects must be detected and have a Kron magnitude measurement in all four DES optical bands
+    \item objects must be detected and have a Kron magnitude measurement in all four DES optical bands
 
-    \item[ii)] field galaxies are limited to unmasked region of the SN-X3 chip \cite{Hartley2020}
+    \item field galaxies are limited to unmasked region of the SN-X3 chip \citep{Hartley2020}
 
-    \item[iii)] objects must not be within a given number (20 in $x$, 50 in $y$) of pixels of the CCD edge, as the co-addition of slightly misaligned images introduced a region of significant noise in this part of the detector
+    \item objects must not be within a given number (20 in $x$, 50 in $y$) of pixels of the CCD edge, as the co-addition of slightly misaligned images introduced a region of significant noise in this part of the detector
 
-    \item[iv)] objects must have a value of 0.95 in the star/galaxy (S/G) separation \texttt{CLASS\_STAR} provided by \texttt{Source Extractor} \citep{Bertin1996}
+    \item to minimise stellar contamination, objects must have a value of 0.95 in the star/galaxy (S/G) separation \texttt{CLASS\_STAR} provided by \texttt{Source Extractor} \citep{Bertin1996}
 
-    \item[v)]  objects must be covered by $ugrizJHK$ photometry with either detections or upper limits
+    \item field galaxies must be covered by $ugrizJHK$ photometry with either detections or upper limits
 
-    \item[vi)] objects must have a spectroscopic or photometric redshift measurement
+    \item objects must have a well-defined spectroscopic or photometric redshift measurement
 
-    \item[vii)] objects must be detected at signal-to-noise ratio (SNR) greater than 3 in the $r$ band
+    \item objects must be detected at signal-to-noise ratio (SNR) greater than 3 in the $r$ band
 
-    \item[viii)] galaxies must be brighter than $m_r \leq 24.5$, as this is the magnitude of the faintest SN host with a spectroscopic redshift.
+    \item galaxies must be brighter than $m_r \leq 24.5$, as this is the magnitude of the faintest SN host with a spectroscopic redshift.
 
-    \item[ix)] galaxies must be within the redshift range $0.2 \leq z \leq 0.6$ (see Section \ref{subsec:incompleteness_SNe} for an explanation of this cut).
+    \item galaxies must be within the redshift range $0.2 \leq z \leq 0.6$ (see Section \ref{subsec:incompleteness_SNe} for an explanation of this cut).
 \end{enumerate}
@@
 The numbers of SN hosts and field galaxies passing these cuts are listed in Table \ref{tab:cuts}.
-The final samples comprise 1204 SN host galaxies and 48,177 field galaxies.
-The volume-weighted mean redshifts are 0.65 and 0.63 for SNe and field galaxies, respectively.
+The final samples comprise 881 SNe and their host galaxies and 48,177 field galaxies.
+The volume-weighted mean redshifts are 0.50 for both SNe and field galaxies.
 
@@
 We estimate global galaxy properties for both the SN host and field galaxies that pass the quality cuts by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{Kelsey2020,Smith2020,Wiseman2020}.
-For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists in the OzDES Global Redshift Catalog \citep{Lidman2020}, or more commonly the photometrically derived value.
+For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists in the OzDES GRC, or more commonly the photometrically derived value.
 We use the stellar population templates of \citet{Bruzual2003} and adopt a \citet{Chabrier2003} initial mass function (IMF).
 The fitting procedure returns a best fitting template and corresponding stellar mass ($M_*$).
-Upper and lower bounds on stellar mass estimates are taken as the largest and smallest values of a given parameter for which the reduced $\chi^2$ parameter corresponds to $\chi^2_{\mathrm{red, min}} +1$.
+Upper and lower bounds on stellar mass estimates are taken as the largest and smallest values of a given parameter for which the reduced $\chi^2$ parameter corresponds to $\chi^2_{\mathrm{red, min}} +2.3$.
+To check that the choice of templates do not bias the result, we also fit the galaxies using the P\'EGASE.2 templates \citep{Fioc1997,LeBorgne2002} and a \citet{Kroupa2001} IMF, and find results consistent within measurement uncertainties.
+This is consistent with the findings of \citet{Smith2020}.
 
@@
 SN hosts are preferentially high mass galaxies, whereas the field galaxy distributions increases down to lower masses, peaking around $10^{8.5}~\mathrm{M}_{\odot}$.
-In the bottom panel, the same field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass function (SMF) from the ZFOURGE survey \citep{Tomczak2014} that best represents the redshift range of the DES field galaxies.
+In the bottom panel, the same field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass function (SMF) from the ZFOURGE survey \citep{Tomczak2014}, whose stellar masses are derived with the same photo-$z$ code, IMF and template library as used here.
 Above $10^{8.5}~\mathrm{M}_{\odot}$, the DES field galaxy distribution closely follows the ZFOURGE SMF for $0.5<z<0.75$, indicating that the DES sample is representative of field galaxies in this redshift range.%To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit.
@@
 
-To correct for these incompleteness, we follow a similar method to that used in the PTF rates analyses of \citet{Frohmaier2019,Frohmaier2020} as well as the DES-SN superluminous SN rate of \citet{Thomas2020}.
+To correct for these incompleteness, we follow a similar method to that used in the PTF rates analyses of \citet{Frohmaier2019} and \citet{Frohmaier2020}.
 We run a suite of simulations using an identical method to that described in detail in \citet{Vincenzi2020}.
@@
 We simulate 230,000 SNe in the redshift range $0.05 \leq z_{\mathrm{SN}} \leq 1.3$.
-The SNe are generated with SEDs based upon the SALT2 model \citep{Guy2007} and trained on the Joint Lightcurve Analysis dataset \citep{Betoule2014}.
-The SALT2 parameters $x_1$ (stretch) and $c$ (colour) are drawn randomly from the intrinsic asymmetric Gaussian distributions described in \citet{Scolnic2016} and "blurred" following the intrinsic scatter model of \citet{Guy2010}, while redshifts are drawn following the volumetric rate evolution of \citet{Frohmaier2019}.
+The SNe are generated and trained in the same way as for the training of SNN.
+SALT2 parameters $x_1$ (stretch) and $c$ (colour) are drawn randomly from the intrinsic asymmetric Gaussian distributions described in \citet{Scolnic2016} and "blurred" following the intrinsic scatter model of \citet{Guy2010}, while redshifts are drawn following the volumetric rate evolution of \citet{Frohmaier2019}.
 The SNe are simulated with explosion epochs $t_0$ uniformly distributed between two months before DES-SN began and two months after it finished.
@@
 A further limiting factor in the SN host sample is the requirement of a spectroscopic redshift.
-The majority of SN host spectroscopic redshifts in DES are provided by the dedicated follow-up survey OzDES, for which the limiting magnitude is around 24 to 24.5 mag in the $r$ band.
+The majority of SN host spectroscopic redshifts in DES are provided by the dedicated follow-up survey OzDES, for which the limiting magnitude is around 24 to 24.5 mag in the $r$ band \citep{Lidman2020}.
 The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citet{Vincenzi2020} who provide the spectroscopic redshift efficiency as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey.
 So that we reduce any bias towards SNe in bright hosts that are easier to obtain spectroscopic redshifts for, we assign each SN in the sample described in Section \ref{subsec:host_sample} a weight equal to the inverse of the spectroscopic efficiency for its host.
-This is equivalent to assuming that an efficiency of 0.1 means that for every ten SNe with hosts at that magnitude, only 1 will make it into the sample.
 
@@
 Instead, the inclusion of any given galaxy in the survey area in the sample is determined simply by whether it is detected above a prescribed threshold in signal-to-noise ratio, i.e.
-the sample is magnitude limited.
-To determine the apparent magnitude limit in each of the optical bands we employ the method of \citet{Johnston2007,Teodoro2010,Johnston2012} (hereafter Completeness I, II, III respectively).
+the sample is magnitude limited modulo the cuts described in Section \ref{subsec:cuts}.
+To determine the apparent magnitude limit in each of the optical bands we employ the method of \citet{Johnston2007}, \citet{Teodoro2010}, and \citet{Johnston2012} (hereafter Completeness I, II, III respectively).
 Test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ are computed based on absolute magnitude and distance modulus by calculating the rank of each galaxy's absolute magnitude (distance modulus) when compared to all other galaxies in a survey within a certain slice of distance modulus (absolute magnitude).
@@
 To correct for incompleteness caused by the magnitude limited nature of the survey we follow the prescription of e.g.
-\citet{Sullivan2006, Smith2012} by using a $V_{\mathrm{max}}$ method based on \citet{Schmidt1968}.
+\citet{Sullivan2006} and \citet{Smith2012} by using a $V_{\mathrm{max}}$ method based on \citet{Schmidt1968}.
 For each galaxy in the sample we calculate the maximum volume within which it would have been observed given its absolute magnitude and $k-$correction.
@@
 
-\subsubsection{Stochasticity of galaxy evolution}
+\subsubsection{Simplifications in the galaxy evolution model}
 
@@
 However, it is well established that SNe Ia show correlations of varying strength between properties of their light curves and host galaxies.
-For example, measures of the light curve duration (e.g.
-decline rate $\Delta m_{15}$, or stretch such as SALT2 $x_1$) are known to correlate with host galaxy properties such as stellar mass \citep{Lampeitl2010,Sullivan2010} and specific SFR \citep{Rigault2018}.
+For example, it is well established that measures of the light curve duration (e.g.
+decline rate $\Delta m_{15}$, or stretch such as SALT2 $x_1$) correlate with host galaxy properties such as morphology \citep{Hamuy1995,Hamuy2000,Mannucci2005}, stellar mass \citep{Kelly2010,Lampeitl2010,Sullivan2010} and specific SFR \citep{Rigault2013,Rigault2018}.
+If such correlations are caused by intrinsic differences in the progenitors or their surroundings, there may be signatures in the DTDs of SNe when divided into smaller samples.
 In this section we split the DES SNe Ia by their colour and stretch and assess how the measured rates and DTDs vary across this parameter space.
@@
 The correlation of progenitor age and WD mass does not easily reproduce such a bimodal distribution, and we encourage further study of the explosion mechanism in order to reconcile this difference.
+
 \subsubsection{The late end of the DTD \label{subsubsec:subtypes}}
@@
 \label{sec:conclusion}
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
+
+Here, we summarise the key findings presented in this paper:
+
+\begin{itemize}
+\item We have measured the rate of SNe Ia per galaxy based on a sample of over 800 SNe and 40,000 galaxies detected by DES.
+We have recovered the relationship between SN rate and galaxy stellar mass seen in SNLS \citep{Sullivan2006} and SDSS \citep{Smith2012} and are mildly consistent with both of those works.
+The power-law slope being less than unity indicates that the rate of SNe is not solely driven by stellar mass, but also other factors such as the star-formation history
+
+\item By simulating the stellar mass assembly of average galaxies across cosmic time following the prescription of \citet{Childress2014} we have recovered an estimate of the SN Ia DTD, finding a good fit to a power-law distribution with an index of $-1.18 \pm0.09$.
+Our measurement of the DTD is fairly consistent with previous measurements \citep[e.g.][]{Graur2013,Maoz2012} and carries signatures predicted by the DD scenario for SNe Ia production.
+
+\item We find strong differences in the slope of the SN rate vs stellar mass between SNe with low and high stretch factors.
+The differing slopes are readily explained by the correlation between stretch and stellar age, since more massive galaxies play host to older stellar populations which are known to give rise to lower-stretch SNe
+
+\item Further investigations of low- and high-stretch SNe reveal two plausible scenarios causing the observed relations.
+Firstly, low- and high-stretch SNe could belong to separate populations with different DTD slopes, resulting from a different set of initial conditions such as binary separation at the epoch of WD formation.
+Alternatively, SNe Ia could follow a single DTD where the relative composition of low- and high-stretch objects could change over time.
+We find a relatively sharp transition at delay times between 0.65 and 0.85~Gyr.
+Such a scenario is compatible with stretch being related to progenitor mass, a paradigm consistent with a sub-$M_{\mathrm{Ch}}$, double-detonation explosion mechanism.
+\end{itemize}
 
@@
 
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
+We thank \textit{some people} for fruitful discussions. 
+We acknowledge \textit{DES and all its institutes}
 

### 2021-02-18 draft.tex

@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=.5\textwidth]{figs/SNuM.png}
-    \caption{SN Ia rate per unit stellar mass as function of galaxy stellar mass.
-Error bars are the same as Fig.
-\ref{fig:rate_raw}.
-SDSS data (orange squares) are taken from \citet{Graur2013}.
-The systematically higher SNuM in DES is likely caused by the higher redshift of the sample.
-}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
-    \label{fig:snum}
-\end{figure}
-
 %\begin{figure}
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/SNuM.png}
+    \caption{SN Ia rate per unit stellar mass as function of galaxy stellar mass.
+Error bars are the same as Fig.
+\ref{fig:rate_raw}.
+SDSS data (orange squares) are taken from \citet{Graur2013}.
+The systematically higher SNuM in DES is likely caused by the higher redshift of the sample.
+}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \label{fig:snum}
+\end{figure}
 By binning both the SN hosts and field galaxies by their stellar mass we measure the mean SN Ia rate per galaxy as a function of stellar mass, $R_{\mathrm{G}}(M_*)$.
@@
 We describe the fitting procedure in full detail in Appendix \ref{appendix:linear_fits}.
-We measure a slope of $0.70\pm0.02$, which is broadly consistent with the values found in SNLS and SDSS by \citet{Sullivan2006} and \citet{Smith2012} respectively.
-It is evident that the linear fit is not consistent with the data across the full range of stellar mass considered.
-In particular, there appear to be two locations of interest: firstly, the slope is steeper at masses lower than $10^9$ M$_{\odot}$; secondly there is an apparent flattening and possibly a turnover at masses around and above $10^{11}$ M$_{\odot}$.
-The most likely cause of these divergences is because the SN rate is driven by the SFH which is not a linear function of stellar mass (see Section \ref{sec:model}).
-Second order effects may also be important, and we address these in the following sections.
+We measure a slope of $0.63\pm0.02$, which is consistent with the value found in weakly star-forming galaxies in SNLS by \citet{Sullivan2006}, but also in passive galaxies in SDSS by \citet{Smith2012}, and in all galaxies in LOSS by \citet{Li2011a}.
 
-\subsection{Rate per unit stellar mass \label{subsec:snum}}
-\textbf{short section showing SNUM and how it matches past results}
+A best fitting slope of less than unity (in log space) indicates a non-linear relationship between SN Ia rate and galaxy stellar mass.
+Indeed, the rate is instead likely to be driven by the DTD which is likely a non-linear function of stellar age.
+Investigating the shape of this DTD forms the basis for the latter part of this paper in Sections \ref{sec:model} and \ref{sec:split_x1_c}.
 
@@
 		\hline
-		Fixed $t_{\mathrm{p}}$ & $-0.97_{-0.05}^{+0.05}$ &  $1.73_{-0.05}^{+0.05}$ & -\\
+		Fixed $t_{\mathrm{p}}$ & $-1.13\pm0.5$ &  $2.08 \pm 0.08$ & -\\
 		Free $t_{\mathrm{p}}$ & $-1.02 _{-0.11} ^{+0.08}$ & $1.86 _{-0.13} ^{+0.19}$ & $0.067 _{-0.023} ^{+0.043}$\\
@@
 By integrating the normalised DTD over cosmic time, we obtain an estimate of the average SN Ia efficiency $N_{\mathrm{Ia}}/M_*$ which represents the number of SNe Ia formed per unit mass of stars formed.
-We measure $N_{\mathrm{Ia}}/M_* = 2.0~_{-1.6}^{+5.0} \times 10^{-3}~\mathrm{SNe}~\mathrm{M}_{\odot}^{-1}$.
+We measure $N_{\mathrm{Ia}}/M_* = 0.9~_{-0.7}^{+4.0} \times 10^{-3}~\mathrm{SNe}~\mathrm{M}_{\odot}^{-1}$, which is consistent with \citet{Graur2011}, \citet{Maoz2011}, \citet{Perrets2012}, and \citet{Graur2013}
 
@@
 		\hline
-		Fiducial & $-1.18\pm0.09$ &  $1.16\pm0.08$ \\
+		Fiducial & $-1.14\pm0.05$ &  $2.08\pm0.08$ \\
 	    $x_1 < 0$ & $-0.79\pm0.08$ &  $1.19 \pm0.05$ \\
@@
 
+\subsection{Rate per unit stellar mass \label{subsec:snum}}
+
+An alternative view on how the rate of SNe relates to environment can be gained by calculated the rate of SNe per year per unit stellar mass: SNuM.
+A measurement of the SNuM is achieved by summing the number of SNe in each stellar mass bin, and dividing by the total stellar mass of field galaxies in that bin.
+We show the SNuM as a function of galaxy stellar mass in Fig.~ \ref{fig:snum}, along with the measurements from SNe discovered in SDSS spectra \citep{Graur2013} at $z\sim0.1$.
+We also calculate the SNuM predicuted by our model for each simulated galaxy at a range of redshifts and plot these as curves in Fig.~\ref{fig:snum}.
+Our model accurately recovers the SNuM measured in DES for the redshift and stellar mass range of the data.
+While the data from \citet{Graur2013} lies slightly higher than our model prediction, the difference is consistent with differences in assumed SFHs and stellar population templates as well as SN detection method.
 \section{The delay-time distribution as a function of supernova properties}

### 2021-02-18 draft.tex
Updates from Overleaf

@@
 SDSS data (orange squares) are taken from \citet{Graur2013}.
-The systematically higher SNuM in DES is likely caused by the higher redshift of the sample.
-}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+The systematically higher SNuM in DES is caused by the higher redshift of the sample, as illustrated by the DTD model prediction (coloured curves) }%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
     \label{fig:snum}
@@
 
-\textbf{Add plot showing that the toy model recreates the stellar mass function?}
-
 %\textbf{TEMPTED TO DITCH THIS SINCE OUR SFR IS SKETCHY}
@@
 		Fixed $t_{\mathrm{p}}$ & $-1.13\pm0.5$ &  $2.08 \pm 0.08$ & -\\
-		Free $t_{\mathrm{p}}$ & $-1.02 _{-0.11} ^{+0.08}$ & $1.86 _{-0.13} ^{+0.19}$ & $0.067 _{-0.023} ^{+0.043}$\\
+		Free $t_{\mathrm{p}}$ & $-1.03 _{-0.07} ^{+0.11}$ & $1.87 _{-0.17} ^{+0.13}$ & $0.07 _{-0.04} ^{+0.03}$\\
 		Fixed $A$, $\beta$ & - & - & $0.047_{-0.007}^{+0.008}$\\
@@
 \ref{eq:dtd}), normalisation $A$ and effective after prompt time $t_{\mathrm{p}}$.
-As per Section \ref{sec:rates}, we constrain the parameters via Bayesian inference, using HMC.
+As per Section \ref{sec:rates}, we constrain the parameters via Bayesian inference, using HMC to explore the posterior distribution.
 At each step of the sampling procedure the model is re-calculated via Eq.
-\ref{eq:galaxy_rate}, and evaluate the likelihood assuming that the rate data are normally distributed about their means.
+\ref{eq:galaxy_rate}, we evaluate the likelihood assuming that the rate data are normally distributed about their means.
 For $\beta$ we adopt a Gaussian prior with hyper-parameters $p(\beta) \sim \mathcal{N}(-1\,,0.3)$.

### 2021-02-18 draft.tex
Updates from Overleaf

@@
 \begin{abstract}
-We use a sample of 881 photometrically classified SNe discovered by the Dark Energy Survey (DES) in the redshift range $0.2 < z <0.6$, along with 40415 field galaxies to calculate the rate of type Ia supernovae (SNe Ia) per galaxy.
+We use a sample of 881 photometrically classified type Ia supernovae (SNe Ia) discovered by the Dark Energy Survey (DES) in the redshift range $0.2 < z <0.6$, along with 40415 field galaxies to calculate the rate of SNe Ia per galaxy.
 We recover the established positive trend of SN Ia rate as a function of galaxy stellar mass across a broad range of scales $8.5 \leq \log(M_*/\mathrm{M}_{\odot}) \leq 11.25$.
@@
 Upon splitting the SN sample by properties of the light curves, we find a strong dependence on DTD slope with the SN stretch parameter, with slower-declining SNe exhibiting a steeper DTD slope.
+We interpret this as a result of a relationship between stretch and progenitor age, and explore the inplications of the result in the context of SN Ia progenitors.
 \end{abstract}
@@
 We simulate SNe using the SuperNova ANAlysis software (\texttt{SNANA} \citealt{Kessler2009a}) integrated into the \texttt{pippin} framework \citep{Hinton2020}.
-We simulate 230,000 SNe in the redshift range $0.05 \leq z_{\mathrm{SN}} \leq 1.3$.
+We simulate \textbf{size of final sim} SNe in the redshift range $0.05 \leq z_{\mathrm{SN}} \leq 1.3$.
 The SNe are generated and trained in the same way as for the training of SNN.
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/beta_A_Qerf1.1_corner.png}
+    \includegraphics[width=.5\textwidth]{figs/beta_A_Qerf1.1_corner_All.png}
     \caption{Posterior distributions for DTD slope $\beta$ and normalisation $A$.
-%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+Displayed point estimates represent the median of the posterior samples.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
     \label{fig:corner_beta_norm}}
@@
     \caption{Posterior distributions for DTD parameters $\beta$, $A$, and $t_{\mathrm{p}}$.
-\textbf{This needs updating once final chains are run.
-Axes labels need sorting.} %The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+We display the log of $A$ for clarity.
+Displayed point estimates represent the median of the posterior samples.
+    %The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
     \label{fig:corner_beta_norm_tp}}
@@
 In reality, we might expect that the transition is not so sharp, but a gradual correlation of delay time with the average stretch of SNe caused by the age vs WD-mass distribution, as predicted by \citet{Shen2021}.
-However we note that the intrinsic stretch distribution may not be a simple Gaussian, but appears to be bimodal \citep{Scolnic2016,Popovic2021}.
-The correlation of progenitor age and WD mass does not easily reproduce such a bimodal distribution, and we encourage further study of the explosion mechanism in order to reconcile this difference.
+However we note that the intrinsic stretch distribution may not be a simple Gaussian, but could instead be bimodal \citep{Scolnic2016,Popovic2021}.
+The correlation of progenitor age and WD mass does not easily reproduce such a bimodal distribution, which may suggest that the sub-$M_{\mathrm{Ch}}$ channel cannot account for all SNe Ia.
 
@@
 In the previous section, we have showed that the slope of the SN Ia rate vs stellar mass relation is different for slow and fast declining supernovae.
-The same is for the most part not true for SNe with different colours (Fig.
+There is no evidence for a similar difference between SNe with different colours (Fig.
 \ref{fig:rate_fitted_split_c}), with best fitting values of $\beta$ of $-1.19\pm0.09$ $-1.09\pm0.08$ for red ($c > 0$) and blue ($c<0$) SNe respectively.
@@
 
-The joint posterior distribution for the slope and intercept are shown in Fig.
+The joint posterior distribution for the slope and intercept of the overall SN rate vs stellar mass are shown in Fig.
 \ref{fig:corner_slope_int}.
@@
 
-\section{Changes to the nominal SFH model}
-\label{appendix:model_adjustments}
-In Section \ref{sec:model} we describe our toy model of galaxy SFHs based on the work of \citet{Childress2014}. Here we
+%\section{Changes to the nominal SFH model}
+%\label{appendix:model_adjustments}
+%In Section \ref{sec:model} we describe our toy model of galaxy SFHs based on the work of %\citet{Childress2014}. Here we
 

### 2021-03-08 draft.tex
Updates from Overleaf

@@
 P. Wiseman,$^{1}$\thanks{E-mail: p.s.wiseman@soton.ac.uk}
-A. N. Other,$^{2}$
-Third Author$^{2,3}$
-and Fourth Author$^{3}$
+M. Sullivan,$^{1}$
+C. Frohmaier,$^{2,1}$
+M. Smith, $^{3}$
+M. Vincenzi, $^{2}$
+et al.
 \\
@@
 We use an empirical model of stellar mass assembly to estimate the average star-formation histories (SFHs) of galaxies across the stellar mass range of our measurement.
-Combining the modelled SFHs with the SN Ia rates to estimate constraints on the SN Ia delay time distribution (DTD), we find the data are best fit by a power-law DTD with index $\beta = -1.14 \pm 0.05$ and normalisation $A = 2.1 \pm0.05 \times 10^{-13}~\mathrm{SNe}~{\mathrm{M}_{\odot}}^{-1}~\mathrm{yr}^{-1}$.
+Combining the modelled SFHs with the SN Ia rates to estimate constraints on the SN Ia delay time distribution (DTD), we find the data are fit well by a power-law DTD with index $\beta = -1.14 \pm 0.05$ and normalisation $A = 2.1 \pm0.05 \times 10^{-13}~\mathrm{SNe}~{\mathrm{M}_{\odot}}^{-1}~\mathrm{yr}^{-1}$.
 Upon splitting the SN sample by properties of the light curves, we find a strong dependence on DTD slope with the SN stretch parameter, with slower-declining SNe exhibiting a steeper DTD slope.
-We interpret this as a result of a relationship between stretch and progenitor age, and explore the inplications of the result in the context of SN Ia progenitors.
+We interpret this as a result of a relationship between stretch and progenitor age, and explore the implications of the result in the context of SN Ia progenitors.
 \end{abstract}
@@
 
-Type Ia supernovae (SNe Ia) are explosions of white dwarf stars (WDs) at masses close to the Chandrasekhar limit of 1.44 $M_{\odot}$ ($M_{\mathrm{Ch}}$.
-The small observed dispersion in their peak brightnesses can be reduced further through empirical relations between brightness and light curve properties, such as decline rate (stretch) or optical colour \citep{Phillips1993,Tripp1998}.
-These properties have led SNe Ia to be used extensively by cosmologists to measure relative distances in the Universe \citep{Perlmutter1998,Riess1998}
+Type Ia supernovae (SNe Ia) are explosions of white dwarf stars (WDs).
+Although SNe Ia show diversity in their observed properties, a large fraction of them display a small dispersion in their peak brightnesses which can be reduced further through empirical relations between brightness and light curve properties, such as decline rate (stretch) or optical colour \citep{Rust1974,Pskovskii1977,Phillips1993,Tripp1998}.
+These properties have led SNe Ia to be used extensively by cosmologists to measure relative distances in the Universe \citep{Riess1998,Perlmutter1999}.
 
-Despite using these relations to correct SN Ia peak brightnesses to within a dispersion of $\sim 0.1$ mag in samples with over one thousand SNe \citep{Scolnic2018}, the exact nature of the progenitor scenarios for SNe Ia is yet to be confirmed.
-While it is accepted that SNe Ia are caused by mass transfer onto a WD from a companion star, multiple possible scenarios exist for the nature of that companion star (see \citealt{Maoz2014} for a review).
-The leading models involve a main sequence (MS) star in the single-degenerate (SD) scenario \citep{Whelan1973,Nomoto1982}, a secondary white dwarf in the double-degenerate (DD) scenario \citep{Tutukov1976,Iben1984,Webbink1984}, while more exotic models such as the core-degenerate (CD) scenario invoke white dwarves merging with the cores of massive stars \citep{Soker2019}.
+Despite using these relations to correct SN Ia peak brightnesses to within a dispersion of $\sim 0.1$ mag in samples with over one thousand SNe \citep{Scolnic2018}, the exact nature of the progenitors of SNe Ia is yet to be confirmed.
+While it is likely that SNe Ia are caused by mass transfer onto a WD from, or violent merger with, a companion star, multiple possible scenarios exist for the nature of that companion star (see \citealt{Maoz2014} for a review).
+The leading models involve a main sequence (MS) star in the single-degenerate (SD) scenario \citep{Whelan1973,Nomoto1982}, a secondary white dwarf in the double-degenerate (DD) scenario \citep{Tutukov1976,Iben1984,Webbink1984}, or more exotic models such as the core-degenerate (CD) scenario which invoke WDs merging with the cores of massive stars \citep{Soker2019}.
 
-The progenitors of a number of core-collapse SNe (CCSNe) have been identified in high-resolution pre-explosion images, allowing detailed analysis of the latter stages of massive star evolution.
-However, this approach has not yet been successful in identifying a progenitor of a SN Ia.
+The progenitors of a number of core-collapse SNe (CCSNe) have been identified in high-resolution pre-explosion images \citep{Smartt2009,Eldridge2013}, allowing detailed analysis of the latter stages of massive star evolution.
+However, this approach has not yet been successful in identifying a progenitor of a SN Ia (although see \citet{McCully2014} for evidence of a progenitor for a type Iax SN).
 Conversely, it has been possible to search for surviving remnants of the binary system -- main sequence stars or white dwarves left behind at the SN location or kicked \citep{Shen2018} -- displaying tentative evidence for a DD scenario.
@@
 Transients were detected and processed using a difference imaging program \citep{Kessler2015} and vetted using a machine learning (ML) algorithm \citep{Goldstein2015}.
-Spectral follow-up was performed on a suite of large optical telescopes \citet{Smith2020a}, leading to the initial publication of a measurement of cosmological parameters using 207 spectroscopically confirmed SNe (\citealt{DESCollaboration2018a}, and references therein).
+Spectral follow-up of live SN candidates was performed on a suite of large optical telescopes \citet{Smith2020a}, leading to the initial publication of a measurement of cosmological parameters using 207 spectroscopically confirmed SNe Ia (\citealt{DESCollaboration2018a}, and references therein).
 \subsection{Supernovae \label{subsec:host_sample}}
 \subsubsection{Photometric classification and quality cuts \label{subsubsec:sn_classify}}
-With over 30,000 transients passing ML cuts it was not possible to obtain spectral follow up of every object.
+With over 30,000 transients passing ML selection it was not possible to obtain spectral follow up of every object.
 Instead we make use of photometric classification in the form of the recurrent neural network classifier \texttt{superNNova} (SNN; \citealt{Moller2019}), mirroring the approach of \citet{Scolnic2020}.
@@
 CCSNe are generated from the templates of \citet{Vincenzi2019}.
-We select SNe with a threshold probability of $P(\mathrm{Ia})\geq0.5$, although the results of this analysis are insensitive to the choice of threshold, since the vast majority of SNe receive classifications close to 1 or 0.
+We select SNe with a threshold probability of $P(\mathrm{Ia})\geq0.5$, although the our analysis is not sensitive to this choice, since the vast majority of SNe receive classifications close to 1 or 0.
 The photometrically classified SNe Ia are then passed through the \texttt{SALT2} framework light curve fitter and are subject to quality cuts on the light curve width (stretch; $x_1$) and colour ($c$) parameters in an identical manner to \citet{Vincenzi2020}: $-3 \leq x_1 \leq 3$, $-0.3 \leq c \leq 0.3$.
-These cuts help to reduce the potential contamination from core-collapse SNe (CCSNe) and outlying thermonuclear SNe.
+This selection helps to reduce the potential contamination from core-collapse SNe (CCSNe) and outlying thermonuclear SNe.
 We impose further cuts on the quality of those measured parameters, which are: the uncertainty on $x_1$: $\sigma_{x_1} <1$; the uncertainty on the date at which the light curve peaked: $\sigma_{t_{\mathrm{peak}}} <2$; the SALT2 fit probability $>0.001$.
@@
 The numbers of SN hosts and field galaxies passing these cuts are listed in Table \ref{tab:cuts}.
-The final samples comprise 881 SNe and their host galaxies and 48,177 field galaxies.
+The final samples comprise 881 SNe and their host galaxies and 40,415 field galaxies.
 The volume-weighted mean redshifts are 0.50 for both SNe and field galaxies.
@@
 
-We estimate global galaxy properties for both the SN host and field galaxies that pass the quality cuts by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{Kelsey2020,Smith2020,Wiseman2020}.
+We estimate global galaxy properties for both the SN host and field galaxies that pass the quality cuts by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{kelsey2021,Smith2020,Wiseman2020}.
 For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists in the OzDES GRC, or more commonly the photometrically derived value.
@@
 By integrating the normalised DTD over cosmic time, we obtain an estimate of the average SN Ia efficiency $N_{\mathrm{Ia}}/M_*$ which represents the number of SNe Ia formed per unit mass of stars formed.
-We measure $N_{\mathrm{Ia}}/M_* = 0.9~_{-0.7}^{+4.0} \times 10^{-3}~\mathrm{SNe}~\mathrm{M}_{\odot}^{-1}$, which is consistent with \citet{Graur2011}, \citet{Maoz2011}, \citet{Perrets2012}, and \citet{Graur2013}
+We measure $N_{\mathrm{Ia}}/M_* = 0.9~_{-0.7}^{+4.0} \times 10^{-3}~\mathrm{SNe}~\mathrm{M}_{\odot}^{-1}$, which is consistent with \citet{Graur2011}, \citet{Maoz2011}, \citet{perrett2012}, and \citet{Graur2013}
 
@@
     \caption{As per Fig.
-\ref{fig:rate_fitted} but with the data split by their stretch parameter $x_1$.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+\ref{fig:rate_fitted} but with the data split by their stretch parameter $x_1$.
+Fits were performed with the DTD slope $\beta$ and normalisation $A$ as free parameters, and prompt time $t_{\mathrm{p}}$ fixed at 0.04 Gyr.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
     \label{fig:rate_fitted_split_x1}}
@@
     \caption{As per Fig.
-\ref{fig:rate_fitted_split_x1} but with the data fit by a two-component DTD.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+\ref{fig:rate_fitted_split_x1} but with the data fit simultaneously by a single two-component DTD, with fixed slope $\beta = -1$ and a prompt fraction that is 1 at short delay times, 0 at large delay times, and a linear function of time between $t_1$ and $t_2$.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
     \label{fig:rate_fitted_split_x1_2c_DTD}}
@@
 If the SN 1991bg-like objects are drawn from the same parent population of WDs as the "normal" SNe Ia, they could explain the lack thereof in the sample.
+We check this briefly by re-examining the objects left out of our sample due to \texttt{SALT2} cuts.
+We find that 75\% of objects left out lie in hosts with $M_*>10^{10}$ M$_{\odot}$, while this percentage is 65\% for the objects that pass the cuts.
+However, of the objects in high-mass galaxies that fail the cuts, only 11 (10\%) fail due to their $x_1$ lying below $-3$, and a total of 20 have $x_1 <-2$ which is the regime populated by SN 1991bg-like objects which is well short of the factor of two by which the DTD model over-predicts the data in the highest mass bin.
 
@@
 Although this is where the data is noisiest, it is worth investigating the possible causes of this divergence.
-A slight preference for SN to be bluer in lower-mass galaxies has been observed \citep{Scolnic2018,Brout2019,Smith2020,Kelsey2020} and could be the same effect seen at low stellar masses here.
+A slight preference for SN to be bluer in lower-mass galaxies has been observed \citep{Scolnic2018,Brout2019,Smith2020,kelsey2021} and could be the same effect seen at low stellar masses here.
 Physically, the dominance of blue SNe at low stellar masses could either be an intrinsic property of the SNe such as a hotter photosphere in explosions of younger, more massive progenitors, or an extrinsic effect such as a lower average dust column density in low-mass host galaxies.

### 2021-03-08 draft.tex

@@
 The progenitors of a number of core-collapse SNe (CCSNe) have been identified in high-resolution pre-explosion images \citep{Smartt2009,Eldridge2013}, allowing detailed analysis of the latter stages of massive star evolution.
-However, this approach has not yet been successful in identifying a progenitor of a SN Ia (although see \citet{McCully2014} for evidence of a progenitor for a type Iax SN).
-Conversely, it has been possible to search for surviving remnants of the binary system -- main sequence stars or white dwarves left behind at the SN location or kicked \citep{Shen2018} -- displaying tentative evidence for a DD scenario.
-Without an observation of a SN Ia progenitor system or remnant companion, there is as yet no direct evidence ruling out any progenitor channel from being a significant contribution to the total population of SNe Ia.
+However, this approach has not yet been successful in identifying a progenitor of a SN Ia (e.g.
+\citealt{Graur2014a,Kelly2014,Graur2019}, although see \citet{McCully2014} for evidence of a progenitor for a type Iax SN).
+Conversely, it has been possible to search for surviving remnants of the binary system -- main sequence stars or WDs left behind at the SN location or kicked out at high velocity \citep[e.g.][]{Schaefer2012,RuizLapuente2012,Kerzendorf2018,Kerzendorf2019}.
+\citet{Shen2018} discovered three high-velocity WDs consistent with models of double-detonation SNe Ia.
+However, without an unambiguous observation of a SN Ia progenitor system or remnant companion, there is as yet no direct evidence ruling out any progenitor channel from providing a significant contribution to the total population of SNe Ia.
 
 Another method of inferring progenitor channels is the study of the SN Ia delay time distribution (DTD).
-The DTD describes the rate at which SNe Ia occur as a function of the delay time $\tau$ since an episode of star-formation, and thus carries characteristic signatures of the progenitor channel (see \citealt{Wang2012} for a review).
-While the SD scenario is able to produce a broad range of functional forms of the DTD, most variants of the DD scenario predict a power-law of the form $\tau^{\beta}$, with $\beta \sim -1$ \citep[e.g][]{Ruiter2009,Mennekens2010}.
+The DTD describes the rate at which SNe Ia occur as a function of the delay time $\tau$ since an episode of star-formation, and thus carries characteristic signatures of the progenitor channel (see \citealt{Wang2012} for a review of the theory, and \citet{Maoz2017} for a review of observations).
+The SD scenario produces a broad range of functional forms for the DTD, most of which fail to account for long delay times \citep{Graur2014}.
+On the other hand, most variants of the DD scenario predict a power-law of the form $\tau^{\beta}$, with $\beta \sim -1$ \citep[e.g][]{Ruiter2009,Mennekens2010}.
 
-A power law DTD implies that most SNe Ia explode soon after star formation, but also that there is a non-neglible fraction that explode on the order of Gyrs after the star formation episode.
-The DTD is therefore non-trivial to measure and various techniques have been developed to infer it indirectly.
+As a statistical distribution acting on timescales from tens of Myr to several Gyr, the DTD is non-trivial to measure and various techniques have been developed to infer it indirectly.
 One such approach is to measure global properties of SN Ia host galaxies.
 Simple examples of such analyses are comparisons of the rates of SNe Ia in hosts that have been split by some observational property, such as morphology or colour, and have shown that SN Ia rate per unit stellar mass (SNuM) is significantly larger in late-type spiral galaxies as well as in bluer galaxies \citep[e.g.][]{Mannucci2005}.
-These observations heavily imply that SNe Ia rates are dependent on recent or ongoing star-formation, and thus that the majority of SNe Ia explode after short delay times.
+These observations were interpreted as showing that SNe Ia are strongly influenced by recent or ongoing star-formation, and thus that the majority of SNe Ia explode after short delay times.
 Conversely, the SNuM in E/S0 and red galaxies is non-negligible, suggesting that there is a secondary, much older component to the DTD \citep{Sullivan2006,Li2011a,Smith2012}.
-The DTD is thus approximated by a two-component ("$A + B$") model, where $A$ and $B$ are the normalisations of the DTD for "prompt" (i.e.
+The DTD was thus approximated to first order by a two-component ("$A + B$") model, where $A$ and $B$ are the normalisations of the DTD for "prompt" (i.e.
 proportional to instantaneous SFR) and "tardy" (i.e.
@@
 
-A complementary technique involves measuring the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008, Graur2013, Frohmaier2019}.
-This technique (the volumetric rate method) is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clusters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Graur2014,Maoz2014}.
+A complementary technique involves measuring the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008, Graur2011,Graur2013, Rodney2014,Frohmaier2019}.
+This technique (the volumetric rate method) is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clusters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Maoz2010,Friedman2018,Freundlich2020}.
 These studies have, almost ubiquitously, found $\beta$ to be consistent with $-1$.
@@
 Instead of comparing \textit{volumetric} rates to the \textit{cosmic} SFH, it is also possible to estimate the SFH of individual galaxies through the modelling of their stellar populations via spectral energy distribution (SED) fitting.
-Works such as \citet{Maoz2011}, \citet{Maoz2012} and \citet{Graur2013} estimated the DTD by measuring SFHs for a sample of field galaxies and comparing them to the number of SNe detected in each galaxy (the SFHR method), and have led to results that suggest a DTD power law with $\beta$ consistent with $-1$ \citep[e.g.][]{Maoz2011,Graur2013}.
+Works such as \citet{Maoz2011}, \citet{Maoz2012}, \citet{Graur2013}, and \citet{Graur2015} estimated the DTD by measuring SFHs for a sample of field galaxies and comparing them to the number of SNe detected in each galaxy (the SFHR method), and have led to results that suggest a DTD power law with $\beta$ consistent with $-1$.
+
 \citet{Childress2014} showed that the $A+B$ parameterisation arises as a direct consequence of the combination of a power-law DTD with the average SFHs of galaxies.
@@
 
-While the majority of observations based on populations point towards a DD scenario for most, if not all, SNe Ia, finding self-consistent explosion models that recreate the observed luminosity function as well as correlations between luminosity, light curve parameters, and host galaxy properties has proven difficult.
-In particular, simulations based around explosions of $M_{\mathrm{Ch}}$ WDs fail to reproduced the observed relationship between SN luminosity and light curve duration (the Phillips relation; \citealt{Phillips1993}) as well as low-luminosity "peculiar" objects known as SN 1991bg-like SNe \citep{Sim2013,Blondin2017}.
-In recent years, attention focussed on explosions of sub-$M_{\mathrm{Ch}}$ WDs triggered by double detonations has led to promising results \citep[e.g.][]{Chen2017,Chen2018,Townsley2019,Gronow2020}.
+The majority of observational evidence based on studies of SN Ia populations thus points towards a DD scenario for most, if not all, SNe Ia.
+However, finding self-consistent explosion models that recreate the observed luminosity function as well as correlations between luminosity, light curve parameters, and host galaxy properties has proven difficult.
+In particular, simulations based around explosions of $M_{\mathrm{Ch}}$ WDs fail to reproduce the observed relationship between SN luminosity and light curve duration as well as "peculiar" objects \citep{Sim2013,Blondin2017}.
+In recent years, attention directed towards explosions of sub-$M_{\mathrm{Ch}}$ WDs triggered by double detonations has led to promising results \citep[e.g.][]{Shen2017,Shen2018,Townsley2019,Gronow2020,Shen2021} although they still struggle to match observations at late times in the light curve evolution \citep{Shen2021,Gronow2021}.
 An additional factor in support of the double-detonation model is that the SN luminosity is related to the mass of the primary WD which can be related to its age, thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Nicolas2020}.
 
-In this work, we combine parts of the traditional methods and derive a new, independent measurement of the SN Ia DTD.
+In this work, we combine parts of the traditional methods and derive a new measurement of the SN Ia DTD.
 Instead of measuring the volumetric rate of SNe Ia, we measure the rate per galaxy as a function of stellar mass, as per \citet{Sullivan2006,Smith2012}.
@@
 
-We introduce the SN host and field galaxy samples in Section \ref{sec:data} and describe our handling of incompleteness in Section \ref{sec:incompleteness}.
+In Section \ref{sec:data} we introduce our large sample of SNe Ia from the Dark Energy Survey as well as our deep sample of field galaxies.
+We describe our detailed handling of incompleteness in Section \ref{sec:incompleteness}.
 We present the SN Ia rate per galaxy in Section \ref{sec:rates}.
-We outline the modelling of star-formation histories and measurement of the DTD in Section \ref{sec:model}.
-In Section \ref{sec:split_x1_c} we investigate how the DTD differs among sub-populations of SNe with different light curve characteristics.
-We conclude in Section \ref{sec:conclusion}.
+We outline our modelling of star-formation histories and our novel measurement of the power-law DTD in Section \ref{sec:model}.
+In Section \ref{sec:split_x1_c} we investigate how the DTD differs among sub-populations of SNe with different light curve characteristics, in particular the stretch, and show stretch to be strongly dependent on progenitor age.
+We conclude in Section \ref{sec:conclusion} by discussing the implications of the result.
 Where relevant, we assume a spatially flat $\Lambda$CDM cosmology with $\Omega_m = 0.3$ and $H_0 = 70 \mathrm{ km s}^{-1}\mathrm{Mpc}^{-1}$.

### 2021-03-10 draft.tex

@@
 
-As a statistical distribution acting on timescales from tens of Myr to several Gyr, the DTD is non-trivial to measure and various techniques have been developed to infer it indirectly.
+As a statistical distribution acting on timescales from tens of Myr to several Gyr after an epoch of star formation, the DTD is non-trivial to measure and various techniques have been developed to infer it indirectly.
 One such approach is to measure global properties of SN Ia host galaxies.
@@
 These observations were interpreted as showing that SNe Ia are strongly influenced by recent or ongoing star-formation, and thus that the majority of SNe Ia explode after short delay times.
-Conversely, the SNuM in E/S0 and red galaxies is non-negligible, suggesting that there is a secondary, much older component to the DTD \citep{Sullivan2006,Li2011a,Smith2012}.
+On the other hand, the SNuM in E/S0 and red galaxies is also non-negligible, suggesting that there is a secondary, much older component to the DTD \citep{Sullivan2006,Li2011a,Smith2012}.
 The DTD was thus approximated to first order by a two-component ("$A + B$") model, where $A$ and $B$ are the normalisations of the DTD for "prompt" (i.e.
@@
 
-\citet{Childress2014} showed that the $A+B$ parameterisation arises as a direct consequence of the combination of a power-law DTD with the average SFHs of galaxies.
+\citet{Childress2014} showed that the $A+B$ approximation arises as a direct consequence of the combination of a power-law DTD with the average SFHs of galaxies -- the prompt component proportional to the amount of on-going star-formation at the epoch of observation, and the tardy component caused by the fact that massive galaxies experienced high SFRs several Gyrs ago.
 The recent advances of integral field spectroscopy (IFS) allows for an extension of the SFHR method, by reconstructing the SFH for hundreds or thousands of local regions of each SN Ia host galaxy.
@@
 \subsection{Dark Energy Survey supernova programme \label{subsec:des}}
-The DES Supernova Programme (DES-SN) is a transient survey based on five six-month seasons of observations with the Dark Energy Camera (DECam; \citealt{Flaugher2015}), designed primarily to measure the light curves of SNe Ia for use as cosmological distance indicators.
+The Dark Energy Survey Supernova Programme (DES-SN) is a transient survey based on five six-month seasons of observations with the Dark Energy Camera (DECam; \citealt{Flaugher2015}), designed primarily to measure the light curves of SNe Ia for use as cosmological distance indicators.
 Transients were detected and processed using a difference imaging program \citep{Kessler2015} and vetted using a machine learning (ML) algorithm \citep{Goldstein2015}.
-Spectral follow-up of live SN candidates was performed on a suite of large optical telescopes \citet{Smith2020a}, leading to the initial publication of a measurement of cosmological parameters using 207 spectroscopically confirmed SNe Ia (\citealt{DESCollaboration2018a}, and references therein).
+Spectral follow-up of live SN candidates was performed on a suite of large optical telescopes \citep{Smith2020a}, leading to the initial publication of a measurement of cosmological parameters using 207 spectroscopically confirmed SNe Ia (\citealt{DESCollaboration2018a}, and references therein).
 \subsection{Supernovae \label{subsec:host_sample}}
@@
 CCSNe are generated from the templates of \citet{Vincenzi2019}.
-We select SNe with a threshold probability of $P(\mathrm{Ia})\geq0.5$, although the our analysis is not sensitive to this choice, since the vast majority of SNe receive classifications close to 1 or 0.
+We select SNe with a threshold probability of $P(\mathrm{Ia})\geq0.5$, although our analysis is not sensitive to this choice, since the vast majority of SNe receive classifications close to 1 or 0.
 The photometrically classified SNe Ia are then passed through the \texttt{SALT2} framework light curve fitter and are subject to quality cuts on the light curve width (stretch; $x_1$) and colour ($c$) parameters in an identical manner to \citet{Vincenzi2020}: $-3 \leq x_1 \leq 3$, $-0.3 \leq c \leq 0.3$.
@@
 \subsubsection{Host galaxy selection \label{subsubsec:sn_hosts}}
-Host galaxies for all transients in DES-SN are retrieved from the DES-SN Deep catalogue, which is derived from the $g, r, i, z$-band coadded images presented in \citet{Wiseman2020}.
-SN are associated to hosts using the directional light radius method \citep[e.g.][]{Sullivan2006,Gupta2016}, and spectroscopic redshifts for host galaxies come from the OzDES Global Redshift Catalog\footnote{\url{https://docs.datacentral.org.au/ozdes/overview/dr2/}} \citep{Yuan2015,Childress2017,Lidman2020}, which comprises galaxies targetted as DES-SN hosts with the OzDES programme as well as redshifts from legacy catalogues in the DES-SN fields.
+Host galaxies for all transients in DES-SN are retrieved from the DES-SN Deep catalogue, a galaxy catalogue from the $g, r, i, z$-band coadded images of the ten DES-SN fields which was presented in \citet{Wiseman2020}.
+SNe are associated to galaxies using the directional light radius (DLR) method \citep[e.g.][]{Sullivan2006,Gupta2016}.
+As is standard across DES-SN analyses, we require a SN-host separation to DLR ratio ($d_{\mathrm{DLR}}$) less than 4 in order to classify a galaxy as a host.
+In the case where multiple galaxies lie within $d_{\mathrm{DLR}}<4$, the object with the lower or lowest value is taken to be the host.
+Spectroscopic redshifts for host galaxies come from the OzDES Global Redshift Catalog (GRC; \footnote{\url{https://docs.datacentral.org.au/ozdes/overview/dr2/}} \citealt{Yuan2015,Childress2017,Lidman2020}), which comprises galaxies targetted as DES-SN hosts with the OzDES programme as well as redshifts from legacy catalogues in the DES-SN fields.
 
@@
 
-To compare the properties of SN hosts to the general galaxy population, we select a sample of field galaxies.
-In order to maintain consistency between the SN host and field galaxy sample selections, we obtain a field galaxy sample from the same catalogue as that from which the SNe are matched to obtain host galaxies.
+To calculate the SN Ia rate per galaxy as a function of stellar mass we require a representative sample of the global galaxy population, which we call our field galaxy sample.
+In order to maintain consistency between the SN host and field galaxy sample selections, we obtain a field galaxy sample from the same catalogue as that from which the SNe are matched to obtain host galaxies (SN Deep; \citealt{Wiseman2020}).
 The steps relevant to this analysis are outlined in the following sections.
@@
 Since the vast majority of objects detected in the SN Deep catalogue do not have a spectroscopic redshift measurement, we rely on photometric redshifts (photo-$z$s).
-Photo-$z$s are taken, where available, from the Y3A2\_DEEP catalogue of \citet{Hartley2020}, and have been estimated using the \texttt{eaZy} code \citep{Brammer2008}.
-\citet{Hartley2020} use deep DES optical photometry alongside DECam $u$-band data and near-infrared (NIR) $J$, $H$, and $K$-band imaging from the ultraVISTA and VIDEO surveys.
+Photo-$z$s are taken, from the DES Y3A2\_DEEP catalogue of \citet{Hartley2020}.
+Y3A2\_DEEP makes use of the same deep DES optical photometry that was used in SN Deep for a subset of the fields (SN-X3, SN-C3 and SN-E2), but adds DECam $u$-band data and near-infrared (NIR) $J$, $H$, and $K$-band imaging from the ultraVISTA and VIDEO surveys.
 The deep optical photometry in Y3A2\_DEEP was stacked using a different technique to that of SN Deep, but the resulting photometry is consistent within $1\sigma$ uncertainties \citep{Wiseman2020}.
+\citet{Hartley2020} estimated photo-$z$'s using the \texttt{eaZy} code \citep{Brammer2008}.
 Photo-$z$ accuracy from \citet{Hartley2020} at $17 < i<24$ is estimated around 0.03 as quantified by the Normalised Absolute Median Deviation (NMAD).
-This accuracy is degraded to 0.07 at $17 < i<26$, a range that includes all galaxies in our sample, but is more than adequate for the purposes of this work, where all field galaxies will be grouped into stellar mass bins of 0.5 dex.
+This accuracy is degraded to 0.07 at $17 < i<26$, a range that includes all galaxies in our sample, but is more than adequate for the purposes of this work, where all field galaxies will be grouped into stellar mass bins of $\log \left(\Delta M_*\right) = 0.25$.
 
@@
 \begin{enumerate}
-    \item objects must be detected and have a Kron magnitude measurement in all four DES optical bands
+    \item objects must be detected and have a Kron magnitude measurement in all four DES optical bands;
 
-    \item field galaxies are limited to unmasked region of the SN-X3 chip \citep{Hartley2020}
+    \item field galaxies are limited to unmasked region of the SN-X3 chip \citep{Hartley2020};
 
-    \item objects must not be within a given number (20 in $x$, 50 in $y$) of pixels of the CCD edge, as the co-addition of slightly misaligned images introduced a region of significant noise in this part of the detector
+    \item objects must not be within a given number (20 in $x$, 50 in $y$) of pixels of the CCD edge, as the co-addition of slightly misaligned images introduced a region of significant noise in this part of the detector;
 
-    \item to minimise stellar contamination, objects must have a value of 0.95 in the star/galaxy (S/G) separation \texttt{CLASS\_STAR} provided by \texttt{Source Extractor} \citep{Bertin1996}
+    \item to minimise stellar contamination, objects must have a value of 0.95 in the star/galaxy (S/G) separation \texttt{CLASS\_STAR} provided by \texttt{Source Extractor} \citep{Bertin1996};
 
-    \item field galaxies must be covered by $ugrizJHK$ photometry with either detections or upper limits
+    \item field galaxies must lie within the area covered by $ugrizJHK$ photometry, with a photometric flux measurement or upper limit present in all bands;
 
-    \item objects must have a well-defined spectroscopic or photometric redshift measurement
+    \item objects must have a spectroscopic redshift measurement or a converged photometric redshift estimate;
 
-    \item objects must be detected at signal-to-noise ratio (SNR) greater than 3 in the $r$ band
+    \item objects must be detected at signal-to-noise ratio (SNR) greater than 3 in the $r$ band;
 
-    \item galaxies must be brighter than $m_r \leq 24.5$, as this is the magnitude of the faintest SN host with a spectroscopic redshift.
+    \item galaxies must be brighter than $m_r \leq 24.5$, as this is the magnitude of the faintest SN host with a spectroscopic redshift;
 
@@
 The fitting procedure returns a best fitting template and corresponding stellar mass ($M_*$).
-Upper and lower bounds on stellar mass estimates are taken as the largest and smallest values of a given parameter for which the reduced $\chi^2$ parameter corresponds to $\chi^2_{\mathrm{red, min}} +2.3$.
-To check that the choice of templates do not bias the result, we also fit the galaxies using the P\'EGASE.2 templates \citep{Fioc1997,LeBorgne2002} and a \citet{Kroupa2001} IMF, and find results consistent within measurement uncertainties.
+Upper and lower bounds on stellar mass estimates are taken as the extrema in the model parameters that are consistent with the data (given the photometric uncertainties) according to their $\chi^2$ statistic, as per \citet{Sullivan2006}.
+To check that the choice of templates does not bias the result, we also fit the galaxies using the P\'EGASE.2 templates \citep{Fioc1997,LeBorgne2002} and a \citet{Kroupa2001} IMF, and find results consistent within measurement uncertainties.
 This is consistent with the findings of \citet{Smith2020}.
@@
 The upper panel, with both the SN hosts and field galaxies displayed, shows the vastly different distributions of the two samples.
-SN hosts are preferentially high mass galaxies, whereas the field galaxy distributions increases down to lower masses, peaking around $10^{8.5}~\mathrm{M}_{\odot}$.
+SN hosts are preferentially high mass galaxies, whereas the field galaxy distribution increases down to lower masses, peaking around $10^{8.5}~\mathrm{M}_{\odot}$.
 In the bottom panel, the same field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass function (SMF) from the ZFOURGE survey \citep{Tomczak2014}, whose stellar masses are derived with the same photo-$z$ code, IMF and template library as used here.
@@
 \label{sec:incompleteness}
-The simple ratio of the number of SN hosts and field galaxies presented at the end of the previous section provides a first approximation of the SN rate per galaxy, and the addition of factor equal to the survey duration normalises the rate to per year.
-However both the SN and field galaxy samples introduced in Sections \ref{subsec:host_sample} and \ref{subsec:field_sample} are affected by incompleteness, which is likely to be the dominant systematic effect in the analysis.
+The simple ratio of the number of SN hosts and field galaxies presented at the end of the previous section provides a first approximation of the SN rate per galaxy, and the addition of a factor equal to the survey duration normalises the rate to per year.
+However, both the SN and field galaxy samples introduced in Sections \ref{subsec:host_sample} and \ref{subsec:field_sample} are affected by incompleteness, which is likely to be the dominant systematic effect in the analysis.
 In this section we describe our method of correcting for various sources incompleteness in the data.
@@
 
-To correct for these incompleteness, we follow a similar method to that used in the PTF rates analyses of \citet{Frohmaier2019} and \citet{Frohmaier2020}.
+To correct for these incompleteness, we follow a similar method to that used in the Palomar Transient Factory rates analyses of \citet{Frohmaier2019} and \citet{Frohmaier2020}.
 We run a suite of simulations using an identical method to that described in detail in \citet{Vincenzi2020}.
@@
 SALT2 parameters $x_1$ (stretch) and $c$ (colour) are drawn randomly from the intrinsic asymmetric Gaussian distributions described in \citet{Scolnic2016} and "blurred" following the intrinsic scatter model of \citet{Guy2010}, while redshifts are drawn following the volumetric rate evolution of \citet{Frohmaier2019}.
-The SNe are simulated with explosion epochs $t_0$ uniformly distributed between two months before DES-SN began and two months after it finished.
+The SNe are simulated with explosion epochs $t_0$ uniformly distributed between two months before DES-SN began and two months after it finished in order to account for all SNe that could have been observed by DES-SN.
 We run mock versions of the DES-SN survey, using the exact cadence, conditions, and zeropoints from the survey itself.
@@
 The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citet{Vincenzi2020} who provide the spectroscopic redshift efficiency as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey.
-So that we reduce any bias towards SNe in bright hosts that are easier to obtain spectroscopic redshifts for, we assign each SN in the sample described in Section \ref{subsec:host_sample} a weight equal to the inverse of the spectroscopic efficiency for its host.
+So that we reduce any bias towards SNe in bright hosts that are easier to obtain spectroscopic redshifts for, the host galaxy spectroscopic redshift efficiency is multiplied by that derived from the SN detection efficiency (Section \ref{subsec:incompleteness_SNe}) to arrive at the final SN efficiency $\eta_{\mathrm{SN},i}$.
 
@@
 To determine the apparent magnitude limit in each of the optical bands we employ the method of \citet{Johnston2007}, \citet{Teodoro2010}, and \citet{Johnston2012} (hereafter Completeness I, II, III respectively).
-Test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ are computed based on absolute magnitude and distance modulus by calculating the rank of each galaxy's absolute magnitude (distance modulus) when compared to all other galaxies in a survey within a certain slice of distance modulus (absolute magnitude).
+We use the test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ from those studies, which are computed based on absolute magnitude (distance modulus).
+Each galaxy is ranked by its absolute magnitude (distance modulus) when compared to all other galaxies in a survey within a certain slice of distance modulus (absolute magnitude).
 For a galaxy of apparent magnitude $m < m_{\mathrm{lim, trial}}$ observed in a survey complete to magnitude $m_{\mathrm{lim, true}}$ where  $m_{\mathrm{lim, trial}} \leq m_{\mathrm{lim, true}}$, the expectation value of the rank is 0.5.
 However, if a trial limiting magnitude $m_{\mathrm{lim, trial}} \geq m_{\mathrm{lim, true}}$, there will be a lack of observed faint objects, such that the expectation value of the rank drops.
+
 Completeness I, II, and III show that for surveys with sharp, well defined magnitude limits the test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ drop sharply.
@@
 Moreover, galaxy redshifts have been estimated using photometry only, and $K$-corrections performed using an imperfect template fit, potentially leading to large systematic and statistical fluctuations in absolute magnitudes and distance moduli.
-To reduce the inhomogeneity while still including  large sample of objects, we split the sample into the deep (X3) and shallow (E2) fields and calculate limiting magnitudes separately.
+To reduce the inhomogeneity while still including  large sample of objects, we limit our sample to include only data from one deep (SN-X3) field.
 Fig.
@@
 \begin{equation}
-    R_{\mathrm{G}} = \frac{N_{\mathrm{SN}}}{N_{\mathrm{G}}} \frac{V_{\mathrm{G}}}{V_{\mathrm{SN}}}\frac{1}{T_{\mathrm{SN  survey}}}\,,
+    R_{\mathrm{G}} = \frac{N_{\mathrm{SN}}}{N_{\mathrm{G}}} \frac{V_{\mathrm{G}}}{V_{\mathrm{SN}}}\frac{1}{T}\,,
 \label{eq:rate1}
 \end{equation}
-where $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ are the respective number of SNe and galaxies detected, $V_{\mathrm{SN}}$ and $V_{\mathrm{G}}$ the volumes from which the SNe and G samples were taken, and $T$ the duration of the SN survey in years.
+where $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ are the respective numbers of SNe and galaxies detected, $V_{\mathrm{SN}}$ and $V_{\mathrm{G}}$ the volumes from which the SNe and galaxy samples were taken, and $T$ the duration of the SN survey in years.
 
@@
 \begin{equation}
-    N_{\mathrm{SN,intrinsic}} = \sum_i^{n_{\mathrm{SN}}}\eta_{\mathrm{SN,}i}\,,
+    N_{\mathrm{SN,intrinsic}} = \sum_i^{n_{\mathrm{SN}}}\eta\left(F,z,t_0,x_1,c,m_{\mathrm{host},r}\right)_{i}\,,
     \label{eq:corr_SN}
@@
 \begin{equation}
-    N_{\mathrm{G,intrinsic}} = \sum_j^{n_{\mathrm{G}}} \eta_{\mathrm{G,}j} 
+    N_{\mathrm{G,intrinsic}} = \sum_j^{n_{\mathrm{G}}} \eta\left(V_{\mathrm{max}}\right)_{j} 
     \label{eq:corr_G}
@@
 For each SN host and field galaxy, we take 100 samples of its stellar mass by drawing at random from its PDF.
-For each of the 100 samples we calculate the SN rate per galaxy in each stellar mass bin via Eq \ref{eq:rate1}, using the completeness-corrected values of $N_{\mathrm{SN}}$ and $N_{\mathrm{SN}}$ from Eqs.
+For each of the 100 samples we calculate the SN rate per galaxy in each stellar mass bin via Eq \ref{eq:rate1}, using the completeness-corrected values of $N_{\mathrm{SN}}$ and $N_{\mathrm{G}}$ from Eqs.
 \ref{eq:corr_SN} and \ref{eq:corr_G} respectively.
@@
 We describe the fitting procedure in full detail in Appendix \ref{appendix:linear_fits}.
-We measure a slope of $0.63\pm0.02$, which is consistent with the value found in weakly star-forming galaxies in SNLS by \citet{Sullivan2006}, but also in passive galaxies in SDSS by \citet{Smith2012}, and in all galaxies in LOSS by \citet{Li2011a}.
+We measure a slope of $0.63\pm0.02$, which is consistent with the value found in weakly star-forming galaxies in the Supernova Legacy Survey by \citet{Sullivan2006}, but also in passive galaxies in SDSS by \citet{Smith2012}, and in all galaxies in the Lick Observatory Supernova Search (LOSS) by \citet{Li2011a}.
 
-A best fitting slope of less than unity (in log space) indicates a non-linear relationship between SN Ia rate and galaxy stellar mass.
-Indeed, the rate is instead likely to be driven by the DTD which is likely a non-linear function of stellar age.
+A linear fit in log space with a best fitting slope of less than unity corresponds to a power-law, and indicates that SN Ia rate is not uniquely determined by host galaxy stellar mass.
+Indeed, the rate is instead likely to be driven by the DTD which is a non-linear function of stellar age.
 Investigating the shape of this DTD forms the basis for the latter part of this paper in Sections \ref{sec:model} and \ref{sec:split_x1_c}.
+The straight line fit in Fig.
+\ref{fig:rate_fitted} deviates from the central values of the data at high stellar mass, the reason for which we investigate in Section \ref{subsec:discussion}.
 
@@
 In Section \ref{sec:rates} and Fig.
-\ref{fig:rate_raw} we showed that the SN Ia rate per galaxy as a function of stellar mass is approximated by, but not perfectly described by, a power-law (and thus a linear relationship in log space).
+\ref{fig:rate_raw} we showed that the SN Ia rate per galaxy as a function of stellar mass is approximated by, but not perfectly described by, a power-law.
 In this section, we introduce a physical model in order to better fit the observed rate vs stellar mass relationship.
@@
 \ref{eq:galaxy_rate} is then used to calculate an expected number of SNe in each galaxy given the effective survey time, which is compared to the observed number in that galaxy (usually 0 and occasionally 1) using Poisson statistics.
-This method relies on either photometry covering several wavelength bands, or optical spectra with high signal-to-noise ratio (S/N), in order to distinguish accurately between SFHs.
-Such accuracy is not possible for the DES sample: we do not possess spectra of all galaxies in the field, and in some cases only have the four optical bands available -- and have a maximum of eight from NUV to NIR -- from which to infer a SFH.
-This lack of detail is compounded by our relying on photometric redshifts which add an extra layer of uncertainty to the calculation.
+This method relies on either photometry covering several wavelength bands, or optical spectra with a high signal-to-noise ratio (S/N), in order to distinguish accurately between SFHs.
+Such accuracy is not possible for the DES sample; we do not possess spectra of all galaxies in the field, and in some cases only have the four optical bands available -- and have a maximum of eight from NUV to NIR -- from which to infer a SFH.
+This lack of detail is compounded by our reliance on photometric redshifts, which add an extra layer of uncertainty to the calculation.
 
@@
 In the model, galaxies are expected to evolve smoothly along the so-called "main sequence of star formation" whereby the SFR of a galaxy of stellar mass $M_*$ at redshift $z$ is determined by a simple relationship (the SMz relation, \citealt{Zahid2012}).
-Specifically, we implement their "fine-tuned" model (C14 Eq.
-A7), whereby the SMz flattens above $z\sim2$ in line with observations \citep{Stark2013}.
-We adjust this model slightly and arrive at a final SMz:
+Specifically, we implement their "fine-tuned" model (Eq.
+A7 in \citealt{Childress2014}), whereby the SMz flattens above $z\sim2$ in line with observations \citep{Stark2013}:
 
@@
     \Psi(M_*,z) = \left(\frac{M_*}{10^{10}}\right)^{0.7}\frac{\exp{\left(1.9z\right)}}{\exp{\left(1.7\left(z-2\right)\right)} + \exp{\left(0.2\left(z-2\right)\right)} } [\mathrm{M}_{\odot} \mathrm{yr}^{-1}]\,.
+    \label{eq:psi_mz}
 \end{equation}
@@
 
-As per \citet{Childress2014} we plant seed galaxies with initial masses of $10^6 \mathrm{M}_{\odot}$ at intervals of 50 Myr for look-back times $1 \leq t_f \leq 10$ Gyr, and 25 Myr for look-back times $10 \leq t_f \leq 13$ Gyr, and evaluate the model with a time step of 0.5 Myr.
+Finally, at time $t$, some time $\tau$ since an epoch of star formation, a fraction of stellar mass is lost.
+We adopt the parametrization used by \citet{Childress2014}, namely that of \citet{Leitner2011} for a Chabrier 2003 IMF:
+
+\begin{equation}
+    f_{\mathrm{ml}} = 0.046\ln \left(\frac{\tau}{0.276~\mathrm{Myr}}+1 \right)
+    \label{eq:fml}
+\end{equation}
+The mass loss at any given time is thus the convolution of the Eqs. \ref{eq:psi_mz} and \ref{eq:fml}:
+\begin{equation}
+    \Delta M_* = \int_0^{t_f} \Psi(M_*(t-\tau),z(t-\tau))\cdot\left(f_{\mathrm{ml}}(\tau + \Delta t) - f_{\mathrm{ml}}(\tau)\right)\mathrm{d}\tau\,.
+    \label{eq:mlt}
+\end{equation}
+The stellar mass formed in each time $t$ (and corresponding redshift $z$) is thus the combination of the mass- and redshift-dependent SFR (Eq.
+\ref{eq:psi_mz}), reduced by the mass- and redshift-dependent quenching penalty (Eq.
+\ref{eq:pq}), minus the mass lost in each time step (Eq.
+\ref{eq:mlt}):
+
+\begin{equation}
+    \frac{M_*(t+\Delta t) - M_*(t)}{\Delta t} = p_Q\left(M_*(t_,z(t)\right)\cdot\Psi(M_*(t),z(t)) - \frac{\Delta M_*}{\Delta t}\,.
+    \label{eq:sfh_model}
+\end{equation}
+
+As per \citet{Childress2014} we plant seed galaxies with initial masses of $10^6 ~\mathrm{M}_{\odot}$ at intervals of 50 Myr for look-back times $1 \leq t_f \leq 10$ Gyr, and 25 Myr for look-back times $10 \leq t_f \leq 13$ Gyr to achieved a more detailed model at early times with high SFR.
+For each seed galaxy, we evaluate Eq.
+\ref{eq:sfh_model} at time steps of 0.5 Myr and record the total mass formed and lost in each of the time steps -- this defines our model SFH to be used as input to Eq.
+\ref{eq:galaxy_rate}.
 
@@
 Galaxies with high masses at $z=0$ formed the vast majority of their stars in the first few Gyr and are now likely to be passive with old stellar populations, while low-mass galaxies are currently strongly star-forming with a vast majority of young stars.
-Galaxies with masses around $10^{10} \mathrm{M}_{\odot}$ are composed of a mixture of young and older stellar populations.
+Galaxies with masses around $10^{10}~\mathrm{M}_{\odot}$ are composed of a mixture of young and old stellar populations.
+\subsubsection{Validating the mass assembly model \label{subsubsec:validate_c14}}
+
+As noted in \citet{Childress2014}, this toy model by construction follows several empirical relations derived from galaxy observations: model galaxies follow the SMz relation and obey quenching prescriptions motivated by observed galaxies.
+Here we make two further checks to validate to show that the model can be used to approximate the stellar age distribution of SN Ia host galaxies in DES.
+
+Firstly, we follow \citet{Childress2014} by summing our SFHs and weighting by the galaxy stellar mass function at $z=0$ to estimate the CSFH.
+We approximate the present-day stellar mass function according to a double Schechter function with parameters from the Galaxy and Mass Assembly survey \citet{Baldry2018}: $\log(M^*)=10.66$, $\phi^*_1=3.96\times10^{-3}$, $\alpha_1=-0.35$, $\phi^*_2=0.79\times10^{-3}$, $\alpha_2=-1.47$.
+The comparison of our approximate CSFH with that measured from observations \citep{Madau2014} is shown in Fig.
+\ref{fig:csfh}.
+As was found in \citet{Childress2014}, the two functions show a good qualitative agreement -- in fact, we find a closer match between the model and observed CSFH, accurately reproducing the peak of cosmic star formation around $z\sim2$ and tracing the declining SFR to the present day.
+
+Secondly, we assess the shape of our SFHs and how they depend on stellar mass by comparing with SFH measurements from the Calar Alto Legacy Integral Field spectrscopy Area survey (CALIFA) as revealed by \citet{GonzaleDelgado2017}.
+Our models agree qualitatively on numerous features of the SFHs: high-mass galaxies form almost all their stars at high redshift; intermediate-mass galaxies display a plateau in their SFR from $\sim4$~Gyr to the present day; low-mass galaxies show an increasing rate of star formation at $z=0$.
+The main discrepancy with the lowest-mass bin of the CALIFA sample $8.6 <\logM<9.8$, which as well as an increasing SFR at low redshift shows a second peak of star formation at large lookback times, which we do not see in our model.
+However, this mass bin spans over one order of magnitude in stellar mass.
+Upon closer inspection of our model, the lower edge of this mass bin corresponds to galaxies that form at a lookback time of 5~Gyr and display a rising SFH.
+At the upper edge, galaxies do indeed form at times $>10$~Gyr and display an early peak followed by exponential decline.
+The combination of these different model SFHs in the low-mass bin thus explain the dual-peaked nature of the observed SFHs in CALIFA.
 
@@
 		\hline
-		Fixed $t_{\mathrm{p}}$ & $-1.13\pm0.5$ &  $2.08 \pm 0.08$ & -\\
+		Fixed $t_{\mathrm{p}}$ & $-1.14\pm0.05$ &  $2.08 \pm 0.08$ & -\\
 		Free $t_{\mathrm{p}}$ & $-1.03 _{-0.07} ^{+0.11}$ & $1.87 _{-0.17} ^{+0.13}$ & $0.07 _{-0.04} ^{+0.03}$\\
@@
 Instead stars with zero-age main-sequence (ZAMS) masses less than $8~\mathrm{M}_{\odot}$ take time to evolve along the main sequence and form WDs and this time is not well constrained.
-In many works this ``prompt time" which we denote $t_{\mathrm{p}}$ is fixed to some value expected to be the minimum time for a star to evolve off the MS and become a WD, such as 40~Myr \citep{Maoz2012,Graur2013,Graur2014}.
+In many works this ``prompt time" which we denote $t_{\mathrm{p}}$ is fixed to some value expected to be the minimum time for a star to evolve off the main sequence and become a WD, such as 40~Myr \citep{Maoz2012,Graur2013,Graur2014}.
 Other studies have left $t_{\mathrm{p}}$ as a free parameter \citep{Heringer2019,Castrillo2020}.
@@
 This improvement provides evidence to support the DTD*SFH model.
-However, the model prediction still diverges from the data at high ($>10^{11.25}$ M$_{\odot}$), suggesting that these data cannot be explained by the our model, but are driven by further processes that we have not included.
+However, the model prediction still diverges from the data at high stellar masses ($>10^{11.25}$ M$_{\odot}$), suggesting that these data cannot be explained by our model, but are driven by further processes that we have not included.
 We discuss these in Section \ref{subsec:discussion}.
@@
 This value is consistent with the majority of previous analyses using various methods.
-Our measurement provides an independent support to the values close to $-1$ found using volumetric rates \citep[e.g.][]{Graur2013,Frohmaier2019}, individual galaxy SFHs \citep[e.g.][]{Maoz2012,Graur2013}, and galaxy clusters \citep[e.g.][]{Maoz2010} although our slope is marginally inconsistent with that of \citet{Heringer2019}.
+Our measurement provides an independent support to the values close to $-1$ found using volumetric rates \citep[e.g.][]{Graur2011,Graur2014,Frohmaier2019}, individual galaxy SFHs \citep[e.g.][]{Maoz2012,Graur2013}, and galaxy clusters \citep[e.g.][]{Maoz2010} although our slope is marginally inconsistent with that of \citet{Heringer2019}.
 
@@
 \citet{Heringer2019} note that the normalisation recovered from the SFHR method is sensitive to the assumed prompt time $t_{\mathrm{p}}$, a degeneracy that is also apparent our method.
+The normalisation is also sensitive to the assumed IMF which can explain this variation \citep{Maoz2017}.
 
 By integrating the normalised DTD over cosmic time, we obtain an estimate of the average SN Ia efficiency $N_{\mathrm{Ia}}/M_*$ which represents the number of SNe Ia formed per unit mass of stars formed.
-We measure $N_{\mathrm{Ia}}/M_* = 0.9~_{-0.7}^{+4.0} \times 10^{-3}~\mathrm{SNe}~\mathrm{M}_{\odot}^{-1}$, which is consistent with \citet{Graur2011}, \citet{Maoz2011}, \citet{perrett2012}, and \citet{Graur2013}
+We measure $N_{\mathrm{Ia}}/M_* = 0.9~_{-0.7}^{+4.0} \times 10^{-3}~\mathrm{SNe}~\mathrm{M}_{\odot}^{-1}$, which is consistent with \citet{Graur2011}, \citet{Maoz2011}, \citet{Perrett2012}, and \citet{Graur2013}
 
@@
 The majority of works in the field have constrained the DTD power-law slope, and many also estimate its normalisation.
-Conversely, few have attempted to constrain the time after a burst of star-formation at which SNe Ia begin to explode -- the prompt time $t_{\mathrm{p}}$.
+Conversely, few have attempted to constrain the prompt time $t_{\mathrm{p}}$.
 In most cases, $t_{\mathrm{p}}$ has been fixed at some fiducial value such as 40~Myr, which is derived from the lifetime of 8~M$_{\odot}$ stars.
@@
 The toy model of stellar mass assembly used in this work includes several assumptions about the evolution of galaxies.
-In particular, it is assumed that galaxies evolve independent of each other, growing up the SFMS until they reach a mass at which they quench and star formation ceases.
+In particular, it is assumed that galaxies evolve independent of each other, growing up the star formation main sequence until they reach a mass at which they quench and star formation ceases.
 While these simplifications describe the average properties of galaxies well \citep{Zahid2012, Childress2014}, they struggle to describe the more stochastic nature of galaxy evolution that occurs at the low and high mass ends: starbursts and quenching episodes, respectively.
@@
 Metallicity has been previously invoked to explain irregularities or divergences from the fiducial DTD \citep[e.g.][]{Strolger2010,Meng2011,Kistler2013}.
-Metallicity may affect the observed rate of SNe in two ways: firstly, it can affect the time taken for a star to evolve along the main sequence ($t_{\mathrm{MS}}$) -- Stellar metallicity has varying effects on the MS lifetime of stars \citep[e.g.][]{Georgy2013,Amard2020}, which is also dependent upon initial rotation and degree of mixing; secondly it can affect the time taken from WD formation to SN Ia explosion -- low metallicity stars should produce higher-mass WDs \citep[e.g.][]{Umeda1999,Marigo2007}, resulting in a higher SN Ia rate \citep{Kistler2013}.
+Metallicity may affect the observed rate of SNe in two ways: firstly, it can affect the time taken for a star to evolve along the main sequence ($t_{\mathrm{MS}}$) -- Stellar metallicity has varying effects on the main-sequence lifetime of stars \citep[e.g.][]{Georgy2013,Amard2020}, which is also dependent upon initial rotation and degree of mixing; secondly it can affect the time taken from WD formation to SN Ia explosion -- low metallicity stars should produce higher-mass WDs \citep[e.g.][]{Umeda1999,Marigo2007}, resulting in a higher SN Ia rate \citep{Kistler2013}, although note that \citet{Kistler2013} did not find any evidence for this in the data.
+\citet{Graur2017a} also found that evolution of SN Ia rates with metallicity is consistent with a DTD of the form  $t^{-1}$.
 
@@
 
-An alternative view on how the rate of SNe relates to environment can be gained by calculated the rate of SNe per year per unit stellar mass: SNuM.
+An alternative view on how the SN Ia rate relates to environment can be gained by calculating the rate of SNe per year per unit stellar mass: SNuM.
 A measurement of the SNuM is achieved by summing the number of SNe in each stellar mass bin, and dividing by the total stellar mass of field galaxies in that bin.
@@
 
-In the previous sections we have considered all SNe that passed the various quality, standardisation, and redshift cuts.
+In the previous sections we considered all SNe that passed the various quality, standardisation, and redshift cuts.
 However, it is well established that SNe Ia show correlations of varying strength between properties of their light curves and host galaxies.
@@
 If such correlations are caused by intrinsic differences in the progenitors or their surroundings, there may be signatures in the DTDs of SNe when divided into smaller samples.
-In this section we split the DES SNe Ia by their colour and stretch and assess how the measured rates and DTDs vary across this parameter space.
+Such a hypothesis was investigated by \citet{Brandt2010} who found evidence for differing DTDs for SNe of low and high stretch, although \citet{Perrett2012} found no evidence for a change in volumetric rate evolution (expected due to the evolution of the CSFR) for the same stretch split.
+In this section we split the DES SNe Ia by their stretch and colour, and assess how the measured rates and DTDs vary across this parameter space.
 To do so we split the sample into sub-samples with $x_1 = 0$ and $c=0$ as the divisions points respectively.
-We repeat the analyses of Sections \ref{sec:rates} and \ref{sec:model}, performing the DTD fitting with a fixed $t_{\mathrm{p}} = 40$~Myr, and present the results in Table \ref{tab:dtd_results_split_lc}.
+We repeat the analyses of Sections \ref{sec:rates} and \ref{sec:model} including all of the previous light curve cuts, performing the DTD fitting with a fixed $t_{\mathrm{p}} = 40$~Myr, and present the results in Table \ref{tab:dtd_results_split_lc}.
 
@@
 \end{figure}
-The SN Ia rate as a function of stellar mass SNe split by stretch is shown in Fig.
+The SN Ia rate as a function of stellar mass for SNe split by stretch is shown in Fig.
 \ref{fig:rate_fitted_split_x1}.
 The evolution of the rate with stellar mass is significantly different for the two sub-samples: high-stretch SNe dominate the rate at low stellar mass but tail off in the higher mass galaxies, while low-stretch SNe are subdominant in low mass galaxies but display a much steeper dependence on stellar mass and make up the vast majority of SNe in high-mass hosts.
-These measurements reflect the observed correlations of $x_1$ with stellar mass and sSFR (and by inference, stellar age) as been seen by \citet{Rigault2013,Rigault2018,Nicolas2020}.
+These measurements reflect the observed correlations of $x_1$ with stellar mass and sSFR (and by inference, stellar age) as been seen by \citet{Rigault2013,Graur2017,Rigault2018,Rose2019,Nicolas2020,Rose2021}.
 The corresponding DTD fit results in a steep power-law $\beta = -1.68 \pm 0.15$ for high-stretch SNe indicative of a population of predominantly prompt SNe, and a much shallower decay slope ($\beta = -0.79 \pm 0.08$) for low-stretch SNe representing a much more delayed population.
+This result provides and intriguing confirmation of that observed in 101 SDSS SNe Ia by \citet{Brand2010} who found
 
@@
 The predominantly high-stretch "prompt" SNe would begin exploding as soon as the WDs are formed (nominally 40 Myr) whereas the mainly low-stretch "tardy" SNe would only begin exploding after an extended period of time of the order 1 Gyr.
-The rates of both populations would both follow the fiducial $t^{-1}$ distribution.
+The rates of both populations would follow the fiducial $t^{-1}$ distribution.
 Such a scenario may be explained by the sub-$M_{\mathrm{Ch}}$ double-detonation paradigm \citep[e.g.][]{Sim2010,Blondin2017,Shen2017a}.
 Sub-$M_{\mathrm{Ch}}$ SNe Ia typically involve the merger of two WDs and the SN luminosity can be correlated with the mass of the primary WD; a correlation between primary WD mass and age would then lead to the different rates, and apparent DTDs, of low and high-stretch SNe observed in this work.
-Such an evolution of light curve properties with age has recently been seen across the full range of "normal" SNe Ia in 1-dimensional simulations by \citet{Shen2021} and is a promising avenue for further investigation.
+Such an evolution of light curve properties with age has recently been seen across the full range of "normal" SNe Ia in 1-dimensional simulations by \citet{Shen2021} and is a promising avenue for further investigation although we note that they struggle to reproduce observed light curves at later times ($t\gtrsim30$~d; \citealt{Shen2021,Gronow2021}).
 
@@
 \ref{fig:rate_fitted_split_x1_2c_DTD}.
-The best fitting values are $t_1 = 0.65 \pm 0.1$~Gyr and $t_2 = 0.85 \pm 0.15$~Gyr, corresponding to a relatively sharp transition between the two populations.
-In reality, we might expect that the transition is not so sharp, but a gradual correlation of delay time with the average stretch of SNe caused by the age vs WD-mass distribution, as predicted by \citet{Shen2021}.
+The best fitting values are somewhat consistent with one another, with $t_1 = 0.65 \pm 0.1$~Gyr and $t_2 = 0.85 \pm 0.15$~Gyr, corresponding to a relatively sharp transition between the two populations.
+Our $t_1$ and $t_2$ are consistent with the transition found by \citet{Brandt2010} who found high-stretch SNe to be confined to delay times $\lesssim 0.4$~Gyr while high-stretch SNe displayed delay times $\gtrsim 2.4$~Gyr.
+These results are somewhat surprising, as we might expect that the transition is not so sharp but a gradual correlation of delay time with the average stretch of SNe caused by the age vs WD-mass distribution, as predicted by \citet{Shen2021}.
 However we note that the intrinsic stretch distribution may not be a simple Gaussian, but could instead be bimodal \citep{Scolnic2016,Popovic2021}.
 The correlation of progenitor age and WD mass does not easily reproduce such a bimodal distribution, which may suggest that the sub-$M_{\mathrm{Ch}}$ channel cannot account for all SNe Ia.
+We also note that our method models the average SFH of galaxies and that the DTD is a statistical distribution: our results do not rule out high-stretch SNe arising from old progenitors, but do suggest that such a scenario is unlikely.
+
+Our transition ages $t_1$ and $t_2$
 
@@
 
-\item By simulating the stellar mass assembly of average galaxies across cosmic time following the prescription of \citet{Childress2014} we have recovered an estimate of the SN Ia DTD, finding a good fit to a power-law distribution with an index of $-1.18 \pm0.09$.
-Our measurement of the DTD is fairly consistent with previous measurements \citep[e.g.][]{Graur2013,Maoz2012} and carries signatures predicted by the DD scenario for SNe Ia production.
+\item By simulating the stellar mass assembly of average galaxies across cosmic time following the prescription of \citet{Childress2014} we have recovered an estimate of the SN Ia DTD, finding a good fit to a power-law distribution with an index of $-1.14 \pm0.05$.
+Our measurement of the DTD is fairly consistent with previous measurements \citep[e.g.][]{Graur2013,Maoz2017} and carries signatures predicted by the DD scenario for SNe Ia production.
 

### 2021-03-10 draft.tex
Updates from Overleaf

@@
 \citealt{Graur2014a,Kelly2014,Graur2019}, although see \citet{McCully2014} for evidence of a progenitor for a type Iax SN).
-Conversely, it has been possible to search for surviving remnants of the binary system -- main sequence stars or WDs left behind at the SN location or kicked out at high velocity \citep[e.g.][]{Schaefer2012,RuizLapuente2012,Kerzendorf2018,Kerzendorf2019}.
+Conversely, it has been possible to search for surviving remnants of the binary system -- main sequence stars or WDs left behind at the SN location or kicked out at high velocity \citep[e.g.][]{Schaefer2012,Ruiz-Lapuente2018,Kerzendorf2018,Kerzendorf2019}.
 \citet{Shen2018} discovered three high-velocity WDs consistent with models of double-detonation SNe Ia.
@@
 A complementary technique involves measuring the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008, Graur2011,Graur2013, Rodney2014,Frohmaier2019}.
-This technique (the volumetric rate method) is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clusters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Maoz2010,Friedman2018,Freundlich2020}.
+This technique (the volumetric rate method) is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clusters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Maoz2010,Friedman2018,Freundlich2021}.
 These studies have, almost ubiquitously, found $\beta$ to be consistent with $-1$.
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/CSFH_MD14.png}
+    \caption{Cosmic star-formation history (CSFH) as approximated by our model (cyan curve) and as a best fit to observations \citep{Madau2014}.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \label{fig:csfh}
+\end{figure}
+
 %%%%%% RESULTS %%%%%%%%
@@
 
-Secondly, we assess the shape of our SFHs and how they depend on stellar mass by comparing with SFH measurements from the Calar Alto Legacy Integral Field spectrscopy Area survey (CALIFA) as revealed by \citet{GonzaleDelgado2017}.
+Secondly, we assess the shape of our SFHs and how they depend on stellar mass by comparing with SFH measurements from the Calar Alto Legacy Integral Field spectrscopy Area survey (CALIFA) as revealed by \citet{GonzalezDelgado2017}.
 Our models agree qualitatively on numerous features of the SFHs: high-mass galaxies form almost all their stars at high redshift; intermediate-mass galaxies display a plateau in their SFR from $\sim4$~Gyr to the present day; low-mass galaxies show an increasing rate of star formation at $z=0$.
-The main discrepancy with the lowest-mass bin of the CALIFA sample $8.6 <\logM<9.8$, which as well as an increasing SFR at low redshift shows a second peak of star formation at large lookback times, which we do not see in our model.
+The main discrepancy with the lowest-mass bin of the CALIFA sample $8.6 <\log M<9.8$, which as well as an increasing SFR at low redshift shows a second peak of star formation at large lookback times, which we do not see in our model.
 However, this mass bin spans over one order of magnitude in stellar mass.

### 2021-03-10 draft.tex

@@
 The corresponding DTD fit results in a steep power-law $\beta = -1.68 \pm 0.15$ for high-stretch SNe indicative of a population of predominantly prompt SNe, and a much shallower decay slope ($\beta = -0.79 \pm 0.08$) for low-stretch SNe representing a much more delayed population.
-This result provides and intriguing confirmation of that observed in 101 SDSS SNe Ia by \citet{Brand2010} who found
+This result provides and intriguing confirmation of that observed in 101 SDSS SNe Ia by \citet{Brandt2010} who found
 
@@
 The rates of both populations would follow the fiducial $t^{-1}$ distribution.
-Such a scenario may be explained by the sub-$M_{\mathrm{Ch}}$ double-detonation paradigm \citep[e.g.][]{Sim2010,Blondin2017,Shen2017a}.
+Such a scenario may be explained by the sub-$M_{\mathrm{Ch}}$ double-detonation paradigm \citep[e.g.][]{Sim2010,Blondin2017,Shen2017}.
 Sub-$M_{\mathrm{Ch}}$ SNe Ia typically involve the merger of two WDs and the SN luminosity can be correlated with the mass of the primary WD; a correlation between primary WD mass and age would then lead to the different rates, and apparent DTDs, of low and high-stretch SNe observed in this work.

### 2021-03-10 draft.tex

@@
 A complementary technique involves measuring the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008, Graur2011,Graur2013, Rodney2014,Frohmaier2019}.
-This technique (the volumetric rate method) is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clusters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Maoz2010,Friedman2018,Freundlich2021}.
+This technique (the volumetric rate method) is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clusters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Maoz2010,Friedmann2018,Freundlich2021}.
 These studies have, almost ubiquitously, found $\beta$ to be consistent with $-1$.
@@
 In recent years, attention directed towards explosions of sub-$M_{\mathrm{Ch}}$ WDs triggered by double detonations has led to promising results \citep[e.g.][]{Shen2017,Shen2018,Townsley2019,Gronow2020,Shen2021} although they still struggle to match observations at late times in the light curve evolution \citep{Shen2021,Gronow2021}.
-An additional factor in support of the double-detonation model is that the SN luminosity is related to the mass of the primary WD which can be related to its age, thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Nicolas2020}.
+An additional factor in support of the double-detonation model is that the SN luminosity is related to the mass of the primary WD, which itself is likely to be related to its age (although this relation is probably complicated by other factors such as accretion rate, metallicity, and the composition of the companion), thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Nicolas2020}.
 
@@
 	\centering
-	\caption{Numbers of field galaxies and SN hosts passing various quality cuts.}
+	\caption{Numbers of field galaxies and SN hosts passing various quality cuts. SNe are derived from must already have passed the masked chips and good redshift cuts before reaching this stage.}
 	\label{tab:cuts}
@@
 		\hline
-		Chosen fields & 1364311  & 1766\\
-	    Kron mag in all bands & 1069004  & 1764 \\
+		Chosen fields & 1364311  & 1441\\
+	    Kron mag in all bands & 1069004  & 1439 \\
 	    Masked chips & 816950  & - \\
 	    Has ugrizJHK photometry & 545748  & -\\
-	    Edge of chip & 481731 & 1716 \\
-	    Star/galaxy separation & 400051 &  1678\\
-	    Has good redshift & 395034 & 1678 \\
-	    SNR $\geq 3$& 338256  & 1678 \\
-	    $m_r \leq 24.5$ & 196109 &  1678 \\
-	    $0.2 \leq z \leq 0.6$ & 48177 & 1414\\
+	    Edge of chip & 481731 & 1401 \\
+	    Star/galaxy separation & 400051 &  1259\\
+	    Has good redshift & 395034 & - \\
+	    SNR $\geq 3$& 338256  & 1259 \\
+	    $m_r \leq 24.5$ & 196109 &  1254 \\
+	    $0.2 \leq z \leq 0.6$ & 48177 & 881\\
 
@@
 Spectral follow-up of live SN candidates was performed on a suite of large optical telescopes \citep{Smith2020a}, leading to the initial publication of a measurement of cosmological parameters using 207 spectroscopically confirmed SNe Ia (\citealt{DESCollaboration2018a}, and references therein).
+Spectroscopic redshifts for host galaxies come from the OzDES Global Redshift Catalog (GRC; \footnote{\url{https://docs.datacentral.org.au/ozdes/overview/dr2/}} \citealt{Yuan2015,Childress2017,Lidman2020}), which comprises galaxies targetted as DES-SN hosts with the OzDES programme as well as redshifts from legacy catalogues in the DES-SN fields.
 \subsection{Supernovae \label{subsec:host_sample}}
@@
 \textbf{Waiting on final sample and a few words from Maria/Anais to complete this bit.} SNe Ia are simulated based on the \texttt{SALT2} model \citep{Guy2007} trained on the Joint Lightcurve Analysis (JLA) data set \citep{Betoule2014}.
-CCSNe are generated from the templates of \citet{Vincenzi2019}.
-We select SNe with a threshold probability of $P(\mathrm{Ia})\geq0.5$, although our analysis is not sensitive to this choice, since the vast majority of SNe receive classifications close to 1 or 0.
+Synthetic CCSNe light curves are generated from the templates of \citet{Vincenzi2019}.
+Given the training set of synthetic light curves, SNN is able to return a classification for observed light curves.
+Before classifying, we remove transients with variability in multiple seasons (likely active galactic nuclei or superluminous SNe).
+SNN is then run on every transient with a host galaxy redshift (see Section \ref{subsubsec:sn_hosts}).
+We define SNe with a threshold probability of $P(\mathrm{Ia})\geq0.5$ as photometrically classified SNe Ia, although our analysis is not sensitive to this choice, since the vast majority of SNe receive classifications close to 1 or 0 \citep{Moller2019}.
 The photometrically classified SNe Ia are then passed through the \texttt{SALT2} framework light curve fitter and are subject to quality cuts on the light curve width (stretch; $x_1$) and colour ($c$) parameters in an identical manner to \citet{Vincenzi2020}: $-3 \leq x_1 \leq 3$, $-0.3 \leq c \leq 0.3$.
@@
 We impose further cuts on the quality of those measured parameters, which are: the uncertainty on $x_1$: $\sigma_{x_1} <1$; the uncertainty on the date at which the light curve peaked: $\sigma_{t_{\mathrm{peak}}} <2$; the SALT2 fit probability $>0.001$.
+The number of SNe passing each stage of these cuts is displayed in Table 2 of \citet{Vincenzi2020} and reduces the $\sim30,000$ objects to 1604 SNe.
+With the addition of the photometric classifier we are left with 1441 SNe with which we proceed to inspect their host galaxies.
 
@@
 In the case where multiple galaxies lie within $d_{\mathrm{DLR}}<4$, the object with the lower or lowest value is taken to be the host.
-Spectroscopic redshifts for host galaxies come from the OzDES Global Redshift Catalog (GRC; \footnote{\url{https://docs.datacentral.org.au/ozdes/overview/dr2/}} \citealt{Yuan2015,Childress2017,Lidman2020}), which comprises galaxies targetted as DES-SN hosts with the OzDES programme as well as redshifts from legacy catalogues in the DES-SN fields.
 
@@
 
-The posterior distributions for the fit parameters are found in Figs.
+The joint and marginal posterior distributions for the fit parameters are found in Figs.
 \ref{fig:corner_beta_norm} and \ref{fig:corner_beta_norm_tp} for the fixed and free $t_{\mathrm{p}}$ fits respectively, and the posterior means and standard deviations are summarised in Table \ref{tab:dtd_results}.
+Fig.
+\ref{fig:corner_beta_norm} shows that there is a correlation between $\beta$ and $A$ which is not seen in the fit with $t_{\mathrm{p}}$ as a free parameter.
+This is likely caused by $\beta$ instead correlating with $t_{\mathrm{p}}$, and being more poorly constrained in the three-parameter fit.
 In Fig.
@@
 The model provides a good fit across a wide range of stellar mass.
-The model clearly diverges from the simple log-linear fit, describing better the suppressed rate at the low and high ends of the stellar mass range, as well as the enhanced rate around $10^{10}$ M$_{\odot}$.
+The model clearly diverges from the simple log-linear fit, describing better the enhanced rate around $10^{10}$ M$_{\odot}$ and surpression at high masses.
 This improvement provides evidence to support the DTD*SFH model.
@@
 A measurement of the SNuM is achieved by summing the number of SNe in each stellar mass bin, and dividing by the total stellar mass of field galaxies in that bin.
-We show the SNuM as a function of galaxy stellar mass in Fig.~ \ref{fig:snum}, along with the measurements from SNe discovered in SDSS spectra \citep{Graur2013} at $z\sim0.1$.
+We show the SNuM as a function of galaxy stellar mass in Fig.~ \ref{fig:snum}, along with the measurements from SNe discovered in SDSS spectra \citep{Graur2013} at $z\sim0.1$ and at $z\sim0$ in LOSS as presented in \citet{Li2011a}.
 We also calculate the SNuM predicuted by our model for each simulated galaxy at a range of redshifts and plot these as curves in Fig.~\ref{fig:snum}.
 Our model accurately recovers the SNuM measured in DES for the redshift and stellar mass range of the data.
-While the data from \citet{Graur2013} lies slightly higher than our model prediction, the difference is consistent with differences in assumed SFHs and stellar population templates as well as SN detection method.
+While the data from LOSS and SDSS lies slightly higher than our model prediction, the difference is consistent with differences in assumed SFHs, IMFs and stellar population templates as well as SN detection method.
+Any true difference between predicted and observed SNuM could be caused by an evolution of the SN Ia production efficiency as a function of redshift; we defer such an investigation to future work with more refined models and measurements.
 \section{The delay-time distribution as a function of supernova properties}
@@
 Our $t_1$ and $t_2$ are consistent with the transition found by \citet{Brandt2010} who found high-stretch SNe to be confined to delay times $\lesssim 0.4$~Gyr while high-stretch SNe displayed delay times $\gtrsim 2.4$~Gyr.
+On the other hand, the transition found here appears to occur at much shorter delay times than the several Gyrs found by \citet{Rose2019}.
 These results are somewhat surprising, as we might expect that the transition is not so sharp but a gradual correlation of delay time with the average stretch of SNe caused by the age vs WD-mass distribution, as predicted by \citet{Shen2021}.
@@
 
-Our transition ages $t_1$ and $t_2$
-
 \subsubsection{The late end of the DTD \label{subsubsec:subtypes}}
@@
 One possibility is that sub-luminous SNe are more numerous in such predominantly old stellar populations, such that the fraction passing our light curve cuts is lower than the rest of the sample.
-Such a phenomenon could be caused by SN Ia sub-classes such as SN 1991bg-like SNe, which are known to explode exclusively in old environments \citep{Perets2010} at delay times as long as $>6$~Gyr \citep{Panther2019}.
+Such a phenomenon could be caused by SN Ia sub-classes such as SN 1991bg-like SNe, which are known to explode exclusively in old environments \citep{Perets2010} at delay times as long as $>6$~Gyr \citep{Panther2019}, and are typically sub-luminous with fast decline rates \citep{Gonzalez-Gaitan2014}.
 If the SN 1991bg-like objects are drawn from the same parent population of WDs as the "normal" SNe Ia, they could explain the lack thereof in the sample.

### 2021-03-10 draft.tex
Updates from Overleaf

@@
 %\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-
+\defcitealias{Childress2014}{C14}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We use an empirical model of stellar mass assembly to estimate the average star-formation histories (SFHs) of galaxies across the stellar mass range of our measurement.
-Combining the modelled SFHs with the SN Ia rates to estimate constraints on the SN Ia delay time distribution (DTD), we find the data are fit well by a power-law DTD with index $\beta = -1.14 \pm 0.05$ and normalisation $A = 2.1 \pm0.05 \times 10^{-13}~\mathrm{SNe}~{\mathrm{M}_{\odot}}^{-1}~\mathrm{yr}^{-1}$.
+Combining the modelled SFHs with the SN Ia rates to estimate constraints on the SN Ia delay time distribution (DTD), we find the data are fit well by a power-law DTD with index $\beta = -1.14 \pm 0.05$ and normalisation $A = 2.1 \pm0.05 \times 10^{-13}~\mathrm{SNe}~{\mathrm{M}_{\odot}}^{-1}~\mathrm{yr}^{-1}$, which correspond to an overall SN Ia production efficiency $N_{\mathrm{Ia}}/M_* = 0.9~_{-0.7}^{+4.0} \times 10^{-3}~\mathrm{SNe}~\mathrm{M}_{\odot}^{-1}$.
 Upon splitting the SN sample by properties of the light curves, we find a strong dependence on DTD slope with the SN stretch parameter, with slower-declining SNe exhibiting a steeper DTD slope.
@@
 Conversely, it has been possible to search for surviving remnants of the binary system -- main sequence stars or WDs left behind at the SN location or kicked out at high velocity \citep[e.g.][]{Schaefer2012,Ruiz-Lapuente2018,Kerzendorf2018,Kerzendorf2019}.
-\citet{Shen2018} discovered three high-velocity WDs consistent with models of double-detonation SNe Ia.
+\citet{Shen2018} discovered three high-velocity WDs consistent with models of double-degenerate, double-detonation SNe Ia.
 However, without an unambiguous observation of a SN Ia progenitor system or remnant companion, there is as yet no direct evidence ruling out any progenitor channel from providing a significant contribution to the total population of SNe Ia.
@@
 
-\citet{Childress2014} showed that the $A+B$ approximation arises as a direct consequence of the combination of a power-law DTD with the average SFHs of galaxies -- the prompt component proportional to the amount of on-going star-formation at the epoch of observation, and the tardy component caused by the fact that massive galaxies experienced high SFRs several Gyrs ago.
+\citet[][hereafter C14]{Childress2014} showed that the $A+B$ approximation arises as a direct consequence of the combination of a power-law DTD with the average SFHs of galaxies -- the prompt component proportional to the amount of on-going star-formation at the epoch of observation, and the tardy component caused by the fact that massive galaxies experienced high SFRs several Gyrs ago.
 The recent advances of integral field spectroscopy (IFS) allows for an extension of the SFHR method, by reconstructing the SFH for hundreds or thousands of local regions of each SN Ia host galaxy.
@@
 The majority of observational evidence based on studies of SN Ia populations thus points towards a DD scenario for most, if not all, SNe Ia.
-However, finding self-consistent explosion models that recreate the observed luminosity function as well as correlations between luminosity, light curve parameters, and host galaxy properties has proven difficult.
-In particular, simulations based around explosions of $M_{\mathrm{Ch}}$ WDs fail to reproduce the observed relationship between SN luminosity and light curve duration as well as "peculiar" objects \citep{Sim2013,Blondin2017}.
-In recent years, attention directed towards explosions of sub-$M_{\mathrm{Ch}}$ WDs triggered by double detonations has led to promising results \citep[e.g.][]{Shen2017,Shen2018,Townsley2019,Gronow2020,Shen2021} although they still struggle to match observations at late times in the light curve evolution \citep{Shen2021,Gronow2021}.
-An additional factor in support of the double-detonation model is that the SN luminosity is related to the mass of the primary WD, which itself is likely to be related to its age (although this relation is probably complicated by other factors such as accretion rate, metallicity, and the composition of the companion), thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Nicolas2020}.
+However, finding self-consistent progenitor and explosion models that recreate the observed luminosity function as well as correlations between luminosity, light curve parameters, and host galaxy properties has proven difficult.
+In particular, simulations based around explosions of $M_{\mathrm{Ch}}$ WDs (linked strongly with the SD scenario but also with many DD scenarios) find difficulty in reproducing the light curves of "normal" SNe Ia as well as "peculiar" objects (\citealt{Ropke2007,Sim2013,Blondin2017}; see \citealt{Maoz2014,Jha2019} for overviews).
+In recent years, attention directed towards explosions of sub-$M_{\mathrm{Ch}}$ WDs triggered by double detonations (primarily related to a DD scenario) has led to promising results \citep[e.g.][]{Shen2017,Shen2018,Townsley2019,Gronow2020,Shen2021} although they still struggle to match observations at late times in the light curve evolution \citep{Shen2021,Gronow2021}.
+An additional factor in support of the double-detonation model is that the SN luminosity is related to the mass of the primary WD, which itself is likely to be related to its age (although this relation is probably complicated by other factors such as accretion rate, metallicity, and the composition of the companion), thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Rose2019,Nicolas2020}.
 
@@
 Instead of measuring the volumetric rate of SNe Ia, we measure the rate per galaxy as a function of stellar mass, as per \citet{Sullivan2006,Smith2012}.
-We use the stellar mass assembly model of \citet{Childress2014} to predict the stellar age distribution of galaxies for a given stellar mass at the mean redshift of our SN sample, and then forward model the DTD by convolving it with the stellar age distribution and comparing the predicted rates to the observed rates.
-
-In Section \ref{sec:data} we introduce our large sample of SNe Ia from the Dark Energy Survey as well as our deep sample of field galaxies.
-We describe our detailed handling of incompleteness in Section \ref{sec:incompleteness}.
-We present the SN Ia rate per galaxy in Section \ref{sec:rates}.
+We use the stellar mass assembly model of \citetalias{Childress2014} to predict the stellar age distribution of galaxies for a given stellar mass at the mean redshift of our SN sample, and then forward model the DTD by convolving it with the stellar age distribution and comparing the predicted rates to the observed rates.
+
+In Section \ref{sec:data} we introduce our large sample of SNe Ia from the Dark Energy Survey (DES) as well as our deep sample of field galaxies that provide an effectively complete control sample from which to measure the rate.
+We describe our detailed handling of SN and galaxy incompleteness in Section \ref{sec:incompleteness}.
+We present the SN Ia rate per galaxy in Section \ref{sec:rates} and show that it is consistent with previous works.
 We outline our modelling of star-formation histories and our novel measurement of the power-law DTD in Section \ref{sec:model}.
 In Section \ref{sec:split_x1_c} we investigate how the DTD differs among sub-populations of SNe with different light curve characteristics, in particular the stretch, and show stretch to be strongly dependent on progenitor age.
-We conclude in Section \ref{sec:conclusion} by discussing the implications of the result.
+We conclude in Section \ref{sec:conclusion} by discussing the implications of the results.
 Where relevant, we assume a spatially flat $\Lambda$CDM cosmology with $\Omega_m = 0.3$ and $H_0 = 70 \mathrm{ km s}^{-1}\mathrm{Mpc}^{-1}$.
-Unless otherwise stated, we assume Gaussian measurement uncertainties quoted at the $1\sigma$ level, and we quote $1\sigma$ credible intervals on derived parameters.
+Unless otherwise stated, we assume Gaussian measurement uncertainties quoted at the $1\sigma$ level, and we quote the posterior median and $1\sigma$ credible intervals on derived parameters.
 Magnitudes are quoted in the AB system \citep{Oke1983}.
@@
 With over 30,000 transients passing ML selection it was not possible to obtain spectral follow up of every object.
-Instead we make use of photometric classification in the form of the recurrent neural network classifier \texttt{superNNova} (SNN; \citealt{Moller2019}), mirroring the approach of \citet{Scolnic2020}.
+Instead we make use of photometric classification in the form of the recurrent neural network classifier \texttt{superNNova} (SNN; \citealt{Moller2019}), foloowing the approach of \citet{Scolnic2020}.
+A full description of the training and fitting of SNN will be presented in Vincenzi et al.
+\textit{in prep} and M\"{o}ller et al.
+\textit{in prep}; we provide a brief overview here.
+
 We train SNN using a large suite of simulated multi-band SN light curves.
-\textbf{Waiting on final sample and a few words from Maria/Anais to complete this bit.} SNe Ia are simulated based on the \texttt{SALT2} model \citep{Guy2007} trained on the Joint Lightcurve Analysis (JLA) data set \citep{Betoule2014}.
+SNe Ia are simulated based on the \texttt{SALT2} model \citep{Guy2007} trained on the Joint Lightcurve Analysis (JLA) data set \citep{Betoule2014}.
 Synthetic CCSNe light curves are generated from the templates of \citet{Vincenzi2019}.
@@
 This selection helps to reduce the potential contamination from core-collapse SNe (CCSNe) and outlying thermonuclear SNe.
-We impose further cuts on the quality of those measured parameters, which are: the uncertainty on $x_1$: $\sigma_{x_1} <1$; the uncertainty on the date at which the light curve peaked: $\sigma_{t_{\mathrm{peak}}} <2$; the SALT2 fit probability $>0.001$.
+We impose further cuts on the quality of those measured parameters, which are: the uncertainty on $x_1$: $\sigma_{x_1} <1$; the uncertainty on the date at which the light curve peaked: $\sigma_{t_{\mathrm{peak}}} <2$; the SALT2 fit probability $>0.01$.
 The number of SNe passing each stage of these cuts is displayed in Table 2 of \citet{Vincenzi2020} and reduces the $\sim30,000$ objects to 1604 SNe.
 With the addition of the photometric classifier we are left with 1441 SNe with which we proceed to inspect their host galaxies.
+While the inclusion of stringent cuts significantly reduces the size of the sample, it greatly enhances the purity and is in line with previous rates analyses of this nature \citep{Sullivan2006} as well as being consistent with other DES-SN analyses \citep[e.g.][]{Kelsey2021}.
 
@@
 
-We estimate global galaxy properties for both the SN host and field galaxies that pass the quality cuts by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{kelsey2021,Smith2020,Wiseman2020}.
+We estimate global galaxy properties for both the SN host and field galaxies that pass the quality cuts by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{Kelsey2021,Smith2020,Wiseman2020}.
 For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists in the OzDES GRC, or more commonly the photometrically derived value.
@@
 These values are consistent with the value at which 50\% of the true sources are detected but have the advantage of being derived from the data without a simulation that is based on assumptions and thus susceptible to bias.
-
 \subsubsection{$V_{\mathrm{max}}$ correction \label{subsubsec:vmax_corr}}
@@
 Vertical error bars are estimated via a Monte-Carlo resampling of the rate given the uncertainties in stellar mass.
-The linear fit is based on all but the lowest and highest mass bins, and takes into account uncertainties in the rate.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+The linear fit is based on all but the lowest and highest mass bins, and takes into account uncertainties in the rate.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
     \label{fig:rate_raw}
@@
 %    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_split_sfr.png}
-%    \caption{The rate per galaxy of SNe Ia as a function of stellar mass for moderately and highly star-forming galaxies, as well as passive galaxies.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+%    \caption{The rate per galaxy of SNe Ia as a function of stellar mass for moderately and highly star-forming galaxies, as well as passive galaxies.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
 %    \label{fig:rate_raw_split_sfr}
@@
     \includegraphics[width=\textwidth]{figs/SFHs_colour.png}
-    \caption{The stellar mass assembly of the Universe as prescribed by the toy model of \citet{Childress2014}.
+    \caption{The stellar mass assembly of the Universe as prescribed by the toy model of \citetalias{Childress2014}.
 Galaxies with high stellar mass at $z=0$ formed the majority of their stars in the distant past, while lower-mass galaxies are still actively star forming in the present day.}
@@
     \includegraphics[width=.5\textwidth]{figs/CSFH_MD14.png}
-    \caption{Cosmic star-formation history (CSFH) as approximated by our model (cyan curve) and as a best fit to observations \citep{Madau2014}.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    \caption{Cosmic star-formation history (CSFH) as approximated by our model (cyan curve) and as a best fit to observations \citep{Madau2014}.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
     \label{fig:csfh}
@@
     \caption{Posterior distributions for DTD slope $\beta$ and normalisation $A$.
-Displayed point estimates represent the median of the posterior samples.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+Displayed point estimates represent the median of the posterior samples.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
     \label{fig:corner_beta_norm}}
@@
 Displayed point estimates represent the median of the posterior samples.
-    %The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+    %The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
     \label{fig:corner_beta_norm_tp}}
@@
 \ref{eq:galaxy_rate}.
-Samples from the posterior distribution of the model log rate are drawn in cyan while the black dashed line is the mean of the posterior.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+Samples from the posterior distribution of the model log rate are drawn in cyan while the black dashed line is the mean of the posterior.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
     \label{fig:rate_fitted}}
@@
 SDSS data (orange squares) are taken from \citet{Graur2013}.
-The systematically higher SNuM in DES is caused by the higher redshift of the sample, as illustrated by the DTD model prediction (coloured curves) }%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+The systematically higher SNuM in DES is caused by the higher redshift of the sample, as illustrated by the DTD model prediction (coloured curves) }%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
     \label{fig:snum}
@@
 
-To model the SFH of galaxies as a function of their stellar mass we adopt the prescription of stellar mass assembly of \citet{Childress2014}, which draws on the work of \citet{Zahid2012}.
+To model the SFH of galaxies as a function of their stellar mass we adopt the prescription of stellar mass assembly of \citetalias{Childress2014}, which draws on the work of \citet{Zahid2012}.
 In the model, galaxies are expected to evolve smoothly along the so-called "main sequence of star formation" whereby the SFR of a galaxy of stellar mass $M_*$ at redshift $z$ is determined by a simple relationship (the SMz relation, \citealt{Zahid2012}).
@@
 
-As galaxies grow, their SFR begins to slow down and eventually shut off almost entirely in a process known as quenching. We adopt the quenching penalty $p_Q$ directly from \citet{Childress2014}:
+As galaxies grow, their SFR begins to slow down and eventually shut off almost entirely in a process known as quenching. We adopt the quenching penalty $p_Q$ directly from \citetalias{Childress2014}:
 \begin{equation}
@@
 Finally, at time $t$, some time $\tau$ since an epoch of star formation, a fraction of stellar mass is lost.
-We adopt the parametrization used by \citet{Childress2014}, namely that of \citet{Leitner2011} for a Chabrier 2003 IMF:
+We adopt the parametrization used by \citetalias{Childress2014}, namely that of \citet{Leitner2011} for a Chabrier 2003 IMF:
 
@@
 
-As per \citet{Childress2014} we plant seed galaxies with initial masses of $10^6 ~\mathrm{M}_{\odot}$ at intervals of 50 Myr for look-back times $1 \leq t_f \leq 10$ Gyr, and 25 Myr for look-back times $10 \leq t_f \leq 13$ Gyr to achieved a more detailed model at early times with high SFR.
+As per \citetalias{Childress2014} we plant seed galaxies with initial masses of $10^6 ~\mathrm{M}_{\odot}$ at intervals of 50 Myr for look-back times $1 \leq t_f \leq 10$ Gyr, and 25 Myr for look-back times $10 \leq t_f \leq 13$ Gyr to achieved a more detailed model at early times with high SFR.
 For each seed galaxy, we evaluate Eq.
@@
 
-As noted in \citet{Childress2014}, this toy model by construction follows several empirical relations derived from galaxy observations: model galaxies follow the SMz relation and obey quenching prescriptions motivated by observed galaxies.
+As noted in \citetalias{Childress2014}, this toy model by construction follows several empirical relations derived from galaxy observations: model galaxies follow the SMz relation and obey quenching prescriptions motivated by observed galaxies.
 Here we make two further checks to validate to show that the model can be used to approximate the stellar age distribution of SN Ia host galaxies in DES.
 
-Firstly, we follow \citet{Childress2014} by summing our SFHs and weighting by the galaxy stellar mass function at $z=0$ to estimate the CSFH.
+Firstly, we follow \citetalias{Childress2014} by summing our SFHs and weighting by the galaxy stellar mass function at $z=0$ to estimate the CSFH.
 We approximate the present-day stellar mass function according to a double Schechter function with parameters from the Galaxy and Mass Assembly survey \citet{Baldry2018}: $\log(M^*)=10.66$, $\phi^*_1=3.96\times10^{-3}$, $\alpha_1=-0.35$, $\phi^*_2=0.79\times10^{-3}$, $\alpha_2=-1.47$.
@@
 \ref{fig:csfh}.
-As was found in \citet{Childress2014}, the two functions show a good qualitative agreement -- in fact, we find a closer match between the model and observed CSFH, accurately reproducing the peak of cosmic star formation around $z\sim2$ and tracing the declining SFR to the present day.
+As was found in \citetalias{Childress2014}, the two functions show a good qualitative agreement -- in fact, we find a closer match between the model and observed CSFH, accurately reproducing the peak of cosmic star formation around $z\sim2$ and tracing the declining SFR to the present day.
 
@@
 \ref{fig:rate_fitted} but with the data split by their stretch parameter $x_1$.
-Fits were performed with the DTD slope $\beta$ and normalisation $A$ as free parameters, and prompt time $t_{\mathrm{p}}$ fixed at 0.04 Gyr.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+Fits were performed with the DTD slope $\beta$ and normalisation $A$ as free parameters, and prompt time $t_{\mathrm{p}}$ fixed at 0.04 Gyr.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
     \label{fig:rate_fitted_split_x1}}
@@
 It is possible that this transition is too narrow and that quenching happens too fast in our model, leading to an under-prediction of the prompt fraction of SNe in the highest mass galaxies.
-To address this issue we rerun the mass assembly model with $\sigma_{\mathrm{Q}} = 1.5$ as per the nominal analysis of \citet{Childress2014} and refit the SN Ia rate data.
+To address this issue we rerun the mass assembly model with $\sigma_{\mathrm{Q}} = 1.5$ as per the nominal analysis of \citetalias{Childress2014} and refit the SN Ia rate data.
 We find that the adapted quenching model does not change the ability of the model to adequately fit the high-mass turnover in the SN rate.
@@
     \caption{As per Fig.
-\ref{fig:rate_fitted_split_x1} but with the data fit simultaneously by a single two-component DTD, with fixed slope $\beta = -1$ and a prompt fraction that is 1 at short delay times, 0 at large delay times, and a linear function of time between $t_1$ and $t_2$.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+\ref{fig:rate_fitted_split_x1} but with the data fit simultaneously by a single two-component DTD, with fixed slope $\beta = -1$ and a prompt fraction that is 1 at short delay times, 0 at large delay times, and a linear function of time between $t_1$ and $t_2$.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
     \label{fig:rate_fitted_split_x1_2c_DTD}}
@@
     \caption{As per Fig.
-\ref{fig:rate_fitted_split_x1} but with the data split by their colour parameter $c$.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citet{Childress2014} model}
+\ref{fig:rate_fitted_split_x1} but with the data split by their colour parameter $c$.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
     \label{fig:rate_fitted_split_c}}
@@
 Although this is where the data is noisiest, it is worth investigating the possible causes of this divergence.
-A slight preference for SN to be bluer in lower-mass galaxies has been observed \citep{Scolnic2018,Brout2019,Smith2020,kelsey2021} and could be the same effect seen at low stellar masses here.
+A slight preference for SN to be bluer in lower-mass galaxies has been observed \citep{Scolnic2018,Brout2019,Smith2020,Kelsey2021} and could be the same effect seen at low stellar masses here.
 Physically, the dominance of blue SNe at low stellar masses could either be an intrinsic property of the SNe such as a hotter photosphere in explosions of younger, more massive progenitors, or an extrinsic effect such as a lower average dust column density in low-mass host galaxies.
@@
 
-\item By simulating the stellar mass assembly of average galaxies across cosmic time following the prescription of \citet{Childress2014} we have recovered an estimate of the SN Ia DTD, finding a good fit to a power-law distribution with an index of $-1.14 \pm0.05$.
+\item By simulating the stellar mass assembly of average galaxies across cosmic time following the prescription of \citetalias{Childress2014} we have recovered an estimate of the SN Ia DTD, finding a good fit to a power-law distribution with an index of $-1.14 \pm0.05$.
 Our measurement of the DTD is fairly consistent with previous measurements \citep[e.g.][]{Graur2013,Maoz2017} and carries signatures predicted by the DD scenario for SNe Ia production.
@@
 %\label{appendix:model_adjustments}
-%In Section \ref{sec:model} we describe our toy model of galaxy SFHs based on the work of %\citet{Childress2014}. Here we
+%In Section \ref{sec:model} we describe our toy model of galaxy SFHs based on the work of %\citetalias{Childress2014}. Here we
 

### 2021-03-11 draft.tex
Updates from Overleaf

@@
 \begin{abstract}
-We use a sample of 881 photometrically classified type Ia supernovae (SNe Ia) discovered by the Dark Energy Survey (DES) in the redshift range $0.2 < z <0.6$, along with 40415 field galaxies to calculate the rate of SNe Ia per galaxy.
-We recover the established positive trend of SN Ia rate as a function of galaxy stellar mass across a broad range of scales $8.5 \leq \log(M_*/\mathrm{M}_{\odot}) \leq 11.25$.
-We find that the SN Ia rate increases with stellar mass roughly linearly in log space, with a slope of $0.63 \pm 0.02$, which is consistent with previous work.
+We use a sample of 809 photometrically classified type Ia supernovae (SNe Ia) discovered by the Dark Energy Survey (DES) along with 40415 field galaxies to calculate the rate of SNe Ia per galaxy in the redshift range $0.2 < z <0.6$.
+We recover the positive trend of SN Ia rate as a function of galaxy stellar mass across a broad range of scales $8.5 \leq \log(M_*/\mathrm{M}_{\odot}) \leq 11.25$.
+We find that the SN Ia rate increases with stellar mass as a power-law with index $0.63 \pm 0.02$, which is consistent with previous work.
 We use an empirical model of stellar mass assembly to estimate the average star-formation histories (SFHs) of galaxies across the stellar mass range of our measurement.
 Combining the modelled SFHs with the SN Ia rates to estimate constraints on the SN Ia delay time distribution (DTD), we find the data are fit well by a power-law DTD with index $\beta = -1.14 \pm 0.05$ and normalisation $A = 2.1 \pm0.05 \times 10^{-13}~\mathrm{SNe}~{\mathrm{M}_{\odot}}^{-1}~\mathrm{yr}^{-1}$, which correspond to an overall SN Ia production efficiency $N_{\mathrm{Ia}}/M_* = 0.9~_{-0.7}^{+4.0} \times 10^{-3}~\mathrm{SNe}~\mathrm{M}_{\odot}^{-1}$.
-Upon splitting the SN sample by properties of the light curves, we find a strong dependence on DTD slope with the SN stretch parameter, with slower-declining SNe exhibiting a steeper DTD slope.
-We interpret this as a result of a relationship between stretch and progenitor age, and explore the implications of the result in the context of SN Ia progenitors.
+Upon splitting the SN sample by properties of the light curves, we find a strong dependence on DTD slope with the SN decline rate, with slower-declining SNe exhibiting a steeper DTD slope.
+We interpret this as a result of a relationship between intrinsic luminosity and progenitor age, and explore the implications of the result in the context of SN Ia progenitors.
 \end{abstract}
@@
 Type Ia supernovae (SNe Ia) are explosions of white dwarf stars (WDs).
-Although SNe Ia show diversity in their observed properties, a large fraction of them display a small dispersion in their peak brightnesses which can be reduced further through empirical relations between brightness and light curve properties, such as decline rate (stretch) or optical colour \citep{Rust1974,Pskovskii1977,Phillips1993,Tripp1998}.
+Although SNe Ia show diversity in their observed properties, a large fraction of them ("non-peculiar" SNe Ia) display a small dispersion in their peak brightnesses which can be reduced further through empirical relations between brightness and light curve properties, such as decline rate (stretch) or optical colour \citep{Rust1974,Pskovskii1977,Phillips1993,Tripp1998}.
 These properties have led SNe Ia to be used extensively by cosmologists to measure relative distances in the Universe \citep{Riess1998,Perlmutter1999}.
@@
 Conversely, it has been possible to search for surviving remnants of the binary system -- main sequence stars or WDs left behind at the SN location or kicked out at high velocity \citep[e.g.][]{Schaefer2012,Ruiz-Lapuente2018,Kerzendorf2018,Kerzendorf2019}.
-\citet{Shen2018} discovered three high-velocity WDs consistent with models of double-degenerate, double-detonation SNe Ia.
+Promising recent results include that from \citet{Shen2018} who discovered three high-velocity WDs consistent with models of double-degenerate, double-detonation SNe Ia.
 However, without an unambiguous observation of a SN Ia progenitor system or remnant companion, there is as yet no direct evidence ruling out any progenitor channel from providing a significant contribution to the total population of SNe Ia.
@@
 Another method of inferring progenitor channels is the study of the SN Ia delay time distribution (DTD).
-The DTD describes the rate at which SNe Ia occur as a function of the delay time $\tau$ since an episode of star-formation, and thus carries characteristic signatures of the progenitor channel (see \citealt{Wang2012} for a review of the theory, and \citet{Maoz2017} for a review of observations).
+The DTD describes the rate at which SNe Ia occur as a function of the delay time $\tau$ since an episode of star-formation, and thus carries characteristic signatures of the progenitor channel (see \citealt{Wang2012} for a review of the theory, and \citealt{Maoz2017} for a review of observations).
 The SD scenario produces a broad range of functional forms for the DTD, most of which fail to account for long delay times \citep{Graur2014}.
@@
 \citet[][hereafter C14]{Childress2014} showed that the $A+B$ approximation arises as a direct consequence of the combination of a power-law DTD with the average SFHs of galaxies -- the prompt component proportional to the amount of on-going star-formation at the epoch of observation, and the tardy component caused by the fact that massive galaxies experienced high SFRs several Gyrs ago.
-The recent advances of integral field spectroscopy (IFS) allows for an extension of the SFHR method, by reconstructing the SFH for hundreds or thousands of local regions of each SN Ia host galaxy.
+Recent advances in integral field spectroscopy (IFS) allow for an extension of the SFHR method, by reconstructing the SFH for hundreds or thousands of local regions of each SN Ia host galaxy.
 Using this method, \citet{Castrillo2020} find a power-law slope of $-1.1\pm0.3$, while \citet{Chen2021} find $-1.4\pm0.3$.
@@
 In recent years, attention directed towards explosions of sub-$M_{\mathrm{Ch}}$ WDs triggered by double detonations (primarily related to a DD scenario) has led to promising results \citep[e.g.][]{Shen2017,Shen2018,Townsley2019,Gronow2020,Shen2021} although they still struggle to match observations at late times in the light curve evolution \citep{Shen2021,Gronow2021}.
-An additional factor in support of the double-detonation model is that the SN luminosity is related to the mass of the primary WD, which itself is likely to be related to its age (although this relation is probably complicated by other factors such as accretion rate, metallicity, and the composition of the companion), thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Rose2019,Nicolas2020}.
+An additional factor in support of the sub-$M_{\mathrm{Ch}}$ model is that the SN luminosity is related to the mass of the primary WD, which itself is likely to be related to its age (although this relation is probably complicated by other factors such as accretion rate, metallicity, and the composition of the companion), thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Rose2019,Nicolas2020}.
+With many models showing promising similarities to observations but each subject to its own drawbacks, it is becoming accepted that more than one progenitor scenario may contribute significantly to the overall population of "normal" SNe Ia; detailed observations are thus required in order to place constraints on the relative fractions of each possible progenitor channel.
 
@@
 We present the SN Ia rate per galaxy in Section \ref{sec:rates} and show that it is consistent with previous works.
-We outline our modelling of star-formation histories and our novel measurement of the power-law DTD in Section \ref{sec:model}.
+We outline our modelling of star-formation histories and our novel constraints on the DTD parameters in Section \ref{sec:model}.
 In Section \ref{sec:split_x1_c} we investigate how the DTD differs among sub-populations of SNe with different light curve characteristics, in particular the stretch, and show stretch to be strongly dependent on progenitor age.
 We conclude in Section \ref{sec:conclusion} by discussing the implications of the results.
-Where relevant, we assume a spatially flat $\Lambda$CDM cosmology with $\Omega_m = 0.3$ and $H_0 = 70 \mathrm{ km s}^{-1}\mathrm{Mpc}^{-1}$.
+Where relevant, we assume a spatially flat $\Lambda$CDM cosmology with $\Omega_m = 0.3$ and $H_0 = 70 \mathrm{~km~s}^{-1}~\mathrm{Mpc}^{-1}$.
 Unless otherwise stated, we assume Gaussian measurement uncertainties quoted at the $1\sigma$ level, and we quote the posterior median and $1\sigma$ credible intervals on derived parameters.
@@
 	    $m_r \leq 24.5$ & 196109 &  1254 \\
-	    $0.2 \leq z \leq 0.6$ & 48177 & 881\\
+	    $0.2 \leq z \leq 0.6$ & 48177 & 809\\
 
@@
 
-In order to measure the rate of SNe Ia per galaxy per year, we require a sample of SNe Ia and a sample of field galaxies that are normalised to the same selection criteria -- the final rate calculation must be corrected for differences in sky area, redshift depth, and survey time.
-In this section, we introduce our SN and field galaxy samples.
+%In an ideal rate measurement a volume-limited and complete sample of galaxies would be observed for a given time, and the number of SNe observed in each galaxy simply counted.
+In practice, apart from at very low redshift where the absolute numbers do not support robust statistical analyses, this is not possible: SNe are detected, classified and followed up based on complicated selection criteria; galaxy surveys are incomplete at faint magnitudes; the timescale of observing seasons cuts off SNe at the beginning and end of each season.
+In order to measure the rate of SNe Ia per galaxy per year, we require a sample of SNe Ia, as well as a sample of all of the possible galaxies ("field" galaxies) that those SNe could have exploded in.
+In practice, SN and galaxy surveys do not cover the same sky area, redshift ranges, times, and have different selection biases.
+In this section, we introduce our SN and field galaxy samples and in Section \ref{sec:incompleteness} we describe our method of correcting the selection effects for both the SN and field galaxy samples.
 
@@
 \subsection{Dark Energy Survey supernova programme \label{subsec:des}}
-The Dark Energy Survey Supernova Programme (DES-SN) is a transient survey based on five six-month seasons of observations with the Dark Energy Camera (DECam; \citealt{Flaugher2015}), designed primarily to measure the light curves of SNe Ia for use as cosmological distance indicators.
+To derive our sample of SNe and field galaxies, we make use of the Dark Energy Survey (DES).
+The DES Supernova Programme (DES-SN) was a transient survey based on five six-month seasons of observations of ten southern hemisphere fields with the Dark Energy Camera (DECam; \citealt{Flaugher2015}), designed primarily to measure the light curves of SNe Ia for use as cosmological distance indicators.
 Transients were detected and processed using a difference imaging program \citep{Kessler2015} and vetted using a machine learning (ML) algorithm \citep{Goldstein2015}.
@@
 Y3A2\_DEEP makes use of the same deep DES optical photometry that was used in SN Deep for a subset of the fields (SN-X3, SN-C3 and SN-E2), but adds DECam $u$-band data and near-infrared (NIR) $J$, $H$, and $K$-band imaging from the ultraVISTA and VIDEO surveys.
-The deep optical photometry in Y3A2\_DEEP was stacked using a different technique to that of SN Deep, but the resulting photometry is consistent within $1\sigma$ uncertainties \citep{Wiseman2020}.
-\citet{Hartley2020} estimated photo-$z$'s using the \texttt{eaZy} code \citep{Brammer2008}.
+The deep optical photometry in Y3A2\_DEEP was stacked using a different technique to that of SN Deep, but the resulting photometry is consistent within $1\sigma$ uncertainties (\citealt{Wiseman2020},Meledorf et al.
+\textit{in prep}).
+\citet{Hartley2020} estimated photo-$z$s using the \texttt{eaZy} code \citep{Brammer2008}.
 Photo-$z$ accuracy from \citet{Hartley2020} at $17 < i<24$ is estimated around 0.03 as quantified by the Normalised Absolute Median Deviation (NMAD).
@@
     \includegraphics[width=.5\textwidth]{figs/mass_hist_linlog_sn_field_BC03.png}
-    \caption{Upper: Distribution of the stellar mass of the SN host (green dot-dashed) and field galaxies (orange solid) used in the analysis.
+    \caption{Upper: Distribution of the stellar mass of the SN host (green dot-dashed) and field galaxies (orange and grey solid) used in the analysis.
 Lower: As upper for field galaxies, but shown on a log scale.
-The distribution closely matches data from the ZFOURGE survey at $0.2<z<0.5$ (cyan dashes) and $0.5<z<0.75$ (magenta dots).}
-    \label{fig:mass_hist_hosts_field}
+The distribution closely matches data from the ZFOURGE survey at $0.5<z<0.75$ (magenta dots).
+The difference between the raw counts and the $V_{\mathrm{max}}$ corrected counts (Section \ref{sec:incompleteness}) is minimal.
+    \label{fig:mass_hist_hosts_field}}
 \end{figure}
@@
 
-    \item field galaxies are limited to unmasked region of the SN-X3 chip \citep{Hartley2020};
+    \item field galaxies are limited to unmasked region of the SN-X3 field \citep{Hartley2020};
 
@@
 
-    \item to minimise stellar contamination, objects must have a value of 0.95 in the star/galaxy (S/G) separation \texttt{CLASS\_STAR} provided by \texttt{Source Extractor} \citep{Bertin1996};
+    \item to minimise stellar contamination, objects must have a value of $<0.95$ in at least one band for the star/galaxy (S/G) separation metric \texttt{CLASS\_STAR} provided by \texttt{Source Extractor} \citep{Bertin1996};
 
@@
 
-    \item objects must have a spectroscopic redshift measurement or a converged photometric redshift estimate;
+    \item objects must have a spectroscopic redshift measurement or a photometric redshift estimate with a well-defined peak in redshift  probability density;
 
@@
 The numbers of SN hosts and field galaxies passing these cuts are listed in Table \ref{tab:cuts}.
-The final samples comprise 881 SNe and their host galaxies and 40,415 field galaxies.
+The final samples comprise 809 SNe and their host galaxies and 40,415 field galaxies.
 The volume-weighted mean redshifts are 0.50 for both SNe and field galaxies.
@@
 
-We estimate global galaxy properties for both the SN host and field galaxies that pass the quality cuts by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{Kelsey2021,Smith2020,Wiseman2020}.
+We estimate global galaxy properties for both the SN host and field galaxies that pass the quality cuts by fitting the photometry with stellar population templates in a method outlined by \citet{Sullivan2006} and consistent to that used in previous DES-SN analyses \citep{Smith2020,Wiseman2020,Kelsey2021}.
 For SN hosts the redshift is fixed at the spectroscopically determined value, while for field galaxies we fix it at either the spectroscopic value if one exists in the OzDES GRC, or more commonly the photometrically derived value.
@@
 The fitting procedure returns a best fitting template and corresponding stellar mass ($M_*$).
-Upper and lower bounds on stellar mass estimates are taken as the extrema in the model parameters that are consistent with the data (given the photometric uncertainties) according to their $\chi^2$ statistic, as per \citet{Sullivan2006}.
+Upper and lower bounds on stellar mass estimates are taken as the extreme values that correspond to templates that are consistent with the data (given the photometric uncertainties) according to their $\chi^2$ statistic, as per \citet{Sullivan2006}.
 To check that the choice of templates does not bias the result, we also fit the galaxies using the P\'EGASE.2 templates \citep{Fioc1997,LeBorgne2002} and a \citet{Kroupa2001} IMF, and find results consistent within measurement uncertainties.
@@
 However, both the SN and field galaxy samples introduced in Sections \ref{subsec:host_sample} and \ref{subsec:field_sample} are affected by incompleteness, which is likely to be the dominant systematic effect in the analysis.
-In this section we describe our method of correcting for various sources incompleteness in the data.
+In this section we describe our method of correcting for various sources of incompleteness in the data.
 
@@
 We run a suite of simulations using an identical method to that described in detail in \citet{Vincenzi2020}.
-We simulate SNe using the SuperNova ANAlysis software (\texttt{SNANA} \citealt{Kessler2009a}) integrated into the \texttt{pippin} framework \citep{Hinton2020}.
-We simulate \textbf{size of final sim} SNe in the redshift range $0.05 \leq z_{\mathrm{SN}} \leq 1.3$.
+We simulate SNe using the SuperNova ANAlysis software (\texttt{SNANA}; \citealt{Kessler2009a}) integrated into the \texttt{pippin} framework \citep{Hinton2020}.
+We simulate $1.1\times 10^6$ SNe in the redshift range $0.05 \leq z_{\mathrm{SN}} \leq 1.3$.
 The SNe are generated and trained in the same way as for the training of SNN.
@@
 The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citet{Vincenzi2020} who provide the spectroscopic redshift efficiency as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey.
-So that we reduce any bias towards SNe in bright hosts that are easier to obtain spectroscopic redshifts for, the host galaxy spectroscopic redshift efficiency is multiplied by that derived from the SN detection efficiency (Section \ref{subsec:incompleteness_SNe}) to arrive at the final SN efficiency $\eta_{\mathrm{SN},i}$.
+So that we reduce any bias towards SNe in bright hosts that are easier to obtain spectroscopic redshifts for, the host galaxy spectroscopic redshift efficiency is multiplied by that derived from the SN detection efficiency (Section \ref{subsec:incompleteness_SNe}) to arrive at the final efficiency for the $i$th SN, $\eta_{\mathrm{SN},i}$.
 
@@
 A correction of $V_{\mathrm{survey}}/V_{\mathrm{max}}$ is applied to all galaxies for which $V_{\mathrm{max}} < V_{\mathrm{survey}}$, where $V_{\mathrm{survey}}$ is the maximum volume reached by the survey.
-In our case this corresponds to the volume at $z=0.8$.
+In our case this corresponds to the volume at $z=0.6$.
 Fig \ref{fig:vmax_field} shows the distribution of the correction among galaxies in the sample.
@@
 Roughly 1\% of objects have a correction greater than 1, with the distribution well described by a power-law function.
+The effect of the $V_{\mathrm{max}}$ correction on the total galaxy counts in each stellar mass bin can be seen in Fig.
+\ref{fig:mass_hist_hosts_field}; indeed, the two histograms are visibly indistinguishable above $10^9~\mathrm{M}_{\odot}$ which indicates a sample that is effectively complete in this mass range in the redshift range of interest.
 
@@
 
-%\textbf{TEMPTED TO DITCH THIS SINCE OUR SFR IS SKETCHY}
-%In order to make a more detailed comparison of our results with those of \citet{Sullivan2006} and \citet{Smith2012}, we split galaxies according to their sSFR: galaxies with sSFR$\leq -11.5$ yr$^{-1}$ are denoted as passive, those with $-11.5 < \mathrm{sSFR} \leq -9.5$ are moderately star-forming, and those with sSFR $>-9.5$ are labelled as highly star-forming.
-The results when split this way are shown in Fig.
-\ref{fig:rate_raw_split_sfr}.
-Star-forming galaxies show a steeper slope than their passive counterparts, with values of $1.10 \pm 0.05$ and $0.84 \pm 0.04$ for moderate and highly star-forming galaxies respectively, while passive galaxies show a much shallower slope of $0.55 \pm 0.08$.
-These values are broadly similar to those measured in SDSS by \citet{Smith2012}, with star-forming galaxies showing steeper slopes than passives (\citet{Smith2012} found 1.01 and 0.72 for SF and passive, respectively).
-We note that we detect no passive galaxies with mass below $10^{10} \mathrm{M}_{\odot}$.
-Above this value, the \citet{Smith2012} data for passive galaxies is considerably flatter than that which we measure.
-On the other hand our results are inconsistent with those found at a similar redshift to the DES data in SLNS \citep{Sullivan2006}, who measured a slope of 1.10 in passives but 0.66 and 0.74 in moderate and highly star-forming galaxies respectively.
-We note that the moderately star-forming slope is thus consistent between DES and SNLS, but the slopes of passive and highly star-forming galaxies are swapped.
 \renewcommand{\arraystretch}{1.2}

### 2021-03-15 draft.tex
Updates from Overleaf

@@
 
-To correct for these incompleteness, we follow a similar method to that used in the Palomar Transient Factory rates analyses of \citet{Frohmaier2019} and \citet{Frohmaier2020}.
+To correct for these incompleteness, we follow a similar method to that used in the Palomar Transient Factory rates analyses of \citet{Frohmaier2019} and \citet{Frohmaier2020}, outlined in \citet{Frohmaier2017}.
 We run a suite of simulations using an identical method to that described in detail in \citet{Vincenzi2020}.

### 2021-03-15 draft.tex
Updates from Overleaf

@@
 \ref{fig:mass_hist_hosts_field}.
-The upper panel, with both the SN hosts and field galaxies displayed, shows the vastly different distributions of the two samples.
+The figure showcases the vastly different distributions of the two samples.
 SN hosts are preferentially high mass galaxies, whereas the field galaxy distribution increases down to lower masses, peaking around $10^{8.5}~\mathrm{M}_{\odot}$.
-In the bottom panel, the same field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass function (SMF) from the ZFOURGE survey \citep{Tomczak2014}, whose stellar masses are derived with the same photo-$z$ code, IMF and template library as used here.
-Above $10^{8.5}~\mathrm{M}_{\odot}$, the DES field galaxy distribution closely follows the ZFOURGE SMF for $0.5<z<0.75$, indicating that the DES sample is representative of field galaxies in this redshift range.%To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit.
+The SN host stellar mass distribution is plotted twice: once as raw counts; once weighted by the host galaxy spectroscopic efficiency (Section \ref{subsec:incompletenss_SN_hosts}).
+The field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass function (SMF) from the ZFOURGE survey \citep{Tomczak2014} scaled to match at $\log (M/\mathrm{M}_{\odot}) = 10$, whose stellar masses are derived with the same photo-$z$ code, IMF and template library as used here.
+Above $10^{8.5}~\mathrm{M}_{\odot}$, the DES field galaxy distribution closely follows the ZFOURGE SMF for $0.5<z<0.75$, indicating that the DES sample is representative of field galaxies in this mass and redshift range.%To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit.
 This procedure is repeated 1000 times.
@@
 The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citet{Vincenzi2020} who provide the spectroscopic redshift efficiency as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey.
+The effects of the host galaxy spectroscopic efficiency are displayed in the upper panel of Fig.
+\ref{fig:mass_hist_hosts_field}, where the normalised histogram weighted by the efficiency is skewed towards lower masses when compared to the unweighted distribution.
 So that we reduce any bias towards SNe in bright hosts that are easier to obtain spectroscopic redshifts for, the host galaxy spectroscopic redshift efficiency is multiplied by that derived from the SN detection efficiency (Section \ref{subsec:incompleteness_SNe}) to arrive at the final efficiency for the $i$th SN, $\eta_{\mathrm{SN},i}$.

### 2021-03-15 draft.tex

@@
     \includegraphics[width=.5\textwidth]{figs/mass_hist_linlog_sn_field_BC03.png}
-    \caption{Upper: Distribution of the stellar mass of the SN host (green dot-dashed) and field galaxies (orange and grey solid) used in the analysis.
-Lower: As upper for field galaxies, but shown on a log scale.
+    \caption{Upper: Distribution of the stellar mass of the SN host galaxies.
+The raw (green dashed) and spectroscopic-efficiency-weighted (blue dot-dashed; Section \ref{subsec:incompletenss_SN_hosts}) histograms are both normalised.
+Lower: As upper but for field galaxies, and shown on a log scale.
 The distribution closely matches data from the ZFOURGE survey at $0.5<z<0.75$ (magenta dots).
-The difference between the raw counts and the $V_{\mathrm{max}}$ corrected counts (Section \ref{sec:incompleteness}) is minimal.
+The difference between the raw counts (grey dotted) and the $V_{\mathrm{max}}$ corrected counts (orange solid; see Section \ref{sec:incompleteness}) is minimal.
     \label{fig:mass_hist_hosts_field}}
@@
     \includegraphics[width=.5\textwidth]{figs/CSFH_MD14.png}
-    \caption{Cosmic star-formation history (CSFH) as approximated by our model (cyan curve) and as a best fit to observations \citep{Madau2014}.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
+    \caption{Cosmic star-formation history (CSFH) as approximated by our model (cyan solid) and as a best fit to observations (magenta dashed; \citealt{Madau2014}).}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
     \label{fig:csfh}

### 2021-03-15 draft.tex
Updates from Overleaf

@@
 \ref{fig:rate_raw}.
-SDSS data (orange squares) are taken from \citet{Graur2013}.
-The systematically higher SNuM in DES is caused by the higher redshift of the sample, as illustrated by the DTD model prediction (coloured curves) }%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
+Literature data are that from SDSS spectra (orange squares; \citealt{Graur2013}) and the LOSS sample (grey dotted; \citealt{Li2011a}).
+The systematically higher SNuM in DES is caused by the higher redshift of the sample, as illustrated by the  prediction of the model using our best fit DTD from Section \ref{subsec:results_dtd} (coloured curves).
+}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
     \label{fig:snum}
@@
 Our model accurately recovers the SNuM measured in DES for the redshift and stellar mass range of the data.
-While the data from LOSS and SDSS lies slightly higher than our model prediction, the difference is consistent with differences in assumed SFHs, IMFs and stellar population templates as well as SN detection method.
-Any true difference between predicted and observed SNuM could be caused by an evolution of the SN Ia production efficiency as a function of redshift; we defer such an investigation to future work with more refined models and measurements.
+While the data from LOSS and SDSS spectra lie slightly higher than our model prediction, the difference is consistent with differences in assumed SFHs, IMFs and stellar population templates as well as SN detection method.
+Any true residual difference between predicted and observed SNuM at different redshifts could be caused by an evolution of the SN Ia production efficiency as a function of redshift; we defer such an investigation to future work with more refined models and measurements.
 \section{The delay-time distribution as a function of supernova properties}

### 2021-03-15 draft.tex
Updates from Overleaf

@@
 With over 30,000 transients passing ML selection it was not possible to obtain spectral follow up of every object.
-Instead we make use of photometric classification in the form of the recurrent neural network classifier \texttt{superNNova} (SNN; \citealt{Moller2019}), foloowing the approach of \citet{Scolnic2020}.
+Instead we make use of photometric classification in the form of the recurrent neural network classifier \texttt{superNNova} (SNN; \citealt{Moller2019}), following the approach of \citet{Scolnic2020}.
 A full description of the training and fitting of SNN will be presented in Vincenzi et al.
@@
 The raw (green dashed) and spectroscopic-efficiency-weighted (blue dot-dashed; Section \ref{subsec:incompletenss_SN_hosts}) histograms are both normalised.
+Comparison samples are PTF (purple; \citealt{Pan2014}) and Pantheon (orange; \citealt{Scolnic2018}).
 Lower: As upper but for field galaxies, and shown on a log scale.
@@
 The SN host stellar mass distribution is plotted twice: once as raw counts; once weighted by the host galaxy spectroscopic efficiency (Section \ref{subsec:incompletenss_SN_hosts}).
+As shown in Fig.
+\ref{fig:mass_hist_hosts_field}, the host stellar mass distribution of the DES-SN sample used in this analysis is qualitatively similar to that from the low redshift Palomar Transient Factory (PTF) sample \citep{Pan2014} as well as the large cosmological Pantheon sample \citep{Scolnic2018}.
+This consistency reflects that seen in the smaller spectroscopically confirmed samples presented in \citet{Wiseman2020} and \citet{Smith2020}.
 The field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass function (SMF) from the ZFOURGE survey \citep{Tomczak2014} scaled to match at $\log (M/\mathrm{M}_{\odot}) = 10$, whose stellar masses are derived with the same photo-$z$ code, IMF and template library as used here.

### 2021-04-19 draft.tex

@@
 \documentclass[fleqn,usenatbib]{mnras}
-
+\usepackage{lineno}
+\linenumbers
 % MNRAS is set in Times font. If you don't have this installed (most LaTeX
@@
 We use a sample of 809 photometrically classified type Ia supernovae (SNe Ia) discovered by the Dark Energy Survey (DES) along with 40415 field galaxies to calculate the rate of SNe Ia per galaxy in the redshift range $0.2 < z <0.6$.
-We recover the positive trend of SN Ia rate as a function of galaxy stellar mass across a broad range of scales $8.5 \leq \log(M_*/\mathrm{M}_{\odot}) \leq 11.25$.
+We recover the known correlation between SN Ia rate and galaxy stellar mass across a broad range of scales $8.5 \leq \log(M_*/\mathrm{M}_{\odot}) \leq 11.25$.
 We find that the SN Ia rate increases with stellar mass as a power-law with index $0.63 \pm 0.02$, which is consistent with previous work.
 We use an empirical model of stellar mass assembly to estimate the average star-formation histories (SFHs) of galaxies across the stellar mass range of our measurement.
-Combining the modelled SFHs with the SN Ia rates to estimate constraints on the SN Ia delay time distribution (DTD), we find the data are fit well by a power-law DTD with index $\beta = -1.14 \pm 0.05$ and normalisation $A = 2.1 \pm0.05 \times 10^{-13}~\mathrm{SNe}~{\mathrm{M}_{\odot}}^{-1}~\mathrm{yr}^{-1}$, which correspond to an overall SN Ia production efficiency $N_{\mathrm{Ia}}/M_* = 0.9~_{-0.7}^{+4.0} \times 10^{-3}~\mathrm{SNe}~\mathrm{M}_{\odot}^{-1}$.
+Combining the modelled SFHs with the SN Ia rates to estimate constraints on the SN Ia delay time distribution (DTD), we find the data are fit well by a power-law DTD with slope index $\beta = -1.14 \pm 0.05$ and normalisation $A = 2.1 \pm0.05 \times 10^{-13}~\mathrm{SNe}~{\mathrm{M}_{\odot}}^{-1}~\mathrm{yr}^{-1}$, which corresponds to an overall SN Ia production efficiency $N_{\mathrm{Ia}}/M_* = 0.9~_{-0.7}^{+4.0} \times 10^{-3}~\mathrm{SNe}~\mathrm{M}_{\odot}^{-1}$.
 Upon splitting the SN sample by properties of the light curves, we find a strong dependence on DTD slope with the SN decline rate, with slower-declining SNe exhibiting a steeper DTD slope.
@@
 
-The progenitors of a number of core-collapse SNe (CCSNe) have been identified in high-resolution pre-explosion images \citep{Smartt2009,Eldridge2013}, allowing detailed analysis of the latter stages of massive star evolution.
+The progenitors of several core-collapse SNe (CCSNe) have been identified in high-resolution pre-explosion images \citep{Smartt2009,Eldridge2013}, allowing detailed analysis of the latter stages of massive star evolution.
 However, this approach has not yet been successful in identifying a progenitor of a SN Ia (e.g.
 \citealt{Graur2014a,Kelly2014,Graur2019}, although see \citet{McCully2014} for evidence of a progenitor for a type Iax SN).
-Conversely, it has been possible to search for surviving remnants of the binary system -- main sequence stars or WDs left behind at the SN location or kicked out at high velocity \citep[e.g.][]{Schaefer2012,Ruiz-Lapuente2018,Kerzendorf2018,Kerzendorf2019}.
+Conversely, there have been searches for surviving remnants of the binary system -- main sequence stars or WDs left behind at the SN location or kicked out at high velocity \citep[e.g.][]{Schaefer2012,Ruiz-Lapuente2018,Kerzendorf2018,Kerzendorf2019}.
 Promising recent results include that from \citet{Shen2018} who discovered three high-velocity WDs consistent with models of double-degenerate, double-detonation SNe Ia.
@@
 
-Another method of inferring progenitor channels is the study of the SN Ia delay time distribution (DTD).
+An indirect method of inferring progenitor channels is the study of the SN Ia delay time distribution (DTD).
 The DTD describes the rate at which SNe Ia occur as a function of the delay time $\tau$ since an episode of star-formation, and thus carries characteristic signatures of the progenitor channel (see \citealt{Wang2012} for a review of the theory, and \citealt{Maoz2017} for a review of observations).
@@
 A complementary technique involves measuring the evolution of the volumetric rate of SNe Ia as a function of redshift and comparing this evolution to the average cosmic star-formation history (CSFH) of the Universe \citep{Gal-Yam2004,Strolger2004,Dahlen2004,Dahlen2008, Graur2011,Graur2013, Rodney2014,Frohmaier2019}.
-This technique (the volumetric rate method) is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clusters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Maoz2010,Friedmann2018,Freundlich2021}.
+This technique (known as the volumetric rate method) is also applicable to galaxy clusters, for which it is assumed that the star-formation histories are strongly peaked at some past epoch and thus that the rate of SNe Ia in clusters as a function of redshift is a more direct measure of the DTD \citep{Maoz2004,Maoz2010,Friedmann2018,Freundlich2021}.
 These studies have, almost ubiquitously, found $\beta$ to be consistent with $-1$.
@@
 To derive our sample of SNe and field galaxies, we make use of the Dark Energy Survey (DES).
-The DES Supernova Programme (DES-SN) was a transient survey based on five six-month seasons of observations of ten southern hemisphere fields with the Dark Energy Camera (DECam; \citealt{Flaugher2015}), designed primarily to measure the light curves of SNe Ia for use as cosmological distance indicators.
-Transients were detected and processed using a difference imaging program \citep{Kessler2015} and vetted using a machine learning (ML) algorithm \citep{Goldstein2015}.
+The DES Supernova Programme (DES-SN) was a transient survey based on five six-month seasons of observations of ten southern hemisphere fields with the Dark Energy Camera (DECam; \citealt{Flaugher2015}).
+The SN survey was designed primarily to measure the light curves of SNe Ia for use as cosmological distance indicators.
+Transients were detected and processed using a difference imaging pipeline \citep{Kessler2015} and image-subtraction artefacts were rejected using a machine learning (ML) algorithm \citep{Goldstein2015}.
 Spectral follow-up of live SN candidates was performed on a suite of large optical telescopes \citep{Smith2020a}, leading to the initial publication of a measurement of cosmological parameters using 207 spectroscopically confirmed SNe Ia (\citealt{DESCollaboration2018a}, and references therein).
@@
 \subsubsection{Photometric classification and quality cuts \label{subsubsec:sn_classify}}
-With over 30,000 transients passing ML selection it was not possible to obtain spectral follow up of every object.
+With over 30,000 discovered transients it was not possible to obtain spectral follow up of every object.
 Instead we make use of photometric classification in the form of the recurrent neural network classifier \texttt{superNNova} (SNN; \citealt{Moller2019}), following the approach of \citet{Scolnic2020}.
@@
 
-We train SNN using a large suite of simulated multi-band SN light curves.
-SNe Ia are simulated based on the \texttt{SALT2} model \citep{Guy2007} trained on the Joint Lightcurve Analysis (JLA) data set \citep{Betoule2014}.
-Synthetic CCSNe light curves are generated from the templates of \citet{Vincenzi2019}.
-Given the training set of synthetic light curves, SNN is able to return a classification for observed light curves.
+We train SNN using a large suite of simulated multi-band SN light curves and their associated host galaxy redshifts, using its default architecture.
+SNe Ia are simulated based on the \texttt{SALT2} model \citep{Guy2007} trained on the Joint Lightcurve Analysis (JLA) data set \citep{Betoule2014} using an identical method to that described in detail in \citet{Vincenzi2020}, and based on the workflow outlined in \citet{Kessler2019}.
+We simulate SNe using the SuperNova ANAlysis software (\texttt{SNANA}; \citealt{Kessler2009a}) integrated into the \texttt{pippin} framework \citep{Hinton2020}.
+SALT2 parameters $x_1$ (stretch) and $c$ (colour) are drawn randomly from the intrinsic asymmetric Gaussian distributions described in \citet{Scolnic2016} and "blurred" following the intrinsic scatter model of \citet{Guy2010}, while redshifts are drawn following the volumetric rate evolution of \citet{Frohmaier2019}.
+Synthetic CCSNe light curves are generated from the templates of \citet{Vincenzi2019}, with a rate following the CSFH of \citet{Madau2014} and normalised by the local Universe rate of \citet{Frohmaier2020}.
+
+Given the training set of synthetic light curves, SNN is able to return a classification (SN Ia, CCSN, or peculiar) for observed light curves.
 Before classifying, we remove transients with variability in multiple seasons (likely active galactic nuclei or superluminous SNe).
 SNN is then run on every transient with a host galaxy redshift (see Section \ref{subsubsec:sn_hosts}).
-We define SNe with a threshold probability of $P(\mathrm{Ia})\geq0.5$ as photometrically classified SNe Ia, although our analysis is not sensitive to this choice, since the vast majority of SNe receive classifications close to 1 or 0 \citep{Moller2019}.
-The photometrically classified SNe Ia are then passed through the \texttt{SALT2} framework light curve fitter and are subject to quality cuts on the light curve width (stretch; $x_1$) and colour ($c$) parameters in an identical manner to \citet{Vincenzi2020}: $-3 \leq x_1 \leq 3$, $-0.3 \leq c \leq 0.3$.
+We define SNe with a threshold probability of $P(\mathrm{Ia})\geq0.5$ as photometrically classified SNe Ia, although our analysis is not sensitive to this choice, since the vast majority of SNe receive classifications close to 1 or 0.
+The photometrically classified SNe Ia are then passed through a \texttt{SALT2} light curve fitting code and are subject to quality cuts on $x_1$ and $c$ in an identical manner to \citet{Vincenzi2020}: $-3 \leq x_1 \leq 3$, $-0.3 \leq c \leq 0.3$.
 This selection helps to reduce the potential contamination from core-collapse SNe (CCSNe) and outlying thermonuclear SNe.
-We impose further cuts on the quality of those measured parameters, which are: the uncertainty on $x_1$: $\sigma_{x_1} <1$; the uncertainty on the date at which the light curve peaked: $\sigma_{t_{\mathrm{peak}}} <2$; the SALT2 fit probability $>0.01$.
+We impose further cuts on the quality of those measured parameters, which are: the uncertainty on $x_1$: $\sigma_{x_1} <1$; the uncertainty on the date at which the light curve has peak brightness: $\sigma_{t_{\mathrm{peak}}} <2$; the SALT2 fit probability\footnote{based on light curve fit $\chi^2$ and number of degrees of freedom.} $>0.01$.
 The number of SNe passing each stage of these cuts is displayed in Table 2 of \citet{Vincenzi2020} and reduces the $\sim30,000$ objects to 1604 SNe.
@@
 While the inclusion of stringent cuts significantly reduces the size of the sample, it greatly enhances the purity and is in line with previous rates analyses of this nature \citep{Sullivan2006} as well as being consistent with other DES-SN analyses \citep[e.g.][]{Kelsey2021}.
+The contamination of this sample from CCSNe according to the simulations of \citet{Vincenzi2020} is expected to be below 3\%, which is close to that of spectroscopic samples \citep{Rubin2015}.
 
@@
 Y3A2\_DEEP makes use of the same deep DES optical photometry that was used in SN Deep for a subset of the fields (SN-X3, SN-C3 and SN-E2), but adds DECam $u$-band data and near-infrared (NIR) $J$, $H$, and $K$-band imaging from the ultraVISTA and VIDEO surveys.
-The deep optical photometry in Y3A2\_DEEP was stacked using a different technique to that of SN Deep, but the resulting photometry is consistent within $1\sigma$ uncertainties (\citealt{Wiseman2020},Meledorf et al.
+The deep optical photometry in Y3A2\_DEEP was stacked using a different technique to that of SN Deep, but the resulting photometry is consistent within $1\sigma$ uncertainties (\citealt{Wiseman2020}, Meledorf et al.
 \textit{in prep}).
 \citet{Hartley2020} estimated photo-$z$s using the \texttt{eaZy} code \citep{Brammer2008}.
-Photo-$z$ accuracy from \citet{Hartley2020} at $17 < i<24$ is estimated around 0.03 as quantified by the Normalised Absolute Median Deviation (NMAD).
-This accuracy is degraded to 0.07 at $17 < i<26$, a range that includes all galaxies in our sample, but is more than adequate for the purposes of this work, where all field galaxies will be grouped into stellar mass bins of $\log \left(\Delta M_*\right) = 0.25$.
+Photo-$z$ accuracy from \citet{Hartley2020} at $17 < i<24$ is estimated around 0.03 as quantified by the Normalised Median Absolute Deviation (NMAD).
+This accuracy is degraded to 0.07 at $17 < i<26$, a range that includes all galaxies in our sample, but is more than adequate for the purposes of this work, where all field galaxies will be grouped into stellar mass bins of $\log \left(\Delta M_*/\mathrm{M}_{\odot}\right) = 0.25$.
+A detailed description of the photo-$z$ accuracy and its dependence on redshift and apparent magnitude is presented in \citet{Hartley2020}.
 
@@
     \caption{Measuring the completeness of the field galaxy sample.
-\textit{Upper}: the $T_{\mathrm{C}}$ statistic as a function of apparent magnitude; \textit{middle} as per \textit{upper}, but for $T_{\mathrm{V}}$; \textit{lower}: the combined, normalised completeness in each band.
+\textit{Upper}: the $T_{\mathrm{C}}$ galaxy completeness statistic (which is calculated by ranking objects by absolute magnitude in slices of distance modulus) as a function of apparent magnitude; \textit{middle} as per \textit{upper}, but for the $T_{\mathrm{V}}$ statistic which is measured by ranking galaxies by distance modulus in slices of absolute magnitude; \textit{lower}: the combined, normalised completeness in each band.
     \label{fig:completeness}}
@@
     \includegraphics[width=0.5\textwidth]{figs/field_vmax.png}
-    \caption{Distribution of $V_{\mathrm{max}}$ corrections applied to field galaxies in the DES sample.
-The majority of galaxies have no correction, and the distribution of the 1\% that do follows a power-law.
+    \caption{Distribution of $V_{\mathrm{max}}$ corrections applied to field galaxies in the DES sample in order to correct for incompleteness.
+The majority of galaxies have no correction, and the distribution of those that do follows a power-law.
     \label{fig:vmax_field}}
@@
 
-    \item field galaxies are limited to unmasked region of the SN-X3 field \citep{Hartley2020};
+    \item field galaxies are limited to unmasked region of the SN-X3 field \citep{Hartley2020} which has an area of 1.52 deg$^2$;
 
@@
 
-    \item field galaxies must lie within the area covered by $ugrizJHK$ photometry, with a photometric flux measurement or upper limit present in all bands;
+    \item field galaxies must covered by $ugrizJHK$ photometry, with a photometric flux measurement or upper limit present in all bands;
 
@@
 Upper and lower bounds on stellar mass estimates are taken as the extreme values that correspond to templates that are consistent with the data (given the photometric uncertainties) according to their $\chi^2$ statistic, as per \citet{Sullivan2006}.
-To check that the choice of templates does not bias the result, we also fit the galaxies using the P\'EGASE.2 templates \citep{Fioc1997,LeBorgne2002} and a \citet{Kroupa2001} IMF, and find results consistent within measurement uncertainties.
+To check for bias caused by template choices, we also fit the galaxies using the P\'EGASE.2 templates \citep{Fioc1997,LeBorgne2002} and a \citet{Kroupa2001} IMF, and find results consistent within measurement uncertainties.
 This is consistent with the findings of \citet{Smith2020}.
@@
 \label{sec:incompleteness}
-The simple ratio of the number of SN hosts and field galaxies presented at the end of the previous section provides a first approximation of the SN rate per galaxy, and the addition of a factor equal to the survey duration normalises the rate to per year.
+The simple ratio of the number of SN hosts and field galaxies presented at the end of the previous section provides a first approximation of the SN rate per galaxy, and the inclusion of a factor equal to the survey duration normalises the rate to per year.
 However, both the SN and field galaxy samples introduced in Sections \ref{subsec:host_sample} and \ref{subsec:field_sample} are affected by incompleteness, which is likely to be the dominant systematic effect in the analysis.
@@
 Since SNe Ia are relatively uniform in absolute luminosity, this form of incompleteness is primarily redshift dependent.
-On the other hand, DES-SN comprises 10 separate pointings, each with different visibility and thus airmass throughout the observing season.
+The large redshift range of DES-SN also means that SNe are probed at different regions of their rest frame SED that vary significantly in luminosity.
+Additionally, DES-SN comprises 10 separate pointings, each with different visibility and thus airmass throughout the observing season.
 These differences lead to different detection efficiencies across the fields.
 
-To correct for these incompleteness, we follow a similar method to that used in the Palomar Transient Factory rates analyses of \citet{Frohmaier2019} and \citet{Frohmaier2020}, outlined in \citet{Frohmaier2017}.
-We run a suite of simulations using an identical method to that described in detail in \citet{Vincenzi2020}.
-We simulate SNe using the SuperNova ANAlysis software (\texttt{SNANA}; \citealt{Kessler2009a}) integrated into the \texttt{pippin} framework \citep{Hinton2020}.
+To correct for these incompleteness, we follow a similar method to that used in the PTF rates analyses of \citet{Frohmaier2019} and \citet{Frohmaier2020}, outlined in \citet{Frohmaier2017}.
 We simulate $1.1\times 10^6$ SNe in the redshift range $0.05 \leq z_{\mathrm{SN}} \leq 1.3$.
-The SNe are generated and trained in the same way as for the training of SNN.
-SALT2 parameters $x_1$ (stretch) and $c$ (colour) are drawn randomly from the intrinsic asymmetric Gaussian distributions described in \citet{Scolnic2016} and "blurred" following the intrinsic scatter model of \citet{Guy2010}, while redshifts are drawn following the volumetric rate evolution of \citet{Frohmaier2019}.
+The SNe are generated in the same way as for the training of SNN (Section \ref{subsubsec:sn_classify}).
 The SNe are simulated with explosion epochs $t_0$ uniformly distributed between two months before DES-SN began and two months after it finished in order to account for all SNe that could have been observed by DES-SN.
@@
 \begin{equation}
-    \eta_{\mathrm{SN},i} (F_i,z_i,t_{0,i},x_1,c) = \left( \frac{N_{\mathrm{obs}}\left(F_i,z_i,t_{0,i},x_1,c\right)}{N_{\mathrm{sim}}\left(F_i,z_i,t_{0,i},x_{1,i},c_i\right)}\right)\,.
+    \eta_{\mathrm{SN},i} (F_i,z_i,t_{0,i},x_{1,i},c_i) = \left( \frac{N_{\mathrm{obs}}\left(F_i,z_i,t_{0,i},x_{1,i},c_i\right)}{N_{\mathrm{sim}}\left(F_i,z_i,t_{0,i},x_{1,i},c_i\right)}\right)\,.
 \end{equation}
@@
 The majority of SN host spectroscopic redshifts in DES are provided by the dedicated follow-up survey OzDES, for which the limiting magnitude is around 24 to 24.5 mag in the $r$ band \citep{Lidman2020}.
-The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citet{Vincenzi2020} who provide the spectroscopic redshift efficiency as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey.
+The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citet{Vincenzi2020} who provide the spectroscopic redshift efficiency $\epsilon_{z_{\mathrm{spec}}} (m^{\mathrm{host}}_{r,i})$ as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey.
 The effects of the host galaxy spectroscopic efficiency are displayed in the upper panel of Fig.
 \ref{fig:mass_hist_hosts_field}, where the normalised histogram weighted by the efficiency is skewed towards lower masses when compared to the unweighted distribution.
-So that we reduce any bias towards SNe in bright hosts that are easier to obtain spectroscopic redshifts for, the host galaxy spectroscopic redshift efficiency is multiplied by that derived from the SN detection efficiency (Section \ref{subsec:incompleteness_SNe}) to arrive at the final efficiency for the $i$th SN, $\eta_{\mathrm{SN},i}$.
+So that we reduce any bias towards SNe in bright hosts that are easier to obtain spectroscopic redshifts for, the host galaxy spectroscopic redshift efficiency is multiplied by that derived from the SN detection efficiency (Section \ref{subsec:incompleteness_SNe}) to arrive at the final efficiency for the $i$th SN:
+\begin{equation}
+    \eta_{\mathrm{SN},i} = \eta_{\mathrm{SN},i} (F_i,z_i,t_{0,i},x_{1,i},c_i)\times \epsilon_{z_{\mathrm{spec}}} (m^{\mathrm{host}}_{r,i})\,.
+\end{equation}
 
@@
 
-Completeness I, II, and III show that for surveys with sharp, well defined magnitude limits the test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ drop sharply.
+Completeness I, II, and III show that for surveys with sharp, well defined magnitude limits the test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ are stable and flat as a function of apparent magnitude up until the magnitude limit, where they drop sharply.
 The DES deep stacks present a more challenging case.
@@
 \citet{Sullivan2006} and \citet{Smith2012} by using a $V_{\mathrm{max}}$ method based on \citet{Schmidt1968}.
-For each galaxy in the sample we calculate the maximum volume within which it would have been observed given its absolute magnitude and $k-$correction.
+For each galaxy in the sample we calculate the maximum volume within which it would have been observed given its absolute magnitude and $k-$correction, and the apparent magnitude limits calculated using the $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ statistics.
 A correction of $V_{\mathrm{survey}}/V_{\mathrm{max}}$ is applied to all galaxies for which $V_{\mathrm{max}} < V_{\mathrm{survey}}$, where $V_{\mathrm{survey}}$ is the maximum volume reached by the survey.
@@
 \begin{equation}
-    N_{\mathrm{SN,intrinsic}} = \sum_i^{n_{\mathrm{SN}}}\eta\left(F,z,t_0,x_1,c,m_{\mathrm{host},r}\right)_{i}\,,
+    N_{\mathrm{SN,intrinsic}} = \sum_i^{n_{\mathrm{SN}}}\eta\left(F,z,t_0,x_1,c,m^{\mathrm{host}}_{r}\right)_{i}\,,
     \label{eq:corr_SN}
@@
 for each SN $i$ and galaxy $j$.
+The volumes $V_{\mathrm{SN}}$ and $V_{\mathrm{G}}$ are calculated from the sky areas from which the respective samples were taken: 1.52 deg$^2$ in the case of the field galaxies \citep{Hartley2020}; 23 deg$^2$ for SNe \citep{Smith2020a}.
+These areas are combined with the redshift interval $[0.2,0.6]$ to determine the total volumes.
 
@@
 \ref{eq:galaxy_rate}.
-Samples from the posterior distribution of the model log rate are drawn in cyan while the black dashed line is the mean of the posterior.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
+Samples from the posterior distribution of the model log rate are drawn in cyan while the black dashed line is the mean of the posterior.
+In red we show the simple log-linear fit from Section \ref{sec:rates}.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
     \label{fig:rate_fitted}}
@@
 The straight line fit in Fig.
-\ref{fig:rate_fitted} deviates from the central values of the data at high stellar mass, the reason for which we investigate in Section \ref{subsec:discussion}.
+\ref{fig:rate_raw} deviates somewhat from the central values of the data at high stellar mass, the reason for which we investigate in Section \ref{subsec:discussion}.
 
@@
 \begin{equation}
-    \Psi(M_*,z) = \left(\frac{M_*}{10^{10}}\right)^{0.7}\frac{\exp{\left(1.9z\right)}}{\exp{\left(1.7\left(z-2\right)\right)} + \exp{\left(0.2\left(z-2\right)\right)} } [\mathrm{M}_{\odot} \mathrm{yr}^{-1}]\,.
+    \Psi(M_*,z) = \left(\frac{M_*}{10^{10}}\right)^{0.7}\frac{\exp{\left(1.9z\right)}}{\exp{\left(1.7\left(z-2\right)\right)} + \exp{\left(0.2\left(z-2\right)\right)} } [\mathrm{M}_{\odot} \mathrm{yr}^{-1}]\,,
     \label{eq:psi_mz}
 \end{equation}
-
+where $M_*$ is given in units of $\mathrm{M}_{\odot}$.
 As galaxies grow, their SFR begins to slow down and eventually shut off almost entirely in a process known as quenching. We adopt the quenching penalty $p_Q$ directly from \citetalias{Childress2014}:
@@
 Firstly, we follow \citetalias{Childress2014} by summing our SFHs and weighting by the galaxy stellar mass function at $z=0$ to estimate the CSFH.
-We approximate the present-day stellar mass function according to a double Schechter function with parameters from the Galaxy and Mass Assembly survey \citet{Baldry2018}: $\log(M^*)=10.66$, $\phi^*_1=3.96\times10^{-3}$, $\alpha_1=-0.35$, $\phi^*_2=0.79\times10^{-3}$, $\alpha_2=-1.47$.
+We approximate the present-day stellar mass function according to a double Schechter function with parameters from the Galaxy and Mass Assembly survey \citet{Baldry2018}: $\log(M^*/\mathrm{M}_{\odot})=10.66$, $\phi^*_1=3.96\times10^{-3}$, $\alpha_1=-0.35$, $\phi^*_2=0.79\times10^{-3}$, $\alpha_2=-1.47$.
 The comparison of our approximate CSFH with that measured from observations \citep{Madau2014} is shown in Fig.
@@
 Our models agree qualitatively on numerous features of the SFHs: high-mass galaxies form almost all their stars at high redshift; intermediate-mass galaxies display a plateau in their SFR from $\sim4$~Gyr to the present day; low-mass galaxies show an increasing rate of star formation at $z=0$.
-The main discrepancy with the lowest-mass bin of the CALIFA sample $8.6 <\log M<9.8$, which as well as an increasing SFR at low redshift shows a second peak of star formation at large lookback times, which we do not see in our model.
+The main discrepancy with the lowest-mass bin of the CALIFA sample $8.6 <\log (M_*/\mathrm{M}_{\odot})<9.8$, which as well as an increasing SFR at low redshift shows a second peak of star formation at large lookback times, which we do not see in our model.
 However, this mass bin spans over one order of magnitude in stellar mass.
@@
 At each step of the sampling procedure the model is re-calculated via Eq.
-\ref{eq:galaxy_rate}, we evaluate the likelihood assuming that the rate data are normally distributed about their means.
-For $\beta$ we adopt a Gaussian prior with hyper-parameters $p(\beta) \sim \mathcal{N}(-1\,,0.3)$.
-We fit for $A$ in log space, and adopt a Gaussian prior (in log space) with hyper-parameters $p(A) \sim \mathcal{N}(-12.7\,, 0.5)$.
+\ref{eq:galaxy_rate}, we evaluate the likelihood assuming that the rate measurements $R_{\mathrm{G}, M_*}$ are described by a Gaussian PDF with mean $\hat R_{\mathrm{G}, M_*}$ and standard deviation $\sigma_{R_{\mathrm{G}, M_*}}$.
+For $\beta$ we adopt a Gaussian prior with hyper-parameters $p(\beta) \sim \mathcal{N}(-1\,,0.5)$.
+We fit for $A$ in log space, and adopt a Gaussian prior (in log space) with hyper-parameters $p(\log(A)) \sim \mathcal{N}(-12.7\,, 0.5)$.
 
@@
 \ref{fig:rate_fitted} we show the SN rate per galaxy predicted by the model assuming the best fitting DTD parameters from Table \ref{tab:dtd_results} compared to the data as presented in Section \ref{sec:rates}.
-The model provides a good fit across a wide range of stellar mass.
-The model clearly diverges from the simple log-linear fit, describing better the enhanced rate around $10^{10}$ M$_{\odot}$ and surpression at high masses.
+Visually, the model provides a good fit across a wide range of stellar mass.
+The model clearly diverges from the simple log-linear fit, describing better the enhanced rate around $10^{10}$ M$_{\odot}$ and suppression at high masses.
 This improvement provides evidence to support the DTD*SFH model.
@@
 the rate of SNe 1 Gyr after star-formation) of $1.73 \pm 0.05 \times 10^{-13}$~M$_{\odot}^{-1}$~yr$^{-1}$.
-\citet{Graur2013} found a value of $7 \times 10^{-14}$~M$_{\odot}^{-1}$~yr$^{-1}$ using the SFH technique, whereas \citet{Heringer2019} report $7 \times 10^{-13}$~M$_{\odot}^{-1}$~yr$^{-1}$.
+\citet{Graur2013} found a value of $0.7 \times 10^{-13}$~M$_{\odot}^{-1}$~yr$^{-1}$ using the SFH technique, whereas \citet{Heringer2019} report $7 \times 10^{-13}$~M$_{\odot}^{-1}$~yr$^{-1}$.
 These results lie either side of our measured value.
@@
 	    $x_1 < 0$ & $-0.79\pm0.08$ &  $1.19 \pm0.05$ \\
-		$x_1 > 0$ & $-1.68 _{ -0.15} ^{ +0.14}$ & $0.51\pm0.12$ \\
-		$c < 0$ & $-1.09 _{ -0.07} ^{ +0.08}$ & $0.89\pm0.04$ \\
+		$x_1 > 0$ & $-1.68\pm0.15$ & $0.51\pm0.12$ \\
+		$c < 0$ & $-1.09\pm0.08$ & $0.89\pm0.04$ \\
 		$c > 0$ & $-1.19\pm0.09$ & $1.16\pm0.08$ \\
@@
 To address this issue we rerun the mass assembly model with $\sigma_{\mathrm{Q}} = 1.5$ as per the nominal analysis of \citetalias{Childress2014} and refit the SN Ia rate data.
-We find that the adapted quenching model does not change the ability of the model to adequately fit the high-mass turnover in the SN rate.
+We find that the adapted quenching model does not result in a better fit to the high-mass turnover in the SN rate.
 
@@
 For example, it is well established that measures of the light curve duration (e.g.
-decline rate $\Delta m_{15}$, or stretch such as SALT2 $x_1$) correlate with host galaxy properties such as morphology \citep{Hamuy1995,Hamuy2000,Mannucci2005}, stellar mass \citep{Kelly2010,Lampeitl2010,Sullivan2010} and specific SFR \citep{Rigault2013,Rigault2018}.
+decline rate, or stretch such as SALT2 $x_1$) correlate with host galaxy properties such as morphology \citep{Hamuy1995,Hamuy2000,Mannucci2005}, stellar mass \citep{Kelly2010,Lampeitl2010,Sullivan2010} and specific SFR \citep{Rigault2013,Rigault2018}.
 If such correlations are caused by intrinsic differences in the progenitors or their surroundings, there may be signatures in the DTDs of SNe when divided into smaller samples.
@@
     \caption{As per Fig.
-\ref{fig:rate_fitted_split_x1} but with the data fit simultaneously by a single two-component DTD, with fixed slope $\beta = -1$ and a prompt fraction that is 1 at short delay times, 0 at large delay times, and a linear function of time between $t_1$ and $t_2$.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
+\ref{fig:rate_fitted_split_x1} but with the data fit simultaneously by a single two-component DTD, with fixed slope $\beta = -1$ and a prompt fraction that is 1 at short delay times, 0 at large delay times, and a linear function of time between $t_1$ (where tardy SNe switch on) and $t_2$ (where prompt SNe turn off).%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
     \label{fig:rate_fitted_split_x1_2c_DTD}}
@@
 The corresponding DTD fit results in a steep power-law $\beta = -1.68 \pm 0.15$ for high-stretch SNe indicative of a population of predominantly prompt SNe, and a much shallower decay slope ($\beta = -0.79 \pm 0.08$) for low-stretch SNe representing a much more delayed population.
-This result provides and intriguing confirmation of that observed in 101 SDSS SNe Ia by \citet{Brandt2010} who found
+The difference in $\beta$ is significant at a level of $3.8\sigma$.
+This result provides an intriguing confirmation of that observed in 101 SDSS SNe Ia by \citet{Brandt2010} who found that low-$x_1$ SNe displayed much longer delay times than those with high $x_1$.
 
@@
 It is then necessary to invoke models in which the WD progenitors of low-stretch SNe evolve on longer timescales than those of high-stretch SNe, for example due to a different initial binary separation distribution or accretion rate.
-In this case, the DTD slopes would indeed take on the different values measured here
+In this case, the DTD slopes would indeed take on the different values measured here.
 
 Alternatively, low- and high-stretch SNe could form via identical evolutionary channels but with a different onset time since the episode of star-formation.
-The predominantly high-stretch "prompt" SNe would begin exploding as soon as the WDs are formed (nominally 40 Myr) whereas the mainly low-stretch "tardy" SNe would only begin exploding after an extended period of time of the order 1 Gyr.
-The rates of both populations would follow the fiducial $t^{-1}$ distribution.
+In this scenario, he predominantly high-stretch "prompt" SNe begin exploding as soon as the WDs are formed (nominally 40 Myr) whereas the mainly low-stretch "tardy" SNe only begin exploding after an extended period of time of the order 1 Gyr.
+The time dependence of both populations would follow the fiducial $t^{-1}$ distribution.
 Such a scenario may be explained by the sub-$M_{\mathrm{Ch}}$ double-detonation paradigm \citep[e.g.][]{Sim2010,Blondin2017,Shen2017}.
-Sub-$M_{\mathrm{Ch}}$ SNe Ia typically involve the merger of two WDs and the SN luminosity can be correlated with the mass of the primary WD; a correlation between primary WD mass and age would then lead to the different rates, and apparent DTDs, of low and high-stretch SNe observed in this work.
+Sub-$M_{\mathrm{Ch}}$ SNe Ia typically involve the merger of two WDs and the SN luminosity can be correlated with the mass of the primary WD; a correlation between primary WD mass and age leads to different DTDs of low and high-stretch SNe and hence the different rates observed in this work.
 Such an evolution of light curve properties with age has recently been seen across the full range of "normal" SNe Ia in 1-dimensional simulations by \citet{Shen2021} and is a promising avenue for further investigation although we note that they struggle to reproduce observed light curves at later times ($t\gtrsim30$~d; \citealt{Shen2021,Gronow2021}).
@@
 The best fitting values are somewhat consistent with one another, with $t_1 = 0.65 \pm 0.1$~Gyr and $t_2 = 0.85 \pm 0.15$~Gyr, corresponding to a relatively sharp transition between the two populations.
-Our $t_1$ and $t_2$ are consistent with the transition found by \citet{Brandt2010} who found high-stretch SNe to be confined to delay times $\lesssim 0.4$~Gyr while high-stretch SNe displayed delay times $\gtrsim 2.4$~Gyr.
+Our $t_1$ and $t_2$ are reminiscent of the transition found by \citet{Brandt2010} who found high-stretch SNe to be confined to delay times $\lesssim 0.4$~Gyr while low-stretch SNe occurred with delay times $\gtrsim 2.4$~Gyr.
 On the other hand, the transition found here appears to occur at much shorter delay times than the several Gyrs found by \citet{Rose2019}.
@@
 The correlation of progenitor age and WD mass does not easily reproduce such a bimodal distribution, which may suggest that the sub-$M_{\mathrm{Ch}}$ channel cannot account for all SNe Ia.
-We also note that our method models the average SFH of galaxies and that the DTD is a statistical distribution: our results do not rule out high-stretch SNe arising from old progenitors, but do suggest that such a scenario is unlikely.
+We also note that our method models the average SFH of galaxies and that the DTD is a statistical distribution: our results do not rule out high-stretch SNe arising from old progenitors, but suggest that such a scenario is unlikely.
 
@@
 
-One possibility is that sub-luminous SNe are more numerous in such predominantly old stellar populations, such that the fraction passing our light curve cuts is lower than the rest of the sample.
-Such a phenomenon could be caused by SN Ia sub-classes such as SN 1991bg-like SNe, which are known to explode exclusively in old environments \citep{Perets2010} at delay times as long as $>6$~Gyr \citep{Panther2019}, and are typically sub-luminous with fast decline rates \citep{Gonzalez-Gaitan2014}.
-If the SN 1991bg-like objects are drawn from the same parent population of WDs as the "normal" SNe Ia, they could explain the lack thereof in the sample.
-We check this briefly by re-examining the objects left out of our sample due to \texttt{SALT2} cuts.
+One possibility is that sub-luminous SNe are more numerous in predominantly old stellar populations, such that the fraction passing our light curve cuts is lower than the rest of the sample.
+Such a phenomenon could be caused by SN Ia sub-classes such as SN 1991bg-like SNe, which are known to explode exclusively in old environments \citep{Perets2010} at delay times as long as $>6$~Gyr \citep{Panther2019}, and are typically sub-luminous with low stretch \citep{Gonzalez-Gaitan2014}.
+If the SN 1991bg-like objects are drawn from the same parent population of WDs as the "normal" SNe Ia, their presence in high-mass hosts could explain the apparent lack of normal SNe Ia in the sample.
+We check this hypothesis briefly by re-examining the objects left out of our sample due to \texttt{SALT2} cuts.
 We find that 75\% of objects left out lie in hosts with $M_*>10^{10}$ M$_{\odot}$, while this percentage is 65\% for the objects that pass the cuts.
 However, of the objects in high-mass galaxies that fail the cuts, only 11 (10\%) fail due to their $x_1$ lying below $-3$, and a total of 20 have $x_1 <-2$ which is the regime populated by SN 1991bg-like objects which is well short of the factor of two by which the DTD model over-predicts the data in the highest mass bin.
+Another issue is that SN 1991bg-like SNe are generally fainter than normal SNe Ia and the massive galaxies in which they explode are typically bright, leading to a lower detection efficiency than that modelled in Section \ref{subsec:incompleteness_SNe}.
+A thorough investigation into the presence of SN Ia sub-types in the DES-SN data set is deferred to a future investigation.
 
@@
 
-In the previous section, we have showed that the slope of the SN Ia rate vs stellar mass relation is different for slow and fast declining supernovae.
-There is no evidence for a similar difference between SNe with different colours (Fig.
-\ref{fig:rate_fitted_split_c}), with best fitting values of $\beta$ of $-1.19\pm0.09$ $-1.09\pm0.08$ for red ($c > 0$) and blue ($c<0$) SNe respectively.
-This lack of difference is in agreement with the findings of \citet{Sullivan2010}.
+In the previous section, we showed that the slope of the SN Ia rate vs stellar mass relation is different for slow and fast declining supernovae.
+We find no evidence for a similar difference between SNe with different colours (Fig.
+\ref{fig:rate_fitted_split_c}), with best fitting values of $\beta$ of $-1.19\pm0.09$ and $-1.09\pm0.08$ for red ($c > 0$) and blue ($c<0$) SNe respectively.
+This consistency is in agreement with the findings of \citet{Sullivan2010}.
 Red SNe appear to have a higher normalisation than blue SNe, with roughly 30\% more red than blue SNe.
 This dominance can be explained by a single population of SNe with an intrinsic colour distribution that is Gaussian and centred on $c=0$ combined with an external dust distribution with an exponential form, systematically shifting the SN colour distribution to the red and causing the higher observed rate of those objects.
-Such a scenario has been proposed by \citet{Brout2020}.
-
-The predictions from the DTD model diverge from the data at low stellar mass ($M_* <10^{9.25}$ M$_{\odot}$), where the rate becomes dominated by blue SNe.
-Although this is where the data is noisiest, it is worth investigating the possible causes of this divergence.
+Such a scenario has been implemented previously in the Multicolor Light-curve Shapes framework \citep{Riess1996,Jha2007}, and recently explored in detail by \citet{Brout2020}.
+
+In Fig.
+\ref{fig:rate_fitted_split_c} the predictions from the DTD model differ from the data at low stellar mass ($\log(M_*/\mathrm{M}_{\odot}) <9.25$).
+Here, the model predicts that red SNe should dominate at the same level as across the full mass range, and the relative difference should remain.
+The data however become dominated by blue SNe.
+Although this is where the data is noisiest due to the low number of SNe, it is worth investigating the possible causes of this divergence.
 A slight preference for SN to be bluer in lower-mass galaxies has been observed \citep{Scolnic2018,Brout2019,Smith2020,Kelsey2021} and could be the same effect seen at low stellar masses here.
@@
 An intermediate explanation is that the SNe in low-mass hosts have a smaller dust column density in the immediate vicinity of the progenitor system, either due to the shorter evolutionary timescale or the higher mass and thus brighter system being less conducive to dust production.
-A detailed exploration of the effects of environment on SN colour will be presented in Kelsey et al.
+A detailed exploration of the effects of environment on SN colour in the DES-SN photometric sample will be presented in Kelsey et al.
 \textit{in prep}.
@@
 \item We have measured the rate of SNe Ia per galaxy based on a sample of over 800 SNe and 40,000 galaxies detected by DES.
-We have recovered the relationship between SN rate and galaxy stellar mass seen in SNLS \citep{Sullivan2006} and SDSS \citep{Smith2012} and are mildly consistent with both of those works.
-The power-law slope being less than unity indicates that the rate of SNe is not solely driven by stellar mass, but also other factors such as the star-formation history
+We find a tight linear relationship between SN rate and galaxy stellar mass as seen in SNLS \citep{Sullivan2006} and SDSS \citep{Smith2012} and constrain the slope to high precision.
+The power-law slope of 0.63 being less than unity indicates that the rate of SNe is not solely driven by stellar mass, but also other factors such as the star-formation history.
 
 \item By simulating the stellar mass assembly of average galaxies across cosmic time following the prescription of \citetalias{Childress2014} we have recovered an estimate of the SN Ia DTD, finding a good fit to a power-law distribution with an index of $-1.14 \pm0.05$.
-Our measurement of the DTD is fairly consistent with previous measurements \citep[e.g.][]{Graur2013,Maoz2017} and carries signatures predicted by the DD scenario for SNe Ia production.
-
-\item We find strong differences in the slope of the SN rate vs stellar mass between SNe with low and high stretch factors.
+Our measurement of the DTD provides a further tight constraint to those of previous measurements \citep[e.g.][]{Graur2013,Maoz2017} and carries signatures predicted by the DD scenario for SNe Ia production.
+
+\item We find strong differences in the slope of the SN rate vs stellar mass between SNe with low and high stretch factors ($3.6\sigma$).
 The differing slopes are readily explained by the correlation between stretch and stellar age, since more massive galaxies play host to older stellar populations which are known to give rise to lower-stretch SNe
@@
 Such a scenario is compatible with stretch being related to progenitor mass, a paradigm consistent with a sub-$M_{\mathrm{Ch}}$, double-detonation explosion mechanism.
+
+\item Red ($c>0$) SNe explode at a higher rate than blue SNe at all mass ranges, we find that DTD decay slope is independent of SN colour.
+We assume that the higher rate of red SNe is caused by the addition of dust to an intrinsically Gaussian colour distribution centred slightly bluewards of $c=0$, but defer a detailed investigation to future work.
 \end{itemize}
@@
 
-We thank \textit{some people} for fruitful discussions. 
-We acknowledge \textit{DES and all its institutes}
+Funding for the DES Projects has been provided by the U.S. Department of Energy, the U.S. National Science Foundation, the Ministry of Science and Education of Spain, 
+the Science and Technology Facilities Council of the United Kingdom, the Higher Education Funding Council for England, the National Center for Supercomputing 
+Applications at the University of Illinois at Urbana-Champaign, the Kavli Institute of Cosmological Physics at the University of Chicago, 
+the Center for Cosmology and Astro-Particle Physics at the Ohio State University,
+the Mitchell Institute for Fundamental Physics and Astronomy at Texas A\&M University, Financiadora de Estudos e Projetos, 
+Funda{\c c}{\~a}o Carlos Chagas Filho de Amparo {\`a} Pesquisa do Estado do Rio de Janeiro, Conselho Nacional de Desenvolvimento Cient{\'i}fico e Tecnol{\'o}gico and 
+the Minist{\'e}rio da Ci{\^e}ncia, Tecnologia e Inova{\c c}{\~a}o, the Deutsche Forschungsgemeinschaft and the Collaborating Institutions in the Dark Energy Survey.
+
+The Collaborating Institutions are Argonne National Laboratory, the University of California at Santa Cruz, the University of Cambridge, Centro de Investigaciones Energ{\'e}ticas, 
+Medioambientales y Tecnol{\'o}gicas-Madrid, the University of Chicago, University College London, the DES-Brazil Consortium, the University of Edinburgh, 
+the Eidgen{\"o}ssische Technische Hochschule (ETH) Z{\"u}rich, 
+Fermi National Accelerator Laboratory, the University of Illinois at Urbana-Champaign, the Institut de Ci{\`e}ncies de l'Espai (IEEC/CSIC), 
+the Institut de F{\'i}sica d'Altes Energies, Lawrence Berkeley National Laboratory, the Ludwig-Maximilians Universit{\"a}t M{\"u}nchen and the associated Excellence Cluster Universe, 
+the University of Michigan, NFS's NOIRLab, the University of Nottingham, The Ohio State University, the University of Pennsylvania, the University of Portsmouth, 
+SLAC National Accelerator Laboratory, Stanford University, the University of Sussex, Texas A\&M University, and the OzDES Membership Consortium.
+
+Based in part on observations at Cerro Tololo Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop.
+ID 2012B-0001; PI: J.
+Frieman), which is managed by the Association of Universities for Research in Astronomy (AURA) under a cooperative agreement with the National Science Foundation.
+
+The DES data management system is supported by the National Science Foundation under Grant Numbers AST-1138766 and AST-1536171.
+The DES participants from Spanish institutions are partially supported by MICINN under grants ESP2017-89838, PGC2018-094773, PGC2018-102021, SEV-2016-0588, SEV-2016-0597, and MDM-2015-0509, some of which include ERDF funds from the European Union.
+IFAE is partially funded by the CERCA program of the Generalitat de Catalunya.
+Research leading to these results has received funding from the European Research
+Council under the European Union's Seventh Framework Program (FP7/2007-2013) including ERC grant agreements 240672, 291329, and 306478.
+We  acknowledge support from the Brazilian Instituto Nacional de Ci\^encia
+e Tecnologia (INCT) do e-Universo (CNPq grant 465376/2014-2).
+
+This manuscript has been authored by Fermi Research Alliance, LLC under Contract No. DE-AC02-07CH11359 with the U.S. Department of Energy, Office of Science, Office of High Energy Physics.
 

### 2021-04-20 draft.tex

@@
 Promising recent results include that from \citet{Shen2018} who discovered three high-velocity WDs consistent with models of double-degenerate, double-detonation SNe Ia.
-However, without an unambiguous observation of a SN Ia progenitor system or remnant companion, there is as yet no direct evidence ruling out any progenitor channel from providing a significant contribution to the total population of SNe Ia.
+However, without an unambiguous observation of a SN Ia progenitor system or remnant companion, there is as yet no direct evidence that any progenitor channel from provides a significant contribution to the total population of SNe Ia.
 
@@
 
-Given the training set of synthetic light curves, SNN is able to return a classification (SN Ia, CCSN, or peculiar) for observed light curves.
+Given the training set of synthetic light curves, SNN returns a classification (SN Ia, CCSN, or peculiar) for observed light curves.
 Before classifying, we remove transients with variability in multiple seasons (likely active galactic nuclei or superluminous SNe).
@@
 The photometrically classified SNe Ia are then passed through a \texttt{SALT2} light curve fitting code and are subject to quality cuts on $x_1$ and $c$ in an identical manner to \citet{Vincenzi2020}: $-3 \leq x_1 \leq 3$, $-0.3 \leq c \leq 0.3$.
-This selection helps to reduce the potential contamination from core-collapse SNe (CCSNe) and outlying thermonuclear SNe.
+This selection helps to reduce the potential contamination from core-collapse SNe (CCSNe) and outlying thermonuclear SNe, as well as removing those in extremely dusty environments.
 We impose further cuts on the quality of those measured parameters, which are: the uncertainty on $x_1$: $\sigma_{x_1} <1$; the uncertainty on the date at which the light curve has peak brightness: $\sigma_{t_{\mathrm{peak}}} <2$; the SALT2 fit probability\footnote{based on light curve fit $\chi^2$ and number of degrees of freedom.} $>0.01$.
@@
 the sample is magnitude limited modulo the cuts described in Section \ref{subsec:cuts}.
-To determine the apparent magnitude limit in each of the optical bands we employ the method of \citet{Johnston2007}, \citet{Teodoro2010}, and \citet{Johnston2012} (hereafter Completeness I, II, III respectively).
+To determine the apparent magnitude limit for galaxies in each of the optical bands we employ the method of \citet{Johnston2007}, \citet{Teodoro2010}, and \citet{Johnston2012} (hereafter Completeness I, II, III respectively).
 We use the test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ from those studies, which are computed based on absolute magnitude (distance modulus).
@@
 Secondly, we assess the shape of our SFHs and how they depend on stellar mass by comparing with SFH measurements from the Calar Alto Legacy Integral Field spectrscopy Area survey (CALIFA) as revealed by \citet{GonzalezDelgado2017}.
-Our models agree qualitatively on numerous features of the SFHs: high-mass galaxies form almost all their stars at high redshift; intermediate-mass galaxies display a plateau in their SFR from $\sim4$~Gyr to the present day; low-mass galaxies show an increasing rate of star formation at $z=0$.
+Our models agree qualitatively on numerous features of the SFHs (their Fig.
+5): high-mass galaxies form almost all their stars at high redshift; intermediate-mass galaxies display a plateau in their SFR from $\sim4$~Gyr to the present day; low-mass galaxies show an increasing rate of star formation at $z=0$.
 The main discrepancy with the lowest-mass bin of the CALIFA sample $8.6 <\log (M_*/\mathrm{M}_{\odot})<9.8$, which as well as an increasing SFR at low redshift shows a second peak of star formation at large lookback times, which we do not see in our model.
@@
 Our measurement provides an independent support to the values close to $-1$ found using volumetric rates \citep[e.g.][]{Graur2011,Graur2014,Frohmaier2019}, individual galaxy SFHs \citep[e.g.][]{Maoz2012,Graur2013}, and galaxy clusters \citep[e.g.][]{Maoz2010} although our slope is marginally inconsistent with that of \citet{Heringer2019}.
+The result is also qualitatively consistent with that of \citet{Strolger2020a} who fit an exponential function DTD rather than a power law.
+However, their best fit model indicated a higher SN rate at long delay times than a $\tau^{-1}$ DTD, which is opposite to the mild preference of our fit which is steeper and thus produces a smaller fraction of SNe at long delay times.
 

### 2021-04-21 draft.tex
Updates from Overleaf

@@
 We perform three fits: one with $t_{\mathrm{p}}$ fixed at 40 Myr, one with it as a free parameter along with $\beta$ and $A$, and a third with $\beta$ and $A$ fixed and  $t_{\mathrm{p}}$ free.
-We fit $t_{\mathrm{p}}$ in log space and adopt a Gaussian prior with hyper-parameters $p(\log(t_{\mathrm{p}})) \sim \mathcal{N}(-1.3\,,0.2)$, which corresponds to being centred around 50~Myr.
+We fit $t_{\mathrm{p}}$ in log space and adopt a Gaussian prior with hyper-parameters $p(\log(t_{\mathrm{p}})) \sim \mathcal{N}(-1.3\,,0.5)$, which corresponds to being centred around 50~Myr.
 Choosing this regime to fit allows more prior weight to be placed on shorter prompt times as per the majority of the literature.
+We use the $\hat{R}$ diagnostic \citep{Vehtari2019} to assess the convergence of MC chains.
+When including $t_{\mathrm{p}}$ as a free parameter, we find that the strong degeneracy between $t_{\mathrm{p}}$ and $A$ cause the sampler to fail to converge with $\hat{R} = 1.3$ for the chains of those two parameters.
 

### 2021-04-21 draft.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/beta_A_Qerf1.1_corner_All.png}
+    \includegraphics[width=.5\textwidth]{figs/fit_dtd_all_A_beta_corner.png}
     \caption{Posterior distributions for DTD slope $\beta$ and normalisation $A$.
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=.5\textwidth]{figs/beta_A_tp_Qerf1.1_corner.png}
-    \caption{Posterior distributions for DTD parameters $\beta$, $A$, and $t_{\mathrm{p}}$.
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=.5\textwidth]{figs/fit_dtd_A_beta_tp_corner.png}
+%    \caption{Posterior distributions for DTD parameters $\beta$, $A$, and $t_{\mathrm{p}}$.
 We display the log of $A$ for clarity.
 Displayed point estimates represent the median of the posterior samples.
-    %The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
-    \label{fig:corner_beta_norm_tp}}
-\end{figure}
+%    %The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
+%    \label{fig:corner_beta_norm_tp}}
+%\end{figure}
 
@@
 Choosing this regime to fit allows more prior weight to be placed on shorter prompt times as per the majority of the literature.
-We use the $\hat{R}$ diagnostic \citep{Vehtari2019} to assess the convergence of MC chains.
+We use the $\hat{R}$ diagnostic of \citep{Vehtari2019} to assess the convergence of MC chains.
 When including $t_{\mathrm{p}}$ as a free parameter, we find that the strong degeneracy between $t_{\mathrm{p}}$ and $A$ cause the sampler to fail to converge with $\hat{R} = 1.3$ for the chains of those two parameters.
-
-The joint and marginal posterior distributions for the fit parameters are found in Figs.
-\ref{fig:corner_beta_norm} and \ref{fig:corner_beta_norm_tp} for the fixed and free $t_{\mathrm{p}}$ fits respectively, and the posterior means and standard deviations are summarised in Table \ref{tab:dtd_results}.
+In subsequent analyses we adopt as our fiducial model that with fixed $t_{\mathrm{p}} =0.04$~Gyr.
+
+The joint and marginal posterior distributions for the fit parameters are found in Fig.
+\ref{fig:corner_beta_norm}, and the posterior means and standard deviations are summarised in Table \ref{tab:dtd_results}.
 Fig.
-\ref{fig:corner_beta_norm} shows that there is a correlation between $\beta$ and $A$ which is not seen in the fit with $t_{\mathrm{p}}$ as a free parameter.
-This is likely caused by $\beta$ instead correlating with $t_{\mathrm{p}}$, and being more poorly constrained in the three-parameter fit.
+\ref{fig:corner_beta_norm} shows that there is a mild correlation between $\beta$ and $A$.
 In Fig.
@@
 In most cases, $t_{\mathrm{p}}$ has been fixed at some fiducial value such as 40~Myr, which is derived from the lifetime of 8~M$_{\odot}$ stars.
-\citet{Castrillo2020} included $t_{\mathrm{p}}$ (which they denote $\Delta$) in their fit, and find a value of $50_{-35}^{+100}$~Myr which is consistent with both 40~Myr as well as our best fitting value of $67_{-23}^{+43}$~Myr for the three-parameter fit and $47_{-7}^{+8}$~Myr with $\beta$ and $A$ fixed.
+\citet{Castrillo2020} included $t_{\mathrm{p}}$ (which they denote $\Delta$) in their fit, and find a value of $50_{-35}^{+100}$~Myr which is consistent with both 40~Myr.
+While we are unable to fit $t_{\mathrm{p}}$ simultaneously with $\beta$ and $A$, by fixing $\beta=-1$ and $\log(A)=-12.75$ we find $t_{\mathrm{p}} =47_{-7}^{+8}$~Myr, which is consistent with the fiducial value of $40$~Myr.
 \citet{Heringer2019} also present fits with varying prompt times, although they don't fit for the parameter itself.
-They find that varying $t_{\mathrm{p}}$ changes the recovered normalisation, which is consistent with the degeneracy seen in our results (Fig.
-\ref{fig:corner_beta_norm_tp}).
-Overall, we find results for $t_{\mathrm{p}}$ that are consistent with the fiducial value of 40~Myr and adopt this value for the remainder of the analysis.
+They find that varying $t_{\mathrm{p}}$ changes the recovered normalisation, which is consistent with the degeneracy encountered in our fits.
+Overall, we conclude that there is no strong evidence for a value of $t_{\mathrm{p}}$ that is different to the fiducial value of 40~Myr and adopt this value for the remainder of the analysis.
 

### 2021-04-21 draft.tex
Updates from Overleaf

@@
 We use the $\hat{R}$ diagnostic of \citep{Vehtari2019} to assess the convergence of MC chains.
-When including $t_{\mathrm{p}}$ as a free parameter, we find that the strong degeneracy between $t_{\mathrm{p}}$ and $A$ cause the sampler to fail to converge with $\hat{R} = 1.3$ for the chains of those two parameters.
+When including $t_{\mathrm{p}}$ as a free parameter, we find that the strong degeneracy between $t_{\mathrm{p}}$ and $A$ cause the sampler to fail to converge with $\hat{R} \sim 1.3$ for the chains of those two parameters.
 In subsequent analyses we adopt as our fiducial model that with fixed $t_{\mathrm{p}} =0.04$~Gyr.
@@
 We report parameter estimates based on the mean and standard deviation of their posterior samples.
+We use the $\hat{R}$ diagnostic of \citep{Vehtari2019} to assess the convergence of MC chains, and only report fits where $\hat{R}\let1.05$
 
@@
 The two parameters are highly degenerate, yet well constrained.
-This degeneracy manifests as the spread of potential linear fits as drawn in light blue on Fig.
+This degeneracy manifests as the spread of potential linear fits as drawn in light green on Fig.
 \ref{fig:rate_fitted}.
 
-%\section{Changes to the nominal SFH model}
-%\label{appendix:model_adjustments}
-%In Section \ref{sec:model} we describe our toy model of galaxy SFHs based on the work of %\citetalias{Childress2014}. Here we
+\section{Posterior distributions for DTD fits}
+
+In this section we present the joint and marginal posterior distributions for the various fits of the DTD presented in Section \ref{sec:split_x1_c}.
+Posteriors have been displayed using v0.33.0 of \texttt{ChainConsumer} \citep{Hinton2016}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/fit_dtd_split_x1_A_beta_corner.png}
+    \caption{Posterior distributions for DTD slope $\beta$ and normalisation $A$ for SNe Ia split by their $x_1$ parameter.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
+    \label{fig:corner_beta_norm_split_x1}}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/fit_dtd_split_c_A_beta_corner.png}
+    \caption{Posterior distributions for DTD slope $\beta$ and normalisation $A$ for SNe Ia split by their $c$ parameter.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
+    \label{fig:corner_beta_norm_split_c}}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{figs/fitjoint_t1_t2_corner.png}
+    \caption{Posterior distributions for $t_1$ and $t_2$ of the model presented in Section \ref{subsec:split_x1}.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
+    \label{fig:corner_t1_t2}}
+\end{figure}
 

### 2021-04-21 draft.tex

@@
     \caption{As per Fig.
-\ref{fig:rate_fitted_split_x1} but with the data fit simultaneously by a single two-component DTD, with fixed slope $\beta = -1$ and a prompt fraction that is 1 at short delay times, 0 at large delay times, and a linear function of time between $t_1$ (where tardy SNe switch on) and $t_2$ (where prompt SNe turn off).%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
+\ref{fig:rate_fitted_split_x1} but with the data fit simultaneously by a single two-component DTD, with fixed slope $\beta = -1$ and a prompt fraction that is 1 at short delay times, 0 at large delay times, and a linear function of time between $t_1 =0.65$~Gyr (where tardy SNe switch on) and $t_2=0.85$~Gyr (where prompt SNe turn off).%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
     \label{fig:rate_fitted_split_x1_2c_DTD}}
@@
 We report parameter estimates based on the mean and standard deviation of their posterior samples.
-We use the $\hat{R}$ diagnostic of \citep{Vehtari2019} to assess the convergence of MC chains, and only report fits where $\hat{R}\let1.05$
+We use the $\hat{R}$ diagnostic of \citep{Vehtari2019} to assess the convergence of MC chains, and only report fits where $\hat{R}<1.05$
 

### 2021-05-20 draft.tex

@@
 This selection helps to reduce the potential contamination from core-collapse SNe (CCSNe) and outlying thermonuclear SNe, as well as removing those in extremely dusty environments.
-We impose further cuts on the quality of those measured parameters, which are: the uncertainty on $x_1$: $\sigma_{x_1} <1$; the uncertainty on the date at which the light curve has peak brightness: $\sigma_{t_{\mathrm{peak}}} <2$; the SALT2 fit probability\footnote{based on light curve fit $\chi^2$ and number of degrees of freedom.} $>0.01$.
+We impose further cuts on the quality of those measured parameters, which are: the uncertainty on $x_1$: $\sigma_{x_1} <1$; the uncertainty on the date at which the light curve has peak brightness: $\sigma_{t_{\mathrm{peak}}} <2$~d; the SALT2 fit probability\footnote{based on light curve fit $\chi^2$ and number of degrees of freedom.} $>0.01$.
 The number of SNe passing each stage of these cuts is displayed in Table 2 of \citet{Vincenzi2020} and reduces the $\sim30,000$ objects to 1604 SNe.
@@
     \caption{The stellar mass assembly of the Universe as prescribed by the toy model of \citetalias{Childress2014}.
+The $y$-axis is the fraction of a galaxy's total mass of formed stars that are formed in each time bin.
 Galaxies with high stellar mass at $z=0$ formed the majority of their stars in the distant past, while lower-mass galaxies are still actively star forming in the present day.}
@@
 \begin{equation}
-    R_{\mathrm{G}} = \int_{t_0}^{\infty} \psi(t_0-\tau)\Phi(\tau)\,d\tau \,,
+    R_{\mathrm{G}} = \int_{t_0}^{t_f} \psi(t_0-\tau)\Phi(\tau)\,d\tau \,,
     \label{eq:galaxy_rate}
 \end{equation}
-where $t_0$ is the epoch at which the galaxy is observed, and $\psi$ is the SFH.
+where $t_0$ is the epoch at which the galaxy is observed, $t_f$ is the time at which the first stars in the galaxy formed, and $\psi$ is the SFH.
 
@@
 		\hline
-		Fixed $t_{\mathrm{p}}$ & $-1.14\pm0.05$ &  $2.08 \pm 0.08$ & -\\
-		Free $t_{\mathrm{p}}$ & $-1.03 _{-0.07} ^{+0.11}$ & $1.87 _{-0.17} ^{+0.13}$ & $0.07 _{-0.04} ^{+0.03}$\\
+		Fixed $t_{\mathrm{p}}$ & $-1.13^{+0.04}_{-0.06}$ &  $2.11^{+0.05}_{-0.12}$ & -\\
+		%Free $t_{\mathrm{p}}$ & $-1.03 _{-0.07} ^{+0.11}$ & $1.87 _{-0.17} ^{+0.13}$ & $0.07 _{-0.04} ^{+0.03}$\\
 		Fixed $A$, $\beta$ & - & - & $0.047_{-0.007}^{+0.008}$\\
@@
 \subsubsection{The DTD power law index \label{subsubsec:compare_beta}}
-We measure a DTD power law index of $-1.14\pm0.05$.
+We measure a DTD power law index of $-1.13^{+0.04}_{-0.06}$.
 This value is consistent with the majority of previous analyses using various methods.
@@
 We measure a DTD normalisation (i.e.
-the rate of SNe 1 Gyr after star-formation) of $1.73 \pm 0.05 \times 10^{-13}$~M$_{\odot}^{-1}$~yr$^{-1}$.
+the rate of SNe 1 Gyr after star-formation) of $2.11^{+0.05}_{-0.12} \times 10^{-13}$~M$_{\odot}^{-1}$~yr$^{-1}$.
 \citet{Graur2013} found a value of $0.7 \times 10^{-13}$~M$_{\odot}^{-1}$~yr$^{-1}$ using the SFH technique, whereas \citet{Heringer2019} report $7 \times 10^{-13}$~M$_{\odot}^{-1}$~yr$^{-1}$.
 These results lie either side of our measured value.
-\citet{Heringer2019} note that the normalisation recovered from the SFHR method is sensitive to the assumed prompt time $t_{\mathrm{p}}$, a degeneracy that is also apparent our method.
+\citet{Heringer2019} note that the normalisation recovered from the SFHR method is degenerate with the assumed prompt time $t_{\mathrm{p}}$, a degeneracy that is also reflected in the non-convergence of our fit that included $t_{\mathrm{p}}$ as a free parameter.
 The normalisation is also sensitive to the assumed IMF which can explain this variation \citep{Maoz2017}.
@@
 		\hline
-		Fiducial & $-1.14\pm0.05$ &  $2.08\pm0.08$ \\
+		Fiducial & $-1.13\pm0.05$ &  $2.11\pm0.08$ \\
 	    $x_1 < 0$ & $-0.79\pm0.08$ &  $1.19 \pm0.05$ \\
-		$x_1 > 0$ & $-1.68\pm0.15$ & $0.51\pm0.12$ \\
-		$c < 0$ & $-1.09\pm0.08$ & $0.89\pm0.04$ \\
-		$c > 0$ & $-1.19\pm0.09$ & $1.16\pm0.08$ \\
+		$x_1 > 0$ & $-1.70^{+0.19}_{-0.10}$ & $0.50^{+0.26}_{-0.09}$ \\
+		$c < 0$ & $-1.11^{+0.05}_{-0.11}$ & $0.90\pm0.04$ \\
+		$c > 0$ & $-1.18\pm0.09$ & $1.14^{+0.11}_{-0.05}$ \\
 		\hline
@@
 Metallicity may affect the observed rate of SNe in two ways: firstly, it can affect the time taken for a star to evolve along the main sequence ($t_{\mathrm{MS}}$) -- Stellar metallicity has varying effects on the main-sequence lifetime of stars \citep[e.g.][]{Georgy2013,Amard2020}, which is also dependent upon initial rotation and degree of mixing; secondly it can affect the time taken from WD formation to SN Ia explosion -- low metallicity stars should produce higher-mass WDs \citep[e.g.][]{Umeda1999,Marigo2007}, resulting in a higher SN Ia rate \citep{Kistler2013}, although note that \citet{Kistler2013} did not find any evidence for this in the data.
-\citet{Graur2017a} also found that evolution of SN Ia rates with metallicity is consistent with a DTD of the form  $t^{-1}$.
+\citet{Graur2017a} also found that evolution of SN Ia rates with metallicity is consistent with a DTD of the form  $\tau^{-1}$.
 
@@
 In this scenario, he predominantly high-stretch "prompt" SNe begin exploding as soon as the WDs are formed (nominally 40 Myr) whereas the mainly low-stretch "tardy" SNe only begin exploding after an extended period of time of the order 1 Gyr.
-The time dependence of both populations would follow the fiducial $t^{-1}$ distribution.
+The time dependence of both populations would follow the fiducial $\tau^{-1}$ distribution.
 Such a scenario may be explained by the sub-$M_{\mathrm{Ch}}$ double-detonation paradigm \citep[e.g.][]{Sim2010,Blondin2017,Shen2017}.
@@
 \ref{fig:rate_fitted_split_x1_2c_DTD}.
-The best fitting values are somewhat consistent with one another, with $t_1 = 0.65 \pm 0.1$~Gyr and $t_2 = 0.85 \pm 0.15$~Gyr, corresponding to a relatively sharp transition between the two populations.
+The best fitting values are somewhat consistent with one another, with $t_1 =0.69^{+0.07}_{-0.13}$~Gyr and $t_2 = 0.81^{+0.13}_{-0.10}$~Gyr, corresponding to a relatively sharp transition between the two populations.
 Our $t_1$ and $t_2$ are reminiscent of the transition found by \citet{Brandt2010} who found high-stretch SNe to be confined to delay times $\lesssim 0.4$~Gyr while low-stretch SNe occurred with delay times $\gtrsim 2.4$~Gyr.

### 2021-05-20 affiliations.tex

\parbox{\textwidth}{
%\scriptsize
$^{1}$ School of Physics and Astronomy, University of Southampton,  Southampton, SO17 1BJ, UK\\
$^{2}$ Universit\'e de Lyon 1, CNRS/IN2P3, Institut de Physique des Deux Infinis, 69622 Villeurbanne Cedex, France\\
$^{3}$ Institute of Cosmology and Gravitation, University of Portsmouth, Portsmouth, PO1 3FX, UK\\
$^{4}$ Department of Physics, Duke University Durham, NC 27708, USA\\
$^{5}$ The Research School of Astronomy and Astrophysics, Australian National University, ACT 2601, Australia\\
$^{6}$ NASA Einstein Fellow\\
$^{7}$ Center for Astrophysics $\vert$ Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{8}$ INAF, Osservatorio Astronomico di Trieste, I-34143 Trieste, Italy\\
$^{9}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
$^{10}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\
$^{11}$ Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA\\
$^{12}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
$^{13}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
$^{14}$ Centre for Gravitational Astrophysics, College of Science, The Australian National University, ACT 2601, Australia\\
$^{15}$ Universit\'e Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
$^{16}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
$^{17}$ Cerro Tololo Inter-American Observatory, NSF's National Optical-Infrared Astronomy Research Laboratory, Casilla 603, La Serena, Chile\\
$^{18}$ Departamento de F\'isica Matem\'atica, Instituto de F\'isica, Universidade de S\~ao Paulo, CP 66318, S\~ao Paulo, SP, 05314-970, Brazil\\
$^{19}$ Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
$^{20}$ Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA\\
$^{21}$ Instituto de F\'{i}sica Te\'orica, Universidade Estadual Paulista, S\~ao Paulo, Brazil\\
$^{22}$ CNRS, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
$^{23}$ Sorbonne Universit\'es, UPMC Univ Paris 06, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
$^{24}$ Department of Physics \& Astronomy, University College London, Gower Street, London, WC1E 6BT, UK\\
$^{25}$ Kavli Institute for Particle Astrophysics \& Cosmology, P. O. Box 2450, Stanford University, Stanford, CA 94305, USA\\
$^{26}$ SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
$^{27}$ Instituto de Astrofisica de Canarias, E-38205 La Laguna, Tenerife, Spain\\
$^{28}$ Universidad de La Laguna, Dpto. Astrofísica, E-38206 La Laguna, Tenerife, Spain\\
$^{29}$ Center for Astrophysical Surveys, National Center for Supercomputing Applications, 1205 West Clark St., Urbana, IL 61801, USA\\
$^{30}$ Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green Street, Urbana, IL 61801, USA\\
$^{31}$ Institut de F\'{\i}sica d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, 08193 Bellaterra (Barcelona) Spain\\
$^{32}$ Astronomy Unit, Department of Physics, University of Trieste, via Tiepolo 11, I-34131 Trieste, Italy\\
$^{33}$ INAF-Osservatorio Astronomico di Trieste, via G. B. Tiepolo 11, I-34143 Trieste, Italy\\
$^{34}$ Institute for Fundamental Physics of the Universe, Via Beirut 2, 34014 Trieste, Italy\\
$^{35}$ Observat\'orio Nacional, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
$^{36}$ Department of Physics, University of Michigan, Ann Arbor, MI 48109, USA\\
$^{37}$ Department of Physics, IIT Hyderabad, Kandi, Telangana 502285, India\\
$^{38}$ Santa Cruz Institute for Particle Physics, Santa Cruz, CA 95064, USA\\
$^{39}$ Institute of Theoretical Astrophysics, University of Oslo. P.O. Box 1029 Blindern, NO-0315 Oslo, Norway\\
$^{40}$ Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain\\
$^{41}$ Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain\\
$^{42}$ Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain\\
$^{43}$ Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
$^{44}$ Kavli Institute for Cosmology, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
$^{45}$ Department of Physics, Stanford University, 382 Via Pueblo Mall, Stanford, CA 94305, USA\\
$^{46}$ Center for Cosmology and Astro-Particle Physics, The Ohio State University, Columbus, OH 43210, USA\\
$^{47}$ Department of Physics, The Ohio State University, Columbus, OH 43210, USA\\
$^{48}$ Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 1, 81679 Munich, Germany\\
$^{49}$ Max Planck Institute for Extraterrestrial Physics, Giessenbachstrasse, 85748 Garching, Germany\\
$^{50}$ Department of Astronomy/Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721-0065, USA\\
$^{51}$ Australian Astronomical Optics, Macquarie University, North Ryde, NSW 2113, Australia\\
$^{52}$ Lowell Observatory, 1400 Mars Hill Rd, Flagstaff, AZ 86001, USA\\
$^{53}$ George P. and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX 77843,  USA\\
$^{54}$ Department of Astronomy, The Ohio State University, Columbus, OH 43210, USA\\
$^{55}$ Radcliffe Institute for Advanced Study, Harvard University, Cambridge, MA 02138\\
$^{56}$ Instituci\'o Catalana de Recerca i Estudis Avan\c{c}ats, E-08010 Barcelona, Spain\\
$^{57}$ Physics Department, 2320 Chamberlin Hall, University of Wisconsin-Madison, 1150 University Avenue Madison, WI  53706-1390\\
$^{58}$ Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton, NJ 08544, USA\\
$^{59}$ Department of Physics and Astronomy, Pevensey Building, University of Sussex, Brighton, BN1 9QH, UK\\
$^{60}$ Computer Science and Mathematics Division, Oak Ridge National Laboratory, Oak Ridge, TN 37831\\
$^{61}$ Universit\"ats-Sternwarte, Fakult\"at f\"ur Physik, Ludwig-Maximilians Universit\"at M\"unchen, Scheinerstr. 1, 81679 M\"unchen, Germany\\
}

### 2021-05-20 draft.tex

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[P. Wiseman et al.]{
-P. Wiseman,$^{1}$\thanks{E-mail: p.s.wiseman@soton.ac.uk}
-M. Sullivan,$^{1}$
-C. Frohmaier,$^{2,1}$
-M. Smith, $^{3}$
-M. Vincenzi, $^{2}$
-et al.
+\author[P. Wiseman et al.]{\parbox{\textwidth}{
+\Large
+P.~Wiseman,$^{1}$
+M.~Sullivan,$^{1}$
+M.~Smith,$^{2,1}$
+C.~Frohmaier,$^{1,3}$
+M.~Vincenzi,$^{3}$
+O.~Graur,$^{3}$
+B.~Popovic,$^{4}$
+P.~Armstrong,$^{5}$
+D.~Brout,$^{6,7}$
+D.~Carollo,$^{8}$
+T.~M.~Davis,$^{9}$
+L.~Galbany,$^{10}$
+S.~R.~Hinton,$^{9}$
+L.~Kelsey,$^{1}$
+R.~Kessler,$^{11,12}$
+G.~F.~Lewis,$^{13}$
+C.~Lidman,$^{14,5}$
+A.~M\"oller,$^{15}$
+R.~C.~Nichol,$^{3}$
+B.~Rose,$^{4}$
+D.~Scolnic,$^{4}$
+M.~Toy,$^{1}$
+B.~E.~Tucker,$^{5}$
+Z.~Zontou,$^{1}$
+J.~Asorey,$^{16}$
+T.~M.~C.~Abbott,$^{17}$
+M.~Aguena,$^{18,19}$
+S.~Allam,$^{20}$
+F.~Andrade-Oliveira,$^{21,19}$
+J.~Annis,$^{20}$
+D.~Bacon,$^{3}$
+E.~Bertin,$^{22,23}$
+D.~Brooks,$^{24}$
+E.~Buckley-Geer,$^{11,20}$
+D.~L.~Burke,$^{25,26}$
+A.~Carnero~Rosell,$^{27,19,28}$
+M.~Carrasco~Kind,$^{29,30}$
+J.~Carretero,$^{31}$
+M.~Costanzi,$^{32,33,34}$
+L.~N.~da Costa,$^{19,35}$
+M.~E.~S.~Pereira,$^{36}$
+S.~Desai,$^{37}$
+H.~T.~Diehl,$^{20}$
+P.~Doel,$^{24}$
+S.~Everett,$^{38}$
+I.~Ferrero,$^{39}$
+B.~Flaugher,$^{20}$
+P.~Fosalba,$^{40,41}$
+J.~Frieman,$^{20,12}$
+J.~Garc\'ia-Bellido,$^{42}$
+E.~Gaztanaga,$^{40,41}$
+T.~Giannantonio,$^{43,44}$
+D.~Gruen,$^{45,25,26}$
+R.~A.~Gruendl,$^{29,30}$
+J.~Gschwend,$^{19,35}$
+G.~Gutierrez,$^{20}$
+D.~L.~Hollowood,$^{38}$
+K.~Honscheid,$^{46,47}$
+B.~Hoyle,$^{48,49}$
+D.~J.~James,$^{7}$
+E.~Krause,$^{50}$
+K.~Kuehn,$^{51,52}$
+N.~Kuropatkin,$^{20}$
+M.~A.~G.~Maia,$^{19,35}$
+J.~L.~Marshall,$^{53}$
+P.~Martini,$^{46,54,55}$
+F.~Menanteau,$^{29,30}$
+R.~Miquel,$^{56,31}$
+R.~Morgan,$^{57}$
+R.~L.~C.~Ogando,$^{19,35}$
+A.~Palmese,$^{20,12}$
+F.~Paz-Chinch\'{o}n,$^{29,43}$
+D.~Petravick,$^{29}$
+A.~Pieres,$^{19,35}$
+A.~A.~Plazas~Malag\'on,$^{58}$
+A.~K.~Romer,$^{59}$
+E.~Sanchez,$^{16}$
+V.~Scarpine,$^{20}$
+M.~Schubnell,$^{36}$
+S.~Serrano,$^{40,41}$
+I.~Sevilla-Noarbe,$^{16}$
+E.~Suchyta,$^{60}$
+M.~E.~C.~Swanson,$^{29}$
+G.~Tarle,$^{36}$
+D.~Thomas,$^{3}$
+C.~To,$^{45,25,26}$
+T.~N.~Varga,$^{49,61}$
+and A.~R.~Walker$^{17}$
+\begin{center} (DES Collaboration) \end{center}
+}
+\vspace{0.4cm}
 \\
+\parbox{\textwidth}{Affiliations are listed at the end of the paper}
 }
-
 % These dates will be filled out by the publisher
@@
 We use an empirical model of stellar mass assembly to estimate the average star-formation histories (SFHs) of galaxies across the stellar mass range of our measurement.
-Combining the modelled SFHs with the SN Ia rates to estimate constraints on the SN Ia delay time distribution (DTD), we find the data are fit well by a power-law DTD with slope index $\beta = -1.14 \pm 0.05$ and normalisation $A = 2.1 \pm0.05 \times 10^{-13}~\mathrm{SNe}~{\mathrm{M}_{\odot}}^{-1}~\mathrm{yr}^{-1}$, which corresponds to an overall SN Ia production efficiency $N_{\mathrm{Ia}}/M_* = 0.9~_{-0.7}^{+4.0} \times 10^{-3}~\mathrm{SNe}~\mathrm{M}_{\odot}^{-1}$.
+Combining the modelled SFHs with the SN Ia rates to estimate constraints on the SN Ia delay time distribution (DTD), we find the data are fit well by a power-law DTD with slope index $\beta = -1.13 \pm 0.05$ and normalisation $A = 2.11 \pm0.05 \times 10^{-13}~\mathrm{SNe}~{\mathrm{M}_{\odot}}^{-1}~\mathrm{yr}^{-1}$, which corresponds to an overall SN Ia production efficiency $N_{\mathrm{Ia}}/M_* = 0.9~_{-0.7}^{+4.0} \times 10^{-3}~\mathrm{SNe}~\mathrm{M}_{\odot}^{-1}$.
 Upon splitting the SN sample by properties of the light curves, we find a strong dependence on DTD slope with the SN decline rate, with slower-declining SNe exhibiting a steeper DTD slope.
@@
 \begin{keywords}
-keyword1 -- keyword2 -- keyword3
+supernovae: general -- galaxies: evolution -- white dwarfs
 \end{keywords}
@@
 Comparison samples are PTF (purple; \citealt{Pan2014}) and Pantheon (orange; \citealt{Scolnic2018}).
-Lower: As upper but for field galaxies, and shown on a log scale.
+Lower: As upper but for field galaxies, and with galaxy frequency shown on a log scale.
 The distribution closely matches data from the ZFOURGE survey at $0.5<z<0.75$ (magenta dots).
@@
 
-    \item field galaxies must covered by $ugrizJHK$ photometry, with a photometric flux measurement or upper limit present in all bands;
+    \item field galaxies must be covered by $ugrizJHK$ photometry, with a photometric flux measurement or upper limit present in all bands;
 
@@
 
-To correct for incompleteness caused by the magnitude limited nature of the survey we follow the prescription of e.g.
-\citet{Sullivan2006} and \citet{Smith2012} by using a $V_{\mathrm{max}}$ method based on \citet{Schmidt1968}.
+To correct for incompleteness caused by the magnitude limited nature of the survey we follow the prescription of \citet{Sullivan2006} and \citet{Smith2012} by using a $V_{\mathrm{max}}$ method based on \citet{Schmidt1968}.
 For each galaxy in the sample we calculate the maximum volume within which it would have been observed given its absolute magnitude and $k-$correction, and the apparent magnitude limits calculated using the $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ statistics.
@@
 We employ a bootstrap Monte-Carlo approach in order to estimate the uncertainty in the value of the rate in each stellar mass bin.
-The probability distribution function (PDF) of each galaxy's stellar mass is represented by the sum of two half Gaussian distributions to represent the asymmetric positive and negative uncertainties derived in the SED fitting stage (Section \ref{sec:data}).
+The probability density function (PDF) of each galaxy's stellar mass is represented by the sum of two half Gaussian distributions to represent the asymmetric positive and negative uncertainties derived in the SED fitting stage (Section \ref{sec:data}).
 For each SN host and field galaxy, we take 100 samples of its stellar mass by drawing at random from its PDF.
@@
 
-A linear fit in log space with a best fitting slope of less than unity corresponds to a power-law, and indicates that SN Ia rate is not uniquely determined by host galaxy stellar mass.
+A best fitting slope of less than unity corresponds to a power-law, and indicates that SN Ia rate is not uniquely determined by host galaxy stellar mass.
 Indeed, the rate is instead likely to be driven by the DTD which is a non-linear function of stellar age.
@@
 We represent the SN Ia DTD by a power law, which we consider effective after some "prompt time" $t_{\mathrm{p}}$, before which its value is set to 0.
-This is generally interpreted as the time taken for WDs to form after the burst of star formation.
+$t_{\mathrm{p}}$ is generally interpreted as the time taken for WDs to form after the burst of star formation.
 The DTD is thus:
@@
 Specifically, we implement their "fine-tuned" model (Eq.
-A7 in \citealt{Childress2014}), whereby the SMz flattens above $z\sim2$ in line with observations \citep{Stark2013}:
+A7 in \citetalias{Childress2014}), whereby the SMz flattens above $z\sim2$ in line with observations \citep{Stark2013}:
 
@@
 We adopt the observationally motivated form of the quenching mass evolution (Eq.
-A8 from \citealt{Childress2014}):
+A8 from \citetalias{Childress2014}):
 \begin{equation}
@@
 As noted in \citetalias{Childress2014}, this toy model by construction follows several empirical relations derived from galaxy observations: model galaxies follow the SMz relation and obey quenching prescriptions motivated by observed galaxies.
-Here we make two further checks to validate to show that the model can be used to approximate the stellar age distribution of SN Ia host galaxies in DES.
+Here we make two further checks to validate that the model can be used to approximate the stellar age distribution of SN Ia host galaxies in DES.
 
@@
 
-Secondly, we assess the shape of our SFHs and how they depend on stellar mass by comparing with SFH measurements from the Calar Alto Legacy Integral Field spectrscopy Area survey (CALIFA) as revealed by \citet{GonzalezDelgado2017}.
+Secondly, we assess the shape of our SFHs and how they depend on stellar mass by comparing with SFH measurements from the Calar Alto Legacy Integral Field spectroscopy Area survey (CALIFA) as revealed by \citet{GonzalezDelgado2017}.
 Our models agree qualitatively on numerous features of the SFHs (their Fig.
@@
 Choosing this regime to fit allows more prior weight to be placed on shorter prompt times as per the majority of the literature.
-We use the $\hat{R}$ diagnostic of \citep{Vehtari2019} to assess the convergence of MC chains.
+We use the $\hat{R}$ diagnostic of \citet{Vehtari2019} to assess the convergence of MC chains.
 When including $t_{\mathrm{p}}$ as a free parameter, we find that the strong degeneracy between $t_{\mathrm{p}}$ and $A$ cause the sampler to fail to converge with $\hat{R} \sim 1.3$ for the chains of those two parameters.
@@
 In particular, it is assumed that galaxies evolve independent of each other, growing up the star formation main sequence until they reach a mass at which they quench and star formation ceases.
-While these simplifications describe the average properties of galaxies well \citep{Zahid2012, Childress2014}, they struggle to describe the more stochastic nature of galaxy evolution that occurs at the low and high mass ends: starbursts and quenching episodes, respectively.
+While these simplifications describe the average properties of galaxies well (\citealt{Zahid2012},\citetalias{Childress2014}), they struggle to describe the more stochastic nature of galaxy evolution that occurs at the low and high mass ends: starbursts and quenching episodes, respectively.
 
@@
 We repeat the analyses of Sections \ref{sec:rates} and \ref{sec:model} including all of the previous light curve cuts, performing the DTD fitting with a fixed $t_{\mathrm{p}} = 40$~Myr, and present the results in Table \ref{tab:dtd_results_split_lc}.
+Posterior distributions for fitted parameters are presented in Appendix \ref{appendix:posteriors}.
 
@@
 These measurements reflect the observed correlations of $x_1$ with stellar mass and sSFR (and by inference, stellar age) as been seen by \citet{Rigault2013,Graur2017,Rigault2018,Rose2019,Nicolas2020,Rose2021}.
-The corresponding DTD fit results in a steep power-law $\beta = -1.68 \pm 0.15$ for high-stretch SNe indicative of a population of predominantly prompt SNe, and a much shallower decay slope ($\beta = -0.79 \pm 0.08$) for low-stretch SNe representing a much more delayed population.
+The corresponding DTD fit results in a steep power-law $\beta =-1.70^{+0.19}_{-0.10}$ for high-stretch SNe indicative of a population of predominantly prompt SNe, and a much shallower decay slope ($\beta = -0.79 \pm 0.08$) for low-stretch SNe representing a much more delayed population.
 The difference in $\beta$ is significant at a level of $3.8\sigma$.
@@
 \ref{fig:rate_fitted_split_x1_2c_DTD}.
-The best fitting values are somewhat consistent with one another, with $t_1 =0.69^{+0.07}_{-0.13}$~Gyr and $t_2 = 0.81^{+0.13}_{-0.10}$~Gyr, corresponding to a relatively sharp transition between the two populations.
+The best fitting values are mildly consistent with one another, with $t_1 =0.69^{+0.07}_{-0.13}$~Gyr and $t_2 = 0.81^{+0.13}_{-0.10}$~Gyr, corresponding to a relatively sharp transition between the two populations.
 Our $t_1$ and $t_2$ are reminiscent of the transition found by \citet{Brandt2010} who found high-stretch SNe to be confined to delay times $\lesssim 0.4$~Gyr while low-stretch SNe occurred with delay times $\gtrsim 2.4$~Gyr.
-On the other hand, the transition found here appears to occur at much shorter delay times than the several Gyrs found by \citet{Rose2019}.
+The transition found in our analysis appears to occur at much shorter delay times than the several Gyrs found by \citet{Rose2019}.
 These results are somewhat surprising, as we might expect that the transition is not so sharp but a gradual correlation of delay time with the average stretch of SNe caused by the age vs WD-mass distribution, as predicted by \citet{Shen2021}.
@@
 All software used in this publication is publicly available.
-In particular, we made extensive use of \texttt{numpy} \citep{Harris2020}, \texttt{Astropy} \citep{AstropyCollaboration2013,AstropyCollaboration2018}, \texttt{matplotlib} \citep{Hunter2007}, \texttt{SciPy} \citep{Virtanen2020}, \texttt{pandas} \citep{Mckinney2010}, \texttt{Stan} \citep{Carpenter2017}, \texttt{seaborn} \citep{Waskom2020}, and \texttt{arviz} \citep{Kumar2019}.
+In particular, we made extensive use of \texttt{numpy} \citep{Harris2020}, \texttt{Astropy} \citep{AstropyCollaboration2013,AstropyCollaboration2018}, \texttt{matplotlib} \citep{Hunter2007}, \texttt{SciPy} \citep{Virtanen2020}, \texttt{pandas} \citep{Mckinney2010}, \texttt{Stan} \citep{Carpenter2017}, \texttt{seaborn} \citep{Waskom2020}, and \texttt{ChainConsumer} \citep{Hinton2016}.
 
 \section*{Acknowledgements}
+We thank J. Michael Burgess for discussions regarding model fitting in Stan.
+
+ P.W. acknowledges support from the Science and Technology Facilities Council (STFC) grant ST/R000506/1. P.W., M.Sullivan and M.Smith acknowledge support from EU/FP7-ERC grant 615929.
 
@@
 
-The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS.
-Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article.
-The statement may refer to original data generated in the course of the study or to third-party data analysed in the article.
-The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.
+The DES-SN photometric SN Ia catalogue and associated host galaxy data will be made available as part of the DES5YR SN cosmology analysis at https://des.ncsa.illinois.edu/releases/sn.
+Field galaxy data including photometric redshifts will appear alongside other data products released as part of the DES Y3 weak lensing cosmology analysis at https://des.ncsa.illinois.edu/releases.
 
@@
 We report parameter estimates based on the mean and standard deviation of their posterior samples.
-We use the $\hat{R}$ diagnostic of \citep{Vehtari2019} to assess the convergence of MC chains, and only report fits where $\hat{R}<1.05$
+We use the $\hat{R}$ diagnostic of \citep{Vehtari2019} to assess the convergence of MC chains, and only accept fits where $\hat{R}<1.05$.
 
@@
 \section{Posterior distributions for DTD fits}
-
+\label{appendix:posteriors}
 In this section we present the joint and marginal posterior distributions for the various fits of the DTD presented in Section \ref{sec:split_x1_c}.
@@
 
+\input{affiliations.tex}
 % Don't change these lines

### 2021-05-21 authlist_end_SNWG.tex
End of final reader

% Author list file generated with: mkauthlist 0+unknown 
% mkauthlist DES-2021-0642_author_list_end_SNWG.csv authlist_end_SNWG.tex -a order.txt -j mnras -sn -f

\author[DES Collaboration]{
\parbox{\textwidth}{
\Large
P.~Wiseman,$^{1}$
M.~Sullivan,$^{1}$
M.~Smith,$^{1}$
C.~Frohmaier,$^{2}$
M.~Vincenzi,$^{2}$
O.~Graur,$^{2}$
B.~Popovic,$^{3}$
P.~Armstrong,$^{4}$
J.~Asorey,$^{5}$
D.~Brout,$^{6,7}$
D.~Carollo,$^{6,8}$
L.~Galbany,$^{9}$
S.~R.~Hinton,$^{10}$
L.~Kelsey,$^{1}$
G.~F.~Lewis,$^{11}$
C.~Lidman,$^{12,4}$
A.~M\"oller,$^{13}$
B.~Rose,$^{3}$
and B.~E.~Tucker$^{4}$
\begin{center} (DES Collaboration) \end{center}
}
\vspace{0.4cm}
\\
\parbox{\textwidth}{
%\scriptsize
$^{1}$ School of Physics and Astronomy, University of Southampton,  Southampton, SO17 1BJ, UK\\
$^{2}$ Institute of Cosmology and Gravitation, University of Portsmouth, Portsmouth, PO1 3FX, UK\\
$^{3}$ Department of Physics, Duke University Durham, NC 27708, USA\\
$^{4}$ The Research School of Astronomy and Astrophysics, Australian National University, ACT 2601, Australia\\
$^{5}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
$^{6}$ \\
$^{7}$ Center for Astrophysics $\vert$ Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{8}$ INAF, Astrophysical Observatory of Turin, I-10025 Pino Torinese, Italy\\
$^{9}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\
$^{10}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
$^{11}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
$^{12}$ Centre for Gravitational Astrophysics, College of Science, The Australian National University, ACT 2601, Australia\\
$^{13}$ Universit\{'e} Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
}
}

### 2021-05-21 authlist_end_FR.tex
updating bib

--- 2021-05-20 affiliations.tex
@@
+% Author list file generated with: mkauthlist 0+unknown 
+% mkauthlist DES-2021-0642_author_list_end_FR.csv authlist_end_FR.tex -j mnras -a order.txt -f
+
+\author[DES Collaboration]{
+\parbox{\textwidth}{
+\Large
+P.~Wiseman,$^{1}$
+M.~Sullivan,$^{1}$
+M.~Smith,$^{2,1}$
+C.~Frohmaier,$^{3,1}$
+M.~Vincenzi,$^{3}$
+O.~Graur,$^{3}$
+B.~Popovic,$^{4}$
+P.~Armstrong,$^{5}$
+D.~Brout,$^{6,7}$
+T.~M.~Davis,$^{8}$
+L.~Galbany,$^{9}$
+S.~R.~Hinton,$^{8}$
+L.~Kelsey,$^{1}$
+R.~Kessler,$^{10,11}$
+C.~Lidman,$^{12,5}$
+A.~M\"oller,$^{13}$
+R.~C.~Nichol,$^{3}$
+B.~Rose,$^{4}$
+D.~Scolnic,$^{4}$
+M.~Toy,$^{1}$
+Z.~Zontou,$^{1}$
+J.~Asorey,$^{14}$
+D.~Carollo,$^{15}$
+K.~Glazebrook,$^{16}$
+G.~F.~Lewis,$^{17}$
+B.~E.~Tucker,$^{5}$
+T.~M.~C.~Abbott,$^{18}$
+M.~Aguena,$^{19}$
+S.~Allam,$^{20}$
+F.~Andrade-Oliveira,$^{21,19}$
+J.~Annis,$^{20}$
+D.~Bacon,$^{3}$
+E.~Bertin,$^{22,23}$
+D.~Brooks,$^{24}$
+E.~Buckley-Geer,$^{10,20}$
+D.~L.~Burke,$^{25,26}$
+A.~Carnero~Rosell,$^{27,19,28}$
+M.~Carrasco~Kind,$^{29,30}$
+J.~Carretero,$^{31}$
+M.~Costanzi,$^{32,33,34}$
+L.~N.~da Costa,$^{19,35}$
+M.~E.~S.~Pereira,$^{36}$
+S.~Desai,$^{37}$
+H.~T.~Diehl,$^{20}$
+P.~Doel,$^{24}$
+S.~Everett,$^{38}$
+I.~Ferrero,$^{39}$
+B.~Flaugher,$^{20}$
+P.~Fosalba,$^{40,41}$
+J.~Frieman,$^{20,11}$
+J.~Garc\'ia-Bellido,$^{42}$
+E.~Gaztanaga,$^{40,41}$
+T.~Giannantonio,$^{43,44}$
+D.~Gruen,$^{45,25,26}$
+R.~A.~Gruendl,$^{29,30}$
+J.~Gschwend,$^{19,35}$
+G.~Gutierrez,$^{20}$
+D.~L.~Hollowood,$^{38}$
+K.~Honscheid,$^{46,47}$
+B.~Hoyle,$^{48,49}$
+D.~J.~James,$^{7}$
+E.~Krause,$^{50}$
+K.~Kuehn,$^{51,52}$
+N.~Kuropatkin,$^{20}$
+M.~A.~G.~Maia,$^{19,35}$
+J.~L.~Marshall,$^{53}$
+P.~Martini,$^{46,54,55}$
+F.~Menanteau,$^{29,30}$
+R.~Miquel,$^{56,31}$
+R.~Morgan,$^{57}$
+R.~L.~C.~Ogando,$^{19,35}$
+A.~Palmese,$^{20,11}$
+F.~Paz-Chinch\'{o}n,$^{29,43}$
+D.~Petravick,$^{29}$
+A.~Pieres,$^{19,35}$
+A.~A.~Plazas~Malag\'on,$^{58}$
+A.~K.~Romer,$^{59}$
+E.~Sanchez,$^{14}$
+V.~Scarpine,$^{20}$
+M.~Schubnell,$^{36}$
+S.~Serrano,$^{40,41}$
+I.~Sevilla-Noarbe,$^{14}$
+M.~Soares-Santos,$^{36}$
+E.~Suchyta,$^{60}$
+M.~E.~C.~Swanson,$^{29}$
+G.~Tarle,$^{36}$
+D.~Thomas,$^{3}$
+C.~To,$^{45,25,26}$
+T.~N.~Varga,$^{49,61}$
+and A.~R.~Walker$^{18}$
+\begin{center} (DES Collaboration) \end{center}
+}
+\vspace{0.4cm}
+\\
 \parbox{\textwidth}{
@@
 $^{7}$ Center for Astrophysics $\vert$ Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
-$^{8}$ INAF, Osservatorio Astronomico di Trieste, I-34143 Trieste, Italy\\
-$^{9}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
-$^{10}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\
-$^{11}$ Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA\\
-$^{12}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
-$^{13}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
-$^{14}$ Centre for Gravitational Astrophysics, College of Science, The Australian National University, ACT 2601, Australia\\
-$^{15}$ Universit\'e Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
-$^{16}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
-$^{17}$ Cerro Tololo Inter-American Observatory, NSF's National Optical-Infrared Astronomy Research Laboratory, Casilla 603, La Serena, Chile\\
-$^{18}$ Departamento de F\'isica Matem\'atica, Instituto de F\'isica, Universidade de S\~ao Paulo, CP 66318, S\~ao Paulo, SP, 05314-970, Brazil\\
+$^{8}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
+$^{9}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\
+$^{10}$ Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA\\
+$^{11}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
+$^{12}$ Centre for Gravitational Astrophysics, College of Science, The Australian National University, ACT 2601, Australia\\
+$^{13}$ Universit\{'e} Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
+$^{14}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
+$^{15}$ INAF, Osservatorio Astronomico di Trieste, I-34143 Trieste, Italy\\
+$^{16}$ Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, Victoria 3122, Australia\\
+$^{17}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
+$^{18}$ Cerro Tololo Inter-American Observatory, NSF's National Optical-Infrared Astronomy Research Laboratory, Casilla 603, La Serena, Chile\\
 $^{19}$ Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
@@
 }
+}

### 2021-05-21 affiliations.tex
Updates from Overleaf

@@
 $^{7}$ Center for Astrophysics $\vert$ Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
-$^{8}$ INAF, Osservatorio Astronomico di Trieste, I-34143 Trieste, Italy\\
-$^{9}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
-$^{10}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\
-$^{11}$ Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA\\
-$^{12}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
-$^{13}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
-$^{14}$ Centre for Gravitational Astrophysics, College of Science, The Australian National University, ACT 2601, Australia\\
-$^{15}$ Universit\'e Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
-$^{16}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
-$^{17}$ Cerro Tololo Inter-American Observatory, NSF's National Optical-Infrared Astronomy Research Laboratory, Casilla 603, La Serena, Chile\\
-$^{18}$ Departamento de F\'isica Matem\'atica, Instituto de F\'isica, Universidade de S\~ao Paulo, CP 66318, S\~ao Paulo, SP, 05314-970, Brazil\\
+$^{8}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
+$^{9}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\
+$^{10}$ Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA\\
+$^{11}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
+$^{12}$ Centre for Gravitational Astrophysics, College of Science, The Australian National University, ACT 2601, Australia\\
+$^{13}$ Universit\'e Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
+$^{14}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
+$^{15}$ INAF, Osservatorio Astronomico di Trieste, I-34143 Trieste, Italy\\
+$^{16}$ Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, Victoria 3122, Australia\\
+$^{17}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
+$^{18}$ Cerro Tololo Inter-American Observatory, NSF's National Optical-Infrared Astronomy Research Laboratory, Casilla 603, La Serena, Chile\\
 $^{19}$ Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\

### 2021-05-21 draft.tex
Updates from Overleaf

@@
 %%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
+\usepackage{eso-pic}% http://ctan.org/pkg/eso-pic
+
+\AddToShipoutPictureBG*{%
+  \AtPageUpperLeft{%
+    \hspace{0.75\paperwidth}%
+    \raisebox{-4.5\baselineskip}{%
+      \makebox[0pt][l]{\textnormal{DES-2021-0642}}
+}}}%
+
+\AddToShipoutPictureBG*{%
+  \AtPageUpperLeft{%
+    \hspace{0.75\paperwidth}%
+    \raisebox{-5.5\baselineskip}{%
+      \makebox[0pt][l]{\textnormal{FERMILAB-PUB-21-245-AE}}
+}}}%
 
@@
 M.~Smith,$^{2,1}$
-C.~Frohmaier,$^{1,3}$
+C.~Frohmaier,$^{3,1}$
 M.~Vincenzi,$^{3}$
@@
 D.~Brout,$^{6,7}$
-D.~Carollo,$^{8}$
-T.~M.~Davis,$^{9}$
-L.~Galbany,$^{10}$
-S.~R.~Hinton,$^{9}$
+T.~M.~Davis,$^{8}$
+L.~Galbany,$^{9}$
+S.~R.~Hinton,$^{8}$
 L.~Kelsey,$^{1}$
-R.~Kessler,$^{11,12}$
-G.~F.~Lewis,$^{13}$
-C.~Lidman,$^{14,5}$
-A.~M\"oller,$^{15}$
+R.~Kessler,$^{10,11}$
+C.~Lidman,$^{12,5}$
+A.~M\"oller,$^{13}$
 R.~C.~Nichol,$^{3}$
@@
 M.~Toy,$^{1}$
+Z.~Zontou,$^{1}$
+J.~Asorey,$^{14}$
+D.~Carollo,$^{15}$
+K.~Glazebrook,$^{16}$
+G.~F.~Lewis,$^{17}$
 B.~E.~Tucker,$^{5}$
-Z.~Zontou,$^{1}$
-J.~Asorey,$^{16}$
-T.~M.~C.~Abbott,$^{17}$
-M.~Aguena,$^{18,19}$
+T.~M.~C.~Abbott,$^{18}$
+M.~Aguena,$^{19}$
 S.~Allam,$^{20}$
@@
 D.~Brooks,$^{24}$
-E.~Buckley-Geer,$^{11,20}$
+E.~Buckley-Geer,$^{10,20}$
 D.~L.~Burke,$^{25,26}$
@@
 P.~Fosalba,$^{40,41}$
-J.~Frieman,$^{20,12}$
+J.~Frieman,$^{20,11}$
 J.~Garc\'ia-Bellido,$^{42}$
@@
 R.~L.~C.~Ogando,$^{19,35}$
-A.~Palmese,$^{20,12}$
+A.~Palmese,$^{20,11}$
 F.~Paz-Chinch\'{o}n,$^{29,43}$
@@
 A.~K.~Romer,$^{59}$
-E.~Sanchez,$^{16}$
+E.~Sanchez,$^{14}$
 V.~Scarpine,$^{20}$
@@
 S.~Serrano,$^{40,41}$
-I.~Sevilla-Noarbe,$^{16}$
+I.~Sevilla-Noarbe,$^{14}$
+M.~Soares-Santos,$^{36}$
 E.~Suchyta,$^{60}$
@@
 T.~N.~Varga,$^{49,61}$
-and A.~R.~Walker$^{17}$
+and A.~R.~Walker$^{18}$
 \begin{center} (DES Collaboration) \end{center}

### 2021-05-25 draft.tex
Updates from Overleaf

@@
 \usepackage{lineno}
-\linenumbers
+%\linenumbers
 % MNRAS is set in Times font. If you don't have this installed (most LaTeX
@@
 \usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
+%\usepackage{amssymb}	% Extra maths symbols
 
@@
 
-%In an ideal rate measurement a volume-limited and complete sample of galaxies would be observed for a given time, and the number of SNe observed in each galaxy simply counted.
-In practice, apart from at very low redshift where the absolute numbers do not support robust statistical analyses, this is not possible: SNe are detected, classified and followed up based on complicated selection criteria; galaxy surveys are incomplete at faint magnitudes; the timescale of observing seasons cuts off SNe at the beginning and end of each season.
 In order to measure the rate of SNe Ia per galaxy per year, we require a sample of SNe Ia, as well as a sample of all of the possible galaxies ("field" galaxies) that those SNe could have exploded in.
@@
 The field galaxy stellar mass distribution is shown on a log scale, along with the stellar mass function (SMF) from the ZFOURGE survey \citep{Tomczak2014} scaled to match at $\log (M/\mathrm{M}_{\odot}) = 10$, whose stellar masses are derived with the same photo-$z$ code, IMF and template library as used here.
-Above $10^{8.5}~\mathrm{M}_{\odot}$, the DES field galaxy distribution closely follows the ZFOURGE SMF for $0.5<z<0.75$, indicating that the DES sample is representative of field galaxies in this mass and redshift range.%To estimate uncertainties on the physical properties, we resample the photometry from a Gaussian distribution formed by the flux measurements and their uncertainties and rerun the SED fit.
-This procedure is repeated 1000 times.
-%%%% INCOMPLETENESS %%%%
+Above $10^{8.5}~\mathrm{M}_{\odot}$, the DES field galaxy distribution closely follows the ZFOURGE SMF for $0.5<z<0.75$, indicating that the DES sample is representative of field galaxies in this mass and redshift range.
 
@@
 
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_split_sfr.png}
-%    \caption{The rate per galaxy of SNe Ia as a function of stellar mass for moderately and highly star-forming galaxies, as well as passive galaxies.}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
-%    \label{fig:rate_raw_split_sfr}
-%\end{figure}
 %%% MODEL %%%
@@
 \end{figure}
-
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=.5\textwidth]{figs/fit_dtd_A_beta_tp_corner.png}
-%    \caption{Posterior distributions for DTD parameters $\beta$, $A$, and $t_{\mathrm{p}}$.
-We display the log of $A$ for clarity.
-Displayed point estimates represent the median of the posterior samples.
-%    %The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
-%    \label{fig:corner_beta_norm_tp}}
-%\end{figure}
-
 \begin{figure}
@@
 
- P.W. acknowledges support from the Science and Technology Facilities Council (STFC) grant ST/R000506/1. P.W., M.Sullivan and M.Smith acknowledge support from EU/FP7-ERC grant 615929.
+ P.W. acknowledges support from the Science and Technology Facilities Council (STFC) grant ST/R000506/1. M.Sullivan and M.Smith acknowledge support from EU/FP7-ERC grant 615929.
 
@@
 \end{figure}
+
 We model the relation with the linear relationship: 
@@
 \label{appendix:posteriors}
-In this section we present the joint and marginal posterior distributions for the various fits of the DTD presented in Section \ref{sec:split_x1_c}.
-Posteriors have been displayed using v0.33.0 of \texttt{ChainConsumer} \citep{Hinton2016}.
 
@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\input{affiliations.tex}
+In this section we present the joint and marginal posterior distributions for the various fits of the DTD presented in Section \ref{sec:split_x1_c}.
+Posteriors have been displayed using v0.33.0 of \texttt{ChainConsumer} \citep{Hinton2016}.
+\clearpage
+\onecolumn
+\parbox{\textwidth}{
+\scriptsize
+$^{1}$ School of Physics and Astronomy, University of Southampton,  Southampton, SO17 1BJ, UK\\
+$^{2}$ Universit\'e de Lyon 1, CNRS/IN2P3, Institut de Physique des Deux Infinis, 69622 Villeurbanne Cedex, France\\
+$^{3}$ Institute of Cosmology and Gravitation, University of Portsmouth, Portsmouth, PO1 3FX, UK\\
+$^{4}$ Department of Physics, Duke University Durham, NC 27708, USA\\
+$^{5}$ The Research School of Astronomy and Astrophysics, Australian National University, ACT 2601, Australia\\
+$^{6}$ NASA Einstein Fellow\\
+$^{7}$ Center for Astrophysics $\vert$ Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
+$^{8}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
+$^{9}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\
+$^{10}$ Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA\\
+$^{11}$ Kavli Institute for Cosmological Physics, University of Chicago, Chicago, IL 60637, USA\\
+$^{12}$ Centre for Gravitational Astrophysics, College of Science, The Australian National University, ACT 2601, Australia\\
+$^{13}$ Universit\'e Clermont Auvergne, CNRS/IN2P3, LPC, F-63000 Clermont-Ferrand, France\\
+$^{14}$ Centro de Investigaciones Energ\'eticas, Medioambientales y Tecnol\'ogicas (CIEMAT), Madrid, Spain\\
+$^{15}$ INAF, Osservatorio Astronomico di Trieste, I-34143 Trieste, Italy\\
+$^{16}$ Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, Victoria 3122, Australia\\
+$^{17}$ Sydney Institute for Astronomy, School of Physics, A28, The University of Sydney, NSW 2006, Australia\\
+$^{18}$ Cerro Tololo Inter-American Observatory, NSF's National Optical-Infrared Astronomy Research Laboratory, Casilla 603, La Serena, Chile\\
+$^{19}$ Laborat\'orio Interinstitucional de e-Astronomia - LIneA, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
+$^{20}$ Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA\\
+$^{21}$ Instituto de F\'{i}sica Te\'orica, Universidade Estadual Paulista, S\~ao Paulo, Brazil\\
+$^{22}$ CNRS, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
+$^{23}$ Sorbonne Universit\'es, UPMC Univ Paris 06, UMR 7095, Institut d'Astrophysique de Paris, F-75014, Paris, France\\
+$^{24}$ Department of Physics \& Astronomy, University College London, Gower Street, London, WC1E 6BT, UK\\
+$^{25}$ Kavli Institute for Particle Astrophysics \& Cosmology, P. O. Box 2450, Stanford University, Stanford, CA 94305, USA\\
+$^{26}$ SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
+$^{27}$ Instituto de Astrofisica de Canarias, E-38205 La Laguna, Tenerife, Spain\\
+$^{28}$ Universidad de La Laguna, Dpto. Astrofísica, E-38206 La Laguna, Tenerife, Spain\\
+$^{29}$ Center for Astrophysical Surveys, National Center for Supercomputing Applications, 1205 West Clark St., Urbana, IL 61801, USA\\
+$^{30}$ Department of Astronomy, University of Illinois at Urbana-Champaign, 1002 W. Green Street, Urbana, IL 61801, USA\\
+$^{31}$ Institut de F\'{\i}sica d'Altes Energies (IFAE), The Barcelona Institute of Science and Technology, Campus UAB, 08193 Bellaterra (Barcelona) Spain\\
+$^{32}$ Astronomy Unit, Department of Physics, University of Trieste, via Tiepolo 11, I-34131 Trieste, Italy\\
+$^{33}$ INAF-Osservatorio Astronomico di Trieste, via G. B. Tiepolo 11, I-34143 Trieste, Italy\\
+$^{34}$ Institute for Fundamental Physics of the Universe, Via Beirut 2, 34014 Trieste, Italy\\
+$^{35}$ Observat\'orio Nacional, Rua Gal. Jos\'e Cristino 77, Rio de Janeiro, RJ - 20921-400, Brazil\\
+$^{36}$ Department of Physics, University of Michigan, Ann Arbor, MI 48109, USA\\
+$^{37}$ Department of Physics, IIT Hyderabad, Kandi, Telangana 502285, India\\
+$^{38}$ Santa Cruz Institute for Particle Physics, Santa Cruz, CA 95064, USA\\
+$^{39}$ Institute of Theoretical Astrophysics, University of Oslo. P.O. Box 1029 Blindern, NO-0315 Oslo, Norway\\
+$^{40}$ Institut d'Estudis Espacials de Catalunya (IEEC), 08034 Barcelona, Spain\\
+$^{41}$ Institute of Space Sciences (ICE, CSIC),  Campus UAB, Carrer de Can Magrans, s/n,  08193 Barcelona, Spain\\
+$^{42}$ Instituto de Fisica Teorica UAM/CSIC, Universidad Autonoma de Madrid, 28049 Madrid, Spain\\
+$^{43}$ Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
+$^{44}$ Kavli Institute for Cosmology, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
+$^{45}$ Department of Physics, Stanford University, 382 Via Pueblo Mall, Stanford, CA 94305, USA\\
+$^{46}$ Center for Cosmology and Astro-Particle Physics, The Ohio State University, Columbus, OH 43210, USA\\
+$^{47}$ Department of Physics, The Ohio State University, Columbus, OH 43210, USA\\
+$^{48}$ Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 1, 81679 Munich, Germany\\
+$^{49}$ Max Planck Institute for Extraterrestrial Physics, Giessenbachstrasse, 85748 Garching, Germany\\
+$^{50}$ Department of Astronomy/Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson, AZ 85721-0065, USA\\
+$^{51}$ Australian Astronomical Optics, Macquarie University, North Ryde, NSW 2113, Australia\\
+$^{52}$ Lowell Observatory, 1400 Mars Hill Rd, Flagstaff, AZ 86001, USA\\
+$^{53}$ George P. and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX 77843,  USA\\
+$^{54}$ Department of Astronomy, The Ohio State University, Columbus, OH 43210, USA\\
+$^{55}$ Radcliffe Institute for Advanced Study, Harvard University, Cambridge, MA 02138\\
+$^{56}$ Instituci\'o Catalana de Recerca i Estudis Avan\c{c}ats, E-08010 Barcelona, Spain\\
+$^{57}$ Physics Department, 2320 Chamberlin Hall, University of Wisconsin-Madison, 1150 University Avenue Madison, WI  53706-1390\\
+$^{58}$ Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton, NJ 08544, USA\\
+$^{59}$ Department of Physics and Astronomy, Pevensey Building, University of Sussex, Brighton, BN1 9QH, UK\\
+$^{60}$ Computer Science and Mathematics Division, Oak Ridge National Laboratory, Oak Ridge, TN 37831\\
+$^{61}$ Universit\"ats-Sternwarte, Fakult\"at f\"ur Physik, Ludwig-Maximilians Universit\"at M\"unchen, Scheinerstr. 1, 81679 M\"unchen, Germany\\
+}
+
 % Don't change these lines

### 2021-06-17 ref_response.tex

--- 2021-05-25 draft.tex
@@
 Despite using these relations to correct SN Ia peak brightnesses to within a dispersion of $\sim 0.1$ mag in samples with over one thousand SNe \citep{Scolnic2018}, the exact nature of the progenitors of SNe Ia is yet to be confirmed.
-While it is likely that SNe Ia are caused by mass transfer onto a WD from, or violent merger with, a companion star, multiple possible scenarios exist for the nature of that companion star (see \citealt{Maoz2014} for a review).
-The leading models involve a main sequence (MS) star in the single-degenerate (SD) scenario \citep{Whelan1973,Nomoto1982}, a secondary white dwarf in the double-degenerate (DD) scenario \citep{Tutukov1976,Iben1984,Webbink1984}, or more exotic models such as the core-degenerate (CD) scenario which invoke WDs merging with the cores of massive stars \citep{Soker2019}.
+While it is likely that SNe Ia are caused by mass transfer onto a WD from, or violent merger with, a companion star, multiple possible scenarios exist for the nature of that companion star (see \citealt{Maoz2014,Ruiter2020} for reviews).
+The leading models involve a main sequence (MS) star in the single-degenerate (SD) scenario \citep{Whelan1973,Nomoto1982}, a secondary white dwarf in the double-degenerate (DD) scenario \citep{Tutukov1976,Iben1984,Webbink1984}, or more exotic models such as the core-degenerate (CD) scenario which invoke WDs merging with the cores of massive stars \citep{Kashi2011,Ilkov2012}.
 
@@
 The SD scenario produces a broad range of functional forms for the DTD, most of which fail to account for long delay times \citep{Graur2014}.
-On the other hand, most variants of the DD scenario predict a power-law of the form $\tau^{\beta}$, with $\beta \sim -1$ \citep[e.g][]{Ruiter2009,Mennekens2010}.
+On the other hand, most variants of the DD scenario predict a power-law of the form $\tau^{\beta}$, with $\beta \sim -1$ \citep[e.g][]{Ruiter2009,Mennekens2010}, although see e.g.
+\citet{Yungelson2017} for DD models that deviate from a $-1$ power-law slope.
 
@@
 Instead of comparing \textit{volumetric} rates to the \textit{cosmic} SFH, it is also possible to estimate the SFH of individual galaxies through the modelling of their stellar populations via spectral energy distribution (SED) fitting.
-Works such as \citet{Maoz2011}, \citet{Maoz2012}, \citet{Graur2013}, and \citet{Graur2015} estimated the DTD by measuring SFHs for a sample of field galaxies and comparing them to the number of SNe detected in each galaxy (the SFHR method), and have led to results that suggest a DTD power law with $\beta$ consistent with $-1$.
+Works such as \citet{Totani2008}, \citet{Maoz2011}, \citet{Maoz2012}, \citet{Graur2013}, and \citet{Graur2015} estimated the DTD by measuring SFHs for a sample of field galaxies and comparing them to the number of SNe detected in each galaxy (the SFHR method), and have led to results that suggest a DTD power law with $\beta$ consistent with $-1$.
 
@@
 An additional factor in support of the sub-$M_{\mathrm{Ch}}$ model is that the SN luminosity is related to the mass of the primary WD, which itself is likely to be related to its age (although this relation is probably complicated by other factors such as accretion rate, metallicity, and the composition of the companion), thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Rose2019,Nicolas2020}.
+Other proposed scenarios include hybrid models in which standard CO WDs merge with hybrid helium-CO WDs \citep{Zenati2019,Perets2019}.
 With many models showing promising similarities to observations but each subject to its own drawbacks, it is becoming accepted that more than one progenitor scenario may contribute significantly to the overall population of "normal" SNe Ia; detailed observations are thus required in order to place constraints on the relative fractions of each possible progenitor channel.
@@
 In this work, we combine parts of the traditional methods and derive a new measurement of the SN Ia DTD.
-Instead of measuring the volumetric rate of SNe Ia, we measure the rate per galaxy as a function of stellar mass, as per \citet{Sullivan2006,Smith2012}.
+Instead of measuring the volumetric rate of SNe Ia, we measure the rate per galaxy as a function of stellar mass, as per \citet{Sullivan2006,Smith2012,Brown2019}.
 We use the stellar mass assembly model of \citetalias{Childress2014} to predict the stellar age distribution of galaxies for a given stellar mass at the mean redshift of our SN sample, and then forward model the DTD by convolving it with the stellar age distribution and comparing the predicted rates to the observed rates.
@@
 We measure a slope of $0.63\pm0.02$, which is consistent with the value found in weakly star-forming galaxies in the Supernova Legacy Survey by \citet{Sullivan2006}, but also in passive galaxies in SDSS by \citet{Smith2012}, and in all galaxies in the Lick Observatory Supernova Search (LOSS) by \citet{Li2011a}.
+Our measured slope is also consistent with that measured in the low-redshift All-Sky Automated Survey for Supernova (ASAS-SN) Bright Supernova Catalogues \citep{Brown2019}, which extends to galaxies with stellar mass as low as $10^7$~M$_{\odot}$.
 
@@
 The evolution of the rate with stellar mass is significantly different for the two sub-samples: high-stretch SNe dominate the rate at low stellar mass but tail off in the higher mass galaxies, while low-stretch SNe are subdominant in low mass galaxies but display a much steeper dependence on stellar mass and make up the vast majority of SNe in high-mass hosts.
-These measurements reflect the observed correlations of $x_1$ with stellar mass and sSFR (and by inference, stellar age) as been seen by \citet{Rigault2013,Graur2017,Rigault2018,Rose2019,Nicolas2020,Rose2021}.
+These measurements reflect the observed correlations of $x_1$ with stellar mass, sSFR (and by inference, stellar age) as been seen by \citet{Rigault2013,Graur2017,Rigault2018,Rose2019,Hakobyan2020,Nicolas2020,Rose2021}, as well as morphology \citep{Hakobyan2020}.
 The corresponding DTD fit results in a steep power-law $\beta =-1.70^{+0.19}_{-0.10}$ for high-stretch SNe indicative of a population of predominantly prompt SNe, and a much shallower decay slope ($\beta = -0.79 \pm 0.08$) for low-stretch SNe representing a much more delayed population.
@@
 
-From the differing DTDs that describe SNe with low and high stretch values we infer that there are either multiple channels through which SN Ia explode which occur on differing timescales, or that the explosion mechanism evolves with progenitor age.
+From the differing DTDs that describe SNe with low and high stretch values we infer that there are either multiple channels through which SN Ia explode which occur on differing timescales (as discussed in \citet{Hakobyan2020}), or that the explosion mechanism evolves with progenitor age.
 Two scenarios, that are not necessarily mutually exclusive, that could lead to different DTD decay rates are as follows.
@@
 These results are somewhat surprising, as we might expect that the transition is not so sharp but a gradual correlation of delay time with the average stretch of SNe caused by the age vs WD-mass distribution, as predicted by \citet{Shen2021}.
-However we note that the intrinsic stretch distribution may not be a simple Gaussian, but could instead be bimodal \citep{Scolnic2016,Popovic2021}.
+However we note that the intrinsic stretch distribution may not be a simple Gaussian, but could instead be bimodal \citep{Scolnic2016,Popovic2021,Nicolas2020}.
 The correlation of progenitor age and WD mass does not easily reproduce such a bimodal distribution, which may suggest that the sub-$M_{\mathrm{Ch}}$ channel cannot account for all SNe Ia.
@@
 One possibility is that sub-luminous SNe are more numerous in predominantly old stellar populations, such that the fraction passing our light curve cuts is lower than the rest of the sample.
-Such a phenomenon could be caused by SN Ia sub-classes such as SN 1991bg-like SNe, which are known to explode exclusively in old environments \citep{Perets2010} at delay times as long as $>6$~Gyr \citep{Panther2019}, and are typically sub-luminous with low stretch \citep{Gonzalez-Gaitan2014}.
+Such a phenomenon could be caused by SN Ia sub-classes such as SN 1991bg-like SNe, which are known to explode exclusively in old environments \citep{Perets2010,Barkhudaryan2019} at delay times as long as $>6$~Gyr \citep{Panther2019}, and are typically sub-luminous with low stretch \citep{Gonzalez-Gaitan2014}.
 If the SN 1991bg-like objects are drawn from the same parent population of WDs as the "normal" SNe Ia, their presence in high-mass hosts could explain the apparent lack of normal SNe Ia in the sample.

### 2021-06-21 ref_response.tex

@@
 To determine the apparent magnitude limit for galaxies in each of the optical bands we employ the method of \citet{Johnston2007}, \citet{Teodoro2010}, and \citet{Johnston2012} (hereafter Completeness I, II, III respectively).
-We use the test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ from those studies, which are computed based on absolute magnitude (distance modulus).
-Each galaxy is ranked by its absolute magnitude (distance modulus) when compared to all other galaxies in a survey within a certain slice of distance modulus (absolute magnitude).
-For a galaxy of apparent magnitude $m < m_{\mathrm{lim, trial}}$ observed in a survey complete to magnitude $m_{\mathrm{lim, true}}$ where  $m_{\mathrm{lim, trial}} \leq m_{\mathrm{lim, true}}$, the expectation value of the rank is 0.5.
+These works provide two complimentary statistics in order to find the limiting magnitude based on ranking of galaxies' absolute magnitudes in a given band $M$ and distance moduli $Z$, named  $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$, respectively.
+Galaxies are first placed in the $M-Z$ plane, which is limited to distance moduli that correspond to the redshift cuts $0.2 <z<0.6$ introduced in Section \ref{subsec:incompleteness_SNe}.
+Each galaxy in the survey is ranked by its $Z$ ($M$) compared to all other galaxies that fall within a slice of width $\delta M$ ($\delta Z$) -- we find that $\delta M = \delta Z = 0.02$~mag provides the best balance between high sampling resolution and an adequate number of galaxies within each slice.
+We then iteratively test different trial limiting apparent magnitudes $m_{\mathrm{lim, trial}}$.
+For a galaxy of apparent magnitude $m < m_{\mathrm{lim, trial}}$ observed in a survey complete to magnitude $m_{\mathrm{lim, true}}$ where  $m_{\mathrm{lim, trial}} \leq m_{\mathrm{lim, true}}$, the expectation value of the rank for a random is 0.5.
 However, if a trial limiting magnitude $m_{\mathrm{lim, trial}} \geq m_{\mathrm{lim, true}}$, there will be a lack of observed faint objects, such that the expectation value of the rank drops.
@@
 Completeness I, II, and III show that for surveys with sharp, well defined magnitude limits the test statistics $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ are stable and flat as a function of apparent magnitude up until the magnitude limit, where they drop sharply.
-The DES deep stacks present a more challenging case.
-They cover a wide area and are compiled from tens of separate CCDs, each with its own detection efficiency.
-Moreover, galaxy redshifts have been estimated using photometry only, and $K$-corrections performed using an imperfect template fit, potentially leading to large systematic and statistical fluctuations in absolute magnitudes and distance moduli.
-To reduce the inhomogeneity while still including  large sample of objects, we limit our sample to include only data from one deep (SN-X3) field.
 Fig.
-\ref{fig:completeness} shows the values of $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$.
-The values of the test statistics increase with $m_{\mathrm{lim, trial}}$ until a peak, before decreasing to stable values at magnitudes far beyond the limit of the survey.
+\ref{fig:completeness} shows the values of $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$ in the DES X3 field.
+The values of the test statistics increase with $m_{\mathrm{lim, trial}}$ until a peak, before decreasing to stable values at magnitudes far beyond the limit of the survey, contrary to the sharp drop in an ideal survey.
 The shape at brighter $m_{\mathrm{lim, trial}}$ is likely caused by incompleteness at the bright end: due to the small sky area, we simply do not probe enough volume to sample the bright end of the galaxy luminosity function well enough for the statistics to be robust.
+
 To approximate an efficiency function, we fit the peak of the statistics with a polynomial function, and then normalise by the maximum and minimum values.
@@
 These values are consistent with the value at which 50\% of the true sources are detected but have the advantage of being derived from the data without a simulation that is based on assumptions and thus susceptible to bias.
+Our final limiting magnitude for each band is the mean of that found from each of  $T_{\mathrm{C}}$ and $T_{\mathrm{V}}$.
 \subsubsection{$V_{\mathrm{max}}$ correction \label{subsubsec:vmax_corr}}
@@
 We measure a slope of $0.63\pm0.02$, which is consistent with the value found in weakly star-forming galaxies in the Supernova Legacy Survey by \citet{Sullivan2006}, but also in passive galaxies in SDSS by \citet{Smith2012}, and in all galaxies in the Lick Observatory Supernova Search (LOSS) by \citet{Li2011a}.
-Our measured slope is also consistent with that measured in the low-redshift All-Sky Automated Survey for Supernova (ASAS-SN) Bright Supernova Catalogues \citep{Brown2019}, which extends to galaxies with stellar mass as low as $10^7$~M$_{\odot}$.
+Our slope is also consistent with that measured in the low-redshift All-Sky Automated Survey for Supernova (ASAS-SN) Bright Supernova Catalogues \citep{Brown2019}, which extends to galaxies with stellar mass as low as $10^7$~M$_{\odot}$.
 

### 2021-06-21 draft.tex

@@
     \centering
+    %\includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.png}
+    \includegraphics[width=0.5\textwidth]{figs/eff_z.png}
+    \caption{SN host galaxy spectroscopic efficiencies as a function of redshift $z$.
+Efficiency curves are grouped by shallow (\{F\}12) and deep (\{F\}3) fields, and averaged over the 5 years of the survey.
+The lower and upper redshift limits for this analysis are indicated by $z_{\mathrm{min}}$ and $z_{\mathrm{max}}$ respectively.
+    \label{fig:eff_z}}
+\end{figure}
+
+\begin{figure}
+    \centering
     \includegraphics[width=0.5\textwidth]{figs/completeness_combined.png}
@@
 The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citet{Vincenzi2020} who provide the spectroscopic redshift efficiency $\epsilon_{z_{\mathrm{spec}}} (m^{\mathrm{host}}_{r,i})$ as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey.
+To assess how $\epsilon_{z_{\mathrm{spec}}} (m^{\mathrm{host}}_{r,i})$ translates into an efficiency as a function of redshift $\epsilon_{z_{\mathrm{spec}}} (z)$ within the redshift limits of our survey, we use a simulation of host galaxies as described in \citet{Vincenzi2020}.
+The simulation uses galaxy photometry from DES Science Verification images, and then selects them as potential SN hosts according a weighting driven by previously measured SN rate - host galaxy relationships.
+We note that this is for display purposes only, so the relationships built into the simulation are not propagated to the final rate measurements.
+For bins in redshift, we find the mean efficiency for measuring a spec-$z$ of all galaxies in the bin via $\epsilon_{z_{\mathrm{spec}}} (m^{\mathrm{host}}_{r,i})$.
+The resulting $\epsilon_{z_{\mathrm{spec}}} (z)$ curves are displayed in Fig.
+\ref{fig:eff_z} and show a high spectroscopic efficiency within the redshift limits of this analysis.
+
 The effects of the host galaxy spectroscopic efficiency are displayed in the upper panel of Fig.
@@
     \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_x1_fitjoint.png}
-    \caption{As per Fig.
+    \caption{\textit{Upper}: Posterior samples of the fraction of "prompt" SNe resulting from the two-population fit, displayed as a function of host galaxy stellar mass. 
+    \textit{Lower}: As per Fig.
 \ref{fig:rate_fitted_split_x1} but with the data fit simultaneously by a single two-component DTD, with fixed slope $\beta = -1$ and a prompt fraction that is 1 at short delay times, 0 at large delay times, and a linear function of time between $t_1 =0.65$~Gyr (where tardy SNe switch on) and $t_2=0.85$~Gyr (where prompt SNe turn off).%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}

### 2021-06-21 ref_response.tex
Updates from Overleaf

@@
 Any true residual difference between predicted and observed SNuM at different redshifts could be caused by an evolution of the SN Ia production efficiency as a function of redshift; we defer such an investigation to future work with more refined models and measurements.
+
+There is tentative evidence in the data for a flattening of the SNum vs stellar mass at $\log(M/\mathrm{M}_{\odot})\leq9.5$, which is broadly predicted by the model and is qualitatively consistent with the shape of the analytic fit of \citet{Kistler2013} while standing in slight tension with the conclusions of \citet{Brown2019}.
+The uncertainty of the measured rates at these low stellar masses prevents us from drawing further conclusions at this stage.
 \section{The delay-time distribution as a function of supernova properties}

### 2021-06-21 ref_response.tex
Updates from Overleaf

@@
 While it is likely that SNe Ia are caused by mass transfer onto a WD from, or violent merger with, a companion star, multiple possible scenarios exist for the nature of that companion star (see \citealt{Maoz2014,Ruiter2020} for reviews).
-The leading models involve a main sequence (MS) star in the single-degenerate (SD) scenario \citep{Whelan1973,Nomoto1982}, a secondary white dwarf in the double-degenerate (DD) scenario \citep{Tutukov1976,Iben1984,Webbink1984}, or more exotic models such as the core-degenerate (CD) scenario which invoke WDs merging with the cores of massive stars \citep{Kashi2011,Ilkov2012}.
+The leading models involve a main sequence (MS) star in the single-degenerate (SD) scenario \citep{Whelan1973,Nomoto1982}, a secondary white dwarf in the double-degenerate (DD) scenario \citep{Tutukov1976,Iben1984,Webbink1984}, or more exotic models such as the core-degenerate (CD) scenario which invoke WDs merging with the cores of massive stars \citep{Kashi2011,Ilkov2011}.
 
@@
 An additional factor in support of the sub-$M_{\mathrm{Ch}}$ model is that the SN luminosity is related to the mass of the primary WD, which itself is likely to be related to its age (although this relation is probably complicated by other factors such as accretion rate, metallicity, and the composition of the companion), thereby providing an explanation for observed relation between light curve stretch and stellar age \citep{Rigault2013,Rigault2018,Rose2019,Nicolas2020}.
-Other proposed scenarios include hybrid models in which standard CO WDs merge with hybrid helium-CO WDs \citep{Zenati2019,Perets2019}.
+Other proposed scenarios include hybrid models in which standard CO WDs merge with hybrid helium-CO WDs \citep{Zenati2019}.
 With many models showing promising similarities to observations but each subject to its own drawbacks, it is becoming accepted that more than one progenitor scenario may contribute significantly to the overall population of "normal" SNe Ia; detailed observations are thus required in order to place constraints on the relative fractions of each possible progenitor channel.

### 2021-06-29 ref_response.tex
Updates from Overleaf

@@
 We thank J. Michael Burgess for discussions regarding model fitting in Stan.
-
- P.W. acknowledges support from the Science and Technology Facilities Council (STFC) grant ST/R000506/1. M.Sullivan and M.Smith acknowledge support from EU/FP7-ERC grant 615929.
+We thank the reviewer, Mickael Rigault, for constructive comments on the manuscript.
+
+ P.W.
+acknowledges support from the Science and Technology Facilities Council (STFC) grant ST/R000506/1.
+M.Su.
+and M.Sm.
+acknowledge support from EU/FP7-ERC grant 615929.
+MS is funded by the European Reearch Council (ERC) under the European Union's Horizon 2020 Research and Innovation program (grant agreement no 759194 - USNAC).
+L.G.
+acknowledges financial support from the Spanish Ministry of Science, Innovation and Universities (MICIU) under the 2019 Ram\'on y Cajal program RYC2019-027683 and from the Spanish MICIU project PID2020-115253GA-I00.
 
@@
 $^{1}$ School of Physics and Astronomy, University of Southampton,  Southampton, SO17 1BJ, UK\\
-$^{2}$ Universit\'e de Lyon 1, CNRS/IN2P3, Institut de Physique des Deux Infinis, 69622 Villeurbanne Cedex, France\\
+$^{2}$ Univ Lyon, Univ Claude Bernard Lyon 1, CNRS, IP2I Lyon / IN2P3, IMR 5822, F-69622, Villeurbanne, France\\
 $^{3}$ Institute of Cosmology and Gravitation, University of Portsmouth, Portsmouth, PO1 3FX, UK\\
@@
 $^{8}$ School of Mathematics and Physics, University of Queensland,  Brisbane, QLD 4072, Australia\\
-$^{9}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\
+$^{9}$ Institute of Space Sciences (ICE, CSIC), Campus UAB, Carrer de Can Magrans, s/n, E-08193 Barcelona, Spain.\\
 $^{10}$ Department of Astronomy and Astrophysics, University of Chicago, Chicago, IL 60637, USA\\

### 2021-07-06 draft.tex
Updates from Overleaf

--- 2021-05-25 draft.tex
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/mass_hist_linlog_sn_field_BC03.png}
+    \includegraphics[width=.5\textwidth]{figs/mass_hist_linlog_sn_field_BC03.pdf}
     \caption{Upper: Distribution of the stellar mass of the SN host galaxies.
@@
     \centering
-    %\includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.png}
-    \includegraphics[width=0.5\textwidth]{figs/SN_efficiencies_z_x1_c.png}
+    %\includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.pdf}
+    \includegraphics[width=0.5\textwidth]{figs/SN_efficiencies_z_x1_c.pdf}
     \caption{ SN detection efficiencies split by DES-SN field, $x_1$ and $c$.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figs/completeness_combined.png}
+    \includegraphics[width=0.5\textwidth]{figs/completeness_combined.pdf}
     \caption{Measuring the completeness of the field galaxy sample.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figs/field_vmax.png}
+    \includegraphics[width=0.5\textwidth]{figs/field_vmax.pdf}
     \caption{Distribution of $V_{\mathrm{max}}$ corrections applied to field galaxies in the DES sample in order to correct for incompleteness.
@@
 The rate at which a host redshift is successfully measured given an apparent magnitude has been extensively modelled by \citet{Vincenzi2020} who provide the spectroscopic redshift efficiency $\epsilon_{z_{\mathrm{spec}}} (m^{\mathrm{host}}_{r,i})$ as a function of host $r$-band magnitude, host galaxy colour, and the year in which the SN was discovered in order to allow for a longer possible spectroscopic exposure time for hosts of SNe discovered earlier in the survey.
+
 The effects of the host galaxy spectroscopic efficiency are displayed in the upper panel of Fig.
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_all.png}
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_all.pdf}
     \caption{The rate per galaxy of SNe Ia as a function of stellar mass.
@@
     \centering
-    \includegraphics[width=\textwidth]{figs/SFHs_colour.png}
+    \includegraphics[width=\textwidth]{figs/SFHs_colour.pdf}
     \caption{The stellar mass assembly of the Universe as prescribed by the toy model of \citetalias{Childress2014}.
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/CSFH_MD14.png}
+    \includegraphics[width=.5\textwidth]{figs/CSFH_MD14.pdf}
     \caption{Cosmic star-formation history (CSFH) as approximated by our model (cyan solid) and as a best fit to observations (magenta dashed; \citealt{Madau2014}).}%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/fit_dtd_all_A_beta_corner.png}
+    \includegraphics[width=.5\textwidth]{figs/fit_dtd_all_A_beta_corner.pdf}
     \caption{Posterior distributions for DTD slope $\beta$ and normalisation $A$.
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1.png}
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1.pdf}
     \caption{Rate per galaxy of SNe Ia as a function of stellar mass (green points) along with the prediction from the best fitting DTD parameters $\beta$, $A$, and $t_{\mathrm{p}}$ forward modelled through Eq.
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/SNuM.png}
+    \includegraphics[width=.5\textwidth]{figs/SNuM.pdf}
     \caption{SN Ia rate per unit stellar mass as function of galaxy stellar mass.
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_x1.png}
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_x1.pdf}
     \caption{As per Fig.
@@
 Any true residual difference between predicted and observed SNuM at different redshifts could be caused by an evolution of the SN Ia production efficiency as a function of redshift; we defer such an investigation to future work with more refined models and measurements.
+
 \section{The delay-time distribution as a function of supernova properties}
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_x1_fitjoint.png}
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_x1_fitjoint.pdf}
     \caption{As per Fig.
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_c.png}
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_c.pdf}
     \caption{As per Fig.
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{figs/fit_fine_BC03_corner.png}
+    \includegraphics[width=0.5\textwidth]{figs/fit_fine_BC03_corner.pdf}
     \caption{Joint posterior distribution for the slope and intercept of the linear fit to the SN rate per galaxy per year as a function of stellar mass (Section \ref{sec:rates}; Fig.
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/fit_dtd_split_x1_A_beta_corner.png}
+    \includegraphics[width=.5\textwidth]{figs/fit_dtd_split_x1_A_beta_corner.pdf}
     \caption{Posterior distributions for DTD slope $\beta$ and normalisation $A$ for SNe Ia split by their $x_1$ parameter.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/fit_dtd_split_c_A_beta_corner.png}
+    \includegraphics[width=.5\textwidth]{figs/fit_dtd_split_c_A_beta_corner.pdf}
     \caption{Posterior distributions for DTD slope $\beta$ and normalisation $A$ for SNe Ia split by their $c$ parameter.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/fitjoint_t1_t2_corner.png}
+    \includegraphics[width=.5\textwidth]{figs/fitjoint_t1_t2_corner.pdf}
     \caption{Posterior distributions for $t_1$ and $t_2$ of the model presented in Section \ref{subsec:split_x1}.%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}

### 2021-07-06 final.tex
Updates from Overleaf

--- 2021-06-29 ref_response.tex
@@
     \centering
-    %\includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.png}
-    \includegraphics[width=0.5\textwidth]{figs/eff_z.png}
+    %\includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.pdf}
+    \includegraphics[width=0.5\textwidth]{figs/eff_z.pdf}
     \caption{SN host galaxy spectroscopic efficiencies as a function of redshift $z$.
@@
     \centering
-    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_x1_fitjoint.png}
-    \caption{As per Fig.
+    \includegraphics[width=.5\textwidth]{figs/rate_vs_mass_DTD_fit_beta_norm_Qerf1.1_split_x1_fitjoint.pdf}
+    \caption{\textit{Upper}: Posterior samples of the fraction of "prompt" SNe resulting from the two-population fit, displayed as a function of host galaxy stellar mass. 
+    \textit{Lower}: As per Fig.
 \ref{fig:rate_fitted_split_x1} but with the data fit simultaneously by a single two-component DTD, with fixed slope $\beta = -1$ and a prompt fraction that is 1 at short delay times, 0 at large delay times, and a linear function of time between $t_1 =0.65$~Gyr (where tardy SNe switch on) and $t_2=0.85$~Gyr (where prompt SNe turn off).%The blue lines indicate the best fitting model based on a $t^{\beta}$ power law DTD convolved with SFHs based on the \citetalias{Childress2014} model}
